---
title: "Preliminary analyses (for April 27)"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
  
---

Please note that lines by date and days sheltering in place are smoothed curves -- they may be poor representations of the data in locations with few participants. For example, the largest number of days sheltering in place only applies to a small portion of participants; lines representing small demographic groups at these large should not be interpreted. 

```{r chunk 1, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
```

```{r packages}
library(here)
library(tidyverse)
library(knitr)
library(kableExtra)
library(haven)
# require(devtools)
# install_version("zipcode", version = "1.0", repos = "http://cran.us.r-project.org")
library(zipcode)
library(ggthemr)
library(corx)
library(papaja)
library(zoo)
```


```{r score datafile, echo = F, warning = F, message = F}
# score master --------------------------------------------------------

source(here("Scripts/score data.R"))
```

```{rchunk 2}
total_weeks = max(scored$Week, na.rm=T)
```

# The effect of sheltering-in-place on well-being {.tabset}

## By number of days {.tabset}

```{r}

trend_days_sheltering = function(variable, dataset, label){

  demo_data = dataset %>%
  select(CaregiverID, 
         days_sheltering, 
         all_of(binary_demos), 
         all_of(variable)) %>%
    rename("variable" = variable) %>%
  gather("demo", "value", all_of(binary_demos)) %>%
  filter(value == 1) %>%
  group_by(demo, days_sheltering) %>%
  summarize(total = n(),
            percent = 100*sum(variable, na.rm=T)/total) %>%
  ungroup() %>% 
  mutate(demo = factor(demo, 
                       levels = binary_demos, 
                       labels = binary_labels))
# create NA rows for days that don't exist
demo_data = expand_grid(
  demo = unique(demo_data$demo),
  days_sheltering = seq(from = min(demo_data$days_sheltering, 
                                   na.rm = T),
                        to = max(demo_data$days_sheltering, 
                                 na.rm=T),
                        by = 1)) %>% 
  full_join(demo_data) %>%
  #create rolling average
  group_by(demo) %>%
  arrange(days_sheltering) %>%
  mutate(percent = rollapplyr(percent, FUN = mean, partial = T, width = 3))

all_data = dataset %>%
  select(CaregiverID, days_sheltering, variable) %>%
  rename("variable" = variable) %>%
  group_by(days_sheltering) %>%
  summarize(total = n(),
            percent = 100*sum(variable, na.rm=T)/total) %>%
  arrange(days_sheltering) %>%
  mutate(percent = rollapplyr(percent, FUN = mean, partial = T, width = 3))

plot = demo_data %>%
  ggplot(aes(x = days_sheltering, y = percent)) +
  geom_smooth(aes(color = demo),se = F) +
  geom_smooth(data = all_data, linetype = "dashed", se = F, color = "black") +
  labs(x = "Days sheltering in place",
       y = "Percent of demographic group",
       title = paste0("__ Percent of caregivers report ", label),
       color = "Key demographics", 
       caption = "Entire sample is represented by the black, dashed line.
       Percent represents rolling 3-day average.") +
  theme_minimal() +
  theme(plot.title.position = "plot")

return.list = list(demo_data = demo_data,
                   all_data = all_data,
                   plot = plot)
}
```


### Caregiver Anxiety

```{r chunk 3}
after_shelter = scored %>%
  filter(Week > 0)

anxiety_plot = trend_days_sheltering(variable = "anxiety_current_some",
                                     dataset = after_shelter, 
                                     label = "some or a lot of anxiety")
anxiety_plot$plot
```

```{r chunk 4, results = 'asis'}
scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos), anxiety) %>%
  mutate(everyone = 1) %>%
  gather("demo", "value", all_of(binary_demos), everyone) %>%
  filter(value == 1) %>%
  mutate(demo = factor(demo, levels = c("everyone", binary_demos),
                       labels = c("Everyone", binary_labels))) %>%
  group_by(demo) %>%
  summarize(cor = cor(days_sheltering, anxiety, use = "pairwise")) %>%
  kable(., digits = 2, 
        col.names = c("Demographic", "Correlation"), 
        caption = "Anxiety is the average of two PROMIS items.")
  
```



### Caregiver Depression

```{r chunk 5}
depress_plot = trend_days_sheltering(variable = "depress_current_some",
                                     dataset = after_shelter, 
                                     label = "some or a lot of depression")
depress_plot$plot

```

```{r chunk 6, results = 'asis'}
scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos), depress) %>%
  mutate(everyone = 1) %>%
  gather("demo", "value", all_of(binary_demos), everyone) %>%
  filter(value == 1) %>%
  mutate(demo = factor(demo, levels = c("everyone", binary_demos),
                       labels = c("Everyone", binary_labels))) %>%
  group_by(demo) %>%
  summarize(cor = cor(days_sheltering, depress, use = "pairwise")) %>%
  kable(., digits = 2, 
        col.names = c("Demographic", "Correlation"), 
        caption = "Depression is the average of two PROMIS items.")
  
```

### Caregiver Stress

```{r chunk 7}
stress_plot = trend_days_sheltering(variable = "stress_current_some",
                                     dataset = after_shelter, 
                                     label = "some or a lot of stress")
stress_plot$plot

```

```{r chunk 8, results = 'asis'}
scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos), stress) %>%
  mutate(everyone = 1) %>%
  gather("demo", "value", all_of(binary_demos), everyone) %>%
  filter(value == 1) %>%
  mutate(demo = factor(demo, levels = c("everyone", binary_demos),
                       labels = c("Everyone", binary_labels))) %>%
  group_by(demo) %>%
  summarize(cor = cor(days_sheltering, stress, use = "pairwise")) %>%
  kable(., digits = 2, 
        col.names = c("Demographic", "Correlation"), 
        caption = "Stress is the respose to a single item.")
  
```

### Child Externalizing

```{r chunk 9}
fussy_plot = trend_days_sheltering(variable = "fussy",
                                     dataset = after_shelter, 
                                     label = "children are sometimes or often fussy or defiant")
fussy_plot$plot
```

```{r chunk 10, results = 'asis'}
scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos), fussy) %>%
  mutate(everyone = 1) %>%
  gather("demo", "value", all_of(binary_demos), everyone) %>%
  filter(value == 1) %>%
  mutate(demo = factor(demo, levels = c("everyone", binary_demos),
                       labels = c("Everyone", binary_labels))) %>%
  group_by(demo) %>%
  summarize(cor = cor(days_sheltering, fussy, use = "pairwise")) %>%
  kable(., digits = 2, 
        col.names = c("Demographic", "Correlation"), 
        caption = "Child fussiness is the response to a single item.")
  
```

### Child Internalizing

```{r chunk 11}
fear_plot = trend_days_sheltering(variable = "fear",
                                     dataset = after_shelter, 
                                     label = "children are sometimes or often fearful or anxious")
fear_plot$plot
```

```{r chunk 12, results = 'asis'}
scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos), fear) %>%
  mutate(everyone = 1) %>%
  gather("demo", "value", all_of(binary_demos), everyone) %>%
  filter(value == 1) %>%
  mutate(demo = factor(demo, levels = c("everyone", binary_demos),
                       labels = c("Everyone", binary_labels))) %>%
  group_by(demo) %>%
  summarize(cor = cor(days_sheltering, fear, use = "pairwise")) %>%
  kable(., digits = 2, 
        col.names = c("Demographic", "Correlation"), 
        caption = "Child fearfulness is the response to a single item.")
  
```

## By group {.tabset}

```{r chunk 13}
shelter_factor = c(
  "No shelter-in-place",
  "Less than 2 weeks",
  "Long-term"
)
```


### Caregiver Anxiety

```{r chunk 14}
anxiety_date_demo = scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos), anxiety_current_some) %>%
  gather("demo", "value", all_of(binary_demos)) %>%
  filter(value == 1) %>%
  mutate(days_sheltering = case_when(
    days_sheltering == 0 ~ "No shelter-in-place",
    days_sheltering >= 14 ~ "Long-term",
    days_sheltering > 0 & days_sheltering <14 ~ "Less than 2 weeks"
  )) %>%
  mutate(days_sheltering= factor(days_sheltering, levels = shelter_factor)) %>%
  group_by(demo, days_sheltering) %>%
  summarize(total = n(),
            percent = 100*sum(anxiety_current_some, na.rm=T)/total) %>%
  ungroup() %>% 
  filter(!is.na(days_sheltering)) %>%
  mutate(demo = factor(demo, 
                       levels = binary_demos, 
                       labels = binary_labels)) %>%
  mutate(days_sheltering= factor(days_sheltering, levels = shelter_factor))

anxiety_date_all = scored %>%
  select(CaregiverID, days_sheltering, anxiety_current_some) %>%
  mutate(days_sheltering = case_when(
    days_sheltering == 0 ~ "No shelter-in-place",
    days_sheltering >= 14 ~ "Long-term",
    days_sheltering > 0 & days_sheltering <14 ~ "Less than 2 weeks"
  )) %>%
  group_by(days_sheltering) %>%
  summarize(total = n(),
            percent = 100*sum(anxiety_current_some, na.rm=T)/total)  %>%
  ungroup() %>% 
  filter(!is.na(days_sheltering))

anxiety_date_demo %>%
  ggplot(aes(x = days_sheltering, y = percent)) +
  geom_bar(aes(fill = demo), stat = "identity") +
  guides(fill = F) +
  labs(x = "",
       y = "Percent of demographic group",
       title = "__ Percent of caregivers report some or a lot of anxiety") +
  facet_wrap(~demo)+
  coord_flip()+
  scale_y_continuous(limits = c(0,100))+
  theme_minimal() +
  theme(plot.title.position = "plot")
```


### Caregiver Depression

```{r chunk 15}
depress_date_demo = scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos), depress_current_some) %>%
  gather("demo", "value", all_of(binary_demos)) %>%
  filter(value == 1) %>%
  mutate(days_sheltering = case_when(
    days_sheltering == 0 ~ "No shelter-in-place",
    days_sheltering >= 14 ~ "Long-term",
    days_sheltering > 0 & days_sheltering <14 ~ "Less than 2 weeks"
  )) %>%
  mutate(days_sheltering= factor(days_sheltering, levels = shelter_factor)) %>%
  group_by(demo, days_sheltering) %>%
  summarize(total = n(),
            percent = 100*sum(depress_current_some, na.rm=T)/total) %>%
  ungroup() %>% 
  filter(!is.na(days_sheltering)) %>%
  mutate(demo = factor(demo, 
                       levels = binary_demos, 
                       labels = binary_labels)) %>%
  mutate(days_sheltering= factor(days_sheltering, levels = shelter_factor))

depress_date_all = scored %>%
  select(CaregiverID, days_sheltering, depress_current_some) %>%
  mutate(days_sheltering = case_when(
    days_sheltering == 0 ~ "No shelter-in-place",
    days_sheltering >= 14 ~ "Long-term",
    days_sheltering > 0 & days_sheltering <14 ~ "Less than 2 weeks"
  )) %>%
  group_by(days_sheltering) %>%
  summarize(total = n(),
            percent = 100*sum(depress_current_some, na.rm=T)/total)  %>%
  ungroup() %>% 
  filter(!is.na(days_sheltering))

depress_date_demo %>%
  ggplot(aes(x = days_sheltering, y = percent)) +
  geom_bar(aes(fill = demo), stat = "identity") +
  guides(fill = F) +
  labs(x = "",
       y = "Percent of demographic group",
       title = "__ Percent of caregivers report some or a lot of depression") +
  facet_wrap(~demo)+
  coord_flip()+
  scale_y_continuous(limits = c(0,100))+
  theme_minimal() +
  theme(plot.title.position = "plot")
```

### Caregiver Stress

```{r chunk 16}
stress_date_demo = scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos), stress_current_some) %>%
  gather("demo", "value", all_of(binary_demos)) %>%
  filter(value == 1) %>%
  mutate(days_sheltering = case_when(
    days_sheltering == 0 ~ "No shelter-in-place",
    days_sheltering >= 14 ~ "Long-term",
    days_sheltering > 0 & days_sheltering <14 ~ "Less than 2 weeks"
  )) %>%
  mutate(days_sheltering= factor(days_sheltering, levels = shelter_factor)) %>%
  group_by(demo, days_sheltering) %>%
  summarize(total = n(),
            percent = 100*sum(stress_current_some, na.rm=T)/total) %>%
  ungroup() %>% 
  filter(!is.na(days_sheltering)) %>%
  mutate(demo = factor(demo, 
                       levels = binary_demos, 
                       labels = binary_labels)) %>%
  mutate(days_sheltering= factor(days_sheltering, levels = shelter_factor))

stress_date_all = scored %>%
  select(CaregiverID, days_sheltering, stress_current_some) %>%
  mutate(days_sheltering = case_when(
    days_sheltering == 0 ~ "No shelter-in-place",
    days_sheltering >= 14 ~ "Long-term",
    days_sheltering > 0 & days_sheltering <14 ~ "Less than 2 weeks"
  )) %>%
  group_by(days_sheltering) %>%
  summarize(total = n(),
            percent = 100*sum(stress_current_some, na.rm=T)/total)  %>%
  ungroup() %>% 
  filter(!is.na(days_sheltering))

stress_date_demo %>%
  ggplot(aes(x = days_sheltering, y = percent)) +
  geom_bar(aes(fill = demo), stat = "identity") +
  guides(fill = F) +
  labs(x = "",
       y = "Percent of demographic group",
       title = "__ Percent of caregivers report some or a lot of stress") +
  facet_wrap(~demo)+
  coord_flip()+
  scale_y_continuous(limits = c(0,100))+
  theme_minimal() +
  theme(plot.title.position = "plot")
```

### Child Externalizing

```{r chunk 17}
fussy_date_demo = scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos), fussy_current_some) %>%
  gather("demo", "value", all_of(binary_demos)) %>%
  filter(value == 1) %>%
  mutate(days_sheltering = case_when(
    days_sheltering == 0 ~ "No shelter-in-place",
    days_sheltering >= 14 ~ "Long-term",
    days_sheltering > 0 & days_sheltering <14 ~ "Less than 2 weeks"
  )) %>%
  mutate(days_sheltering= factor(days_sheltering, levels = shelter_factor)) %>%
  group_by(demo, days_sheltering) %>%
  summarize(total = n(),
            percent = 100*sum(fussy_current_some, na.rm=T)/total) %>%
  ungroup() %>% 
  filter(!is.na(days_sheltering)) %>%
  mutate(demo = factor(demo, 
                       levels = binary_demos, 
                       labels = binary_labels)) %>%
  mutate(days_sheltering= factor(days_sheltering, levels = shelter_factor))

fussy_date_all = scored %>%
  select(CaregiverID, days_sheltering, fussy_current_some) %>%
  mutate(days_sheltering = case_when(
    days_sheltering == 0 ~ "No shelter-in-place",
    days_sheltering >= 14 ~ "Long-term",
    days_sheltering > 0 & days_sheltering <14 ~ "Less than 2 weeks"
  )) %>%
  group_by(days_sheltering) %>%
  summarize(total = n(),
            percent = 100*sum(fussy_current_some, na.rm=T)/total)  %>%
  ungroup() %>% 
  filter(!is.na(days_sheltering))

fussy_date_demo %>%
  ggplot(aes(x = days_sheltering, y = percent)) +
  geom_bar(aes(fill = demo), stat = "identity") +
  guides(fill = F) +
  labs(x = "",
       y = "Percent of demographic group",
       title = "__ Percent of caregivers report children are sometimes or often defiant") +
  facet_wrap(~demo)+
  coord_flip()+
  scale_y_continuous(limits = c(0,100))+
  theme_minimal() +
  theme(plot.title.position = "plot")
```

### Child Internalizing

```{r chunk 18}
fear_date_demo = scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos), fear_current_some) %>%
  gather("demo", "value", all_of(binary_demos)) %>%
  filter(value == 1) %>%
  mutate(days_sheltering = case_when(
    days_sheltering == 0 ~ "No shelter-in-place",
    days_sheltering >= 14 ~ "Long-term",
    days_sheltering > 0 & days_sheltering <14 ~ "Less than 2 weeks"
  )) %>%
  mutate(days_sheltering= factor(days_sheltering, levels = shelter_factor)) %>%
  group_by(demo, days_sheltering) %>%
  summarize(total = n(),
            percent = 100*sum(fear_current_some, na.rm=T)/total) %>%
  ungroup() %>% 
  filter(!is.na(days_sheltering)) %>%
  mutate(demo = factor(demo, 
                       levels = binary_demos, 
                       labels = binary_labels)) %>%
  mutate(days_sheltering= factor(days_sheltering, levels = shelter_factor))

fear_date_all = scored %>%
  select(CaregiverID, days_sheltering, fear_current_some) %>%
  mutate(days_sheltering = case_when(
    days_sheltering == 0 ~ "No shelter-in-place",
    days_sheltering >= 14 ~ "Long-term",
    days_sheltering > 0 & days_sheltering <14 ~ "Less than 2 weeks"
  )) %>%
  group_by(days_sheltering) %>%
  summarize(total = n(),
            percent = 100*sum(fear_current_some, na.rm=T)/total)  %>%
  ungroup() %>% 
  filter(!is.na(days_sheltering))

fear_date_demo %>%
  ggplot(aes(x = days_sheltering, y = percent)) +
  geom_bar(aes(fill = demo), stat = "identity") +
  guides(fill = F) +
  labs(x = "",
       y = "Percent of demographic group",
       title = "__ Percent of caregivers report children are sometimes or often too fearful or anxious") +
  facet_wrap(~demo)+
  coord_flip()+
  scale_y_continuous(limits = c(0,100))+
  theme_minimal() +
  theme(plot.title.position = "plot")
```

## Moderated by income {.tabset}

### Caregiver Anxiety

```{r chunk 19}
anx_model = function(x){
  model = lm(anxiety ~ days_sheltering*income, data = x)
  return(model)
}

test = scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos), 
         anxiety, income) %>%
  mutate(income = income/1000,everyone = 1) %>%
  gather("demo", "value", all_of(binary_demos), everyone) %>%
  filter(value == 1) %>%
  mutate(demo = factor(demo, levels = c("everyone", binary_demos),
                       labels = c("Everyone", binary_labels))) %>%
  group_by(demo) %>%
  mutate(income = income-mean(income, na.rm=T),
         days_sheltering = days_sheltering-mean(days_sheltering,na.rm=T)) %>%
  nest() %>%
  arrange(demo) %>%
  mutate(model = map(data, anx_model)) %>%
  mutate(tidy = map(model, broom::tidy)) %>%
  unnest(tidy) %>%
  ungroup() %>%
  select(-demo, -data, -model) %>%
  kable(., digits = c(0,2,2,2,3),
        col.names = c("Term", "Coefficient", "SE", "t", "p-value"),
        caption = "Income and days have been centered within demographic group.") %>%
  kable_styling() %>%
  group_rows("Everyone", 1, 4) %>%
  group_rows(binary_labels[1], 5, 8) %>%
  group_rows(binary_labels[2], 9, 12) %>%
  group_rows(binary_labels[3], 13, 16) %>%
  group_rows(binary_labels[4], 17, 20) %>%
  group_rows(binary_labels[5], 21, 24) %>%
  group_rows(binary_labels[6], 25, 28) %>%
  group_rows(binary_labels[7], 29, 32) %>%
  group_rows(binary_labels[8], 33, 36)

```

### Caregiver Depression

```{r}
scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos),
         depress, income) %>%
  mutate(income = income/1000,everyone = 1) %>%
  gather("demo", "value", all_of(binary_demos), everyone) %>%
  filter(value == 1) %>%
  mutate(demo = factor(demo, levels = c("everyone", binary_demos),
                       labels = c("Everyone", binary_labels))) %>%
  group_by(demo) %>%
  mutate(income = income-mean(income, na.rm=T),
         days_sheltering = days_sheltering-mean(days_sheltering,na.rm=T)) %>%
  nest() %>%
  arrange(demo) %>%
  mutate(model = map(data,
                     .f = function(x) lm(depress ~ days_sheltering*income, data = x))) %>%
  mutate(tidy = map(model, broom::tidy)) %>%
  unnest(tidy) %>%
  ungroup() %>%
  select(-demo, -data, -model) %>%
  kable(., digits = c(0,2,2,2,3),
        col.names = c("Term", "Coefficient", "SE", "t", "p-value"),
        caption = "Income and days have been centered within demographic group.") %>%
  kable_styling() %>%
  group_rows("Everyone", 1, 4) %>%
  group_rows(binary_labels[1], 5, 8) %>%
  group_rows(binary_labels[2], 9, 12) %>%
  group_rows(binary_labels[3], 13, 16) %>%
  group_rows(binary_labels[4], 17, 20) %>%
  group_rows(binary_labels[5], 21, 24) %>%
  group_rows(binary_labels[6], 25, 28) %>%
  group_rows(binary_labels[7], 29, 32) %>%
  group_rows(binary_labels[8], 33, 36)

```

### Caregiver Stress

```{r}
scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos),
         stress, income) %>%
  mutate(income = income/1000,everyone = 1) %>%
  gather("demo", "value", all_of(binary_demos), everyone) %>%
  filter(value == 1) %>%
  mutate(demo = factor(demo, levels = c("everyone", binary_demos),
                       labels = c("Everyone", binary_labels))) %>%
  group_by(demo) %>%
  mutate(income = income-mean(income, na.rm=T),
         days_sheltering = days_sheltering-mean(days_sheltering,na.rm=T)) %>%
  nest() %>%
  arrange(demo) %>%
  mutate(model = map(data,
                     .f = function(x) lm(stress ~ days_sheltering*income, data = x))) %>%
  mutate(tidy = map(model, broom::tidy)) %>%
  unnest(tidy) %>%
  ungroup() %>%
  select(-demo, -data, -model) %>%
  kable(., digits = c(0,2,2,2,3),
        col.names = c("Term", "Coefficient", "SE", "t", "p-value"),
        caption = "Income and days have been centered within demographic group.") %>%
  kable_styling() %>%
  group_rows("Everyone", 1, 4) %>%
  group_rows(binary_labels[1], 5, 8) %>%
  group_rows(binary_labels[2], 9, 12) %>%
  group_rows(binary_labels[3], 13, 16) %>%
  group_rows(binary_labels[4], 17, 20) %>%
  group_rows(binary_labels[5], 21, 24) %>%
  group_rows(binary_labels[6], 25, 28) %>%
  group_rows(binary_labels[7], 29, 32) %>%
  group_rows(binary_labels[8], 33, 36)

```

### Child Externalizing

```{r}
scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos),
         fussy, income) %>%
  mutate(income = income/1000,everyone = 1) %>%
  gather("demo", "value", all_of(binary_demos), everyone) %>%
  filter(value == 1) %>%
  mutate(demo = factor(demo, levels = c("everyone", binary_demos),
                       labels = c("Everyone", binary_labels))) %>%
  group_by(demo) %>%
  mutate(income = income-mean(income, na.rm=T),
         days_sheltering = days_sheltering-mean(days_sheltering,na.rm=T)) %>%
  nest() %>%
  arrange(demo) %>%
  mutate(model = map(data,
                     .f = function(x) lm(fussy ~ days_sheltering*income, data = x))) %>%
  mutate(tidy = map(model, broom::tidy)) %>%
  unnest(tidy) %>%
  ungroup() %>%
  select(-demo, -data, -model) %>%
  kable(., digits = c(0,2,2,2,3),
        col.names = c("Term", "Coefficient", "SE", "t", "p-value"),
        caption = "Income and days have been centered within demographic group.") %>%
  kable_styling() %>%
  group_rows("Everyone", 1, 4) %>%
  group_rows(binary_labels[1], 5, 8) %>%
  group_rows(binary_labels[2], 9, 12) %>%
  group_rows(binary_labels[3], 13, 16) %>%
  group_rows(binary_labels[4], 17, 20) %>%
  group_rows(binary_labels[5], 21, 24) %>%
  group_rows(binary_labels[6], 25, 28) %>%
  group_rows(binary_labels[7], 29, 32) %>%
  group_rows(binary_labels[8], 33, 36)

```

### Child Internalizing

```{r}
scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos),
         fear, income) %>%
  mutate(income = income/1000,everyone = 1) %>%
  gather("demo", "value", all_of(binary_demos), everyone) %>%
  filter(value == 1) %>%
  mutate(demo = factor(demo, levels = c("everyone", binary_demos),
                       labels = c("Everyone", binary_labels))) %>%
  group_by(demo) %>%
  mutate(income = income-mean(income, na.rm=T),
         days_sheltering = days_sheltering-mean(days_sheltering,na.rm=T)) %>%
  nest() %>%
  arrange(demo) %>%
  mutate(model = map(data,
                     .f = function(x) lm(fear ~ days_sheltering*income, data = x))) %>%
  mutate(tidy = map(model, broom::tidy)) %>%
  unnest(tidy) %>%
  ungroup() %>%
  select(-demo, -data, -model) %>%
  kable(., digits = c(0,2,2,2,3),
        col.names = c("Term", "Coefficient", "SE", "t", "p-value"),
        caption = "Income and days have been centered within demographic group.") %>%
  kable_styling() %>%
  group_rows("Everyone", 1, 4) %>%
  group_rows(binary_labels[1], 5, 8) %>%
  group_rows(binary_labels[2], 9, 12) %>%
  group_rows(binary_labels[3], 13, 16) %>%
  group_rows(binary_labels[4], 17, 20) %>%
  group_rows(binary_labels[5], 21, 24) %>%
  group_rows(binary_labels[6], 25, 28) %>%
  group_rows(binary_labels[7], 29, 32) %>%
  group_rows(binary_labels[8], 33, 36)

```

# The effect of sheltering-in-place on education and childcare {.tabset}

## Parent education

```{r}
parent_edu_date_demo = scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos), parent_edu_interrupt) %>%
  gather("demo", "value", all_of(binary_demos)) %>%
  filter(value == 1) %>%
  group_by(demo, days_sheltering) %>%
  summarize(total = n(),
            percent = 100*sum(parent_edu_interrupt, na.rm=T)/total) %>%
  ungroup() %>%
  mutate(demo = factor(demo,
                       levels = binary_demos,
                       labels = binary_labels))

parent_edu_date_all = scored %>%
  select(CaregiverID, days_sheltering, parent_edu_interrupt) %>%
  group_by(days_sheltering) %>%
  summarize(total = n(),
            percent = 100*sum(parent_edu_interrupt, na.rm=T)/total)

parent_edu_date_demo %>%
  ggplot(aes(x = days_sheltering, y = percent)) +
  geom_smooth(aes(color = demo),se = F) +
  geom_smooth(data = parent_edu_date_all, linetype = "dashed", se = F, color = "black") +
  labs(x = "Days sheltering in place",
       y = "Percent of demographic group",
       title = "__ Percent of caregivers reporting interrupted education",
       color = "Key demographics",
       caption = "Entire sample is represented by the black, dashed line.") +
  theme_minimal() +
  theme(plot.title.position = "plot")
```

## Child education

```{r}
child_edu_date_demo = scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos), child_edu_interrupt) %>%
  gather("demo", "value", all_of(binary_demos)) %>%
  filter(value == 1) %>%
  group_by(demo, days_sheltering) %>%
  summarize(total = n(),
            percent = 100*sum(child_edu_interrupt, na.rm=T)/total) %>%
  ungroup() %>%
  mutate(demo = factor(demo,
                       levels = binary_demos,
                       labels = binary_labels))

child_edu_date_all = scored %>%
  select(CaregiverID, days_sheltering, child_edu_interrupt) %>%
  group_by(days_sheltering) %>%
  summarize(total = n(),
            percent = 100*sum(child_edu_interrupt, na.rm=T)/total)

child_edu_date_demo %>%
  ggplot(aes(x = days_sheltering, y = percent)) +
  geom_smooth(aes(color = demo),se = F) +
  geom_smooth(data = child_edu_date_all, linetype = "dashed", se = F, color = "black") +
  labs(x = "Days sheltering in place",
       y = "Percent of demographic group",
       title = "__ Percent of caregivers reporting interrupted child's education",
       color = "Key demographics",
       caption = "Entire sample is represented by the black, dashed line.") +
  theme_minimal() +
  theme(plot.title.position = "plot")
```

## Childcare by family member

```{r}
scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos), hours_familyCC_current) %>%
  mutate(everyone = 1) %>%
  gather("demo", "value", everyone, all_of(binary_demos)) %>%
  filter(value == 1) %>%
  mutate(days_sheltering = case_when(
    days_sheltering == 0 ~ "No shelter-in-place",
    days_sheltering >= 14 ~ "Long-term",
    days_sheltering > 0 & days_sheltering <14 ~ "Less than 2 weeks"
  )) %>%
  mutate(days_sheltering = factor(days_sheltering,
                                 levels = shelter_factor)) %>%
  filter(!is.na(days_sheltering)) %>%
  mutate(demo = factor(demo,
                       levels = c("everyone", binary_demos),
                       labels = c("Everyone", binary_labels))) %>%
  ggplot(aes(x = as.factor(days_sheltering), y = hours_familyCC_current)) +
  geom_boxplot() +
  labs(x = "Days sheltering in place",
       y = "Percent of demographic group",
       title = "Hours of childcare by family members") +
  theme_minimal() +
  facet_wrap(~demo)+
  theme(plot.title.position = "plot")
```

## Childcare by non-family member

```{r}
scored %>%
  select(CaregiverID, days_sheltering, all_of(binary_demos), hours_nonfamilyCC_current) %>%
  mutate(everyone = 1) %>%
  gather("demo", "value", everyone, all_of(binary_demos)) %>%
  filter(value == 1) %>%
  mutate(days_sheltering = case_when(
    days_sheltering == 0 ~ "No shelter-in-place",
    days_sheltering >= 14 ~ "Long-term",
    days_sheltering > 0 & days_sheltering <14 ~ "Less than 2 weeks"
  )) %>%
  mutate(days_sheltering = factor(days_sheltering,
                                 levels = shelter_factor)) %>%
  filter(!is.na(days_sheltering)) %>%
  mutate(demo = factor(demo,
                       levels = c("everyone", binary_demos),
                       labels = c("Everyone", binary_labels))) %>%
  ggplot(aes(x = as.factor(days_sheltering), y = hours_nonfamilyCC_current)) +
  geom_boxplot() +
  labs(x = "Days sheltering in place",
       y = "Percent of demographic group",
       title = "Hours of childcare by nonfamily members") +
  theme_minimal() +
  facet_wrap(~demo)+
  theme(plot.title.position = "plot")
```

# Working parents {.tabset}

## Parent well-being

```{r}
scored %>%
  mutate(worker = case_when(
    essential == 1 ~ "Essential worker",
    working_current == 1 & essential == 0 ~ "Non-essential worker"
  )) %>%
  select(worker, num_children, anxiety, depress, stress) %>%
  gather("Emotion", "value", -worker, -num_children) %>%
  filter(!is.na(worker)) %>%
  filter(!is.na(num_children)) %>%
  ggplot(aes(x = num_children, y = value, color = worker)) +
  geom_boxplot() +
  facet_grid(Emotion~.) +
  labs(x = "",
         y = "Rating",
         title = "Emotion by group")+
  theme_minimal() +
  theme(legend.position = "bottom")
```

```{r}
scored %>%
  mutate(worker = case_when(
    essential == 1 ~ "Essential worker",
    working_current == 1 & essential == 0 ~ "Non-essential worker"
  )) %>%
  select(worker, num_children, anxiety, depress, stress) %>%
  gather("Emotion", "value", -worker, -num_children) %>%
  filter(!is.na(worker)) %>%
  filter(!is.na(num_children)) %>%
  group_by(Emotion, num_children, worker) %>%
  summarize(m = mean(value, na.rm=T),
            sd = sd(value, na.rm=T),
            se = sd/sqrt(n()),
            moe = se*1.96) %>%
  ggplot(aes(x = num_children, y = m, fill = worker)) +
  geom_bar(stat = "identity", position = position_dodge(.8)) +
  geom_errorbar(aes(ymin = m-moe, ymax = m+moe),
                position = position_dodge(.8),
                width = .2)+
  facet_grid(Emotion~.) +
  labs(x = "",
         y = "Average rating",
         title = "Group average of emotion",
         caption = "Error bars are estimates")+
  theme_minimal()+
  theme(legend.position = "bottom")
```


## Child well-being

```{r}
scored %>%
  mutate(worker = case_when(
    essential == 1 ~ "Essential worker",
    working_current == 1 & essential == 0 ~ "Non-essential worker"
  )) %>%
  select(worker, num_children, fussy, fear) %>%
  gather("Emotion", "value", -worker, -num_children) %>%
  filter(!is.na(worker)) %>%
  filter(!is.na(num_children)) %>%
  ggplot(aes(x = num_children, y = value, color = worker)) +
  geom_boxplot() +
  facet_grid(Emotion~.) +
  labs(x = "",
         y = "Rating",
         title = "Emotion by group")+
  theme_minimal() +
  theme(legend.position = "bottom")
```

```{r}
scored %>%
  mutate(worker = case_when(
    essential == 1 ~ "Essential worker",
    working_current == 1 & essential == 0 ~ "Non-essential worker"
  )) %>%
  select(worker, num_children, fussy, fear) %>%
  gather("Emotion", "value", -worker, -num_children) %>%
  filter(!is.na(worker)) %>%
  filter(!is.na(num_children)) %>%
  group_by(Emotion, num_children, worker) %>%
  summarize(m = mean(value, na.rm=T),
            sd = sd(value, na.rm=T),
            se = sd/sqrt(n()),
            moe = se*1.96) %>%
  ggplot(aes(x = num_children, y = m, fill = worker)) +
  geom_bar(stat = "identity", position = position_dodge(.8)) +
  geom_errorbar(aes(ymin = m-moe, ymax = m+moe),
                position = position_dodge(.8),
                width = .2)+
  facet_grid(Emotion~.) +
  labs(x = "",
         y = "Average rating",
         title = "Group average of emotion",
         caption = "Error bars are estimates")+
  theme_minimal()+
  theme(legend.position = "bottom")
```

# Demographic correlations

```{r}
scored %>%
  select(binary_demos, anxiety, depress, stress, fear, fussy, days_sheltering, total_cases, new_cases_twoweeks, growth_cases_oneweek, total_deaths_per1000) %>%
  cor(., use = "pairwise") %>%
  corrplot::corrplot()
```

```{r, results='asis'}
# create table with corx
cor <-  scored %>%
  select(all_of(binary_demos), anxiety, depress, stress, fear, fussy, days_sheltering, total_cases, new_cases_twoweeks, growth_cases_oneweek, total_deaths_per1000) %>%
  mutate_all(as.numeric) %>%
  cor(., use = "pairwise")

rownames(cor) = paste0(1:nrow(cor), ". ", rownames(cor))
colnames(cor) = paste0(1:nrow(cor))

kable(cor, digits = 2, caption = "Correlations between study variables.")
```


