---
title: "Income and race/ethnicity"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---



```{r chunk 1, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
```

```{r packages}
library(here)
```

```{r childcare-1}
source(here("Scripts/score data.R"))

outcomes = c("anxiety", "depress", "lonely", "stress", "fussy", "fear")
outcomes_p = paste0(outcomes, "_current_lots")

source(here("Functions/pomp.R"))

scored = scored %>%
  mutate_at(vars("anxiety","depress"), pomp_ad) %>%
  mutate_at("stress", pomp_stress) %>%
  mutate_at("lonely", pomp_lonely) %>%
  mutate_at(vars("fussy", "fear"), pomp_child)  %>%
  mutate(everyone = 1)

source(here("Scripts/demo groups.R"))

source(here("Functions/summarizing_report.R"))
# 
# demo_groups = c( "native", 
#   "asian", 
#   "black", 
#   "hawaii", 
#   "white", 
#   "other_race", 
#   "latinx")
# 
# demo_labels = demo_labels[which(demo_groups %in% demo_groups)]
# demo_groups = demo_groups[which(demo_groups %in% demo_groups)]

scored = scored %>%
  mutate(
    poc_lowincome = ifelse((white == 0 | latinx == 1) & poverty200 == 1, 1,0),
    poc_hghincome = ifelse((white == 0 | latinx == 1) & poverty200 == 0, 1,0),
    white_hghincome = ifelse((white == 1 & latinx == 0) & poverty200 == 0, 1,0),
    white_lowincome = ifelse((white == 1 & latinx == 0) & poverty200 == 1, 1,0),
    black_lowincome = ifelse(black == 1 & poverty200 == 1, 1, 0),
    black_hghincome = ifelse(black == 1 & poverty200 == 0, 1, 0),
    latinx_lowincome = ifelse(latinx == 1 & poverty200 == 1, 1, 0),
    latinx_hghincome = ifelse(latinx == 1 & poverty200 == 0, 1, 0)
  )

demo_groups = c("everyone",
  "white_hghincome", "white_lowincome", 
                "poc_hghincome", "poc_lowincome",  
                "black_hghincome", "black_lowincome",
                "latinx_hghincome", "latinx_lowincome")
demo_labels = c("All caregivers",
  "White, high income", "White, low income", 
                "POC, high income", "POC, low income", 
                "African American, high income", "African American, low income",
                "Latinx, high income", "Latinx, low income")



cc_binary = c("cc2_centerbased","cc2_unpaid","cc2_paid","cc2_homebased")
cc_demo_labels = c("Center-based care",
                     "Unpaid care by relative/friend/neighbor",
                     "Paid care by relative/friend/neighbor",
                     "Home-based paid childcare")

```

```{r access-by-race-1}
scored_all = scored
max_weeks = max(scored$Week)
scored = scored %>%
  group_by(CaregiverID) %>%
  filter(Week == 0 | Week == max(Week)) %>%
  ungroup()
```

# Some numbers

```{r access-by-race-2, results = 'asis'}
nums = scored %>%
  filter(Week > 0) %>%
  gather(demo, group, all_of(demo_groups)) %>%
  filter(group == 1) %>%
  group_by(Week, demo) %>%
  summarize(Count = n()) %>%
  ungroup() %>%
  mutate(Week = paste("Week", Week)) %>%
  spread(Week, Count) 
nums$Total = apply(nums[,-1], 1, sum)
nums %>%
  mutate(demo = factor(demo, levels = demo_groups, labels = demo_labels)) %>%
  kable(.)
```


# Access to health care

```{r access-by-race-3}
healthcare = scored %>%
  mutate(access_telehealth = ifelse(access_telehealth == 1 | access_mentalhealth == 1, 1, 0)) %>%
  filter(Week > 0) %>%
  select(Week, all_of(demo_groups), contains("access_telehealth"), contains("mentalhealth")) %>%
  gather(demo, group, all_of(demo_groups)) %>%
  filter(group == 1) %>%
  select(-group) %>%
  gather(health, response, -Week, -demo) %>%
  filter(!is.na(response)) %>%
  mutate(health = factor(health, 
                         levels = c("access_telehealth", 
                                    "access_telehealth_self", 
                                    "access_telehealth_child", 
                                    "access_mentalhealth"),
                         labels = c("Access healthcare", 
                                    "For self", "For child", "Mental health"))) %>%
  mutate(demo = factor(demo, levels = demo_groups, labels = demo_labels))

healthcare %>%
  separate(demo, into =c("demo", "income"), sep =",") %>%
  group_by(demo,income,health) %>%
  summarize(Count = sum(response),
            Percent = 100*Count/n()) %>%
  ggplot(aes(x = health, y = Percent, fill = health)) +
  geom_bar(stat = "identity") +
  guides(fill = F) +
  labs(x = "") +
  coord_flip()+
  facet_grid(demo~income)+
  theme_minimal()
```

```{r access-by-race-4}

powered = nums$demo[which(nums$Total > 200)]
powered = demo_labels[demo_groups %in% powered]

healthcare %>%
#  # filter(demo %in% powered) %>%
  separate(demo, into =c("demo", "income"), sep =",") %>%
  group_by(Week, demo,income, health) %>%
  summarize(Count = sum(response),
            Percent = 100*Count/n()) %>%
  ggplot(aes(x = Week, y = Percent, color = demo)) +
  geom_point()+
  geom_line() +
  scale_x_continuous(breaks= c(1:max_weeks)) +
  facet_grid(income~health) +
  theme_minimal() +
  theme(legend.position = "top")
```

## Missesd well-baby

```{r access-by-race-5}
scored %>%
  filter(Week > 0) %>%
  select(missed_wellbaby, all_of(demo_groups)) %>%
  gather(demo, group, all_of(demo_groups)) %>%
  filter(group == 1) %>%
  select(-group) %>%
  filter(!is.na(missed_wellbaby)) %>%
  group_by(demo) %>%
  summarize(Count = sum(missed_wellbaby),
         Percent = 100*Count/n()) %>%
  ungroup() %>%
  mutate(demo = factor(demo, levels = demo_groups,labels = demo_labels))%>%
  separate(demo, into =c("demo", "income"), sep =",") %>%
  ggplot(aes(x = demo, y = Percent, fill = demo)) +
  geom_bar(stat = "identity") +
  coord_flip()+
  guides(fill = F)+
  labs(title = "___ Percent of caregivers report missing a well-baby visit")+
  facet_wrap(~income)+
  theme_minimal() +
  theme(plot.title.position = "plot")
```

```{r access-by-race-6}
scored %>%
  filter(Week > 0) %>%
  select(Week, missed_wellbaby, all_of(demo_groups)) %>%
  gather(demo, group, all_of(demo_groups)) %>%
  filter(group == 1) %>%
  select(-group) %>%
  filter(!is.na(missed_wellbaby)) %>%
  group_by(demo, Week) %>%
  summarize(Count = sum(missed_wellbaby),
            Percent = 100*Count/n()) %>%
  ungroup() %>%
    mutate(demo = factor(demo, levels = demo_groups,labels = demo_labels))%>%
  separate(demo, into =c("demo", "income"), sep =",") %>%
  ggplot(aes(x = Week, y = Percent, color = demo)) +
  geom_point() +
  geom_line() +
  labs(title = "__ of caregivers report missing a well-baby visit") +
  facet_wrap(~income, nrow = 2)+
  scale_y_continuous()+
  theme_minimal()
```

### Which visit missed?

```{r access-by-race-7}
scored %>%
  filter(Week > 0) %>%
  filter(missed_wellbaby == 1) %>%
  select(CaregiverID, all_of(demo_groups), 
         contains("which_wellbaby")) %>%
  gather("demo", "groups", all_of(demo_groups)) %>%
  filter(groups == 1) %>%
  select(-groups) %>%
  gather("which", "age", contains("which")) %>%
  filter(!is.na(age)) %>%
  mutate(age = factor(age, levels = c(1:14),
                      labels = c("3-5 days",
                                 "1 month",
                                 "2 months",
                                 "4 months",
                                 "6 months",
                                 "9 months",
                                 "12 months",
                                 "15 months",
                                 "18 months",
                                 "24 months",
                                 "2.5 years",
                                 "3 years",
                                 "4 years",
                                 "5 years"))) %>%
group_by(demo, age) %>%
  summarize(Count = n()) %>%
  group_by(demo) %>%
  mutate(Percent = 100*Count/sum(Count)) %>%
  ungroup() %>%
  mutate(demo = factor(demo, levels = demo_groups,
                       labels = demo_labels)) %>%
  separate(demo, into =c("demo", "income"), sep =",") %>%
  ggplot(aes(x = age, y = Count)) +
  geom_bar(stat = "identity") +
  coord_flip()+
  facet_grid(demo~income)
  
```

### Miss vaccine when miss well-baby

```{r access-by-race-8}
scored %>%
  filter(Week > 0) %>%
mutate(vacc_mean = rowMeans(select(., starts_with("miss_v")), 
                            na.rm = TRUE),
       vaccine_missed = ceiling(vacc_mean),
       vaccine_missed = factor(vaccine_missed, 
                               levels = c(0,1, NaN),
                               labels = c("Did not miss", "Missed vaccine", "No information"))) %>%
  group_by(vaccine_missed) %>%
  summarize(Count = n()) %>%
  ggplot(aes(y = Count, x = vaccine_missed)) +
  geom_bar(stat = "identity")+
  labs(x = "" )+
  coord_flip()
```


## Barriers to healthcare

```{r, eval = F}
scored %>%
  filter(Week > 0) %>%
  gather(barrier, value, barriers) %>%
  filter(!is.na(value)) %>%
  group_by(barrier) %>%
  summarize(Count = sum(value),
            Percent = 100*Count/n())
```


```{r access-by-race-9}
barriers = find_items("hc_barrier", scored)
barrier_labels = c("Cost", "Time away from work", "Childcare", "Concerned about COVID-19", "Caring for family members", "Other")

scored %>%
  filter(Week > 0) %>%
  select(all_of(demo_groups), all_of(barriers)) %>%
  gather(demo, group, all_of(demo_groups)) %>%
  filter(group == 1) %>%
  select(-group) %>%
  gather("Barrier", "value", -demo) %>%
  filter(!is.na(value)) %>%
  group_by(demo, Barrier) %>%
  summarize(Count = sum(value),
            Percent = 100*Count/n()) %>%
  ungroup() %>%
  mutate(Barrier = factor(Barrier, 
                          levels = barriers,
                          labels = barrier_labels),
         demo = factor(demo, levels = demo_groups,
                       labels = demo_labels)) %>%
  separate(demo, into =c("demo", "income"), sep =",") %>%
  group_by(demo, income) %>%
  mutate(Barrier = fct_reorder(Barrier, Percent, .fun='identity')) %>%
  ggplot(aes(x = Barrier, y = Percent, fill = Barrier))+
  geom_bar(stat = "identity") +
  coord_flip()+
  guides(fill = F)+
  facet_grid(demo~income)

```


# Access to childcare

```{r childcare-4, results = 'asis'}
BefAft = scored %>%
  mutate(Week = ifelse(Week == 0, "Bef", "During"))

BefAft = BefAft %>%
  select(Week, all_of(cc_binary), all_of(demo_groups)) %>%
  gather("Variable", "value", all_of(cc_binary)) %>%
  gather("Demo", "group", all_of(demo_groups)) %>%
  filter(!is.na(value)) %>%
  filter(group == 1) %>%
  group_by(Demo, Week, Variable) %>%
  summarize(Count = sum(value),
            Percent = 100*Count/n()) 

table = BefAft %>%
  gather("stat", "value", Count, Percent) %>%
  unite(Week, Week, stat, sep = "_") %>%
  spread(Week, value) %>%
  ungroup() %>%
  mutate(Variable = factor(Variable, levels = cc_binary, labels = cc_demo_labels),
         Change_count = During_Count - Bef_Count, 
         Change_percent = During_Percent - Bef_Percent) %>%
  arrange(Demo, Variable) 

#build groupings

first.row = sapply(demo_groups, first_instance, string = table$Demo)
last.row = sapply(demo_groups, last_instance, string = table$Demo)

each_string = paste0("group_rows(group_label = \" ", 
                     demo_labels, 
                     "\" , start_row = ", 
                     first.row, 
                     ", end_row = ", 
                     last.row, 
                     ")")
each_string = paste(each_string, collapse = " %>% ")

# table code
beginning = "table %>% 
  select(-Demo) %>% 
  kable(., digits = c(0, 0, 1, 0, 1, 0, 1),
        col.names = c(\"Type of childcare\", \"Count\", \"Percent\", \"Count\", \"Percent\", \"Count\", \"Percent\")) %>%
  kable_styling() %>%
  add_header_above(c(\" \", \"Pre-pandemic\" = 2, \"During pandemic\" = 2, \"Change\" = 2)) %>%"

eval(parse(text = paste0(beginning, each_string)))
```

```{r childcare-5}

BefAft %>%
  ungroup() %>%
  gather("stat", "value", Count, Percent) %>%
  unite(Week, Week, stat, sep = "_") %>%
  spread(Week, value) %>%
  mutate(Variable = factor(Variable, 
                           levels = cc_binary, 
                           labels = cc_demo_labels),
         Demo = factor(Demo, levels = demo_groups, labels = demo_labels),
         Change_percent = During_Percent - Bef_Percent) %>%
  ggplot(aes(x = Variable, y = Change_percent, fill = Demo)) +
  geom_bar(stat = "identity", position = "dodge", color = "white") +
  scale_y_continuous("Change in percent (not percent change)") +
  scale_x_discrete("", breaks = NULL) +
  coord_flip() +
  facet_wrap(~Variable, scales = "free") +
  theme(legend.position = "top")

# BefAft %>%
#   ungroup() %>%
#   gather("stat", "value", Count, Percent) %>%
#   unite(Week, Week, stat, sep = "_") %>%
#   spread(Week, value) %>%
#   mutate(Variable = factor(Variable, 
#                            levels = cc_binary, 
#                            labels = cc_demo_labels),
#          Demo = factor(Demo, levels = demo_groups, labels = demo_labels),
#          Change_percent = During_Percent - Bef_Percent) %>%
#   ggplot(aes(x = Demo, y = Change_percent, fill = Variable)) +
#   geom_bar(stat = "identity", position = "dodge", color = "white") +
#   scale_y_continuous("Change in percent (not percent change)") +
#   scale_x_discrete("", breaks = NULL) +
#   coord_flip() + 
#   facet_wrap(~Demo, scales = "free") +
#   theme(legend.position = "top")
```

# Access to other services or support

```{r access-by-race-10, eval = T}
othersupport = scored %>%
  filter(Week > 0) %>%
  select(Week, all_of(demo_groups), access_parenting, access_fitness, access_education) %>%
  gather(demo, group, all_of(demo_groups)) %>%
  filter(group == 1) %>%
  select(-group) %>%
  gather(services, response, -Week, -demo) %>%
  filter(!is.na(response)) %>%
  mutate(services = factor(services, 
                         levels = c("access_parenting", 
                                    "access_fitness", 
                                    "access_education"),
                         labels = c("Parenting support", 
                                    "Fitness classes", "Educational classes"))) %>%
  mutate(demo = factor(demo, levels = demo_groups, labels = demo_labels)) %>%
  separate(demo, into =c("demo", "income"), sep =",")
```

```{r eval = F}
othersupport %>%
  group_by(demo,services, income) %>%
  summarize(Count = sum(response),
            Percent = 100*Count/n()) %>%
  ggplot(aes(x = services, y = Percent, fill = services)) +
  geom_bar(stat = "identity") +
  guides(fill = F) +
  labs(x = "") +
  facet_grid(demo~income)+
  coord_flip()+
  theme_minimal()
```

```{r access-by-race-11}
othersupport %>%
  # filter(demo %in% powered) %>%
  group_by(Week, demo, services) %>%
  summarize(Count = sum(response),
            Percent = 100*Count/n()) %>%
  ggplot(aes(x = Week, y = Percent, color = demo)) +
  geom_point()+
  geom_line() +
  scale_x_continuous(breaks= c(1:max_weeks)) +
  facet_wrap(~services, ncol = 3) +
  theme_minimal() +
  theme(legend.position = "top")
```

# Insurance

```{r access-by-race-12}
scored %>%
  filter(Week > 0) %>%
  select(all_of(demo_groups), insurance, child_insurance) %>%
  gather("demo", "group", -insurance, -child_insurance) %>%
  filter(group == 1) %>%
  gather("type", "insurance", contains("insur")) %>%
  group_by(demo, type) %>%
  filter(!is.na(insurance)) %>%
  summarise(Count = sum(insurance),
            Percent = 100*Count/n()) %>%
  ungroup() %>%
  mutate(demo = factor(demo, 
                       levels = demo_groups,
                       labels = demo_labels),
         type = factor(type, 
                       levels =c("insurance", "child_insurance"), 
                       labels = c("Self", "Child"))) %>%
   separate(demo, into =c("demo", "income"), sep =",") %>%
  ggplot(aes(x = demo, y = Percent, fill = demo)) +
  geom_bar(stat = "identity") +
  facet_grid(income~type) +
  coord_flip()+
  guides(fill = F)+
  theme_minimal()
```


# Income

```{r access-by-race-13}
scored %>%
  filter(Week > 0) %>%
  select(income_decreaed, all_of(demo_groups)) %>%
  gather(demo, group, all_of(demo_groups)) %>%
  filter(group == 1) %>%
  select(-group) %>%
  filter(!is.na(income_decreaed)) %>%
  group_by(demo) %>%
  summarize(Count = sum(income_decreaed),
         Percent = 100*Count/n()) %>%
  ungroup() %>%
  mutate(demo = factor(demo, levels = demo_groups,labels = demo_labels))%>%
  ggplot(aes(x = demo, y = Percent, fill = demo)) +
  geom_bar(stat = "identity") +
  coord_flip()+
  guides(fill = F)+
  labs(title = "___ Percent of caregivers report decreased income since start of pandemic")+
  theme_minimal() +
  theme(plot.title.position = "plot")
```


## Difficulty paying for basic necessities
```{r access-by-race-14, eval = F}
scored %>%
  filter(Week > 0) %>%
  select(all_of(demo_groups), contains("diff_pay")) %>%
  gather("demo", "group", all_of(demo_groups)) %>%
  filter(group == 1) %>%
  select(-group) %>%
  gather(category, value, contains("diff_pay")) %>%
  mutate(category = gsub("diff_pay_", "", category)) %>%
  filter(!is.na(value)) %>%
  group_by(demo, category) %>%
  summarise(Count = sum(value),
            Percent = 100*Count/n()) %>%
  ungroup() %>%  
  mutate(category = fct_reorder(category, Percent, .fun='mean'),
         demo =factor(demo, levels = demo_groups, 
                       labels = demo_labels)) %>%
  #separate(demo, into =c("demo", "income"), sep =",")%>%
  ggplot(aes(x = demo, y = Percent, fill = demo)) +
  geom_bar(stat = "identity") +
  coord_flip()+
  guides(fill = F)+
  facet_grid(~category) +
  theme_minimal()
```

```{r access-by-race-15}
scored %>%
  filter(Week > 0) %>%
  select(all_of(demo_groups), contains("diff_pay")) %>%
  gather("demo", "group", all_of(demo_groups)) %>%
  filter(group == 1) %>%
  select(-group) %>%
  gather(category, value, contains("diff_pay")) %>%
  mutate(category = gsub("diff_pay_", "", category)) %>%
  filter(!is.na(value)) %>%
  group_by(demo, category) %>%
  summarise(Count = sum(value),
            Percent = 100*Count/n()) %>%
  ungroup() %>%
  mutate(category = fct_reorder(category, Percent, .fun='mean'),
         demo = factor(demo, levels = demo_groups, 
                       labels = demo_labels)) %>%
  separate(demo, into =c("demo", "income"), sep =",") %>%
  ggplot(aes(x = category, y = Percent, fill = category)) +
  geom_bar(stat = "identity") +
  coord_flip()+
  guides(fill = F)+
  facet_grid(income~demo) +
  theme_minimal()
```

```{r access-by-race-16}
scored_all %>%
  select(Week, all_of(demo_groups), contains("diff_pay")) %>%
  gather("demo", "group", all_of(demo_groups)) %>%
  filter(group == 1) %>%
  select(-group) %>%
  gather(category, value, contains("diff_pay")) %>%
  mutate(category = gsub("diff_pay_", "", category)) %>%
  filter(!is.na(value)) %>%
  group_by(Week, demo, category) %>%
  summarise(Count = sum(value),
            Percent = 100*Count/n()) %>%
  ungroup() %>%
  mutate(demo = factor(demo, 
                       levels = demo_groups,
                       labels = demo_labels)) %>%
   separate(demo, into =c("demo", "income"), sep =",") %>%
  # filter(demo %in% powered) %>%
  ggplot(aes(x = Week, y = Percent, color = category)) +
  geom_point()+
  geom_line()+
  facet_grid(demo~income) +
  theme_minimal()+
  theme(legend.position = "top")
```


<!-- ## Federal stimulus check -->
<!-- Received JOB.016 -->
<!-- Expect JOB.017.a -->
<!-- Why not JOB.017b -->

# Mental health/ emotional well-being {.tabset}

## Anxiety
```{r access-by-race-17}
anxiety_date_demo = scored %>%
  select(CaregiverID, Week, all_of(demo_groups), anxiety_current_some) %>%
  gather("demo", "value", all_of(demo_groups)) %>%
  filter(value == 1) %>%
  group_by(demo, Week) %>%
  summarize(total = n(),
            percent = 100*sum(anxiety_current_some, na.rm=T)/total) %>%
  ungroup() %>% 
  mutate(demo = factor(demo, 
                       levels = demo_groups, 
                       labels = demo_labels))  %>%
   separate(demo, into =c("demo", "income"), sep =",") 

anxiety_date_all = scored %>%
  select(CaregiverID, Week, anxiety_current_some) %>%
  group_by(Week) %>%
  summarize(total = n(),
            percent = 100*sum(anxiety_current_some, na.rm=T)/total) 

anxiety_date_demo %>%
  ggplot(aes(x = Week, y = percent)) +
  geom_point(aes(color = demo)) + 
  geom_line(aes(color = demo)) +
  geom_point(data = anxiety_date_all)+
  geom_line(data = anxiety_date_all, linetype = "dashed") +
  labs(x = "Week",
       y = "Percent of demographic group",
       title = "__ Percent of caregivers report some or a lot of anxiety",
       color = "Key demographics", 
       caption = "Entire sample is represented by the black, dashed line.") +
  facet_grid(demo~income)+
  theme_minimal() +
  theme(plot.title.position = "plot")
```

## Depression
```{r access-by-race-18}
depress_date_demo = scored %>%
  select(CaregiverID, Week, all_of(demo_groups), depress_current_some) %>%
  gather("demo", "value", all_of(demo_groups)) %>%
  filter(value == 1) %>%
  group_by(demo, Week) %>%
  summarize(total = n(),
            percent = 100*sum(depress_current_some, na.rm=T)/total) %>%
  ungroup() %>% 
  mutate(demo = factor(demo, 
                       levels = demo_groups, 
                       labels = demo_labels)) %>%
   separate(demo, into =c("demo", "income"), sep =",") 

depress_date_all = scored %>%
  select(CaregiverID, Week, depress_current_some) %>%
  group_by(Week) %>%
  summarize(total = n(),
            percent = 100*sum(depress_current_some, na.rm=T)/total) 

depress_date_demo %>%
  ggplot(aes(x = Week, y = percent)) +
  geom_point(aes(color = demo)) + 
  geom_line(aes(color = demo)) +
  geom_point(data = depress_date_all)+
  geom_line(data = depress_date_all, linetype = "dashed") +
  labs(x = "Week",
       y = "Percent of demographic group",
       title = "__ Percent of caregivers report some or a lot of depression",
       color = "Key demographics", 
       caption = "Entire sample is represented by the black, dashed line.") +
    facet_grid(demo~income)+
theme_minimal() +
  theme(plot.title.position = "plot")
```

## Stress
```{r access-by-race-19}
stress_date_demo = scored %>%
  select(CaregiverID, Week, all_of(demo_groups), stress_current_some) %>%
  gather("demo", "value", all_of(demo_groups)) %>%
  filter(value == 1) %>%
  group_by(demo, Week) %>%
  summarize(total = n(),
            percent = 100*sum(stress_current_some, na.rm=T)/total) %>%
  ungroup() %>% 
  mutate(demo = factor(demo, 
                       levels = demo_groups, 
                       labels = demo_labels)) %>%
   separate(demo, into =c("demo", "income"), sep =",") 

stress_date_all = scored %>%
  select(CaregiverID, Week, stress_current_some) %>%
  group_by(Week) %>%
  summarize(total = n(),
            percent = 100*sum(stress_current_some, na.rm=T)/total) 

stress_date_demo %>%
  ggplot(aes(x = Week, y = percent)) +
  geom_point(aes(color = demo)) + 
  geom_line(aes(color = demo)) +
  geom_point(data = stress_date_all)+
  geom_line(data = stress_date_all, linetype = "dashed") +
  labs(x = "Week",
       y = "Percent of demographic group",
       title = "__ Percent of caregivers report some or a lot of stress",
       color = "Key demographics", 
       caption = "Entire sample is represented by the black, dashed line.") +
    facet_grid(demo~income)+
theme_minimal() +
  theme(plot.title.position = "plot")
```

## Loneliness
```{r access-by-race-20}
lonely_date_demo = scored %>%
  select(CaregiverID, Week, all_of(demo_groups), lonely_current_some) %>%
  gather("demo", "value", all_of(demo_groups)) %>%
  filter(value == 1) %>%
  group_by(demo, Week) %>%
  summarize(total = n(),
            percent = 100*sum(lonely_current_some, na.rm=T)/total) %>%
  ungroup() %>% 
  mutate(demo = factor(demo, 
                       levels = demo_groups, 
                       labels = demo_labels)) %>%
   separate(demo, into =c("demo", "income"), sep =",") 

lonely_date_all = scored %>%
  select(CaregiverID, Week, lonely_current_some) %>%
  group_by(Week) %>%
  summarize(total = n(),
            percent = 100*sum(lonely_current_some, na.rm=T)/total) 

lonely_date_demo %>%
  ggplot(aes(x = Week, y = percent)) +
  geom_point(aes(color = demo)) + 
  geom_line(aes(color = demo)) +
  geom_point(data = lonely_date_all)+
  geom_line(data = lonely_date_all, linetype = "dashed") +
  labs(x = "Week",
       y = "Percent of demographic group",
       title = "__ Percent of caregivers report some or a lot of loneliness",
       color = "Key demographics", 
       caption = "Entire sample is represented by the black, dashed line.") +
    facet_grid(demo~income)+
theme_minimal() +
  theme(plot.title.position = "plot")
```

## Child Externalizing
```{r access-by-race-21}
fussy_date_demo = scored %>%
  select(CaregiverID, Week, all_of(demo_groups), fussy_current_some) %>%
  gather("demo", "value", all_of(demo_groups)) %>%
  filter(value == 1) %>%
  group_by(demo, Week) %>%
  summarize(total = n(),
            percent = 100*sum(fussy_current_some, na.rm=T)/total) %>%
  ungroup() %>% 
  mutate(demo = factor(demo, 
                       levels = demo_groups, 
                       labels = demo_labels)) %>%
   separate(demo, into =c("demo", "income"), sep =",") 

fussy_date_all = scored %>%
  select(CaregiverID, Week, fussy_current_some) %>%
  group_by(Week) %>%
  summarize(total = n(),
            percent = 100*sum(fussy_current_some, na.rm=T)/total) 

fussy_date_demo %>%
  ggplot(aes(x = Week, y = percent)) +
  geom_point(aes(color = demo)) + 
  geom_line(aes(color = demo)) +
  geom_point(data = fussy_date_all)+
  geom_line(data = fussy_date_all, linetype = "dashed") +
  labs(x = "Week",
       y = "Percent of demographic group",
       title = "__ Percent of caregivers report children are sometimes or often fussy or defiant",
       color = "Key demographics", 
       caption = "Entire sample is represented by the black, dashed line.") +
    facet_grid(demo~income)+
theme_minimal() +
  theme(plot.title.position = "plot")
```

## Child Internalizing
```{r access-by-race-22}
fear_date_demo = scored %>%
  select(CaregiverID, Week, all_of(demo_groups), fear_current_some) %>%
  gather("demo", "value", all_of(demo_groups)) %>%
  filter(value == 1) %>%
  group_by(demo, Week) %>%
  summarize(total = n(),
            percent = 100*sum(fear_current_some, na.rm=T)/total) %>%
  ungroup() %>% 
  mutate(demo = factor(demo, 
                       levels = demo_groups, 
                       labels = demo_labels)) %>%
   separate(demo, into =c("demo", "income"), sep =",") 

fear_date_all = scored %>%
  select(CaregiverID, Week, fear_current_some) %>%
  group_by(Week) %>%
  summarize(total = n(),
            percent = 100*sum(fear_current_some, na.rm=T)/total) 

fear_date_demo %>%
  ggplot(aes(x = Week, y = percent)) +
  geom_point(aes(color = demo)) + 
  geom_line(aes(color = demo)) +
  geom_point(data = fear_date_all)+
  geom_line(data = fear_date_all, linetype = "dashed") +
  labs(x = "Week",
       y = "Percent of demographic group",
       title = "__ Percent of caregivers report children are sometimes or often too fearful or anxious",
       color = "Key demographics", 
       caption = "Entire sample is represented by the black, dashed line.") +
    facet_grid(demo~income)+
theme_minimal() +
  theme(plot.title.position = "plot")
```
