---
title: "Racial inequality begins in early childhood"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
  
---


```{r blm-1, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
```

```{r blm-2 }
weighted = F

report = ifelse(weighted, "ARE WEIGHTED", "ARE NOT WEIGHTED")
```

Responses `r report` by race.

Rural communities are defined as zipcodes with density smaller than 500 people per square mile. Urban areas are zipcodes with density greater than 1000 people per square mile. Zipcodes between these two extremes are omitted. 



```{r blm-3 }
library(here)
```

```{r blm-4 }
percent_by_group = function(data, outcome, group, weights, na.rm=T){

  cross = count(data, {{outcome}}, {{group}},
                wt = {{weights}})
  names(cross) = c("outcome","group","n")
  if(na.rm){
    cross = filter(cross, !is.na(group) & !is.na(outcome))
  }
  cross = cross %>%
    dplyr::group_by(group) %>%
    mutate(percent = 100*n/sum(n)) %>%
    ungroup %>%
    mutate(group = as.factor(group),
           outcome = as.factor(outcome))
  return(cross)
}

histogram_plot = function(data, outcome, group, labels_v, weights){
  
  df = data %>%
    dplyr::select({{outcome}}, {{group}}, {{weights}})
  names(df) = c("outcome_v", "group_v","weight_v")
    
  df = df %>%
    filter(!is.na(group_v)) %>%
    mutate(group_v = factor(group_v, labels = labels_v)) 
  
  means = df %>%
    dplyr::group_by(group_v) %>%
    dplyr::summarize(m = wtd.mean(outcome_v, 
                                  weights = weight_v, 
                                  na.rm=T),
                     m = round(m, 2))
  
  plot = df %>%
    ggplot(aes(x = outcome_v)) + 
    geom_histogram(aes(y = ..density..)) +
    geom_vline(aes(xintercept = m,
                   color = group_v),
               data = means) +
    scale_color_brewer("Means", 
                       palette = "Dark2", 
                       labels = c(means$m))+
    facet_wrap(~group_v, ncol = 1) +
    labs(x = "",
         y = "Density",
         title = deparse(substitute(outcome))) +
    theme_pubclean()
  
  return(plot)
  }
```


```{r blm-5, echo = F, warning = F, message = F}
## score master --------------------------------------------------------
source(here("Scripts/score data.R"))
```

```{r blm-6 }
#select most recent timepoint for each participant
scored = scored %>%
  dplyr::group_by(CaregiverID) %>%
  filter(Week == max(Week)) %>%
  ungroup()
```

```{r blm-7 }

nation = c(
  "native",
  "asian",
  "black",
  "hawaii",
  "white",
  "other",
  "multiple")

nation_labels = c(
  "American Indian/Alaska Native",
  "Asian",
  "Black/African American",
  "Native Hawaiian/Pacific Islander",
  "White/Caucasian",
  "Other race",
  "Multiple races")

#currently population perecentages are manually copied from from file Population_Weights_ACS_2018 in Data Management R3/CC_Clean_Survey Data/00_R3 MasterFile
pop_percent = data.frame(
  race_cat = c("White/Caucasian",
               "Black/African American", 
               "American Indian/Alaska Native",
               "Asian",
                "Native Hawaiian/Pacific Islander",
                "Other race"),
  pop_percent = c(72.20,12.70,0.90,5.60,0.20,5.00))

scored = scored %>%
  mutate(race_cat = ifelse(race_cat == "Multiple races", 
                           "Other race", 
                           race_cat)) 

scored = scored %>%
  dplyr::group_by(race_cat) %>%
  dplyr::summarize(count = n()) %>%
  ungroup() %>%
  mutate(sample_percent = 100*count/sum(count)) %>%
  full_join(pop_percent) %>%
  mutate(weight = pop_percent/sample_percent) %>%
  dplyr::select(race_cat, weight) %>%
  full_join(scored)

if(!weighted) scored$weight = 1
```

```{r blm-8 }
scored = scored %>%
  mutate(
    compare1 = case_when(
      black == 1 ~ "1", 
      white == 1 ~ "0",
      TRUE ~ NA_character_),
    compare2 = case_when(
      black == 1 ~ "1", 
      latinx == 1 ~ "1",
      white == 1 ~ "0",
      TRUE ~ NA_character_),
    compare3 = case_when(
      black == 1 ~ "1", 
      latinx == 1 ~ "1",
      native == 1 ~ "1",
      hawaii == 1 ~ "1",
      other_race == 1 ~ "1",
      white == 1 ~ "0",
      TRUE ~ NA_character_),
    compare4 = case_when(
      black == 1 ~ "1", 
      latinx == 1 ~ "1",
      native == 1 ~ "1",
      hawaii == 1 ~ "1",
      other_race == 1 ~ "1",
      asian == 1 ~ "1",
      white == 1 ~ "0",
      TRUE ~ NA_character_)
    ) %>%
  select(-black, -white)

labels1 = c("white", "black")
labels2 = c("white", "black + latinx")
labels3 = c("white", "poc (minus asian)")
labels4 = c("white", "poc")
labelsi = levels(scored$income.cat)
labels5 = c("Midwest","Northeast", "South", "West")
labels6 = c("Rural","Urban")
```

```{r blm-9 }
library(weights)
library(ggpubr)
library(dplyr)
```

# Sample sizes

```{r blm-10 }
ss = scored %>%
  select(contains("compare")) %>%
  gather("compare", value) %>%
  filter(!is.na(value)) %>%
  dplyr::group_by(compare, value) %>%
  dplyr::summarize(n = n()) %>%
  mutate(value = paste0("x",value))%>%
  spread(value, n) 
```

| Comparison | Group 1 | Group 2 |
|-----------:|:-------:|:-------:|
|  1 | Black          | White |
|           | `r ss[1, 3]`   | `r ss[1, 2]`    |
|  2 | Black + LatinX | White |
|           | `r ss[2, 3]`   | `r ss[2, 2]`    |
|  3 | POC (minus Asian) | White |
|           | `r ss[3, 3]`   | `r ss[3, 2]`    |
|  4 | POC  | White |
|           | `r ss[4, 3]`   | `r ss[4, 2]`    |

# Well-being

## Anxiety{.tabset}

### Black

```{r blm-11 }
histogram_plot(scored, anxiety, compare1, labels1, weight)
```

```{r blm-12, eval = !weighted}
t.test(anxiety~compare1, data = scored)
```

```{r blm-13, eval = weighted}
wtd.t.test(x = scored$anxiety[scored$compare1 == "0"], 
           y = scored$anxiety[scored$compare1 == "1"],
           weight = scored$weight[scored$compare1 == "0"],
           weighty = scored$weight[scored$compare1 == "1"])
```

### Black + LatinX

```{r blm-14 }
histogram_plot(scored, anxiety, compare2, labels2, weight)
```

```{r blm-15, eval = !weighted}
t.test(anxiety~compare2, data = scored)
```

```{r blm-16, eval = weighted}

wtd.t.test(x = scored$anxiety[scored$compare2 == "0"], 
           y = scored$anxiety[scored$compare2 == "1"],
           weight = scored$weight[scored$compare2 == "0"],
           weighty = scored$weight[scored$compare2 == "1"])
```

### People of Color (minus Asian)

```{r blm-17 }
histogram_plot(scored, anxiety, compare3, labels3, weight)
```

```{r blm-18, eval = !weighted}
t.test(anxiety~compare3, data = scored)
```

```{r blm-19, eval = weighted}

wtd.t.test(x = scored$anxiety[scored$compare3 == "0"], 
           y = scored$anxiety[scored$compare3 == "1"],
           weight = scored$weight[scored$compare3 == "0"],
           weighty = scored$weight[scored$compare3 == "1"])
```


### People of Color 

```{r blm-20 }
histogram_plot(scored, anxiety, compare4, labels4, weight)
```

```{r blm-21, eval = !weighted}
t.test(anxiety~compare4, data = scored)
```

```{r blm-22, eval = weighted}

wtd.t.test(x = scored$anxiety[scored$compare4 == "0"], 
           y = scored$anxiety[scored$compare4 == "1"],
           weight = scored$weight[scored$compare4 == "0"],
           weighty = scored$weight[scored$compare4 == "1"])
```

### By income

```{r blm-23 }
histogram_plot(scored, anxiety, income.cat, labelsi, weight)
```


```{r blm-24, eval = !weighted}
anova(lm(anxiety ~ income.cat, data = scored))
```

```{r blm-25, eval = weighted}
anova(lm(anxiety ~ income.cat, data = scored, weights = scored$weight))
```

### Geographic Region

```{r blm-26 }
histogram_plot(scored, anxiety, region, labels5, weight)
```

```{r blm-27, eval = !weighted}
anova(lm(anxiety ~ region, data = scored))
```

```{r blm-28, eval = weighted}
anova(lm(anxiety ~ region, data = scored, weights = scored$weight))
```

### Rural/Urban

```{r blm-29 }
histogram_plot(scored, anxiety, rural, labels6, weight)
```

```{r blm-30, eval = !weighted}
t.test(anxiety~rural, data = scored)
```

```{r blm-31, eval = weighted}

wtd.t.test(x = scored$anxiety[scored$rural == "rural"], 
           y = scored$anxiety[scored$rural == "urban"],
           weight = scored$weight[scored$rural == "rural"],
           weighty = scored$weight[scored$rural == "urban"])
```

## Depression{.tabset}

### Black

```{r blm-32 }
histogram_plot(scored, depress, compare1, labels1, weight)
```

```{r blm-33, eval = !weighted}
t.test(depress~compare1, data = scored)
```

```{r blm-34, eval = weighted}

wtd.t.test(x = scored$depress[scored$compare1 == "0"], 
           y = scored$depress[scored$compare1 == "1"],
           weight = scored$weight[scored$compare1 == "0"],
           weighty = scored$weight[scored$compare1 == "1"])
```

### Black + LatinX

```{r blm-35 }
histogram_plot(scored, depress, compare2, labels2, weight)
```

```{r blm-36, eval = !weighted}
t.test(depress~compare2, data = scored)
```

```{r blm-37, eval = weighted}

wtd.t.test(x = scored$depress[scored$compare2 == "0"], 
           y = scored$depress[scored$compare2 == "1"],
           weight = scored$weight[scored$compare2 == "0"],
           weighty = scored$weight[scored$compare2 == "1"])
```

### People of Color (minus Asian)

```{r blm-38 }
histogram_plot(scored, depress, compare3, labels3, weight)
```

```{r blm-39, eval = !weighted}
t.test(depress~compare3, data = scored)
```

```{r blm-40, eval = weighted}

wtd.t.test(x = scored$depress[scored$compare3 == "0"], 
           y = scored$depress[scored$compare3 == "1"],
           weight = scored$weight[scored$compare3 == "0"],
           weighty = scored$weight[scored$compare3 == "1"])
```


### People of Color 

```{r blm-41 }
histogram_plot(scored, depress, compare4, labels4, weight)
```

```{r blm-42, eval = !weighted}
t.test(depress~compare4, data = scored)
```

```{r blm-43, eval = weighted}

wtd.t.test(x = scored$depress[scored$compare4 == "0"], 
           y = scored$depress[scored$compare4 == "1"],
           weight = scored$weight[scored$compare4 == "0"],
           weighty = scored$weight[scored$compare4 == "1"])
```

### By income

```{r blm-44 }
histogram_plot(scored, depress, income.cat, labelsi, weight)
```


```{r blm-45, eval = !weighted}
anova(lm(depress ~ income.cat, data = scored))
```

```{r blm-46, eval = weighted}
anova(lm(depress ~ income.cat, data = scored, weights = scored$weight))
```

### Geographic Region

```{r blm-47 }
histogram_plot(scored, depress, region, labels5, weight)
```


```{r blm-48, eval = !weighted}
anova(lm(depress ~ region, data = scored))
```

```{r blm-49, eval = weighted}
anova(lm(depress ~ region, data = scored, weights = scored$weight))
```

### Rural/Urban

```{r blm-50 }
histogram_plot(scored, depress, rural, labels6, weight)
```

```{r blm-51, eval = !weighted}
t.test(depress~rural, data = scored)
```

```{r blm-52, eval = weighted}

wtd.t.test(x = scored$depress[scored$rural == "rural"], 
           y = scored$depress[scored$rural == "urban"],
           weight = scored$weight[scored$rural == "rural"],
           weighty = scored$weight[scored$rural == "urban"])
```

## Stress{.tabset}

### Black

```{r blm-53 }
histogram_plot(scored, stress, compare1, labels1, weight)
```

```{r blm-54, eval = !weighted}
t.test(stress~compare1, data = scored)
```

```{r blm-55, eval = weighted}
wtd.t.test(x = scored$stress[scored$compare1 == "0"], 
           y = scored$stress[scored$compare1 == "1"],
           weight = scored$weight[scored$compare1 == "0"],
           weighty = scored$weight[scored$compare1 == "1"])
```

### Black + LatinX

```{r blm-56 }
histogram_plot(scored, stress, compare2, labels2, weight)

```

```{r blm-57, eval = !weighted}
t.test(stress~compare2, data = scored)
```

```{r blm-58, eval = weighted}

wtd.t.test(x = scored$stress[scored$compare2 == "0"], 
           y = scored$stress[scored$compare2 == "1"],
           weight = scored$weight[scored$compare2 == "0"],
           weighty = scored$weight[scored$compare2 == "1"])
```

### People of Color (minus Asian)

```{r blm-59 }
histogram_plot(scored, stress, compare3, labels3, weight)

```

```{r blm-60, eval = !weighted}
t.test(stress~compare3, data = scored)
```

```{r blm-61, eval = weighted}

wtd.t.test(x = scored$stress[scored$compare3 == "0"], 
           y = scored$stress[scored$compare3 == "1"],
           weight = scored$weight[scored$compare3 == "0"],
           weighty = scored$weight[scored$compare3 == "1"])
```


### People of Color 

```{r blm-62 }
histogram_plot(scored, stress, compare4, labels4, weight)

```

```{r blm-63, eval = !weighted}
t.test(stress~compare4, data = scored)
```

```{r blm-64, eval = weighted}

wtd.t.test(x = scored$stress[scored$compare4 == "0"], 
           y = scored$stress[scored$compare4 == "1"],
           weight = scored$weight[scored$compare4 == "0"],
           weighty = scored$weight[scored$compare4 == "1"])
```

### By income

```{r blm-65 }
histogram_plot(scored, stress, income.cat, labelsi, weight)
```


```{r blm-66, eval = !weighted}
anova(lm(stress ~ income.cat, data = scored))
```

```{r blm-67, eval = weighted}
anova(lm(stress ~ income.cat, data = scored, weights = scored$weight))
```

### Geographic Region

```{r blm-68 }
histogram_plot(scored, stress, region, labelsi, weight)
```


```{r blm-69, eval = !weighted}
anova(lm(stress ~ region, data = scored))
```

```{r blm-70, eval = weighted}
anova(lm(stress ~ region, data = scored, weights = scored$weight))
```

### Rural/Urban

```{r blm-71 }
histogram_plot(scored, stress, rural, labels6, weight)

```

```{r blm-72, eval = !weighted}
t.test(stress~rural, data = scored)
```

```{r blm-73, eval = weighted}

wtd.t.test(x = scored$stress[scored$rural == "rural"], 
           y = scored$stress[scored$rural == "urban"],
           weight = scored$weight[scored$rural == "rural"],
           weighty = scored$weight[scored$rural == "urban"])
```

## Loneliness{.tabset}

### Black

```{r blm-74 }
histogram_plot(scored, lonely, compare1, labels1, weight)
```

```{r blm-75, eval = !weighted}
t.test(lonely~compare1, data = scored)
```

```{r blm-76, eval = weighted}

wtd.t.test(x = scored$lonely[scored$compare1 == "0"], 
           y = scored$lonely[scored$compare1 == "1"],
           weight = scored$weight[scored$compare1 == "0"],
           weighty = scored$weight[scored$compare1 == "1"])
```

### Black + LatinX

```{r blm-77 }
histogram_plot(scored, lonely, compare2, labels2, weight)
```

```{r blm-78, eval = !weighted}
t.test(lonely~compare2, data = scored)
```

```{r blm-79, eval = weighted}

wtd.t.test(x = scored$lonely[scored$compare2 == "0"], 
           y = scored$lonely[scored$compare2 == "1"],
           weight = scored$weight[scored$compare2 == "0"],
           weighty = scored$weight[scored$compare2 == "1"])
```

### People of Color (minus Asian)

```{r blm-80 }
histogram_plot(scored, lonely, compare3, labels3, weight)
```

```{r blm-81, eval = !weighted}
t.test(lonely~compare3, data = scored)
```

```{r blm-82, eval = weighted}

wtd.t.test(x = scored$lonely[scored$compare3 == "0"], 
           y = scored$lonely[scored$compare3 == "1"],
           weight = scored$weight[scored$compare3 == "0"],
           weighty = scored$weight[scored$compare3 == "1"])
```


### People of Color 

```{r blm-83 }
histogram_plot(scored, lonely, compare4, labels4, weight)
```

```{r blm-84, eval = !weighted}
t.test(lonely~compare4, data = scored)
```

```{r blm-85, eval = weighted}

wtd.t.test(x = scored$lonely[scored$compare4 == "0"], 
           y = scored$lonely[scored$compare4 == "1"],
           weight = scored$weight[scored$compare4 == "0"],
           weighty = scored$weight[scored$compare4 == "1"])
```


### By income

```{r blm-86 }
histogram_plot(scored, lonely, income.cat, labelsi, weight)
```


```{r blm-87, eval = !weighted}
anova(lm(lonely ~ income.cat, data = scored))
```

```{r blm-88, eval = weighted}
anova(lm(lonely ~ income.cat, data = scored, weights = scored$weight))
```

### Geographic Region

```{r blm-89 }
histogram_plot(scored, lonely, region, labelsi, weight)
```


```{r blm-90, eval = !weighted}
anova(lm(lonely ~ region, data = scored))
```

```{r blm-91, eval = weighted}
anova(lm(lonely ~ region, data = scored, weights = scored$weight))
```

### Rural/Urban

```{r blm-92 }
histogram_plot(scored, lonely, rural, labels6, weight)
```

```{r blm-93, eval = !weighted}
t.test(lonely~rural, data = scored)
```

```{r blm-94, eval = weighted}

wtd.t.test(x = scored$lonely[scored$rural == "rural"], 
           y = scored$lonely[scored$rural == "urban"],
           weight = scored$weight[scored$rural == "rural"],
           weighty = scored$weight[scored$rural == "urban"])
```
## Child Externalizing{.tabset}

### Black

```{r blm-95 }
histogram_plot(scored, fussy, compare1, labels1, weight)
```

```{r blm-96, eval = !weighted}
t.test(fussy~compare1, data = scored)
```

```{r blm-97, eval = weighted}
wtd.t.test(x = scored$fussy[scored$compare1 == "0"], 
           y = scored$fussy[scored$compare1 == "1"],
           weight = scored$weight[scored$compare1 == "0"],
           weighty = scored$weight[scored$compare1 == "1"])
```

### Black + LatinX

```{r blm-98 }
histogram_plot(scored, fussy, compare2, labels2, weight)
```

```{r blm-99, eval = !weighted}
t.test(fussy~compare2, data = scored)
```

```{r blm-100, eval = weighted}

wtd.t.test(x = scored$fussy[scored$compare2 == "0"], 
           y = scored$fussy[scored$compare2 == "1"],
           weight = scored$weight[scored$compare2 == "0"],
           weighty = scored$weight[scored$compare2 == "1"])
```

### People of Color (minus Asian)

```{r blm-101 }
histogram_plot(scored, fussy, compare3, labels3, weight)
```

```{r blm-102, eval = !weighted}
t.test(fussy~compare3, data = scored)
```

```{r blm-103, eval = weighted}

wtd.t.test(x = scored$fussy[scored$compare3 == "0"], 
           y = scored$fussy[scored$compare3 == "1"],
           weight = scored$weight[scored$compare3 == "0"],
           weighty = scored$weight[scored$compare3 == "1"])
```


### People of Color 

```{r blm-104 }
histogram_plot(scored, fussy, compare4, labels4, weight)
```

```{r blm-105, eval = !weighted}
t.test(fussy~compare4, data = scored)
```

```{r blm-106, eval = weighted}

wtd.t.test(x = scored$fussy[scored$compare4 == "0"], 
           y = scored$fussy[scored$compare4 == "1"],
           weight = scored$weight[scored$compare4 == "0"],
           weighty = scored$weight[scored$compare4 == "1"])
```



### By income

```{r blm-107 }
histogram_plot(scored, fussy, income.cat, labelsi, weight)
```


```{r blm-108, eval = !weighted}
anova(lm(fussy ~ income.cat, data = scored))
```

```{r blm-109, eval = weighted}
anova(lm(fussy ~ income.cat, data = scored, weights = scored$weight))
```

### Geographic Region

```{r blm-110 }
histogram_plot(scored, fussy, income.cat, labelsi, weight)
```


```{r blm-111, eval = !weighted}
anova(lm(fussy ~ income.cat, data = scored))
```

```{r blm-112, eval = weighted}
anova(lm(fussy ~ income.cat, data = scored, weights = scored$weight))
```

### Rural/Urban

```{r blm-113 }
histogram_plot(scored, fussy, rural, labels6, weight)
```

```{r blm-114, eval = !weighted}
t.test(fussy~rural, data = scored)
```

```{r blm-115, eval = weighted}

wtd.t.test(x = scored$fussy[scored$rural == "rural"], 
           y = scored$fussy[scored$rural == "urban"],
           weight = scored$weight[scored$rural == "rural"],
           weighty = scored$weight[scored$rural == "urban"])
```
## Child Internalizing{.tabset}

### Black

```{r blm-116 }
histogram_plot(scored, fear, compare1, labels1, weight)
```

```{r blm-117, eval = !weighted}
t.test(fear~compare1, data = scored)
```

```{r blm-118, eval = weighted}

wtd.t.test(x = scored$fear[scored$compare1 == "0"], 
           y = scored$fear[scored$compare1 == "1"],
           weight = scored$weight[scored$compare1 == "0"],
           weighty = scored$weight[scored$compare1 == "1"])
```

### Black + LatinX

```{r blm-119 }
histogram_plot(scored, fear, compare2, labels2, weight)

```

```{r blm-120, eval = !weighted}
t.test(fear~compare2, data = scored)
```

```{r blm-121, eval = weighted}

wtd.t.test(x = scored$fear[scored$compare2 == "0"], 
           y = scored$fear[scored$compare2 == "1"],
           weight = scored$weight[scored$compare2 == "0"],
           weighty = scored$weight[scored$compare2 == "1"])
```

### People of Color (minus Asian)

```{r blm-122 }
histogram_plot(scored, fear, compare3, labels3, weight)

```

```{r blm-123, eval = !weighted}
t.test(fear~compare3, data = scored)
```

```{r blm-124, eval = weighted}

wtd.t.test(x = scored$fear[scored$compare3 == "0"], 
           y = scored$fear[scored$compare3 == "1"],
           weight = scored$weight[scored$compare3 == "0"],
           weighty = scored$weight[scored$compare3 == "1"])
```


### People of Color 

```{r blm-125 }
histogram_plot(scored, fear, compare4, labels4, weight)

```

```{r blm-126, eval = !weighted}
t.test(fear~compare4, data = scored)
```

```{r blm-127, eval = weighted}

wtd.t.test(x = scored$fear[scored$compare4 == "0"], 
           y = scored$fear[scored$compare4 == "1"],
           weight = scored$weight[scored$compare4 == "0"],
           weighty = scored$weight[scored$compare4 == "1"])
```

### By income

```{r blm-128 }
histogram_plot(scored, fear, income.cat, labelsi, weight)

```


```{r blm-129, eval = !weighted}
anova(lm(fear ~ income.cat, data = scored))
```

```{r blm-130, eval = weighted}
anova(lm(fear ~ income.cat, data = scored, weights = scored$weight))
```

### Geographic Region

```{r blm-131 }
histogram_plot(scored, fear, income.cat, labelsi, weight)

```


```{r blm-132, eval = !weighted}
anova(lm(fear ~ income.cat, data = scored))
```

```{r blm-133, eval = weighted}
anova(lm(fear ~ income.cat, data = scored, weights = scored$weight))
```

### Rural/Urban

```{r blm-134 }
histogram_plot(scored, fear, rural, labels6, weight)

```

```{r blm-135, eval = !weighted}
t.test(fear~rural, data = scored)
```

```{r blm-136, eval = weighted}

wtd.t.test(x = scored$fear[scored$rural == "rural"], 
           y = scored$fear[scored$rural == "urban"],
           weight = scored$weight[scored$rural == "rural"],
           weighty = scored$weight[scored$rural == "urban"])
```

# Work benefits

## Income{.tabset}

### Black

```{r blm-137 }
histogram_plot(scored, income, compare1, labels1, weight)

```

```{r blm-138, eval = !weighted}
t.test(income~compare1, data = scored)
```

```{r blm-139, eval = weighted}

wtd.t.test(x = scored$income[scored$compare1 == "0"], 
           y = scored$income[scored$compare1 == "1"],
           weight = scored$weight[scored$compare1 == "0"],
           weighty = scored$weight[scored$compare1 == "1"])
```

### Black + LatinX

```{r blm-140 }
histogram_plot(scored, income, compare2, labels2, weight)
```

```{r blm-141, eval = !weighted}
t.test(income~compare2, data = scored)
```

```{r blm-142, eval = weighted}

wtd.t.test(x = scored$income[scored$compare2 == "0"], 
           y = scored$income[scored$compare2 == "1"],
           weight = scored$weight[scored$compare2 == "0"],
           weighty = scored$weight[scored$compare2 == "1"])
```

### People of Color (minus Asian)

```{r blm-143 }
histogram_plot(scored, income, compare3, labels3, weight)
```

```{r blm-144, eval = !weighted}
t.test(income~compare3, data = scored)
```

```{r blm-145, eval = weighted}

wtd.t.test(x = scored$income[scored$compare3 == "0"], 
           y = scored$income[scored$compare3 == "1"],
           weight = scored$weight[scored$compare3 == "0"],
           weighty = scored$weight[scored$compare3 == "1"])
```


### People of Color 

```{r blm-146 }
histogram_plot(scored, income, compare4, labels4, weight)
```

```{r blm-147, eval = !weighted}
t.test(income~compare4, data = scored)
```

```{r blm-148, eval = weighted}

wtd.t.test(x = scored$income[scored$compare4 == "0"], 
           y = scored$income[scored$compare4 == "1"],
           weight = scored$weight[scored$compare4 == "0"],
           weighty = scored$weight[scored$compare4 == "1"])
```

### Geographic Region

```{r blm-149 }
histogram_plot(scored, income, region, labelsi, weight)
```


```{r blm-150, eval = !weighted}
anova(lm(income ~ region, data = scored))
```

```{r blm-151, eval = weighted}
anova(lm(income ~ region, data = scored, weights = scored$weight))
```

### Rural/Urban

```{r blm-152 }
histogram_plot(scored, income, rural, labels6, weight)
```

```{r blm-153, eval = !weighted}
t.test(income~rural, data = scored)
```

```{r blm-154, eval = weighted}

wtd.t.test(x = scored$income[scored$rural == "rural"], 
           y = scored$income[scored$rural == "urban"],
           weight = scored$weight[scored$rural == "rural"],
           weighty = scored$weight[scored$rural == "urban"])
```
## Sick Leave {.tabset}

### Black

```{r blm-155 }
percent_by_group(scored, sick_leave, compare1, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels1) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-156, eval = !weighted}
chisq.test(scored$sick_leave, scored$compare1)
```

```{r blm-157, eval = weighted}
weights::wtd.chi.sq(scored$sick_leave,
                scored$compare1,
                weight = scored$weight)
```

### Black + LatinX

```{r blm-158 }
percent_by_group(scored, sick_leave, compare2, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels2) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-159, eval = !weighted}
chisq.test(scored$sick_leave, scored$compare2)
```

```{r blm-160, eval = weighted}
weights::wtd.chi.sq(scored$sick_leave,
                scored$compare2,
                weight = scored$weight)
```

### People of Color (minus Asian)

```{r blm-161 }
percent_by_group(scored, sick_leave, compare3, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels3) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-162, eval = !weighted}
chisq.test(scored$sick_leave, scored$compare3)
```

```{r blm-163, eval = weighted}
weights::wtd.chi.sq(scored$sick_leave,
                scored$compare3,
                weight = scored$weight)
```


### People of Color 

```{r blm-164 }
percent_by_group(scored, sick_leave, compare4, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels4) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-165, eval = !weighted}
chisq.test(scored$sick_leave, scored$compare4)
```

```{r blm-166, eval = weighted}
weights::wtd.chi.sq(scored$sick_leave,
                scored$compare4,
                weight = scored$weight)
```

### By income

```{r blm-167 }
percent_by_group(scored, sick_leave, income.cat, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labelsi) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-168, eval = !weighted}
chisq.test(scored$sick_leave, scored$income.cat)
```

```{r blm-169, eval = weighted}
weights::wtd.chi.sq(scored$sick_leave,
                scored$income.cat,
                weight = scored$weight)
```

### Geographic Region

```{r blm-170 }
percent_by_group(scored, sick_leave, region, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels5) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-171, eval = !weighted}
chisq.test(scored$sick_leave, scored$region)
```

```{r blm-172, eval = weighted}
weights::wtd.chi.sq(scored$sick_leave,
                scored$region,
                weight = scored$weight)
```

### Rural/Urban

```{r blm-173 }
percent_by_group(scored, sick_leave, rural, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels6) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-174, eval = !weighted}
chisq.test(scored$sick_leave, scored$rural)
```

```{r blm-175, eval = weighted}
weights::wtd.chi.sq(scored$sick_leave,
                scored$rural,
                weight = scored$weight)
```
# Employment

## Unemployed {.tabset}

### Black

```{r blm-176 }
percent_by_group(scored, unemployed, compare1, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels1) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```


```{r blm-177, eval = !weighted}
chisq.test(scored$unemployed, scored$compare1)
```

```{r blm-178, eval = weighted}
weights::wtd.chi.sq(scored$unemployed,
                scored$compare1,
                weight = scored$weight)
```

### Black + LatinX

```{r blm-179 }
percent_by_group(scored, unemployed, compare2, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels2) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```



```{r blm-180, eval = !weighted}
chisq.test(scored$unemployed, scored$compare2)
```

```{r blm-181, eval = weighted}
weights::wtd.chi.sq(scored$unemployed,
                scored$compare2,
                weight = scored$weight)
```

### People of Color (minus Asian)

```{r blm-182 }
percent_by_group(scored, unemployed, compare3, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels3) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```



```{r blm-183, eval = !weighted}
chisq.test(scored$unemployed, scored$compare3)
```

```{r blm-184, eval = weighted}
weights::wtd.chi.sq(scored$unemployed,
                scored$compare3,
                weight = scored$weight)
```

### People of Color 

```{r blm-185 }
percent_by_group(scored, unemployed, compare4, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels4) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```


```{r blm-186, eval = !weighted}
chisq.test(scored$unemployed, scored$compare4)
```

```{r blm-187, eval = weighted}
weights::wtd.chi.sq(scored$unemployed,
                scored$compare4,
                weight = scored$weight)
```


### By income

```{r blm-188 }
percent_by_group(scored, unemployed, income.cat, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("") +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```


```{r blm-189, eval = !weighted}
chisq.test(scored$unemployed, scored$income.cat)
```

```{r blm-190, eval = weighted}
weights::wtd.chi.sq(scored$unemployed,
                scored$income.cat,
                weight = scored$weight)
```

### Geographic Region

```{r blm-191 }
percent_by_group(scored, unemployed, region, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels5) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```


```{r blm-192, eval = !weighted}
chisq.test(scored$unemployed, scored$region)
```

```{r blm-193, eval = weighted}
weights::wtd.chi.sq(scored$unemployed,
                scored$region,
                weight = scored$weight)
```

### Rural/Urban

```{r blm-194 }
percent_by_group(scored, unemployed, rural, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels6) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```


```{r blm-195, eval = !weighted}
chisq.test(scored$unemployed, scored$rural)
```

```{r blm-196, eval = weighted}
weights::wtd.chi.sq(scored$unemployed,
                scored$rural,
                weight = scored$weight)
```
## Lost employment{.tabset}

"Has your level of employment decreased due to the coronavirus (COVID-19) pandemic?"

### Black

```{r blm-197 }
percent_by_group(scored, employment_decreased, compare1, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white") +
  scale_x_discrete("", labels = labels1) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-198, eval = !weighted}
chisq.test(scored$employment_decreased, scored$compare1)
```

```{r blm-199, eval = weighted}
weights::wtd.chi.sq(scored$employment_decreased,
                scored$compare1,
                weight = scored$weight)
```

### Black + LatinX

```{r blm-200 }
percent_by_group(scored, employment_decreased, compare2, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels2) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```


```{r blm-201, eval = !weighted}
chisq.test(scored$employment_decreased, scored$compare2)
```

```{r blm-202, eval = weighted}
weights::wtd.chi.sq(scored$employment_decreased,
                scored$compare2,
                weight = scored$weight)
```

### People of Color (minus Asian)

```{r blm-203 }
percent_by_group(scored, employment_decreased, compare3, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels3) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-204, eval = !weighted}
chisq.test(scored$employment_decreased, scored$compare3)
```

```{r blm-205, eval = weighted}
weights::wtd.chi.sq(scored$employment_decreased,
                scored$compare3,
                weight = scored$weight)
```


### People of Color 

```{r blm-206 }
percent_by_group(scored, employment_decreased, compare4, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels4) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-207, eval = !weighted}
chisq.test(scored$employment_decreased, scored$compare4)
```

```{r blm-208, eval = weighted}
weights::wtd.chi.sq(scored$employment_decreased,
                scored$compare4,
                weight = scored$weight)
```

### By income

```{r blm-209 }
percent_by_group(scored, employment_decreased, income.cat, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("") +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-210, eval = !weighted}
chisq.test(scored$employment_decreased, scored$income.cat)
```

```{r blm-211, eval = weighted}
weights::wtd.chi.sq(scored$employment_decreased,
                scored$income.cat,
                weight = scored$weight)
```

### Geographic Region

```{r blm-212 }
percent_by_group(scored, employment_decreased, region, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels5) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-213, eval = !weighted}
chisq.test(scored$employment_decreased, scored$region)
```

```{r blm-214, eval = weighted}
weights::wtd.chi.sq(scored$employment_decreased,
                scored$region,
                weight = scored$weight)
```


### Rural/Urban

```{r blm-215 }
percent_by_group(scored, employment_decreased, rural, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels6) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-216, eval = !weighted}
chisq.test(scored$employment_decreased, scored$rural)
```

```{r blm-217, eval = weighted}
weights::wtd.chi.sq(scored$employment_decreased,
                scored$rural,
                weight = scored$weight)
```

## Among unemployed

```{r blm-218 }
unemployed = scored %>%
  filter(unemployed == 1)

ss = unemployed %>%
  select(contains("compare")) %>%
  gather("compare", value) %>%
  filter(!is.na(value)) %>%
  dplyr::group_by(compare, value) %>%
  dplyr::summarize(n = n()) %>%
  mutate(value = paste0("x",value))%>%
  spread(value, n) 
```

| Comparison | Group 1 | Group 2 |
|-----------:|:-------:|:-------:|
|  1 | Black          | White |
|           | `r ss[1, 3]`   | `r ss[1, 2]`    |
|  2 | Black + LatinX | White |
|           | `r ss[2, 3]`   | `r ss[2, 2]`    |
|  3 | POC (minus Asian) | White |
|           | `r ss[3, 3]`   | `r ss[3, 2]`    |
|  4 | POC  | White |
|           | `r ss[4, 3]`   | `r ss[4, 2]`    |

### Have access to free food{.tabset}

#### Black

```{r blm-219 }
percent_by_group(unemployed, free_food, compare1, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels1) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-220, eval = !weighted}
chisq.test(unemployed$free_food, unemployed$compare1)
```

```{r blm-221, eval = weighted}
weights::wtd.chi.sq(unemployed$free_food,
                unemployed$compare1,
                weight = unemployed$weight)
```

#### Black + LatinX

```{r blm-222 }
percent_by_group(unemployed, free_food, compare2, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels2) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-223, eval = !weighted}
chisq.test(unemployed$free_food, unemployed$compare2)
```

```{r blm-224, eval = weighted}
weights::wtd.chi.sq(unemployed$free_food,
                unemployed$compare2,
                weight = unemployed$weight)
```

#### People of Color (minus Asian)

```{r blm-225 }
percent_by_group(unemployed, free_food, compare3, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels3) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-226, eval = !weighted}
chisq.test(unemployed$free_food, unemployed$compare3)
```

```{r blm-227, eval = weighted}
weights::wtd.chi.sq(unemployed$free_food,
                unemployed$compare3,
                weight = unemployed$weight)
```


#### People of Color

```{r blm-228 }
percent_by_group(unemployed, free_food, compare4, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels4) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-229, eval = !weighted}
chisq.test(unemployed$free_food, unemployed$compare4)
```

```{r blm-230, eval = weighted}
weights::wtd.chi.sq(unemployed$free_food,
                unemployed$compare4,
                weight = unemployed$weight)
```

#### By income

```{r blm-231 }
percent_by_group(unemployed, free_food, income.cat, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labelsi) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-232, eval = !weighted}
chisq.test(unemployed$free_food, unemployed$income.cat)
```

```{r blm-233, eval = weighted}
weights::wtd.chi.sq(unemployed$free_food,
                unemployed$income.cat,
                weight = unemployed$weight)
```

#### Geographic Region

```{r blm-234 }
percent_by_group(unemployed, free_food, region, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels5) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-235, eval = !weighted}
chisq.test(unemployed$free_food, unemployed$region)
```

```{r blm-236, eval = weighted}
weights::wtd.chi.sq(unemployed$free_food,
                unemployed$region,
                weight = unemployed$weight)
```

#### Rural/Urban

```{r blm-237 }
percent_by_group(unemployed, free_food, rural, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels6) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-238, eval = !weighted}
chisq.test(unemployed$free_food, unemployed$rural)
```

```{r blm-239, eval = weighted}
weights::wtd.chi.sq(unemployed$free_food,
                unemployed$rural,
                weight = unemployed$weight)
```
### Lost free lunch for child(ren){.tabset}

#### Black

```{r blm-240 }
percent_by_group(unemployed, lost_free_lunch, compare1, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels1) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-241, eval = !weighted}
chisq.test(unemployed$lost_free_lunch, unemployed$compare1)
```

```{r blm-242, eval = weighted}
weights::wtd.chi.sq(unemployed$lost_free_lunch,
                unemployed$compare1,
                weight = unemployed$weight)
```

#### Black + LatinX

```{r blm-243 }
percent_by_group(unemployed, lost_free_lunch, compare2, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels2) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-244, eval = !weighted}
chisq.test(unemployed$lost_free_lunch, unemployed$compare2)
```

```{r blm-245, eval = weighted}
weights::wtd.chi.sq(unemployed$lost_free_lunch,
                unemployed$compare2,
                weight = unemployed$weight)
```

#### People of Color (minus Asian)

```{r blm-246 }
percent_by_group(unemployed, lost_free_lunch, compare3, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels3) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-247, eval = !weighted}
chisq.test(unemployed$lost_free_lunch, unemployed$compare3)
```

```{r blm-248, eval = weighted}
weights::wtd.chi.sq(unemployed$lost_free_lunch,
                unemployed$compare3,
                weight = unemployed$weight)
```


#### People of Color

```{r blm-249 }
percent_by_group(unemployed, lost_free_lunch, compare4, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels4) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-250, eval = !weighted}
chisq.test(unemployed$lost_free_lunch, unemployed$compare4)
```

```{r blm-251, eval = weighted}
weights::wtd.chi.sq(unemployed$lost_free_lunch,
                unemployed$compare4,
                weight = unemployed$weight)
```

#### By income

```{r blm-252 }
percent_by_group(unemployed, lost_free_lunch, income.cat, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labelsi) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-253, eval = !weighted}
chisq.test(unemployed$lost_free_lunch, unemployed$income.cat)
```

```{r blm-254, eval = weighted}
weights::wtd.chi.sq(unemployed$lost_free_lunch,
                unemployed$income.cat,
                weight = unemployed$weight)
```

#### Geographic Region

```{r blm-255 }
percent_by_group(unemployed, lost_free_lunch, region, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels5) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-256, eval = !weighted}
chisq.test(unemployed$lost_free_lunch, unemployed$v)
```

```{r blm-257, eval = weighted}
weights::wtd.chi.sq(unemployed$lost_free_lunch,
                unemployed$region,
                weight = unemployed$weight)
```

#### Rural/Urban

```{r blm-258 }
percent_by_group(unemployed, lost_free_lunch, rural, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels6) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-259, eval = !weighted}
chisq.test(unemployed$lost_free_lunch, unemployed$rural)
```

```{r blm-260, eval = weighted}
weights::wtd.chi.sq(unemployed$lost_free_lunch,
                unemployed$rural,
                weight = unemployed$weight)
```
# Childcare 

## Plans for next month

### Same as right now{.tabset}

#### Black

```{r blm-261 }
percent_by_group(scored, plan_cc_samenow, compare1, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels1) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-262, eval = !weighted}
chisq.test(scored$plan_cc_samenow, scored$compare1)
```

```{r blm-263, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_samenow,
                scored$compare1,
                weight = scored$weight)
```

#### Black + LatinX

```{r blm-264 }
percent_by_group(scored, plan_cc_samenow, compare2, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels2) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-265, eval = !weighted}
chisq.test(scored$plan_cc_samenow, scored$compare2)
```

```{r blm-266, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_samenow,
                scored$compare2,
                weight = scored$weight)
```

#### People of Color (minus Asian)

```{r blm-267 }
percent_by_group(scored, plan_cc_samenow, compare3, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels3) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-268, eval = !weighted}
chisq.test(scored$plan_cc_samenow, scored$compare3)
```

```{r blm-269, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_samenow,
                scored$compare3,
                weight = scored$weight)
```


#### People of Color

```{r blm-270 }
percent_by_group(scored, plan_cc_samenow, compare4, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels4) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-271, eval = !weighted}
chisq.test(scored$plan_cc_samenow, scored$compare4)
```

```{r blm-272, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_samenow,
                scored$compare4,
                weight = scored$weight)
```

#### By income

```{r blm-273 }
percent_by_group(scored, plan_cc_samenow, income.cat, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labelsi) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-274, eval = !weighted}
chisq.test(scored$plan_cc_samenow, scored$income.cat)
```

```{r blm-275, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_samenow,
                scored$income.cat,
                weight = scored$weight)
```

#### Geographic Region

```{r blm-276 }
percent_by_group(scored, plan_cc_samenow, region, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels5) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-277, eval = !weighted}
chisq.test(scored$plan_cc_samenow, scored$region)
```

```{r blm-278, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_samenow,
                scored$region,
                weight = scored$weight)
```

#### Rural/Urban

```{r blm-279 }
percent_by_group(scored, plan_cc_samenow, rural, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels6) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-280, eval = !weighted}
chisq.test(scored$plan_cc_samenow, scored$rural)
```

```{r blm-281, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_samenow,
                scored$rural,
                weight = scored$weight)
```
### Different arrangement{.tabset}

#### Black

```{r blm-282 }
percent_by_group(scored, plan_cc_differ, compare1, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels1) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-283, eval = !weighted}
chisq.test(scored$plan_cc_differ, scored$compare1)
```

```{r blm-284, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_differ,
                scored$compare1,
                weight = scored$weight)
```

#### Black + LatinX

```{r blm-285 }
percent_by_group(scored, plan_cc_differ, compare2, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels2) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-286, eval = !weighted}
chisq.test(scored$plan_cc_differ, scored$compare2)
```

```{r blm-287, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_differ,
                scored$compare2,
                weight = scored$weight)
```

#### People of Color (minus Asian)

```{r blm-288 }
percent_by_group(scored, plan_cc_differ, compare3, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels3) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-289, eval = !weighted}
chisq.test(scored$plan_cc_differ, scored$compare3)
```

```{r blm-290, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_differ,
                scored$compare3,
                weight = scored$weight)
```


#### People of Color

```{r blm-291 }
percent_by_group(scored, plan_cc_differ, compare4, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels4) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-292, eval = !weighted}
chisq.test(scored$plan_cc_differ, scored$compare4)
```

```{r blm-293, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_differ,
                scored$compare4,
                weight = scored$weight)
```

#### By income

```{r blm-294 }
percent_by_group(scored, plan_cc_differ, income.cat, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labelsi) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-295, eval = !weighted}
chisq.test(scored$plan_cc_differ, scored$income.cat)
```

```{r blm-296, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_differ,
                scored$income.cat,
                weight = scored$weight)
```

#### Geographic Region

```{r blm-297 }
percent_by_group(scored, plan_cc_differ, region, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels5) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-298, eval = !weighted}
chisq.test(scored$plan_cc_differ, scored$region)
```

```{r blm-299, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_differ,
                scored$region,
                weight = scored$weight)
```

#### Rural/Urban

```{r blm-300 }
percent_by_group(scored, plan_cc_differ, rural, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels6) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-301, eval = !weighted}
chisq.test(scored$plan_cc_differ, scored$rural)
```

```{r blm-302, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_differ,
                scored$rural,
                weight = scored$weight)
```

### Same as during pandemic{.tabset}

#### Black

```{r blm-303 }
percent_by_group(scored, plan_cc_sameCOVID, compare1, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels1) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-304, eval = !weighted}
chisq.test(scored$plan_cc_sameCOVID, scored$compare1)
```

```{r blm-305, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_sameCOVID,
                scored$compare1,
                weight = scored$weight)
```

#### Black + LatinX

```{r blm-306 }
percent_by_group(scored, plan_cc_sameCOVID, compare2, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels2) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-307, eval = !weighted}
chisq.test(scored$plan_cc_sameCOVID, scored$compare2)
```

```{r blm-308, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_sameCOVID,
                scored$compare2,
                weight = scored$weight)
```

#### People of Color (minus Asian)

```{r blm-309 }
percent_by_group(scored, plan_cc_sameCOVID, compare3, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels3) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-310, eval = !weighted}
chisq.test(scored$plan_cc_sameCOVID, scored$compare3)
```

```{r blm-311, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_sameCOVID,
                scored$compare3,
                weight = scored$weight)
```


#### People of Color

```{r blm-312 }
percent_by_group(scored, plan_cc_sameCOVID, compare4, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels4) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-313, eval = !weighted}
chisq.test(scored$plan_cc_sameCOVID, scored$compare4)
```

```{r blm-314, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_sameCOVID,
                scored$compare4,
                weight = scored$weight)
```

#### By income

```{r blm-315 }
percent_by_group(scored, plan_cc_sameCOVID, income.cat, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labelsi) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-316, eval = !weighted}
chisq.test(scored$plan_cc_sameCOVID, scored$income.cat)
```

```{r blm-317, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_sameCOVID,
                scored$income.cat,
                weight = scored$weight)
```

#### Geographic Region

```{r blm-318 }
percent_by_group(scored, plan_cc_sameCOVID, region, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels5) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-319, eval = !weighted}
chisq.test(scored$plan_cc_sameCOVID, scored$region)
```

```{r blm-320, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_sameCOVID,
                scored$region,
                weight = scored$weight)
```

#### Rural/Urban

```{r blm-321 }
percent_by_group(scored, plan_cc_sameCOVID, rural, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels6) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-322, eval = !weighted}
chisq.test(scored$plan_cc_sameCOVID, scored$rural)
```

```{r blm-323, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_sameCOVID,
                scored$rural,
                weight = scored$weight)
```

### Don't know{.tabset}

#### Black

```{r blm-324 }
percent_by_group(scored, plan_cc_dontknow, compare1, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels1) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-325, eval = !weighted}
chisq.test(scored$plan_cc_dontknow, scored$compare1)
```

```{r blm-326, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_dontknow,
                scored$compare1,
                weight = scored$weight)
```

#### Black + LatinX

```{r blm-327 }
percent_by_group(scored, plan_cc_dontknow, compare2, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels2) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-328, eval = !weighted}
chisq.test(scored$plan_cc_dontknow, scored$compare2)
```

```{r blm-329, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_dontknow,
                scored$compare2,
                weight = scored$weight)
```

#### People of Color (minus Asian)

```{r blm-330 }
percent_by_group(scored, plan_cc_dontknow, compare3, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels3) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-331, eval = !weighted}
chisq.test(scored$plan_cc_dontknow, scored$compare3)
```

```{r blm-332, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_dontknow,
                scored$compare3,
                weight = scored$weight)
```


#### People of Color

```{r blm-333 }
percent_by_group(scored, plan_cc_dontknow, compare4, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels4) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-334, eval = !weighted}
chisq.test(scored$plan_cc_dontknow, scored$compare4)
```

```{r blm-335, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_dontknow,
                scored$compare4,
                weight = scored$weight)
```

#### By income

```{r blm-336 }
percent_by_group(scored, plan_cc_dontknow, income.cat, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labelsi) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-337, eval = !weighted}
chisq.test(scored$plan_cc_dontknow, scored$income.cat)
```

```{r blm-338, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_dontknow,
                scored$income.cat,
                weight = scored$weight)
```

#### Geographic Region

```{r blm-339 }
percent_by_group(scored, plan_cc_dontknow, income.cat, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels5) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-340, eval = !weighted}
chisq.test(scored$plan_cc_dontknow, scored$income.cat)
```

```{r blm-341, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_dontknow,
                scored$income.cat,
                weight = scored$weight)
```


#### Rural/Urban

```{r blm-342 }
percent_by_group(scored, plan_cc_dontknow, rural, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels6) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-343, eval = !weighted}
chisq.test(scored$plan_cc_dontknow, scored$rural)
```

```{r blm-344, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_dontknow,
                scored$rural,
                weight = scored$weight)
```
## Lost type of childcare{.tabset}

```{r blm-345 }
scored = scored %>%
  mutate(
    lostcc_center = ifelse(priorcc_center == 1 & expect_center == 0, 1, 0),
    lostcc_relativemyhome = ifelse(priorcc_relativemyhome == 1 & expect_relativemyhome == 0, 1, 0),
    lostcc_relativetheirhome = ifelse(priorcc_relativetheirhome == 1 & expect_relativetheirhome == 0, 1, 0),
    lostcc_promyhome = ifelse(priorcc_promyhome == 1 & expect_promyhome == 0, 1, 0),
    lostcc_theirhome = ifelse(priorcc_theirhome == 1 & expect_theirhome == 0, 1, 0),
    lostcc_parents = ifelse(priorcc_parents == 1 & expect_parents == 0, 1, 0))

scored = scored %>%
  select(CaregiverID, contains("lostcc")) %>%
  gather(type, value, -CaregiverID) %>%
  dplyr::group_by(CaregiverID) %>%
  filter(!is.na(value)) %>%
  dplyr::summarize(lostCC_sum = sum(value),
            lostCC = ifelse(lostCC_sum > 0, 1, 0)) %>%
  full_join(scored)
```


### Black

```{r blm-346 }
percent_by_group(scored, lostCC, compare1, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels1) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-347, eval = !weighted}
chisq.test(scored$lostCC, scored$compare1)
```

```{r blm-348, eval = weighted}
weights::wtd.chi.sq(scored$lostCC,
                scored$compare1,
                weight = scored$weight)
```

### Black + LatinX

```{r blm-349 }
percent_by_group(scored, lostCC, compare2, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels2) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-350, eval = !weighted}
chisq.test(scored$lostCC, scored$compare2)
```

```{r blm-351, eval = weighted}
weights::wtd.chi.sq(scored$lostCC,
                scored$compare2,
                weight = scored$weight)
```

### People of Color (minus Asian)

```{r blm-352 }
percent_by_group(scored, lostCC, compare3, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels3) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-353, eval = !weighted}
chisq.test(scored$lostCC, scored$compare3)
```

```{r blm-354, eval = weighted}
weights::wtd.chi.sq(scored$lostCC,
                scored$compare3,
                weight = scored$weight)
```


### People of Color

```{r blm-355 }
percent_by_group(scored, lostCC, compare4, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels4) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-356, eval = !weighted}
chisq.test(scored$lostCC, scored$compare4)
```

```{r blm-357, eval = weighted}
weights::wtd.chi.sq(scored$lostCC,
                scored$compare4,
                weight = scored$weight)
```

### By income

```{r blm-358 }
percent_by_group(scored, plan_cc_dontknow, income.cat, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labelsi) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-359, eval = !weighted}
chisq.test(scored$plan_cc_dontknow, scored$income.cat)
```

```{r blm-360, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_dontknow,
                scored$income.cat,
                weight = scored$weight)
```


### Geographic Region

```{r blm-361 }
percent_by_group(scored, plan_cc_dontknow, region, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels5) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-362, eval = !weighted}
chisq.test(scored$plan_cc_dontknow, scored$region)
```

```{r blm-363, eval = weighted}
weights::wtd.chi.sq(scored$plan_cc_dontknow,
                scored$region,
                weight = scored$weight)
```



### Rural/Urban

```{r blm-364 }
percent_by_group(scored, lostCC, rural, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels6) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-365, eval = !weighted}
chisq.test(scored$lostCC, scored$rural)
```

```{r blm-366, eval = weighted}
weights::wtd.chi.sq(scored$lostCC,
                scored$rural,
                weight = scored$weight)
```

## Type of care for the next month

### Center-based{.tabset}

#### Black

```{r blm-367 }
percent_by_group(scored, expect_center, compare1, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels1) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-368, eval = !weighted}
chisq.test(scored$expect_center, scored$compare1)
```

```{r blm-369, eval = weighted}
weights::wtd.chi.sq(scored$expect_center,
                scored$compare1,
                weight = scored$weight)
```

#### Black + LatinX

```{r blm-370 }
percent_by_group(scored, expect_center, compare2, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels2) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-371, eval = !weighted}
chisq.test(scored$expect_center, scored$compare2)
```

```{r blm-372, eval = weighted}
weights::wtd.chi.sq(scored$expect_center,
                scored$compare2,
                weight = scored$weight)
```

#### People of Color (minus Asian)

```{r blm-373 }
percent_by_group(scored, expect_center, compare3, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels3) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-374, eval = !weighted}
chisq.test(scored$expect_center, scored$compare3)
```

```{r blm-375, eval = weighted}
weights::wtd.chi.sq(scored$expect_center,
                scored$compare3,
                weight = scored$weight)
```


#### People of Color

```{r blm-376 }
percent_by_group(scored, expect_center, compare4, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels4) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-377, eval = !weighted}
chisq.test(scored$expect_center, scored$compare4)
```

```{r blm-378, eval = weighted}
weights::wtd.chi.sq(scored$expect_center,
                scored$compare4,
                weight = scored$weight)
```

#### By income

```{r blm-379 }
percent_by_group(scored, expect_center, income.cat, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labelsi) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-380, eval = !weighted}
chisq.test(scored$expect_center, scored$income.cat)
```

```{r blm-381, eval = weighted}
weights::wtd.chi.sq(scored$expect_center,
                scored$income.cat,
                weight = scored$weight)
```

#### Geographic Region

```{r blm-382 }
percent_by_group(scored, expect_center, region, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels5) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-383, eval = !weighted}
chisq.test(scored$expect_center, scored$region)
```

```{r blm-384, eval = weighted}
weights::wtd.chi.sq(scored$expect_center,
                scored$region,
                weight = scored$weight)
```

#### Rural/Urban

```{r blm-385 }
percent_by_group(scored, expect_center, rural, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels6) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-386, eval = !weighted}
chisq.test(scored$expect_center, scored$rural)
```

```{r blm-387, eval = weighted}
weights::wtd.chi.sq(scored$expect_center,
                scored$rural,
                weight = scored$weight)
```
### Care by relatives{.tabset}

```{r blm-388 }
scored = scored %>%
  mutate(expect_relative = ifelse(expect_relativemyhome == 1 | expect_relativetheirhome == 1, 1, 0))
```

#### Black

```{r blm-389 }
percent_by_group(scored, expect_relative, compare1, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels1) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-390, eval = !weighted}
chisq.test(scored$expect_relative, scored$compare1)
```

```{r blm-391, eval = weighted}
weights::wtd.chi.sq(scored$expect_relative,
                scored$compare1,
                weight = scored$weight)
```

#### Black + LatinX

```{r blm-392 }
percent_by_group(scored, expect_relative, compare2, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels2) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-393, eval = !weighted}
chisq.test(scored$expect_relative, scored$compare2)
```

```{r blm-394, eval = weighted}
weights::wtd.chi.sq(scored$expect_relative,
                scored$compare2,
                weight = scored$weight)
```

#### People of Color (minus Asian)

```{r blm-395 }
percent_by_group(scored, expect_relative, compare3, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels3) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-396, eval = !weighted}
chisq.test(scored$expect_relative, scored$compare3)
```

```{r blm-397, eval = weighted}
weights::wtd.chi.sq(scored$expect_relative,
                scored$compare3,
                weight = scored$weight)
```


#### People of Color

```{r blm-398 }
percent_by_group(scored, expect_relative, compare4, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels4) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-399, eval = !weighted}
chisq.test(scored$expect_relative, scored$compare4)
```

```{r blm-400, eval = weighted}
weights::wtd.chi.sq(scored$expect_relative,
                scored$compare4,
                weight = scored$weight)
```

#### By income

```{r blm-401 }
percent_by_group(scored, expect_relative, income.cat, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labelsi) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-402, eval = !weighted}
chisq.test(scored$expect_relative, scored$income.cat)
```

```{r blm-403, eval = weighted}
weights::wtd.chi.sq(scored$expect_relative,
                scored$income.cat,
                weight = scored$weight)
```

#### Geographic Region

```{r blm-404 }
percent_by_group(scored, expect_relative, region, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels5) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-405, eval = !weighted}
chisq.test(scored$expect_relative, scored$region)
```

```{r blm-406, eval = weighted}
weights::wtd.chi.sq(scored$expect_relative,
                scored$region,
                weight = scored$weight)
```

#### Rural/Urban

```{r blm-407 }
percent_by_group(scored, expect_relative, rural, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels6) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-408, eval = !weighted}
chisq.test(scored$expect_relative, scored$rural)
```

```{r blm-409, eval = weighted}
weights::wtd.chi.sq(scored$expect_relative,
                scored$rural,
                weight = scored$weight)
```
### Professional (non-centerbased){.tabset}

```{r blm-410 }
scored = scored %>%
  mutate(expect_pro = ifelse(expect_promyhome == 1 | expect_theirhome == 1, 1, 0))
```

#### Black

```{r blm-411 }
percent_by_group(scored, expect_pro, compare1, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels1) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-412, eval = !weighted}
chisq.test(scored$expect_pro, scored$compare1)
```

```{r blm-413, eval = weighted}
weights::wtd.chi.sq(scored$expect_pro,
                scored$compare1,
                weight = scored$weight)
```

#### Black + LatinX

```{r blm-414 }
percent_by_group(scored, expect_pro, compare2, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels2) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-415, eval = !weighted}
chisq.test(scored$expect_pro, scored$compare2)
```

```{r blm-416, eval = weighted}
weights::wtd.chi.sq(scored$expect_pro,
                scored$compare2,
                weight = scored$weight)
```

#### People of Color (minus Asian)

```{r blm-417 }
percent_by_group(scored, expect_pro, compare3, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels3) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-418, eval = !weighted}
chisq.test(scored$expect_pro, scored$compare3)
```

```{r blm-419, eval = weighted}
weights::wtd.chi.sq(scored$expect_pro,
                scored$compare3,
                weight = scored$weight)
```


#### People of Color

```{r blm-420 }
percent_by_group(scored, expect_pro, compare4, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels4) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-421, eval = !weighted}
chisq.test(scored$expect_pro, scored$compare4)
```

```{r blm-422, eval = weighted}
weights::wtd.chi.sq(scored$expect_pro,
                scored$compare4,
                weight = scored$weight)
```

#### By income

```{r blm-423 }
percent_by_group(scored, expect_pro, income.cat, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labelsi) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-424, eval = !weighted}
chisq.test(scored$expect_pro, scored$income.cat)
```

```{r blm-425, eval = weighted}
weights::wtd.chi.sq(scored$expect_pro,
                scored$income.cat,
                weight = scored$weight)
```


#### Geographic Region

```{r blm-426 }
percent_by_group(scored, expect_pro, region, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels5) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-427, eval = !weighted}
chisq.test(scored$expect_pro, scored$region)
```

```{r blm-428, eval = weighted}
weights::wtd.chi.sq(scored$expect_pro,
                scored$region,
                weight = scored$weight)
```

#### Rural/Urban

```{r blm-429 }
percent_by_group(scored, expect_pro, rural, weight) %>%
  ggplot(aes(x = group, y = percent, fill = outcome)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(percent), group = outcome, y = 5),
            position = position_dodge(.8),
            color = "white")+
  scale_x_discrete("", labels = labels6) +
  scale_y_continuous("Frequency (%)")+
  scale_fill_brewer(palette = "Dark2", labels = c("No", "Yes")) +
  theme_pubclean()
```

```{r blm-430, eval = !weighted}
chisq.test(scored$expect_pro, scored$rural)
```

```{r blm-431, eval = weighted}
weights::wtd.chi.sq(scored$expect_pro,
                scored$rural,
                weight = scored$weight)
```

```{r}
detach("package:weights", unload=TRUE)
detach("package:Hmisc", unload=TRUE)
```

