---
title: "Canary in the coal mine"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---



```{r chunk 1, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
```

```{r packages}
library(here)
library(ggpubr)
```

```{r childcare-1}
source(here("Scripts/score data.R")) 

completedWeek9 = scored %>%
  filter(Week == 9) 
completedWeek9 = completedWeek9$CaregiverID

scored = scored %>%
  filter(CaregiverID %in% completedWeek9) %>%
  filter(Week %in% c(0,9))

# groups
scored = scored %>%
  mutate(
    poc = case_when(
      race_cat == "White/Caucasian" ~ "White",
      race_cat == "Asian" ~ NA_character_,
      !is.na(race_cat) ~ "POC (non Asian)",
      TRUE ~ NA_character_),
    pocA = case_when(
      race_cat == "White/Caucasian" ~ "White",
      race_cat == "Asian" ~ "POC",
      !is.na(race_cat) ~ "POC",
      TRUE ~ NA_character_),
    whiteO = case_when(
      race_cat == "White/Caucasian" ~ "White",
      !is.na(race_cat) ~ "Non-white",
      TRUE ~ NA_character_),
    poverty150 = factor(poverty150, levels = c(0,1), 
                        labels = c("High Income", "Low Income")),
    conflictSource = factor(conflictSource, 
                            labels = c("Being confident that my family has health insurance",
                                       "Not being so socially isolated",
                                       "Having lower levels of worry and stress ",
                                       "Knowing we can pay for food ",
                                       "Knowing we can pay my rent/mortgage/housing expenses",
                                       "Knowing my/our job is secure",
                                       "Being able to meet my child's social and emotional needs",
                                       "Knowing we have access to childcare"))) %>%
  select(CaregiverID, Week, contains("conflict"), contains("cohesive"), poc, pocA, whiteO, poverty150)
```

```{r canary-1}
scored_prepost = scored %>%
  select(-contains("Source")) %>%
  gather("key", "value", 
         contains("conflict"), contains("cohesive")) %>%
  mutate(Week = ifelse(Week == 0, "pre", "post")) %>%
  spread(Week, value) %>%
  mutate(change = post-pre) %>%
  select(-pre, -post) %>%
  spread(key, change)
```

```{r, eval = F}
did_increase = function(x){
  x = ifelse(x > 0, 1, 0)
}

scored_prepost %>%
  mutate_at(vars(contains("conflict")), did_increase) %>%
  gather("variable", "value", contains("conflict")) %>%
  filter(!is.na(value)) %>%
  group_by(variable) %>%
  summarize(Percent = 100*sum(value)/n())
```


# Descriptives

Weeks used in these analyses are `r unique(scored$Week)`.

```{r canary-2, results = 'asis'}
test = scored %>%
  select_if(function(col)  is.character(col)| is.factor(col)) %>%
  select(-CaregiverID) 

apply(test, 2, table) %>%
  kable(.) %>%
  kable_styling() %>%
  scroll_box(width = "100%")
```


```{r canary-3, results = 'asis'}
scored %>%
  select_if(is.numeric) %>%
  psych::describe( fast = T) %>%
  kable(., caption = "Descriptives of numeric variables", digits = 2) %>%
  kable_styling(full_width = T)
```

```{r canary-4}
scored %>%
  select_if(is.numeric) %>%
  cor(., use = "pairwise") %>%
  corrplot::corrplot(method = "number")
```

```{r canary-5}
scored = scored %>%
  mutate(Week = ifelse(Week == 0, "Pre", "Post"),
         Week = factor(Week, levels = c("Pre", "Post")))
```


```{r functions}
source(here("Functions/compare_pre-post.R"))
```


# Total Conflict

Families have many different ways of trying to settle their differences. This is a list of things that might happen when your family has differences. Please mark how many times each of these things happened in the last week. Please also think about a typical week in your family’s like prior to the coronavirus (COVID-19) pandemic, and mark how many times each of these things happened. If one of these things did not occur, then select “This has not happened" for that question. 

- I insulted or swore or shouted or yelled at my partner 
- I shouted, yelled, or screamed at my child 
- I criticized or said mean things to my child 
- I felt like throwing things or slamming doors 
- My partner insulted or swore or shouted or yelled at me 
- My partner shouted, yelled, or screamed at my child 
- My partner criticized my child 
- My child had a temper tantrum 
- My child argued with me 
- My child argued with my partner 

## Pre-post{.tabset}

### Overall

```{r canary-6}
test = pre_post_overall(scored, conflict_total)
test$plot
```

```{r canary-7, results = 'asis'}
test$pairwise
```

### POC

```{r canary-8}
test = pre_post_group(scored, pocA, conflict_total)
test$plot
```

```{r canary-9, results = 'asis'}
test$pairwise
```


### Poverty line

```{r canary-10}
test = pre_post_group(scored, poverty150, conflict_total)
test$plot
```

```{r canary-11, results = 'asis'}
test$pairwise
```

## Change{.tabset}


### Overall

```{r canary-12}
test = change_overall(scored_prepost, conflict_total)
test$plot
```

```{r canary-13, results = 'asis'}
test$ttest
```

### POC

```{r canary-14}
test = change_group(scored_prepost, pocA, conflict_total)
test$plot
```

```{r canary-15, results = 'asis'}
test$ttest
```


### Poverty line

```{r canary-16}
test = change_group(scored_prepost, poverty150, conflict_total)
test$plot
```

```{r canary-17, results = 'asis'}
test$ttest
```

# Spousal Conflict

Families have many different ways of trying to settle their differences. This is a list of things that might happen when your family has differences. Please mark how many times each of these things happened in the last week. Please also think about a typical week in your family’s like prior to the coronavirus (COVID-19) pandemic, and mark how many times each of these things happened. If one of these things did not occur, then select “This has not happened" for that question. 

- I insulted or swore or shouted or yelled at my partner 
- My partner insulted or swore or shouted or yelled at me 

## Pre-post{.tabset}


### Overall

```{r canary-18}
test = pre_post_overall(scored, conflict_parent)
test$plot
```

```{r canary-19, results = 'asis'}
test$pairwise
```

### POC

```{r canary-20}
test = pre_post_group(scored, pocA, conflict_parent)
test$plot
```

```{r canary-21, results = 'asis'}
test$pairwise
```


### Poverty line

```{r canary-22}
test = pre_post_group(scored, poverty150, conflict_parent)
test$plot
```

```{r canary-23, results = 'asis'}
test$pairwise
```

## Change{.tabset}


### Overall

```{r canary-24}
test = change_overall(scored_prepost, conflict_parent)
test$plot
```

```{r canary-25, results = 'asis'}
test$ttest
```
### POC

```{r canary-26}
test = change_group(scored_prepost, pocA, conflict_parent)
test$plot
```

```{r canary-27, results = 'asis'}
test$ttest
```

### Poverty line

```{r canary-28}
test = change_group(scored_prepost, poverty150, conflict_parent)
test$plot
```

```{r canary-29, results = 'asis'}
test$ttest
```

# Child-parent Conflict

Families have many different ways of trying to settle their differences. This is a list of things that might happen when your family has differences. Please mark how many times each of these things happened in the last week. Please also think about a typical week in your family’s like prior to the coronavirus (COVID-19) pandemic, and mark how many times each of these things happened. If one of these things did not occur, then select “This has not happened" for that question. 

- I shouted, yelled, or screamed at my child 
- I criticized or said mean things to my child 
- My partner shouted, yelled, or screamed at my child 
- My partner criticized my child 
- My child had a temper tantrum 
- My child argued with me 
- My child argued with my partner 

## Pre-post{.tabset}


### Overall

```{r canary-30}
test = pre_post_overall(scored, conflict_child)
test$plot
```

```{r canary-31, results = 'asis'}
test$pairwise
```

### POC

```{r canary-32}
test = pre_post_group(scored, pocA, conflict_child)
test$plot
```

```{r canary-33, results = 'asis'}
test$pairwise
```


### Poverty line

```{r canary-34}
test = pre_post_group(scored, poverty150, conflict_child)
test$plot
```

```{r canary-35, results = 'asis'}
test$pairwise
```

## Change{.tabset}


### Overall

```{r canary-36}
test = change_overall(scored_prepost, conflict_child)
test$plot
```

```{r canary-37, results = 'asis'}
test$ttest
```
### POC

```{r canary-38}
test = change_group(scored_prepost, pocA, conflict_child)
test$plot
```

```{r canary-39, results = 'asis'}
test$ttest
```



### Poverty line

```{r canary-40}
test = change_group(scored_prepost, poverty150, conflict_child)
test$plot
```

```{r canary-41, results = 'asis'}
test$ttest
```

# Cohesiveness

When you and your child have spent time together, how often did you do the following? 

- I let my child know I really care about them 
- I was loving and affectionate toward my child 
- I was supportive and understanding toward my child 
- I told my child I love them 

## Pre-post{.tabset}


### Overall

```{r canary-42}
test = pre_post_overall(scored, cohesive)
test$plot
```

```{r canary-43, results = 'asis'}
test$pairwise
```

### POC

```{r canary-44}
test = pre_post_group(scored, pocA, cohesive)
test$plot
```

```{r canary-45, results = 'asis'}
test$pairwise
```


### Poverty line

```{r canary-46}
test = pre_post_group(scored, poverty150, cohesive)
test$plot
```

```{r canary-47, results = 'asis'}
test$pairwise
```

## Change{.tabset}


### Overall

```{r canary-48}
test = change_overall(scored_prepost, cohesive)
test$plot
```

```{r canary-49, results = 'asis'}
test$ttest
```
### POC

```{r canary-50}
test = change_group(scored_prepost, pocA, cohesive)
test$plot
```

```{r canary-51, results = 'asis'}
test$ttest
```


### Poverty line

```{r canary-52}
test = change_group(scored_prepost, poverty150, cohesive)
test$plot
```

```{r canary-53, results = 'asis'}
test$ttest
```

# Source of conflict

## Separated{.tabset}

Think about the sources of conflict for your family. Which of the following would help decrease conflict the most right now? [Only select one]

### Overall

```{r}
scored %>%
  filter(!is.na(conflictSource)) %>%
  group_by(conflictSource) %>%
  summarize(Count = n()) %>%
  ungroup() %>%
  mutate(Percent = 100*Count/sum(Count),
         N = sum(Count)) %>%
  mutate(MOE = pmap_dbl(.l = list(Percent, N), .f = percent_moe)) %>%
  ggplot(aes(x = reorder(conflictSource, Percent), y = Percent)) +
  geom_bar(stat = "identity", alpha = .8) +
  geom_errorbar(aes(ymin = Percent - MOE, ymax = Percent + MOE), width = .5) +
  geom_text(aes(label = paste0(round(Percent),
                              "\n(", round(MOE,1), ")")), 
            color = "white", y = 1) +
  labs(x = "",
       y = "Percent",
       title = "Overall sample") +
  coord_flip() +
  theme_pubclean() +
  theme(plot.title.position = "plot")
```

### POC

```{r, out.width="100%"}
scored %>%
  filter(!is.na(conflictSource) & !is.na(pocA)) %>%
  group_by(conflictSource, pocA) %>%
  summarize(Count = n()) %>%
  ungroup() %>%
  group_by(pocA)%>%
  mutate(Percent = 100*Count/sum(Count),
         N = sum(Count)) %>%
  mutate(MOE = pmap_dbl(.l = list(Percent, N), .f = percent_moe)) %>%
  ggplot(aes(x = reorder(conflictSource, Percent), y = Percent)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = Count, y = Percent + 5), color = "black", size = 3) +
  geom_text(aes(label = paste0(round(Percent),
                              "\n(", round(MOE,1), ")")), 
            color = "white", y = 1.5, size = 3) +
  labs(x = "",
       y = "Percent",
       title = "By Ethnicity") +
  coord_flip() +
  facet_wrap(~pocA) +
  theme_pubclean() +
  theme(plot.title.position = "plot")
```


### Poverty line

```{r, out.width="100%"}
scored %>%
  filter(!is.na(conflictSource) & !is.na(poverty150)) %>%
  group_by(conflictSource, poverty150) %>%
  summarize(Count = n()) %>%
  ungroup() %>%
  group_by(poverty150)%>%
  mutate(Percent = 100*Count/sum(Count),
         N = sum(Count)) %>%
  mutate(MOE = pmap_dbl(.l = list(Percent, N), .f = percent_moe)) %>%
  ggplot(aes(x = reorder(conflictSource, Percent), y = Percent)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = Count, y = Percent + 5), color = "black", size = 3) +
  geom_text(aes(label = paste0(round(Percent),
                              "\n(", round(MOE,1), ")")), 
            color = "white", y = 1.5, size = 3) +
  labs(x = "",
       y = "Percent",
       title = "By Income") +
  coord_flip() +
  facet_wrap(~poverty150) +
  theme_pubclean() +
  theme(plot.title.position = "plot")
```

## Aggregated{.tabset}

Financial
- Being confident that my family has health insurance
- Knowing we can pay for food
- Knowing we can pay my rent/mortgage/housing expenses
- Knowing my/our job is secure
Socio/Emotional
- Not being so socially isolated
- Having lower levels of worry and stress
- Being able to meet my child's social and emotional needs

```{r}
scored = scored %>%
  mutate(conflictSource_agg = case_when(
    conflictSource %in% c("Being confident that my family has health insurance", 
                          "Knowing we can pay for food", 
                          "Knowing we can pay my rent/mortgage/housing expenses", 
                          "Knowing my/our job is secure") ~ "Financial",
    conflictSource %in% c("Not being so socially isolated", 
                          "Having lower levels of worry and stress", 
                          "Being able to meet my child's social and emotional needs") ~ "Socio/Emotional",
  ))
```


### Overall

```{r}
scored %>%
  filter(!is.na(conflictSource_agg)) %>%
  group_by(conflictSource_agg) %>%
  summarize(Count = n()) %>%
  ungroup() %>%
  mutate(Percent = 100*Count/sum(Count),
         N = sum(Count)) %>%
  mutate(MOE = pmap_dbl(.l = list(Percent, N), .f = percent_moe)) %>%
  ggplot(aes(x = reorder(conflictSource_agg, Percent), y = Percent)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(round(Percent),
                              "\n(", round(MOE,1), ")")), 
            color = "white", y = 10) +
  labs(x = "",
       y = "Percent",
       title = "Overall sample") +
  coord_flip() +
  theme_pubclean() +
  theme(plot.title.position = "plot")
```

### POC

```{r, out.width="100%"}
scored %>%
  filter(!is.na(conflictSource_agg) & !is.na(pocA)) %>%
  group_by(conflictSource_agg, pocA) %>%
  summarize(Count = n()) %>%
  ungroup() %>%
  group_by(pocA)%>%
  mutate(Percent = 100*Count/sum(Count),
         N = sum(Count)) %>%
  mutate(MOE = pmap_dbl(.l = list(Percent, N), .f = percent_moe)) %>%
  ggplot(aes(x = reorder(conflictSource_agg, Percent), y = Percent)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = Count, y = Percent + 10), color = "black", size = 3) +
  geom_text(aes(label = paste0(round(Percent),
                              "\n(", round(MOE,1), ")")), 
            color = "white", y = 5, size = 3) +
  labs(x = "",
       y = "Percent",
       title = "Overall sample") +
  coord_flip() +
  facet_wrap(~pocA) +
  theme_pubclean() +
  theme(plot.title.position = "plot")
```


### Poverty line

```{r, out.width="100%"}
scored %>%
  filter(!is.na(conflictSource_agg) & !is.na(poverty150)) %>%
  group_by(conflictSource_agg, poverty150) %>%
  summarize(Count = n()) %>%
  ungroup() %>%
  group_by(poverty150)%>%
  mutate(Percent = 100*Count/sum(Count),
         N = sum(Count)) %>%
  mutate(MOE = pmap_dbl(.l = list(Percent, N), .f = percent_moe)) %>%
  ggplot(aes(x = reorder(conflictSource_agg, Percent), y = Percent)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = Count, y = Percent + 10), color = "black", size = 3) +
  geom_text(aes(label = paste0(round(Percent),
                              "\n(", round(MOE,1), ")")), 
            color = "white", y = 5, size = 3) +
  labs(x = "",
       y = "Percent",
       title = "Overall sample") +
  coord_flip() +
  facet_wrap(~poverty150) +
  theme_pubclean() +
  theme(plot.title.position = "plot")
```
