---
title: "Childcare follow-up"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include = FALSE}
library(here)
library(knitr)
library(readr)
library(haven)
library(tidyverse)
library(lavaan)
```


```{r, echo=FALSE, message = FALSE}
#Define functions
moe.p = function(p, n){
  q = 1-p
  moe = 1.96*sqrt((p*q)/n)
  return(moe)
}

moe.m = function(sd,n){
  moe = 1.96*sd/sqrt(n)
  return(moe)}

combine.cat = function(x, cols, id, newvar.name){
  subset = x[,c(id, "Week", cols)]
  names(subset) = c("id", "Week", paste0("X",1:length(cols)))
  subset = suppressWarnings(gather(subset, "key", "value", -id, -Week))
  subset = filter(subset, !is.na(value))
  subset$key = gsub("X", "", subset$key)
  subset = group_by(subset, id, Week)
  subset = summarise(subset, newvar = paste(key, collapse = ",")) %>% ungroup()
  names(subset) = c(id,"Week", newvar.name)
  x = suppressMessages(full_join(x, subset))
  return(x)
}

find_items = function(string, data2){
  items = names(data2)
  locations = which(grepl(string, items))
  final = items[locations]
  return(final)
}

my.max = function(x) ifelse (!all(is.na(x)), max(x,na.rm = TRUE), NA)
my.min = function(x) ifelse (!all(is.na(x)), min(x,na.rm = TRUE), NA)
```

```{r, echo=FALSE, message = FALSE, warning = FALSE, include=FALSE}
master_2020 <- read_sav(here("../../Data Management R3/CC_Clean Survey Data/00_R3 MasterFile/MasterFile_groupings_2020.sav"))
master_2021 <- read_sav(here("../../Data Management R3/CC_Clean Survey Data/00_R3 MasterFile/MasterFile_groupings_2021.sav"))

master <- full_join (master_2020, master_2021)

# Remove cases should be excluded
master <- master %>%
  filter ( CaregiverID != "" & is.na(Exclude) == T)

master = master %>%
  group_by(CaregiverID, Week) %>%
  filter(row_number() == max(row_number())) %>%
  ungroup()

total_week <- my.max(master$Week)

```

```{r, echo=FALSE, message = FALSE, warning = FALSE}
#Code demographics
master <- master %>%
  mutate (month = case_when(
                  Week == 0 ~ "Pre-COVID",
                  Week >0 & Week <= 4 ~ "April",
                  Week >=5 & Week <=8 ~ "May",
                  Week >=9 & Week <=13 ~ "June",
                  Week >=14 & Week <=17 ~ "July",
                  Week >=18 & Week <=21 ~ "August",
                  Week >=22 & Week <=26 ~ "September",
                  Week >=27 ~ "October"), 
           baseline = case_when (Week - BaselineWeek == 1 ~ 1, 
                                 Week - BaselineWeek > 1 ~ 0))

##Race/ethnicity - 1 = black, 2 = latinx, 3 = white

master <- master %>%
  mutate (RaceGroup = na_if (RaceGroup, 99))%>%
    mutate(
      minority = ifelse(RaceGroup != 5, 1, 0),
      black = ifelse(RaceGroup == 3, 1, 0),
      native = ifelse(RaceGroup == 1, 1, 0),
      asian = ifelse(RaceGroup == 2, 1, 0),
      hawaii = ifelse(RaceGroup == 4, 1, 0),
      white = ifelse(RaceGroup == 5, 1, 0),
      other_race = ifelse(RaceGroup %in% c(6, 7), 1, 0))

master <- master %>%
      mutate(latinx = case_when(
        DEMO.008 == 1 ~ 1,
        DEMO.008 == 0 ~ 0,
        DEMO.008.2 == 0 ~ 0,
        DEMO.008.2 == 1 ~ 1,
        DEMO.008.2 == 2 ~ 1,
        DEMO.008.3_1 == 1 ~ 0,
        DEMO.008.3_2 == 1 ~ 1,
        DEMO.008.3_3 == 1 ~ 1,
        DEMO.008.3_4 == 1 ~ 1,
        DEMO.008.3_5 == 1 ~ 1,
        DEMO.008.3_6 == 1 ~ 1,
        DEMO.008.3_7 == 1 ~ 1,
        TRUE ~ NA_real_))

master <- master %>%
mutate (race_ethnic = case_when(
      black == 1 ~ "1",
      latinx == 1 ~ "2",
      !is.na(black) ~ "3",
      !is.na(latinx) ~ "3",
      TRUE ~ NA_character_))  

##Povertyline - 0 = high income, 1 = low income
master <- master %>%
  mutate (poverty_cat = FPL.2019.UM.150)

#Material hardship
master <- master %>%
  combine.cat(cols = find_items("FSTR.002_.{1}$", master), 
              id = "CaregiverID",
              newvar.name = "FSTR.002_cat")
  

master <- master %>%
  mutate (diff_pay_food = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("1", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_), 
          diff_pay_utilities = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("3", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_house = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("2", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_healthcare = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("4", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_social = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("5", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_emotional = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("6", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_childcare = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("7", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_other = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("8", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_))

master <- master %>%
  rowwise() %>%
  mutate(material_hardship = case_when(
    Week == 0 ~ NA_real_,
    TRUE ~ sum(c_across(starts_with("diff_pay_")), na.rm=T))) %>%
  ungroup() %>%
  mutate(num_hardship = material_hardship,
    material_hardship = ifelse(material_hardship > 0, 1, 0)) 

## Children with special needs
master <- combine.cat(x = master, 
                       cols = find_items("HEALTH.005_[0-9]{1}$", master), 
                       id = "CaregiverID",
                       newvar.name = "HEALTH.005_cat")
master <- master %>%
   mutate (disability = case_when (HEALTH.005_1 == 1 ~ 1,
                                   HEALTH.005_2 == 1 ~ 1,
                                   HEALTH.005_3 == 1 ~ 1,
                                   HEALTH.005_4 == 1 ~ 1,
                                   HEALTH.005_5 == 1 ~ 0,
                                   HEALTH.005_6 == 1 ~ 1,
                                   TRUE ~ NA_real_))


## Single parent status
master <- master %>%
  mutate (single = case_when (
                   DEMO.002 %in% c(3,4,5,7,8)~1, 
                   DEMO.011 %in% c(2,4)~1,
                   !is.na(DEMO.002)~0,
                   !is.na(DEMO.011)~0,
                   TRUE ~ NA_real_))
                     
## Employment status
master <- combine.cat (x = master,
                       cols = find_items ("JOB.010_.{1,2}$", master), 
                       id = "CaregiverID",
                       newvar.name = "JOB.010_cat")
  
master$JOB.010_cat = gsub("10", "0", master$JOB.010_cat)
master$working_pre = ifelse (grepl("[1,2,6]", master$JOB.010_cat), 1, 0)
master = combine.cat (x = master,
                       cols = find_items ("JOB.008_.{1,2}$", master), 
                       id = "CaregiverID",
                       newvar.name = "JOB.008_cat")
master$JOB.008_cat = gsub("10", "0", master$JOB.008_cat)
master <- master %>%
  mutate (work_status = case_when(
                        grepl ("1", JOB.008_cat) ~ "1", 
                        grepl ("2", JOB.008_cat) ~ "1", 
                        grepl ("3", JOB.008_cat) ~ "0", 
                        grepl ("4", JOB.008_cat) ~ "0", 
                        grepl ("5", JOB.008_cat) ~ "1", 
                        JOB.008.2 == 1 ~ "1",
                        JOB.008.2 %in% c(2,3) ~ "0",
                        TRUE~NA_character_),
          work_status_pre = case_when(
                        grepl ("1", JOB.010_cat) ~ "1", 
                        grepl ("2", JOB.010_cat) ~ "1", 
                        grepl ("3", JOB.010_cat) ~ "0", 
                        grepl ("4", JOB.010_cat) ~ "0", 
                        grepl ("5", JOB.010_cat) ~ "1", 
                        TRUE~NA_character_))
#1 = stable employed 2 = became unemployed 3 = became employed4 = stable unemployed

# Region
master <- master %>%
  mutate (region = na_if (DEMO.001.b, 5))

master_dem <- master %>%
  group_by (CaregiverID) %>%
  summarise (BaselineWeek = my.max (BaselineWeek),
             race_ethnic = my.max(race_ethnic),
             poverty_cat = my.max(poverty_cat),
             disability = my.max (disability),
             single = my.max (single),
             work_status = my.max (work_status),
             work_status_pre = my.max (work_status_pre), 
             region = my.max(region), 
             gender = my.min(DEMO.006))%>%
  mutate ( ep_change = case_when(
                        work_status == 1 & work_status_pre == 1 ~ "1", 
                        work_status == 1 & work_status_pre == 0 ~ "2", 
                        work_status == 0 & work_status_pre == 1 ~ "3", 
                        work_status == 0 & work_status_pre == 0 ~ "4", 
                        TRUE~NA_character_))%>%
  mutate (race_ethnic = case_when (
                        race_ethnic == 1 ~ "Black", 
                        race_ethnic == 2 ~ "Latinx", 
                        race_ethnic == 3 ~ "White", 
                        TRUE~NA_character_),
          poverty_cat = case_when (
                        poverty_cat == 1 ~ "Below 150%FPL", 
                        poverty_cat == 0 ~ "Above 150%FPL", 
                        TRUE~NA_character_),
          disability = case_when (
                        disability == 1 ~ "With disability", 
                        disability == 0 ~ "Without disability", 
                        TRUE~NA_character_),
          single = case_when (
                        single == 1 ~ "Single parent", 
                        single == 0 ~ "Dual parent", 
                        TRUE~NA_character_),
          work_status = case_when (
                        work_status == 1 ~ "Employed", 
                        work_status == 0 ~ "Unemployed", 
                        TRUE~NA_character_),
          work_status_pre = case_when (
                        work_status_pre == 1 ~ "Employed", 
                        work_status_pre == 0 ~ "Unemployed", 
                        TRUE~NA_character_),
          ep_change = case_when (
                        ep_change == 1 ~ "Stable employed", 
                        ep_change == 2 ~ "Became employed", 
                        ep_change == 3 ~ "Became unemployed",
                        ep_change == 4 ~ "Stable unemployed",
                        TRUE~NA_character_), 
          region = case_when (
                        region == 1 ~ "Northeast", 
                        region == 2 ~ "Midwest", 
                        region == 3 ~ "South", 
                        region == 4 ~ "West",
                        TRUE~NA_character_))
```

```{r, echo=FALSE, message = FALSE, warning = FALSE}
CaregiverID_fl <- master%>%
  mutate (follow_up = ifelse(SurveyType == 2, 1, 0))%>%
  group_by (CaregiverID)%>%
  summarise (follow_up = my.max (follow_up))%>%
  ungroup()%>%
  filter (follow_up == 1)%>%
  select (CaregiverID)

CaregiverID_fl <- as.character (CaregiverID_fl$CaregiverID)
  
master_fl <- master %>%
  filter (CaregiverID %in% CaregiverID_fl)

master_dem_fl <- master_dem %>%
  filter (CaregiverID %in% CaregiverID_fl)

```


```{r, echo=FALSE, message = FALSE, warning = FALSE}
# Extract Relevant Variables

cc <- master %>%
  select (CaregiverID, StartDate, Week, baseline, POLICY.009.a, POLICY.009.a.2, POLICY.009.b, contains ("POLICY.015"), contains ("POLICY.016"))
  
cc_nd <- cc%>%
  mutate (POLICY.009.a = na_if (POLICY.009.a, 3), 
          POLICY.009.a.2 = na_if (POLICY.009.a.2, 3), 
          POLICY.009.b = na_if (POLICY.009.b, 3),
          non_parent_pre = case_when (POLICY.009.a == 1 | POLICY.009.a.2 == 1 ~ 1,
                                      POLICY.009.a == 2 | POLICY.009.a.2 == 2 ~ 0),
          non_parent_crt = case_when (POLICY.009.b == 1 ~ 1,
                                      POLICY.009.b == 2 ~ 0),
          center_based_pre = ifelse (POLICY.015_1 == 1 | POLICY.015.2_1 == 1, 1, 0),
          unpaid_pre = ifelse (POLICY.015_2 == 1 | POLICY.015.2_2 == 1, 1, 0),
          paid_pre = ifelse (POLICY.015_3 == 1 | POLICY.015.2_3 == 1, 1, 0),
          home_based_pre = ifelse (POLICY.015_4 == 1 | POLICY.015.2_4 == 1, 1, 0),
          rel_other_parent_pre = ifelse (POLICY.015.a_1 == 1 | POLICY.015.a.2_1 == 1, 1, 0),
          rel_sibling_pre = ifelse (POLICY.015.a_2 == 1 | POLICY.015.a.2_2 == 1, 1, 0),
          rel_grandparent_pre = ifelse (POLICY.015.a_3 == 1 | POLICY.015.a.2_3 == 1, 1, 0),
          rel_other_relative_pre = ifelse (POLICY.015.a_4 == 1 | POLICY.015.a.2_4 == 1, 1, 0),
          rel_friend_pre = ifelse (POLICY.015.a_5 == 1 | POLICY.015.a.2_5 == 1, 1, 0),
          rel_neighbor_pre = ifelse (POLICY.015.a_6 == 1 | POLICY.015.a.2_6 == 1, 1, 0),
          center_based_crt = POLICY.016_1, 
          unpaid_crt = POLICY.016_2,
          paid_crt = POLICY.016_3,
          home_based_crt = POLICY.016_4,
          rel_other_parent_crt = POLICY.016.a_1,
          rel_sibling_crt = POLICY.016.a_2,
          rel_grandparent_crt = POLICY.016.a_3,
          rel_other_relative_crt = POLICY.016.a_4,
          rel_friend_crt = POLICY.016.a_5,
          rel_neighbor_crt = POLICY.016.a_6
         )

num_responses = function(x){length(which(!is.na(x)))}
cc.num <- cc_nd %>%
  group_by(Week) %>%
  summarize_all(num_responses) %>%
  gather("Variable", "num_responses",-Week) %>%
  mutate(week = paste0("Week", Week),
         week = factor(Week, levels = paste0("Week", c(1:total_week)))) %>%
  spread(Week, num_responses)
  
  
cc_nd <- merge (x = master_dem, y = cc_nd,  by.x = "CaregiverID", by.y = "CaregiverID", all.y = T)
cc_nd_rct <- cc_nd %>%
  group_by (CaregiverID)%>%
  filter (Week == max (Week))%>%
  ungroup()

```

# 0. Sample Disclaimer
  * This set of analyses on material hardship is based on responses collected from 5,336 caregivers between the dates of April 6th 2020 and March 20th 2021. These caregivers represent a range of voices: 6.60% are non-Latinx Black/African American, 14.75% are Latinx, and 27.96% live at or below 1.5 times the federal poverty line.  Proportions/percentages are calculated based on the item-level response rates, not out of the total sample size. The data for these analyses are not weighted. \

# 1. Overall Nonparental Childcare 
```{r, echo=FALSE, message = FALSE, warning = FALSE}
cc_pre <- cc_nd %>%
  group_by (CaregiverID)%>%
  summarise (non_parent_pre = my.max (non_parent_pre))%>%
  ungroup()%>%
  summarise (n = n(),
             prop = sum (non_parent_pre, na.rm = T)/n)%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          date = as.Date("2020-01-01"), 
          Week = 0)

cc_crt <- cc_nd %>%
  filter (Week %in% c(4,5,6,9,10,11,12,14,15,16,17,19,21,23,25,29,30,31,32,34,36,40,42,46,48))%>%
  group_by (Week)%>%
  summarise (n = n(),
             prop = sum (non_parent_crt, na.rm = T)/n, 
             date = as.Date(min (StartDate)))%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe)

cc_smy <- rbind (cc_pre, cc_crt)

cc_smy %>%
  ggplot(mapping = aes (x = date, y = prop*100)) +   
  geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  theme(legend.position = "none")+                                # Remove legend or change legend position
  theme(axis.text.x = element_text(angle = 45))+
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  geom_text(aes(label = round(prop*100,2)),vjust = -0.5, size = 2.5, color = "black",  position = position_dodge(1))

```

## 1.1 By race/ethnicity

```{r, echo=FALSE, message = FALSE, warning = FALSE}
cc_pre <- cc_nd %>%
  group_by (CaregiverID)%>%
  summarise (non_parent_pre = my.max (non_parent_pre),
             race_ethnic= my.max(race_ethnic) )%>%
  ungroup()%>%
  filter (race_ethnic!= "NA")%>%
  group_by (race_ethnic)%>%
  summarise (n = n(),
             prop = sum (non_parent_pre, na.rm = T)/n)%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          date = as.Date("2020-01-01"), 
          Week = 0)

cc_crt <- cc_nd %>%
  filter (Week %in% c(4,5,6,9,10,11,12,14,15,16,17,19,21,23,25,29,30,31,32,34,36,40,42,46, 48))%>%
  filter (race_ethnic!= "NA")%>%
  group_by (Week, race_ethnic)%>%
  summarise (n = n(),
             prop = sum (non_parent_crt, na.rm = T)/n, 
             date = as.Date(min (StartDate)))%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe)

cc_smy <- rbind (cc_pre, cc_crt)

cc_smy %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = race_ethnic)) +   
  geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  theme(legend.position = "none")+                                # Remove legend or change legend position
  theme(axis.text.x = element_text(angle = 45))+
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  facet_wrap (~race_ethnic)
  
  

```

## 1.2 By poverty level
```{r, echo=FALSE, message = FALSE, warning = FALSE}
cc_pre <- cc_nd %>%
  group_by (CaregiverID)%>%
  summarise (non_parent_pre = my.max (non_parent_pre),
             poverty_cat= my.max(poverty_cat) )%>%
  ungroup()%>%
  filter (poverty_cat!= "NA")%>%
  group_by (poverty_cat)%>%
  summarise (n = n(),
             prop = sum (non_parent_pre, na.rm = T)/n)%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          date = as.Date("2020-01-01"), 
          Week = 0)

cc_crt <- cc_nd %>%
  filter (Week %in% c(4,5,6,9,10,11,12,14,15,16,17,19,21,23,25,29,30,31,32,34,36,40,42,46,48))%>%
  filter (poverty_cat!= "NA")%>%
  group_by (Week, poverty_cat)%>%
  summarise (n = n(),
             prop = sum (non_parent_crt, na.rm = T)/n, 
             date = as.Date(min (StartDate)))%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe)

cc_smy <- rbind (cc_pre, cc_crt)

cc_smy %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = poverty_cat)) +   
  geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  theme(legend.position = "none")+                                # Remove legend or change legend position
  theme(axis.text.x = element_text(angle = 45))+
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  facet_wrap (~poverty_cat)
  

```

# 2. Different Types of Nonparental Childcare
```{r, echo=FALSE, message = FALSE, warning = FALSE}
cc_pre <- cc_nd %>%
  group_by (CaregiverID)%>%
  summarise (center_based_pre = my.max (center_based_pre), 
             paid_pre = my.max (paid_pre), 
             unpaid_pre = my.max (unpaid_pre), 
             home_based_pre = my.max (home_based_pre), 
             )%>%
  ungroup()%>%
  summarise (n = n(),
             center_based = sum (center_based_pre, na.rm = T)/n, 
             paid = sum (paid_pre, na.rm = T)/n,
             unpaid = sum (unpaid_pre, na.rm = T)/n,
             home_based = sum (home_based_pre, na.rm = T)/n, 
             )%>%
  pivot_longer (cols = c("center_based", "paid", "unpaid", "home_based"), names_to = "type", values_to = "prop")%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          date = as.Date("2020-01-01"), 
          Week = 0)

cc_crt <- cc_nd %>%
  filter (Week %in% c(5,6,9,10,11,12,14,15,16,17,19,21,23,25,30,32,34,36,40,42,46, 48))%>%
  group_by (Week)%>%
   summarise (n = n(),
             center_based = sum (center_based_crt, na.rm = T)/n, 
             paid = sum (paid_crt, na.rm = T)/n,
             unpaid = sum (unpaid_crt, na.rm = T)/n,
             home_based = sum (home_based_crt, na.rm = T)/n, 
             date = as.Date(min (StartDate)))%>%
  pivot_longer (cols = c("center_based", "paid", "unpaid", "home_based"), names_to = "type", values_to = "prop")%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe)

cc_smy <- rbind (cc_pre, cc_crt)

cc_smy %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = type)) +   
  geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 45))+
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  facet_wrap (~type, nrow = 2)+
  theme(legend.position = "none")+
  ggtitle(label = "Four types: center-based, home-based, paid, unpaid")

```

```{r, echo=FALSE, message = FALSE, warning = FALSE}
cc_pre <- cc_nd %>%
  mutate (non_center_pre = ifelse (paid_pre == 1|unpaid_pre==1|home_based_pre==1, 1, 0))%>%
  group_by (CaregiverID)%>%
  summarise (center_based_pre = my.max (center_based_pre), 
             non_center_pre = my.max (non_center_pre) 
             )%>%
  ungroup()%>%
  summarise (n = n(),
             center_based = sum (center_based_pre, na.rm = T)/n, 
             non_center = sum (non_center_pre, na.rm = T)/n
             )%>%
  pivot_longer (cols = c("center_based", "non_center"), names_to = "type", values_to = "prop")%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          date = as.Date("2020-01-01"), 
          Week = 0)

cc_crt <- cc_nd %>%
  mutate (non_center_crt = ifelse (paid_crt == 1|unpaid_crt==1|home_based_crt==1, 1, 0))%>%
  filter (Week %in% c(5,6,9,10,11,12,14,15,16,17,19,21,23,25,30,32,34,36,40,42,46, 48))%>%
  group_by (Week)%>%
   summarise (n = n(),
             center_based = sum (center_based_crt, na.rm = T)/n, 
             non_center = sum (non_center_crt, na.rm = T)/n,
             date = as.Date(min (StartDate)))%>%
  pivot_longer (cols = c("center_based", "non_center"), names_to = "type", values_to = "prop")%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe)

cc_smy <- rbind (cc_pre, cc_crt)

cc_smy %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = type)) +   
  geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 45))+
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  facet_wrap (~type, nrow = 1)+
  ggtitle(label = "Two types: center-based vs. non-center-based")

```


## 2.1 By race/ethnicity
```{r, echo=FALSE, message = FALSE, warning = FALSE}
cc_pre <- cc_nd %>%
  group_by (CaregiverID)%>%
  summarise (center_based_pre = my.max (center_based_pre), 
             paid_pre = my.max (paid_pre), 
             unpaid_pre = my.max (unpaid_pre), 
             home_based_pre = my.max (home_based_pre), 
             race_ethnic= my.max (race_ethnic)
             )%>%
  ungroup()%>%
  filter (race_ethnic != "NA")%>%
  group_by (race_ethnic)%>%
  summarise (n = n(),
             center_based = sum (center_based_pre, na.rm = T)/n, 
             paid = sum (paid_pre, na.rm = T)/n,
             unpaid = sum (unpaid_pre, na.rm = T)/n,
             home_based = sum (home_based_pre, na.rm = T)/n, 
             )%>%
  pivot_longer (cols = c("center_based", "paid", "unpaid", "home_based"), names_to = "type", values_to = "prop")%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          date = as.Date("2020-01-01"), 
          Week = 0)

cc_crt <- cc_nd %>%
  filter (Week %in% c(5,6,9,10,11,12,14,15,16,17,19,21,23,25,30,32,34,36,40,42,46, 48))%>%
  filter (race_ethnic != "NA")%>%
   group_by (Week, race_ethnic)%>%
   summarise (n = n(),
             center_based = sum (center_based_crt, na.rm = T)/n, 
             paid = sum (paid_crt, na.rm = T)/n,
             unpaid = sum (unpaid_crt, na.rm = T)/n,
             home_based = sum (home_based_crt, na.rm = T)/n, 
             date = as.Date(min (StartDate)))%>%
  pivot_longer (cols = c("center_based", "paid", "unpaid", "home_based"), names_to = "type", values_to = "prop")%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe)

cc_smy <- rbind (cc_pre, cc_crt)

cc_smy %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = race_ethnic)) +   
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 45))+
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  facet_wrap (~type, nrow = 2)+
  ggtitle(label = "Four types: center-based, home-based, paid, unpaid")

```

```{r, echo=FALSE, message = FALSE, warning = FALSE}
cc_pre <- cc_nd %>%
  mutate (non_center_pre = ifelse (paid_pre == 1|unpaid_pre==1|home_based_pre==1, 1, 0))%>%
  group_by (CaregiverID)%>%
  summarise (center_based_pre = my.max (center_based_pre), 
             non_center_pre = my.max (non_center_pre), 
             race_ethnic= my.max (race_ethnic)
             )%>%
  ungroup()%>%
  filter (race_ethnic != "NA")%>%
  group_by (race_ethnic)%>%
  summarise (n = n(),
             center_based = sum (center_based_pre, na.rm = T)/n, 
             non_center = sum (non_center_pre, na.rm = T)/n
             )%>%
  pivot_longer (cols = c("center_based", "non_center"), names_to = "type", values_to = "prop")%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          date = as.Date("2020-01-01"), 
          Week = 0)

cc_crt <- cc_nd %>%
  mutate (non_center_crt = ifelse (paid_crt == 1|unpaid_crt==1|home_based_crt==1, 1, 0))%>%
  filter (Week %in% c(5,6,9,10,11,12,14,15,16,17,19,21,23,25,30,32,34,36,40,42,46, 48))%>%
  filter (race_ethnic != "NA")%>%
  group_by (Week, race_ethnic)%>%
   summarise (n = n(),
             center_based = sum (center_based_crt, na.rm = T)/n, 
             non_center = sum (non_center_crt, na.rm = T)/n,
             date = as.Date(min (StartDate)), 
             race_ethnic= my.max (race_ethnic))%>%
  pivot_longer (cols = c("center_based", "non_center"), names_to = "type", values_to = "prop")%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe)

cc_smy <- rbind (cc_pre, cc_crt)

cc_smy %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = race_ethnic)) +   
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 45))+
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  facet_wrap (~type, nrow = 1)+
  ggtitle(label = "Two types: center-based vs. non-center-based")

```

## 2.2 By poverty level
```{r, echo=FALSE, message = FALSE, warning = FALSE}
cc_pre <- cc_nd %>%
  group_by (CaregiverID)%>%
  summarise (center_based_pre = my.max (center_based_pre), 
             paid_pre = my.max (paid_pre), 
             unpaid_pre = my.max (unpaid_pre), 
             home_based_pre = my.max (home_based_pre), 
             poverty_cat= my.max (poverty_cat)
             )%>%
  ungroup()%>%
  filter (poverty_cat != "NA")%>%
  group_by (poverty_cat)%>%
  summarise (n = n(),
             center_based = sum (center_based_pre, na.rm = T)/n, 
             paid = sum (paid_pre, na.rm = T)/n,
             unpaid = sum (unpaid_pre, na.rm = T)/n,
             home_based = sum (home_based_pre, na.rm = T)/n, 
             )%>%
  pivot_longer (cols = c("center_based", "paid", "unpaid", "home_based"), names_to = "type", values_to = "prop")%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          date = as.Date("2020-01-01"), 
          Week = 0)

cc_crt <- cc_nd %>%
  filter (Week %in% c(5,6,9,10,11,12,14,15,16,17,19,21,23,25,30,32,34,36,40,42,46, 48))%>%
  filter (poverty_cat != "NA")%>%
   group_by (Week, poverty_cat)%>%
   summarise (n = n(),
             center_based = sum (center_based_crt, na.rm = T)/n, 
             paid = sum (paid_crt, na.rm = T)/n,
             unpaid = sum (unpaid_crt, na.rm = T)/n,
             home_based = sum (home_based_crt, na.rm = T)/n, 
             date = as.Date(min (StartDate)))%>%
  pivot_longer (cols = c("center_based", "paid", "unpaid", "home_based"), names_to = "type", values_to = "prop")%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe)

cc_smy <- rbind (cc_pre, cc_crt)

cc_smy %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = poverty_cat)) +   
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 45))+
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  facet_wrap (~type, nrow = 2)+
  ggtitle(label = "Four types: center-based, home-based, paid, unpaid")
```

```{r, echo=FALSE, message = FALSE, warning = FALSE}
cc_pre <- cc_nd %>%
  mutate (non_center_pre = ifelse (paid_pre == 1|unpaid_pre==1|home_based_pre==1, 1, 0))%>%
  group_by (CaregiverID)%>%
  summarise (center_based_pre = my.max (center_based_pre), 
             non_center_pre = my.max (non_center_pre), 
             poverty_cat= my.max (poverty_cat)
             )%>%
  ungroup()%>%
  filter (poverty_cat != "NA")%>%
  group_by (poverty_cat)%>%
  summarise (n = n(),
             center_based = sum (center_based_pre, na.rm = T)/n, 
             non_center = sum (non_center_pre, na.rm = T)/n
             )%>%
  pivot_longer (cols = c("center_based", "non_center"), names_to = "type", values_to = "prop")%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          date = as.Date("2020-01-01"), 
          Week = 0)

cc_crt <- cc_nd %>%
  mutate (non_center_crt = ifelse (paid_crt == 1|unpaid_crt==1|home_based_crt==1, 1, 0))%>%
  filter (Week %in% c(5,6,9,10,11,12,14,15,16,17,19,21,23,25,30,32,34,36,40,42,46, 48))%>%
  filter (poverty_cat != "NA")%>%
  group_by (Week, poverty_cat)%>%
   summarise (n = n(),
             center_based = sum (center_based_crt, na.rm = T)/n, 
             non_center = sum (non_center_crt, na.rm = T)/n,
             date = as.Date(min (StartDate)), 
             poverty_cat= my.max (poverty_cat))%>%
  pivot_longer (cols = c("center_based", "non_center"), names_to = "type", values_to = "prop")%>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe)

cc_smy <- rbind (cc_pre, cc_crt)

cc_smy %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = poverty_cat)) +   
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 45))+
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  facet_wrap (~type, nrow = 1)+
  ggtitle(label = "Two types: center-based vs. non-center-based")

```