---
title: "Child & Parent Mental Health Trend"
author: "Sihong"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include = FALSE}
library(here)
library(knitr)
library(readr)
library(haven)
library(tidyverse)
library(lavaan)
```

```{r, echo=FALSE, message = FALSE}
#Define functions
moe.p = function(p, n){
  q = 1-p
  moe = 1.96*sqrt((p*q)/n)
  return(moe)
}

moe.m = function(sd,n){
  moe = 1.96*sd/sqrt(n)
  return(moe)}

combine.cat = function(x, cols, id, newvar.name){
  subset = x[,c(id, "Week", cols)]
  names(subset) = c("id", "Week", paste0("X",1:length(cols)))
  subset = suppressWarnings(gather(subset, "key", "value", -id, -Week))
  subset = filter(subset, !is.na(value))
  subset$key = gsub("X", "", subset$key)
  subset = group_by(subset, id, Week)
  subset = summarise(subset, newvar = paste(key, collapse = ",")) %>% ungroup()
  names(subset) = c(id,"Week", newvar.name)
  x = suppressMessages(full_join(x, subset))
  return(x)
}

find_items = function(string, data2){
  items = names(data2)
  locations = which(grepl(string, items))
  final = items[locations]
  return(final)
}

my.max = function(x) ifelse (!all(is.na(x)), max(x,na.rm = TRUE), NA)
my.min = function(x) ifelse (!all(is.na(x)), min(x,na.rm = TRUE), NA)
```

```{r, echo=FALSE, message = FALSE, warning = FALSE, include=FALSE}
master_2020 <- read_sav(here("../../Data Management R3/CC_Clean Survey Data/00_R3 MasterFile/MasterFile_groupings_2020.sav"))
master_2021 <- read_sav(here("../../Data Management R3/CC_Clean Survey Data/00_R3 MasterFile/MasterFile_groupings_2021.sav"))

master <- full_join (master_2020, master_2021)

# Remove cases should be excluded
master <- master %>%
  filter ( CaregiverID != "" & is.na(Exclude) == T)

master = master %>%
  group_by(CaregiverID, Week) %>%
  filter(row_number() == max(row_number())) %>%
  ungroup()

total_week <- my.max(master$Week)

```

```{r, echo=FALSE, message = FALSE, warning = FALSE}
#Code demographics
master <- master %>%
  mutate (month = case_when(
                  Week == 0 ~ "Pre-COVID",
                  Week >0 & Week <= 4 ~ "April",
                  Week >=5 & Week <=8 ~ "May",
                  Week >=9 & Week <=13 ~ "June",
                  Week >=14 & Week <=17 ~ "July",
                  Week >=18 & Week <=21 ~ "August",
                  Week >=22 & Week <=26 ~ "September",
                  Week >=27 ~ "October"), 
           baseline = case_when (Week - BaselineWeek == 1 ~ 1, 
                                 Week - BaselineWeek > 1 ~ 0))

##Race/ethnicity - 1 = black, 2 = latinx, 3 = white

master <- master %>%
  mutate (RaceGroup = na_if (RaceGroup, 99))%>%
    mutate(
      minority = ifelse(RaceGroup != 5, 1, 0),
      black = ifelse(RaceGroup == 3, 1, 0),
      native = ifelse(RaceGroup == 1, 1, 0),
      asian = ifelse(RaceGroup == 2, 1, 0),
      hawaii = ifelse(RaceGroup == 4, 1, 0),
      white = ifelse(RaceGroup == 5, 1, 0),
      other_race = ifelse(RaceGroup %in% c(6, 7), 1, 0))

master <- master %>%
      mutate(latinx = case_when(
        DEMO.008 == 1 ~ 1,
        DEMO.008 == 0 ~ 0,
        DEMO.008.2 == 0 ~ 0,
        DEMO.008.2 == 1 ~ 1,
        DEMO.008.2 == 2 ~ 1,
        TRUE ~ NA_real_))

master <- master %>%
mutate (race_ethnic = case_when(
      black == 1 ~ "1",
      latinx == 1 ~ "2",
      !is.na(black) ~ "3",
      !is.na(latinx) ~ "3",
      TRUE ~ NA_character_))  

##Povertyline - 0 = high income, 1 = low income
master <- master %>%
  mutate (poverty_cat = FPL.2019.UM.150)

#Material hardship
master <- master %>%
  combine.cat(cols = find_items("FSTR.002_.{1}$", master), 
              id = "CaregiverID",
              newvar.name = "FSTR.002_cat")
  

master <- master %>%
  mutate (diff_pay_food = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("1", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_), 
          diff_pay_utilities = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("3", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_house = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("2", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_healthcare = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("4", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_social = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("5", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_emotional = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("6", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_childcare = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("7", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_other = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("8", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_))

master <- master %>%
  rowwise() %>%
  mutate(material_hardship = case_when(
    Week == 0 ~ NA_real_,
    TRUE ~ sum(c_across(starts_with("diff_pay_")), na.rm=T))) %>%
  ungroup() %>%
  mutate(num_hardship = material_hardship,
    material_hardship = ifelse(material_hardship > 0, 1, 0)) 

## Children with special needs
master <- combine.cat(x = master, 
                       cols = find_items("HEALTH.005_[0-9]{1}$", master), 
                       id = "CaregiverID",
                       newvar.name = "HEALTH.005_cat")
master <- master %>%
   mutate (disability = case_when (HEALTH.005_1 == 1 ~ 1,
                                   HEALTH.005_2 == 1 ~ 1,
                                   HEALTH.005_3 == 1 ~ 1,
                                   HEALTH.005_4 == 1 ~ 1,
                                   HEALTH.005_5 == 1 ~ 0,
                                   HEALTH.005_6 == 1 ~ 1,
                                   TRUE ~ NA_real_))


## Single parent status
master <- master %>%
  mutate (single = case_when (
                   DEMO.002 %in% c(3,4,5,7,8)~1, 
                   DEMO.011 %in% c(2,4)~1,
                   !is.na(DEMO.002)~0,
                   !is.na(DEMO.011)~0,
                   TRUE ~ NA_real_))
                     
## Employment status
master <- combine.cat (x = master,
                       cols = find_items ("JOB.010_.{1,2}$", master), 
                       id = "CaregiverID",
                       newvar.name = "JOB.010_cat")
  
master$JOB.010_cat = gsub("10", "0", master$JOB.010_cat)
master$working_pre = ifelse (grepl("[1,2,6]", master$JOB.010_cat), 1, 0)
master = combine.cat (x = master,
                       cols = find_items ("JOB.008_.{1,2}$", master), 
                       id = "CaregiverID",
                       newvar.name = "JOB.008_cat")
master$JOB.008_cat = gsub("10", "0", master$JOB.008_cat)
master <- master %>%
  mutate (work_status = case_when(
                        grepl ("1", JOB.008_cat) ~ "1", 
                        grepl ("2", JOB.008_cat) ~ "1", 
                        grepl ("3", JOB.008_cat) ~ "0", 
                        grepl ("4", JOB.008_cat) ~ "0", 
                        grepl ("5", JOB.008_cat) ~ "1", 
                        JOB.008.2 == 1 ~ "1",
                        JOB.008.2 %in% c(2,3) ~ "0",
                        TRUE~NA_character_),
          work_status_pre = case_when(
                        grepl ("1", JOB.010_cat) ~ "1", 
                        grepl ("2", JOB.010_cat) ~ "1", 
                        grepl ("3", JOB.010_cat) ~ "0", 
                        grepl ("4", JOB.010_cat) ~ "0", 
                        grepl ("5", JOB.010_cat) ~ "1", 
                        TRUE~NA_character_))
#1 = stable employed 2 = became unemployed 3 = became employed4 = stable unemployed

# Region
master <- master %>%
  mutate (region = na_if (DEMO.001.b, 5))

master_dem <- master %>%
  group_by (CaregiverID) %>%
  summarise (BaselineWeek = my.max (BaselineWeek),
             race_ethnic = my.max(race_ethnic),
             poverty_cat = my.max(poverty_cat),
             disability = my.max (disability),
             single = my.max (single),
             work_status = my.max (work_status),
             work_status_pre = my.max (work_status_pre), 
             region = my.max(region), 
             gender = my.min(DEMO.006))%>%
  mutate ( ep_change = case_when(
                        work_status == 1 & work_status_pre == 1 ~ "1", 
                        work_status == 1 & work_status_pre == 0 ~ "2", 
                        work_status == 0 & work_status_pre == 1 ~ "3", 
                        work_status == 0 & work_status_pre == 0 ~ "4", 
                        TRUE~NA_character_))%>%
  mutate (race_ethnic = case_when (
                        race_ethnic == 1 ~ "Black", 
                        race_ethnic == 2 ~ "Latinx", 
                        race_ethnic == 3 ~ "White", 
                        TRUE~NA_character_),
          poverty_cat = case_when (
                        poverty_cat == 1 ~ "Below 150%FPL", 
                        poverty_cat == 0 ~ "Above 150%FPL", 
                        TRUE~NA_character_),
          disability = case_when (
                        disability == 1 ~ "With disability", 
                        disability == 0 ~ "Without disability", 
                        TRUE~NA_character_),
          single = case_when (
                        single == 1 ~ "Single parent", 
                        single == 0 ~ "Dual parent", 
                        TRUE~NA_character_),
          work_status = case_when (
                        work_status == 1 ~ "Employed", 
                        work_status == 0 ~ "Unemployed", 
                        TRUE~NA_character_),
          work_status_pre = case_when (
                        work_status_pre == 1 ~ "Employed", 
                        work_status_pre == 0 ~ "Unemployed", 
                        TRUE~NA_character_),
          ep_change = case_when (
                        ep_change == 1 ~ "Stable employed", 
                        ep_change == 2 ~ "Became employed", 
                        ep_change == 3 ~ "Became unemployed",
                        ep_change == 4 ~ "Stable unemployed",
                        TRUE~NA_character_), 
          region = case_when (
                        region == 1 ~ "Northeast", 
                        region == 2 ~ "Midwest", 
                        region == 3 ~ "South", 
                        region == 4 ~ "West",
                        TRUE~NA_character_))
```

```{r, echo=FALSE, message = FALSE, warning = FALSE}
CaregiverID_fl <- master%>%
  mutate (follow_up = ifelse(SurveyType == 2, 1, 0))%>%
  group_by (CaregiverID)%>%
  summarise (follow_up = my.max (follow_up))%>%
  ungroup()%>%
  filter (follow_up == 1)

CaregiverID_fl <- as.character (CaregiverID_fl$CaregiverID)
  
master_fl <- master %>%
  filter (CaregiverID %in% CaregiverID_fl)

master_dem_fl <- master_dem %>%
  filter (CaregiverID %in% CaregiverID_fl)

```

```{r, echo=FALSE, message = FALSE, warning = FALSE}
# Extract Relevant Variables
##RL questions - online learning
mh <- master_fl %>%
  dplyr::select (CaregiverID, StartDate, Week, SurveyType, Source,contains ("PHQ"), contains ("GAD"), STRESS.001, STRESS.002, LONE.001.a, LONE.001.b, contains("CBCL") )

mh$depress_crt= rowMeans(mh[,find_items("PHQ.002.[a-b]$", mh)], na.rm=T)
mh$anxiety_crt = rowMeans(mh[,find_items("GAD2.002.[a-b]$", mh)], na.rm=T)
mh$depress_pre= rowMeans(mh[,find_items("PHQ.001.[a-b]$", mh)], na.rm=T)
mh$anxiety_pre = rowMeans(mh[,find_items("GAD2.001.[a-b]$", mh)], na.rm=T)

mh <- mh %>%
  mutate (depress_crt_r = depress_crt/3*100,
          anxiety_crt_r =anxiety_crt/3*100,
          stress_crt_r = STRESS.002/4*100,
          lonely_crt_r = LONE.001.b/4*100, 
          depress_pre_r = depress_pre/3*100,
          anxiety_pre_r =anxiety_pre/3*100,
          stress_pre_r = STRESS.001/4*100,
          lonely_pre_r = LONE.001.a/4*100)%>%
  rename (fussy_cr1 = CBCL.002.a,
          fussy_cr2 = CBCL.005.a,
          fussy_cr3 = CBCL.008.a,
          fussy_cr4 = CBCL.011.a,
          fussy_cr5 = CBCL.014.a,
          fear_cr1 = CBCL.002.b,
          fear_cr2 = CBCL.005.b,
          fear_cr3 = CBCL.008.b,
          fear_cr4 = CBCL.011.b,
          fear_cr5 = CBCL.014.b, 
          fussy_pr1 = CBCL.001.a,
          fussy_pr2 = CBCL.004.a,
          fussy_pr3 = CBCL.007.a,
          fussy_pr4 = CBCL.010.a,
          fussy_pr5 = CBCL.013.a,
          fear_pr1 = CBCL.001.b,
          fear_pr2 = CBCL.004.b,
          fear_pr3 = CBCL.007.b,
          fear_pr4 = CBCL.010.b,
          fear_pr5 = CBCL.013.b)

fussy_pre_items = c(find_items("fussy_pr", mh))
fear_pre_items = c(find_items("fear_pr", mh))
fussy_crt_items = c(find_items("fussy_cr", mh))
fear_crt_items = c(find_items("fear_cr", mh))

mh$fussy_pre = rowMeans(mh[,fussy_pre_items], na.rm=T)/2*100
mh$fear_pre = rowMeans(mh[,fear_pre_items], na.rm=T)/2*100
mh$fussy_crt = rowMeans(mh[,fussy_crt_items], na.rm=T)/2*100
mh$fear_crt = rowMeans(mh[,fear_crt_items], na.rm=T)/2*100

cp_crt_items = c("fussy_crt", "fear_crt")
cp_pre_items = c("fussy_pre", "fear_pre")

mh$cp_total_crt = rowMeans (mh[, cp_crt_items], na.rm=T)
mh$cp_total_pre = rowMeans (mh[, cp_pre_items], na.rm=T)

pmh_crt_variable = c("depress_crt_r", "anxiety_crt_r", "stress_crt_r", "lonely_crt_r")
pmh_pre_variable = c("depress_pre_r", "anxiety_pre_r", "stress_pre_r", "lonely_pre_r")
mh$pmh_total_crt = rowMeans(mh[, pmh_crt_variable], na.rm = T)
mh$pmh_total_pre = rowMeans(mh[, pmh_pre_variable], na.rm = T)

mh_pre <- mh %>%
  group_by (CaregiverID)%>%
  summarise (pmh_total_pre = mean (pmh_total_pre, na.rm = T), 
             cp_total_pre = mean (cp_total_pre, na.rm = T),
             depress_pre = mean(depress_pre_r, na.rm = T), 
             anxiety_pre = mean(anxiety_pre_r, na.rm = T), 
             lonely_pre = mean(lonely_pre_r, na.rm = T), 
             stress_pre = mean(stress_pre_r, na.rm = T), 
             fussy_pre = mean(fussy_pre, na.rm = T), 
             fear_pre = mean(fear_pre, na.rm = T), 
             )%>%
  ungroup()

mh_pre = merge (x = mh_pre, y = master_dem_fl, by.x = "CaregiverID", by.y = "CaregiverID")

mh_crt = mh%>%
  dplyr::select(CaregiverID, Week, SurveyType, StartDate, pmh_total_crt, cp_total_crt, depress_crt_r, anxiety_crt_r, lonely_crt_r, stress_crt_r, fussy_crt, fear_crt)

mh_crt <- merge (x = mh_crt, y = master_dem_fl, by.x = "CaregiverID", by.y = "CaregiverID")%>%
  filter (SurveyType == 2)

mh_rct <- mh %>%
  group_by (CaregiverID)%>%
  filter (Week == max (Week))%>%
  ungroup()
mh_rct <- merge (x = mh_rct, y = master_dem_fl, by.x = "CaregiverID", by.y = "CaregiverID")

```

# 0. Sample Disclaimer
  * This set of analyses on well-being is based on responses collected from 5,336 caregivers between the dates of April 6th 2020 and March 20th 2021. These caregivers represent a range of voices: 7.13% are non-Latinx Black/African American, 12.62% are Latinx, and 27.95% live at or below 1.5 times the federal poverty line. Only data from follow-up surveys were included in the analyses for "current mental health" situations.  Proportions/percentages are calculated based on the item-level response rates, not out of the total sample size. The data for these analyses are not weighted. 

  
# 1. Trend of Parent Mental Health
```{r, echo=FALSE, message = FALSE, warning = FALSE}
mh_pre_mean <- mh_pre %>%
  summarise (n = n(),
             total = mean (pmh_total_pre, na.rm = T), 
             depress = mean (depress_pre, na.rm = T), 
             anxiety = mean (anxiety_pre, na.rm = T), 
             stress = mean (stress_pre, na.rm = T), 
             lonely = mean (lonely_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "mean")

mh_pre_sd <- mh_pre %>%
  summarise (total = sd (pmh_total_pre, na.rm = T), 
             depress = sd (depress_pre, na.rm = T), 
             anxiety = sd (anxiety_pre, na.rm = T), 
             stress = sd (stress_pre, na.rm = T), 
             lonely = sd (lonely_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "sd")

mh_pre_smy <- merge (mh_pre_mean, mh_pre_sd)%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe, 
          Week = 0,
          date = as.Date("2020-01-01"))

mh_crt_mean <- mh_crt %>%
  group_by (Week)%>%
  summarise (n = n(),
             date = as.Date(min (StartDate)),
             total = mean (pmh_total_crt, na.rm = T), 
             depress = mean (depress_crt_r, na.rm = T), 
             anxiety = mean (anxiety_crt_r, na.rm = T), 
             stress = mean (stress_crt_r, na.rm = T), 
             lonely = mean (lonely_crt_r, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "mean")

mh_crt_sd <- mh_crt %>%
  group_by (Week)%>%
  summarise (total = sd (pmh_total_crt, na.rm = T), 
             depress = sd (depress_crt_r, na.rm = T), 
             anxiety = sd (anxiety_crt_r, na.rm = T), 
             stress = sd (stress_crt_r, na.rm = T), 
             lonely = sd (lonely_crt_r, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "sd")

mh_crt_smy <- merge (mh_crt_mean, mh_crt_sd, by.x = c("probs", "Week"), by.y = c("probs", "Week"))%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe)

mh_smy <- rbind (mh_pre_smy, mh_crt_smy)

mh_smy %>%
  filter (probs == "total")%>%
  ggplot(mapping = aes (x = date, y = mean)) +   
  geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Total Mental Health Problems")

mh_smy %>%
  filter (probs != "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = probs)) +   
  geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Breakdown of Different Mental Health Problems")
```

## 1.1 By race/ethnicity
```{r, echo=FALSE, message = FALSE, warning = FALSE}
mh_pre_mean <- mh_pre %>%
  filter (race_ethnic!= "NA")%>%
  group_by (race_ethnic)%>%
  summarise (n = n(),
             total = mean (pmh_total_pre, na.rm = T), 
             depress = mean (depress_pre, na.rm = T), 
             anxiety = mean (anxiety_pre, na.rm = T), 
             stress = mean (stress_pre, na.rm = T), 
             lonely = mean (lonely_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "mean")

mh_pre_sd <- mh_pre %>%
  filter (race_ethnic!= "NA")%>%
  group_by (race_ethnic)%>%
  summarise (total = sd (pmh_total_pre, na.rm = T), 
             depress = sd (depress_pre, na.rm = T), 
             anxiety = sd (anxiety_pre, na.rm = T), 
             stress = sd (stress_pre, na.rm = T), 
             lonely = sd (lonely_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "sd")

mh_pre_smy <- merge (mh_pre_mean, mh_pre_sd)%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe, 
          Week = 0,
          date = as.Date("2020-01-01"))

mh_crt_mean <- mh_crt %>%
  filter (race_ethnic!= "NA")%>%
  group_by (Week, race_ethnic)%>%
  summarise (n = n(),
             date = as.Date(min (StartDate)),
             total = mean (pmh_total_crt, na.rm = T), 
             depress = mean (depress_crt_r, na.rm = T), 
             anxiety = mean (anxiety_crt_r, na.rm = T), 
             stress = mean (stress_crt_r, na.rm = T), 
             lonely = mean (lonely_crt_r, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "mean")

mh_crt_sd <- mh_crt %>%
  filter (race_ethnic!= "NA")%>%
  group_by (Week, race_ethnic)%>%
  summarise (total = sd (pmh_total_crt, na.rm = T), 
             depress = sd (depress_crt_r, na.rm = T), 
             anxiety = sd (anxiety_crt_r, na.rm = T), 
             stress = sd (stress_crt_r, na.rm = T), 
             lonely = sd (lonely_crt_r, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "sd")

mh_crt_smy <- merge (mh_crt_mean, mh_crt_sd, by.x = c("probs", "Week", "race_ethnic"), by.y = c("probs", "Week", "race_ethnic"))%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe)

mh_smy <- rbind (mh_pre_smy, mh_crt_smy)

mh_smy %>%
  filter (probs == "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = race_ethnic)) +   
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Total Mental Health Problems")+
  facet_wrap (~race_ethnic)

mh_smy %>%
  filter (probs != "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = probs)) +   
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Breakdown of Different Mental Health Problems")+
  facet_wrap (~race_ethnic, nrow = 1)
```

## 1.2 By poverty level
```{r, echo=FALSE, message = FALSE, warning = FALSE}
mh_pre_mean <- mh_pre %>%
  filter (poverty_cat!= "NA")%>%
  group_by (poverty_cat)%>%
  summarise (n = n(),
             total = mean (pmh_total_pre, na.rm = T), 
             depress = mean (depress_pre, na.rm = T), 
             anxiety = mean (anxiety_pre, na.rm = T), 
             stress = mean (stress_pre, na.rm = T), 
             lonely = mean (lonely_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "mean")

mh_pre_sd <- mh_pre %>%
  filter (poverty_cat!= "NA")%>%
  group_by (poverty_cat)%>%
  summarise (total = sd (pmh_total_pre, na.rm = T), 
             depress = sd (depress_pre, na.rm = T), 
             anxiety = sd (anxiety_pre, na.rm = T), 
             stress = sd (stress_pre, na.rm = T), 
             lonely = sd (lonely_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "sd")

mh_pre_smy <- merge (mh_pre_mean, mh_pre_sd)%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe, 
          Week = 0,
          date = as.Date("2020-01-01"))

mh_crt_mean <- mh_crt %>%
  filter (poverty_cat!= "NA")%>%
  group_by (Week, poverty_cat)%>%
  summarise (n = n(),
             date = as.Date(min (StartDate)),
             total = mean (pmh_total_crt, na.rm = T), 
             depress = mean (depress_crt_r, na.rm = T), 
             anxiety = mean (anxiety_crt_r, na.rm = T), 
             stress = mean (stress_crt_r, na.rm = T), 
             lonely = mean (lonely_crt_r, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "mean")

mh_crt_sd <- mh_crt %>%
  filter (poverty_cat!= "NA")%>%
  group_by (Week, poverty_cat)%>%
  summarise (total = sd (pmh_total_crt, na.rm = T), 
             depress = sd (depress_crt_r, na.rm = T), 
             anxiety = sd (anxiety_crt_r, na.rm = T), 
             stress = sd (stress_crt_r, na.rm = T), 
             lonely = sd (lonely_crt_r, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "sd")

mh_crt_smy <- merge (mh_crt_mean, mh_crt_sd, by.x = c("probs", "Week", "poverty_cat"), by.y = c("probs", "Week", "poverty_cat"))%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe)

mh_smy <- rbind (mh_pre_smy, mh_crt_smy)

mh_smy %>%
  filter (probs == "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = poverty_cat)) +   
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Total Mental Health Problems")

mh_smy %>%
  filter (probs != "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = probs)) +   
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Breakdown of Different Mental Health Problems")+
  facet_wrap (~poverty_cat, nrow = 1)
```

## 1.3 By child disability status
```{r, echo=FALSE, message = FALSE, warning = FALSE}
mh_pre_mean <- mh_pre %>%
  filter (disability!= "NA")%>%
  group_by (disability)%>%
  summarise (n = n(),
             total = mean (pmh_total_pre, na.rm = T), 
             depress = mean (depress_pre, na.rm = T), 
             anxiety = mean (anxiety_pre, na.rm = T), 
             stress = mean (stress_pre, na.rm = T), 
             lonely = mean (lonely_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "mean")

mh_pre_sd <- mh_pre %>%
  filter (disability!= "NA")%>%
  group_by (disability)%>%
  summarise (total = sd (pmh_total_pre, na.rm = T), 
             depress = sd (depress_pre, na.rm = T), 
             anxiety = sd (anxiety_pre, na.rm = T), 
             stress = sd (stress_pre, na.rm = T), 
             lonely = sd (lonely_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "sd")

mh_pre_smy <- merge (mh_pre_mean, mh_pre_sd)%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe, 
          Week = 0,
          date = as.Date("2020-01-01"))

mh_crt_mean <- mh_crt %>%
  filter (disability!= "NA")%>%
  group_by (Week, disability)%>%
  summarise (n = n(),
             date = as.Date(min (StartDate)),
             total = mean (pmh_total_crt, na.rm = T), 
             depress = mean (depress_crt_r, na.rm = T), 
             anxiety = mean (anxiety_crt_r, na.rm = T), 
             stress = mean (stress_crt_r, na.rm = T), 
             lonely = mean (lonely_crt_r, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "mean")

mh_crt_sd <- mh_crt %>%
  filter (disability!= "NA")%>%
  group_by (Week, disability)%>%
  summarise (total = sd (pmh_total_crt, na.rm = T), 
             depress = sd (depress_crt_r, na.rm = T), 
             anxiety = sd (anxiety_crt_r, na.rm = T), 
             stress = sd (stress_crt_r, na.rm = T), 
             lonely = sd (lonely_crt_r, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "sd")

mh_crt_smy <- merge (mh_crt_mean, mh_crt_sd, by.x = c("probs", "Week", "disability"), by.y = c("probs", "Week", "disability"))%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe)

mh_smy <- rbind (mh_pre_smy, mh_crt_smy)

mh_smy %>%
  filter (probs == "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = disability)) +   
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Total Mental Health Problems")

mh_smy %>%
  filter (probs != "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = probs)) +   
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Breakdown of Different Mental Health Problems")+
  facet_wrap (~disability, nrow = 1)
```

## 1.4 By single parent status
```{r, echo=FALSE, message = FALSE, warning = FALSE}
mh_pre_mean <- mh_pre %>%
  filter (single!= "NA")%>%
  group_by (single)%>%
  summarise (n = n(),
             total = mean (pmh_total_pre, na.rm = T), 
             depress = mean (depress_pre, na.rm = T), 
             anxiety = mean (anxiety_pre, na.rm = T), 
             stress = mean (stress_pre, na.rm = T), 
             lonely = mean (lonely_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "mean")

mh_pre_sd <- mh_pre %>%
  filter (single!= "NA")%>%
  group_by (single)%>%
  summarise (total = sd (pmh_total_pre, na.rm = T), 
             depress = sd (depress_pre, na.rm = T), 
             anxiety = sd (anxiety_pre, na.rm = T), 
             stress = sd (stress_pre, na.rm = T), 
             lonely = sd (lonely_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "sd")

mh_pre_smy <- merge (mh_pre_mean, mh_pre_sd)%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe, 
          Week = 0,
          date = as.Date("2020-01-01"))

mh_crt_mean <- mh_crt %>%
  filter (single!= "NA")%>%
  group_by (Week, single)%>%
  summarise (n = n(),
             date = as.Date(min (StartDate)),
             total = mean (pmh_total_crt, na.rm = T), 
             depress = mean (depress_crt_r, na.rm = T), 
             anxiety = mean (anxiety_crt_r, na.rm = T), 
             stress = mean (stress_crt_r, na.rm = T), 
             lonely = mean (lonely_crt_r, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "mean")

mh_crt_sd <- mh_crt %>%
  filter (single!= "NA")%>%
  group_by (Week, single)%>%
  summarise (total = sd (pmh_total_crt, na.rm = T), 
             depress = sd (depress_crt_r, na.rm = T), 
             anxiety = sd (anxiety_crt_r, na.rm = T), 
             stress = sd (stress_crt_r, na.rm = T), 
             lonely = sd (lonely_crt_r, na.rm = T))%>%
  pivot_longer (cols = c("total", "depress", "anxiety", "stress", "lonely"), names_to = "probs", values_to = "sd")

mh_crt_smy <- merge (mh_crt_mean, mh_crt_sd, by.x = c("probs", "Week", "single"), by.y = c("probs", "Week", "single"))%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe)

mh_smy <- rbind (mh_pre_smy, mh_crt_smy)

mh_smy %>%
  filter (probs == "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = single)) +   
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Total Mental Health Problems")

mh_smy %>%
  filter (probs != "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = probs)) +   
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Breakdown of Different Mental Health Problems")+
  facet_wrap (~single, nrow = 1)
```

# 2. Trend of Child Mental Health
```{r, echo=FALSE, message = FALSE, warning = FALSE}
mh_pre_mean <- mh_pre %>%
  summarise (n = n(),
             total = mean (cp_total_pre, na.rm = T), 
             fussy = mean (fussy_pre, na.rm = T), 
             fear = mean (fear_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "mean")

mh_pre_sd <- mh_pre %>%
  summarise (total = sd (cp_total_pre, na.rm = T), 
             fussy = sd (fussy_pre, na.rm = T), 
             fear = sd (fear_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "sd")

mh_pre_smy <- merge (mh_pre_mean, mh_pre_sd)%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe, 
          Week = 0,
          date = as.Date("2020-01-01"))

mh_crt_mean <- mh_crt %>%
  group_by (Week)%>%
  summarise (n = n(),
             date = as.Date(min (StartDate)),
             total = mean (cp_total_crt, na.rm = T), 
             fussy = mean (fussy_crt, na.rm = T), 
             fear = mean (fear_crt, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "mean")

mh_crt_sd <- mh_crt %>%
  group_by (Week)%>%
  summarise (total = sd (cp_total_crt, na.rm = T), 
             fussy = sd (fussy_crt, na.rm = T), 
             fear = sd (fear_crt, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "sd")


mh_crt_smy <- merge (mh_crt_mean, mh_crt_sd, by.x = c("probs", "Week"), by.y = c("probs", "Week"))%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe)

mh_smy <- rbind (mh_pre_smy, mh_crt_smy)

mh_smy %>%
  filter (probs == "total")%>%
  ggplot(mapping = aes (x = date, y = mean)) +   
  geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Total Mental Health Problems")

mh_smy %>%
  filter (probs != "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = probs)) +   
  geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Breakdown of Different Mental Health Problems")
```

## 2.1 By race/ethnicity

```{r, echo=FALSE, message = FALSE, warning = FALSE}
mh_pre_mean <- mh_pre %>%
  filter (race_ethnic!= "NA")%>%
  group_by (race_ethnic)%>%
  summarise (n = n(),
             total = mean (cp_total_pre, na.rm = T), 
             fussy = mean (fussy_pre, na.rm = T), 
             fear = mean (fear_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "mean")

mh_pre_sd <- mh_pre %>%
  filter (race_ethnic!= "NA")%>%
  group_by (race_ethnic)%>%
  summarise (total = sd (cp_total_pre, na.rm = T), 
             fussy = sd (fussy_pre, na.rm = T), 
             fear = sd (fear_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "sd")

mh_pre_smy <- merge (mh_pre_mean, mh_pre_sd)%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe, 
          Week = 0,
          date = as.Date("2020-01-01"))

mh_crt_mean <- mh_crt %>%
  filter (race_ethnic!= "NA")%>%
  group_by (Week, race_ethnic)%>%
  summarise (n = n(),
             date = as.Date(min (StartDate)),
             total = mean (cp_total_crt, na.rm = T), 
             fussy = mean (fussy_crt, na.rm = T), 
             fear = mean (fear_crt, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "mean")

mh_crt_sd <- mh_crt %>%
  filter (race_ethnic!= "NA")%>%
  group_by (Week, race_ethnic)%>%
  summarise (total = sd (cp_total_crt, na.rm = T), 
             fussy = sd (fussy_crt, na.rm = T), 
             fear = sd (fear_crt, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "sd")


mh_crt_smy <- merge (mh_crt_mean, mh_crt_sd, by.x = c("probs", "Week", "race_ethnic"), by.y = c("probs", "Week", "race_ethnic"))%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe)

mh_smy <- rbind (mh_pre_smy, mh_crt_smy)

mh_smy %>%
  filter (probs == "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = race_ethnic)) +   
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Total Mental Health Problems")+
  facet_wrap (~race_ethnic, nrow = 1)

mh_smy %>%
  filter (probs != "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = probs)) +   
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Breakdown of Different Mental Health Problems")+
  facet_wrap (~race_ethnic, nrow = 1)
```

## 2.2 By poverty level

```{r, echo=FALSE, message = FALSE, warning = FALSE}
mh_pre_mean <- mh_pre %>%
  filter (poverty_cat!= "NA")%>%
  group_by (poverty_cat)%>%
  summarise (n = n(),
             total = mean (cp_total_pre, na.rm = T), 
             fussy = mean (fussy_pre, na.rm = T), 
             fear = mean (fear_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "mean")

mh_pre_sd <- mh_pre %>%
  filter (poverty_cat!= "NA")%>%
  group_by (poverty_cat)%>%
  summarise (total = sd (cp_total_pre, na.rm = T), 
             fussy = sd (fussy_pre, na.rm = T), 
             fear = sd (fear_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "sd")

mh_pre_smy <- merge (mh_pre_mean, mh_pre_sd)%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe, 
          Week = 0,
          date = as.Date("2020-01-01"))

mh_crt_mean <- mh_crt %>%
  filter (poverty_cat!= "NA")%>%
  group_by (Week, poverty_cat)%>%
  summarise (n = n(),
             date = as.Date(min (StartDate)),
             total = mean (cp_total_crt, na.rm = T), 
             fussy = mean (fussy_crt, na.rm = T), 
             fear = mean (fear_crt, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "mean")

mh_crt_sd <- mh_crt %>%
  filter (poverty_cat!= "NA")%>%
  group_by (Week, poverty_cat)%>%
  summarise (total = sd (cp_total_crt, na.rm = T), 
             fussy = sd (fussy_crt, na.rm = T), 
             fear = sd (fear_crt, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "sd")


mh_crt_smy <- merge (mh_crt_mean, mh_crt_sd, by.x = c("probs", "Week", "poverty_cat"), by.y = c("probs", "Week", "poverty_cat"))%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe)

mh_smy <- rbind (mh_pre_smy, mh_crt_smy)

mh_smy %>%
  filter (probs == "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = poverty_cat)) +   
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Total Mental Health Problems")

mh_smy %>%
  filter (probs != "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = probs)) +   
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Breakdown of Different Mental Health Problems")+
  facet_wrap (~poverty_cat, nrow = 1)
```

## 2.3 By child disability status

```{r, echo=FALSE, message = FALSE, warning = FALSE}
mh_pre_mean <- mh_pre %>%
  filter (disability!= "NA")%>%
  group_by (disability)%>%
  summarise (n = n(),
             total = mean (cp_total_pre, na.rm = T), 
             fussy = mean (fussy_pre, na.rm = T), 
             fear = mean (fear_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "mean")

mh_pre_sd <- mh_pre %>%
  filter (disability!= "NA")%>%
  group_by (disability)%>%
  summarise (total = sd (cp_total_pre, na.rm = T), 
             fussy = sd (fussy_pre, na.rm = T), 
             fear = sd (fear_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "sd")

mh_pre_smy <- merge (mh_pre_mean, mh_pre_sd)%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe, 
          Week = 0,
          date = as.Date("2020-01-01"))

mh_crt_mean <- mh_crt %>%
  filter (disability!= "NA")%>%
  group_by (Week, disability)%>%
  summarise (n = n(),
             date = as.Date(min (StartDate)),
             total = mean (cp_total_crt, na.rm = T), 
             fussy = mean (fussy_crt, na.rm = T), 
             fear = mean (fear_crt, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "mean")

mh_crt_sd <- mh_crt %>%
  filter (disability!= "NA")%>%
  group_by (Week, disability)%>%
  summarise (total = sd (cp_total_crt, na.rm = T), 
             fussy = sd (fussy_crt, na.rm = T), 
             fear = sd (fear_crt, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "sd")


mh_crt_smy <- merge (mh_crt_mean, mh_crt_sd, by.x = c("probs", "Week", "disability"), by.y = c("probs", "Week", "disability"))%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe)

mh_smy <- rbind (mh_pre_smy, mh_crt_smy)

mh_smy %>%
  filter (probs == "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = disability)) +   
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Total Mental Health Problems")

mh_smy %>%
  filter (probs != "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = probs)) +   
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Breakdown of Different Mental Health Problems")+
  facet_wrap (~disability, nrow = 1)
```

## 2.4 By single parent status

```{r, echo=FALSE, message = FALSE, warning = FALSE}
mh_pre_mean <- mh_pre %>%
  filter (single!= "NA")%>%
  group_by (single)%>%
  summarise (n = n(),
             total = mean (cp_total_pre, na.rm = T), 
             fussy = mean (fussy_pre, na.rm = T), 
             fear = mean (fear_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "mean")

mh_pre_sd <- mh_pre %>%
  filter (single!= "NA")%>%
  group_by (single)%>%
  summarise (total = sd (cp_total_pre, na.rm = T), 
             fussy = sd (fussy_pre, na.rm = T), 
             fear = sd (fear_pre, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "sd")

mh_pre_smy <- merge (mh_pre_mean, mh_pre_sd)%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe, 
          Week = 0,
          date = as.Date("2020-01-01"))

mh_crt_mean <- mh_crt %>%
  filter (single!= "NA")%>%
  group_by (Week, single)%>%
  summarise (n = n(),
             date = as.Date(min (StartDate)),
             total = mean (cp_total_crt, na.rm = T), 
             fussy = mean (fussy_crt, na.rm = T), 
             fear = mean (fear_crt, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "mean")

mh_crt_sd <- mh_crt %>%
  filter (single!= "NA")%>%
  group_by (Week, single)%>%
  summarise (total = sd (cp_total_crt, na.rm = T), 
             fussy = sd (fussy_crt, na.rm = T), 
             fear = sd (fear_crt, na.rm = T))%>%
  pivot_longer (cols = c("total", "fussy", "fear"), names_to = "probs", values_to = "sd")


mh_crt_smy <- merge (mh_crt_mean, mh_crt_sd, by.x = c("probs", "Week", "single"), by.y = c("probs", "Week", "single"))%>%
  mutate (moe = map2_dbl(sd, n, moe.m), 
          ci_low = mean-moe,
          ci_high = mean+moe)

mh_smy <- rbind (mh_pre_smy, mh_crt_smy)

mh_smy %>%
  filter (probs == "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = single)) +   
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Total Mental Health Problems")

mh_smy %>%
  filter (probs != "total")%>%
  ggplot(mapping = aes (x = date, y = mean, fill = probs)) +   
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .3) +
  geom_line() +
  labs (y = "Mean") +                                                 # y axis label
  labs (x = "Date") +                                                 # x axis label
  theme(axis.text.x = element_text(angle = 45))+                  # Change x axis label to 45 angle degree
  scale_x_date (date_breaks = "2 month", date_labels ="%b %Y")+
  ggtitle (label = "Breakdown of Different Mental Health Problems")+
  facet_wrap (~single, nrow = 1)
```