---
title: "Childcare"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
  
---


```{r chunk 1, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
```

```{r packages}
library(here)
```

```{r childcare-1}
source(here("Scripts/score data.R"))

outcomes = c("anxiety", "depress", "lonely", "stress", "fussy", "fear")
outcomes_p = paste0(outcomes, "_current_lots")

source(here("Functions/pomp.R"))

scored = scored %>%
  mutate_at(vars("anxiety","depress"), pomp_ad) %>%
  mutate_at("stress", pomp_stress) %>%
  mutate_at("lonely", pomp_lonely) %>%
  mutate_at(vars("fussy", "fear"), pomp_child) 

source(here("Scripts/demo groups.R"))

binary_demos = binary_demos[!grepl("working", binary_demos)]
binary_labels = binary_labels[!grepl("Working", binary_labels)]

cc_binary = c("cc2_centerbased","cc2_unpaid","cc2_paid","cc2_homebased")
cc_binary_labels = c("Center-based care",
                     "Unpaid care by relative/friend/neighbor",
                     "Paid care by relative/friend/neighbor",
                     "Home-based paid childcare")


source(here("Functions/summarizing_report.R"))
```

# Pre- vs post- changes in childcare

These analyses include retrospective reports of pre-pandemic childcare and the current experience reported the most recent time a caregiver participates in the RAPID survey.

## Types of childcare used{.tabset}

### Total sample

```{r childcare-2, results = 'asis'}
BefAft = scored %>%
  filter(Week == 0 | Week == 6) %>%
  mutate(Week = ifelse(Week == 0, "Bef", "During"))

BefAft = BefAft %>%
  select(Week, all_of(cc_binary)) %>%
  gather("Variable", "value", -Week) %>%
  filter(!is.na(value)) %>%
  group_by(Week, Variable) %>%
  summarize(Count = sum(value),
            Percent = 100*Count/n()) 

BefAft %>%
  gather("stat", "value", Count, Percent) %>%
  unite(Week, Week, stat, sep = "_") %>%
  spread(Week, value) %>%
  mutate(Variable = factor(Variable, levels = cc_binary, labels = cc_binary_labels),
         Change_count = During_Count - Bef_Count, 
         Change_percent = During_Percent - Bef_Percent) %>%
  arrange(Variable) %>%
  kable(., digits = c(0, 0, 1, 0, 1, 0, 1),
        col.names = c("Type of childcare", "Count", "Percent", "Count", "Percent", "Count", "Percent")) %>%
  kable_styling() %>%
  add_header_above(c(" ", "Pre-pandemic" = 2, "During pandemic" = 2, "Change" = 2))
```

```{r childcare-3, out.width=c('50%', '50%'), fig.show='hold'}
BefAft %>%
  ungroup() %>%
  mutate(Variable = factor(Variable, 
                           levels = cc_binary, 
                           labels = cc_binary_labels),
         Week = factor(Week, 
                       levels = c("Bef", "During"), 
                       labels = c("Pre-pandemic", "During pandemic"))) %>%
  ggplot(aes(x = Variable, y = Percent, fill = Week)) +
    geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +
  theme(legend.position = "top")

BefAft %>%
  gather("stat", "value", Count, Percent) %>%
  unite(Week, Week, stat, sep = "_") %>%
  spread(Week, value) %>%
  mutate(Variable = factor(Variable, 
                           levels = cc_binary, 
                           labels = cc_binary_labels),
         Change_percent = During_Percent - Bef_Percent) %>%
  ggplot(aes(x = Variable, y = Change_percent)) +
    geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous("Change in percent (not percent change)") +
  coord_flip() +
  theme(legend.position = "top")
```

### By demographic

```{r childcare-4, results = 'asis'}
BefAft = scored %>%
  filter(Week == 0 | Week == 5) %>%
  mutate(Week = ifelse(Week == 0, "Bef", "During"))

BefAft = BefAft %>%
  select(Week, all_of(cc_binary), all_of(binary_demos)) %>%
  gather("Variable", "value", all_of(cc_binary)) %>%
  gather("Demo", "group", all_of(binary_demos)) %>%
  filter(!is.na(value)) %>%
  filter(group == 1) %>%
  group_by(Demo, Week, Variable) %>%
  summarize(Count = sum(value),
            Percent = 100*Count/n()) 

table = BefAft %>%
  gather("stat", "value", Count, Percent) %>%
  unite(Week, Week, stat, sep = "_") %>%
  spread(Week, value) %>%
  ungroup() %>%
  mutate(Variable = factor(Variable, levels = cc_binary, labels = cc_binary_labels),
         Demo = factor(Demo, levels = binary_demos),
         Change_count = During_Count - Bef_Count, 
         Change_percent = During_Percent - Bef_Percent) %>%
  arrange(Demo, Variable) 

#build groupings

demo_groups = binary_demos %in% unique(table$Demo)

first.row = sapply(binary_demos[demo_groups], first_instance, string = table$Demo)
last.row = sapply(binary_demos[demo_groups], last_instance, string = table$Demo)

each_string = paste0("group_rows(group_label = \" ", 
                     binary_labels[demo_groups], 
                     "\" , start_row = ", 
                     first.row, 
                     ", end_row = ", 
                     last.row, 
                     ")")
each_string = paste(each_string, collapse = " %>% ")

# table code
beginning = "table %>% 
  select(-Demo) %>% 
  kable(., digits = c(0, 0, 1, 0, 1, 0, 1),
        col.names = c(\"Type of childcare\", \"Count\", \"Percent\", \"Count\", \"Percent\", \"Count\", \"Percent\")) %>%
  kable_styling() %>%
  add_header_above(c(\" \", \"Pre-pandemic\" = 2, \"During pandemic\" = 2, \"Change\" = 2)) %>%"

eval(parse(text = paste0(beginning, each_string)))
```

```{r childcare-5, out.width=c('50%', '50%'), fig.show='hold'}

BefAft %>%
  ungroup() %>%
  gather("stat", "value", Count, Percent) %>%
  unite(Week, Week, stat, sep = "_") %>%
  spread(Week, value) %>%
  mutate(Variable = factor(Variable, 
                           levels = cc_binary, 
                           labels = cc_binary_labels),
         Demo = factor(Demo, levels = binary_demos, labels = binary_labels),
         Change_percent = During_Percent - Bef_Percent) %>%
  ggplot(aes(x = Variable, y = Change_percent, fill = Demo)) +
  geom_bar(stat = "identity", position = "dodge", color = "white") +
  scale_y_continuous("Change in percent (not percent change)") +
  scale_x_discrete("", breaks = NULL) +
  coord_flip() +
  facet_wrap(~Variable, scales = "free") +
  theme(legend.position = "top")

BefAft %>%
  ungroup() %>%
  gather("stat", "value", Count, Percent) %>%
  unite(Week, Week, stat, sep = "_") %>%
  spread(Week, value) %>%
  mutate(Variable = factor(Variable, 
                           levels = cc_binary, 
                           labels = cc_binary_labels),
         Demo = factor(Demo, levels = binary_demos, labels = binary_labels),
         Change_percent = During_Percent - Bef_Percent) %>%
  ggplot(aes(x = Demo, y = Change_percent, fill = Variable)) +
  geom_bar(stat = "identity", position = "dodge", color = "white") +
  scale_y_continuous("Change in percent (not percent change)") +
  scale_x_discrete("", breaks = NULL) +
  coord_flip() + 
  facet_wrap(~Demo, scales = "free") +
  theme(legend.position = "top")
```

<!-- # Changes in childcare since the pandemic started -->

<!-- ```{r childcare-6} -->
<!-- scored %>% -->
<!--   filter(Week > 0) %>% -->
<!--   select(Week, all_of(cc_binary)) %>% -->
<!--   gather("var", "value", all_of(cc_binary)) %>% -->
<!--   filter(!is.na(value)) %>% -->
<!--   group_by(Week, var) %>% -->
<!--   summarize(Count = sum(value), -->
<!--             Percent = 100*Count/n()) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(var = factor(var, levels = cc_binary, labels = cc_binary_labels)) %>% -->
<!--   ggplot(aes(x = Week, y = Percent, color = var)) + -->
<!--   geom_point() + -->
<!--   geom_line() + -->
<!--   theme_minimal() +  -->
<!--   theme(legend.position = "top") -->
<!-- ``` -->

<!-- ```{r childcare-7} -->
<!-- scored %>% -->
<!--   filter(Week > 0) %>% -->
<!--   select(Week, all_of(cc_binary), all_of(binary_demos)) %>% -->
<!--   gather("var", "value", all_of(cc_binary)) %>% -->
<!--   gather("Demo", "group", all_of(binary_demos)) %>% -->
<!--   filter(!is.na(value)) %>% -->
<!--   filter(group == 1) %>% -->
<!--   group_by(Demo, Week, var) %>% -->
<!--   summarize(Count = sum(value), -->
<!--             Percent = 100*Count/n()) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(var = factor(var, levels = cc_binary, labels = cc_binary_labels), -->
<!--          Demo = factor(Demo, levels = binary_demos, labels = binary_labels)) %>% -->
<!--   ggplot(aes(x = Week, y = Percent, color = var)) + -->
<!--   geom_point() + -->
<!--   geom_line() + -->
<!--   theme_minimal() +  -->
<!--   facet_wrap(~Demo) + -->
<!--   theme(legend.position = "top") -->
<!-- ``` -->

<!-- ```{r childcare-8} -->
<!-- scored %>% -->
<!--   filter(Week > 0) %>% -->
<!--   select(Week, all_of(cc_binary), all_of(binary_demos)) %>% -->
<!--   gather("var", "value", all_of(cc_binary)) %>% -->
<!--   gather("Demo", "group", all_of(binary_demos)) %>% -->
<!--   filter(!is.na(value)) %>% -->
<!--   filter(group == 1) %>% -->
<!--   group_by(Demo, Week, var) %>% -->
<!--   summarize(Count = sum(value), -->
<!--             Percent = 100*Count/n()) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(var = factor(var, levels = cc_binary, labels = cc_binary_labels), -->
<!--          Demo = factor(Demo, levels = binary_demos, labels = binary_labels)) %>% -->
<!--   ggplot(aes(x = Week, y = Percent, color = Demo)) + -->
<!--   geom_point() + -->
<!--   geom_line() + -->
<!--   theme_minimal() +  -->
<!--   facet_wrap(~var) + -->
<!--   theme(legend.position = "top") -->
<!-- ``` -->


# Effect on well-being {.tabset}

All mental health variables have been POMP scored for ease of interpretation and combination. Scores range from 0 to 100, with low scores indicating better mental health and high scores indicating more mental health problems. 

```{r}

# means by change
affect_by_change = function(x){
  x %>%
  filter(!is.na(e.value)) %>%
  group_by(change) %>%
  summarize(mean = mean(e.value),
            n = n(),
            cv = qt(.975, df = n-1),
            sem = sd(e.value)/sqrt(n),
            lower = mean-(cv*sem),
            upper = mean+(cv*sem)) %>%
  mutate(change = factor(change, levels = c(-1, 0, 1),
                         labels = c("Lost care", "No change", "Gained care"))) %>%
  select(change, mean, lower, upper)
  }


BefAft = scored %>%
  filter(Week == 0 | Week == BaselineWeek) %>%
  mutate(Week = ifelse(Week == 0, "Bef", "During"))

change_care = BefAft %>%
  select(CaregiverID, Week, all_of(cc_binary)) %>%
  gather(var, value, all_of(cc_binary)) %>%
  spread(Week, value) %>%
  mutate(change = During-Bef)

changes = BefAft %>%
  filter(Week == "During") %>%
  select(CaregiverID, all_of(outcomes)) %>%
  full_join(change_care) %>%
  gather("emotion", "e.value", all_of(outcomes)) %>%
  group_by(emotion, var) %>%
  nest() %>%
  mutate(output = purrr::map(data, affect_by_change)) %>%
  select(emotion, var, output) %>%
  unnest() 
```

## Anxiety

```{r anxiety}
changes %>%
  filter(emotion == "anxiety") %>%
  ggplot(aes(x = change, y = mean, fill = change)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .5) +
  facet_wrap(~var) +
  theme_minimal() +
  guides(fill = F)
```

## Depression

```{r depress}
changes %>%
  filter(emotion == "depress") %>%
  ggplot(aes(x = change, y = mean, fill = change)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .5) +
  facet_wrap(~var) +
  theme_minimal() +
  guides(fill = F)
```

## Stress

```{r stress}
changes %>%
  filter(emotion == "stress") %>%
  ggplot(aes(x = change, y = mean, fill = change)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .5) +
  facet_wrap(~var) +
  theme_minimal() +
  guides(fill = F)
```

## Loneliness
```{r lonely}
changes %>%
  filter(emotion == "lonely") %>%
  ggplot(aes(x = change, y = mean, fill = change)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .5) +
  facet_wrap(~var) +
  theme_minimal() +
  guides(fill = F)
```

## Child externalizing

```{r fussy}
changes %>%
  filter(emotion == "fussy") %>%
  ggplot(aes(x = change, y = mean, fill = change)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .5) +
  facet_wrap(~var) +
  theme_minimal() +
  guides(fill = F)
```

## Child internalizing

```{r fear}
changes %>%
  filter(emotion == "fear") %>%
  ggplot(aes(x = change, y = mean, fill = change)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .5) +
  facet_wrap(~var) +
  theme_minimal() +
  guides(fill = F)
```

