---
title: "COVID Infection Analyses"
author: "Sihong"
date: "11/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include = FALSE}
library(here)
library(tidyverse)
library(knitr)
library(kableExtra)
library(readr)
library(haven)
library(BSDA)
library(naniar)
```


```{r, echo=FALSE, message = FALSE}
#Define functions
moe.p = function(p, n){
  q = 1-p
  moe = 1.96*sqrt((p*q)/n)
  return(moe)
}

moe.m = function(sd,n){
  moe = 1.96*sd/sqrt(n)
  return(moe)}

combine.cat = function(x, cols, id, newvar.name){
  subset = x[,c(id, "Week", cols)]
  names(subset) = c("id", "Week", paste0("X",1:length(cols)))
  subset = suppressWarnings(gather(subset, "key", "value", -id, -Week))
  subset = filter(subset, !is.na(value))
  subset$key = gsub("X", "", subset$key)
  subset = group_by(subset, id, Week)
  subset = summarize(subset, newvar = paste(key, collapse = ",")) %>% ungroup()
  names(subset) = c(id,"Week", newvar.name)
  x = suppressMessages(full_join(x, subset))
  return(x)
}

find_items = function(string, data2){
  items = names(data2)
  locations = which(grepl(string, items))
  final = items[locations]
  return(final)
}

my.max = function(x) ifelse (!all(is.na(x)), max(x,na.rm = TRUE), NA)
```

```{r, echo=FALSE, message = FALSE, warning = FALSE, include=FALSE}
#OR load master data file
master_2020 <- read_sav(here("../../Data Management R3/CC_Clean Survey Data/00_R3 MasterFile/MasterFile_groupings_2020.sav"))
master_2021 <- read_sav(here("../../Data Management R3/CC_Clean Survey Data/00_R3 MasterFile/MasterFile_groupings_2021.sav"))

master <- full_join (master_2020, master_2021)

# Remove cases should be excluded
master <- master %>%
  filter ( CaregiverID != "" & is.na(Exclude) == T)

master = master %>%
  group_by(CaregiverID, Week) %>%
  ungroup()

total_week <- my.max(master$Week)


```

```{r, echo=FALSE, message = FALSE, warning = FALSE}
#Code demographics
master <- master %>%
  mutate (month = case_when(
                  Week == 0 ~ "Pre-COVID",
                  Week >0 & Week <= 4 ~ "April",
                  Week >=5 & Week <=8 ~ "May",
                  Week >=9 & Week <=13 ~ "June",
                  Week >=14 & Week <=17 ~ "July",
                  Week >=18 & Week <=21 ~ "August",
                  Week >=22 & Week <=26 ~ "September",
                  Week >=27 ~ "October"), 
           baseline = case_when (Week - BaselineWeek == 1 ~ 1, 
                                 Week - BaselineWeek > 1 ~ 0))

##Race/ethnicity - 1 = black, 2 = latinx, 3 = white

master <- master %>%
    mutate(
      minority = ifelse(RaceGroup != 5, 1, 0),
      black = ifelse(RaceGroup == 3, 1, 0),
      native = ifelse(RaceGroup == 1, 1, 0),
      asian = ifelse(RaceGroup == 2, 1, 0),
      hawaii = ifelse(RaceGroup == 4, 1, 0),
      white = ifelse(RaceGroup == 5, 1, 0),
      other_race = ifelse(RaceGroup %in% c(6, 7), 1, 0))

master <- master %>%
      mutate(latinx = case_when(
        DEMO.008 == 1 ~ 1,
        DEMO.008 == 0 ~ 0,
        DEMO.008.2 == 0 ~ 0,
        DEMO.008.2 == 1 ~ 1,
        DEMO.008.2 == 2 ~ 1,
        TRUE ~ NA_real_))

master <- master %>%
mutate (race_ethnic = case_when(
      black == 1 ~ "1",
      latinx == 1 ~ "2",
      !is.na(black) ~ "3",
      !is.na(latinx) ~ "3",
      TRUE ~ NA_character_))  

##Povertyline - 0 = high income, 1 = low income
master <- master %>%
  mutate (poverty_cat = FPL.2019.UM.150)

#Material hardship
master <- master %>%
  combine.cat(cols = find_items("FSTR.002_.{1}$", master), 
              id = "CaregiverID",
              newvar.name = "FSTR.002_cat")
  

master <- master %>%
  mutate (diff_pay_food = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("1", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_), 
          diff_pay_utilities = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("3", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_house = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("2", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_healthcare = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("4", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_social = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("5", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_emotional = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("6", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_childcare = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("7", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_other = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("8", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_))

master <- master %>%
  rowwise() %>%
  mutate(material_hardship = case_when(
    Week == 0 ~ NA_real_,
    TRUE ~ sum(c_across(starts_with("diff_pay_")), na.rm=T))) %>%
  ungroup() %>%
  mutate(num_hardship = material_hardship,
    material_hardship = ifelse(material_hardship > 0, 1, 0)) 

## Children with special needs
master <- combine.cat(x = master, 
                       cols = find_items("HEALTH.005_[0-9]{1}$", master), 
                       id = "CaregiverID",
                       newvar.name = "HEALTH.005_cat")
master <- master %>%
   mutate (disability = ifelse(grepl("[1-4]", HEALTH.005_cat), 1, 0))


## Single parent status
master <- master %>%
  mutate (single = case_when (
                   DEMO.002 %in% c(3,4,5,7,8)~1, 
                   DEMO.011 %in% c(2,4)~1,
                   !is.na(DEMO.002)~0,
                   !is.na(DEMO.011)~0,
                   TRUE ~ NA_real_))
                     
## Employment status
master <- combine.cat (x = master,
                       cols = find_items ("JOB.010_.{1,2}$", master), 
                       id = "CaregiverID",
                       newvar.name = "JOB.010_cat")
  
master$JOB.010_cat = gsub("10", "0", master$JOB.010_cat)
master$working_pre = ifelse (grepl("[1,2,6]", master$JOB.010_cat), 1, 0)
master = combine.cat (x = master,
                       cols = find_items ("JOB.008_.{1,2}$", master), 
                       id = "CaregiverID",
                       newvar.name = "JOB.008_cat")
master$JOB.008_cat = gsub("10", "0", master$JOB.008_cat)
master <- master %>%
  mutate (work_status = case_when(
                        grepl ("1", JOB.008_cat) ~ "1", 
                        grepl ("2", JOB.008_cat) ~ "1", 
                        grepl ("3", JOB.008_cat) ~ "0", 
                        grepl ("4", JOB.008_cat) ~ "0", 
                        grepl ("5", JOB.008_cat) ~ "1", 
                        JOB.008.2 == 1 ~ "1",
                        JOB.008.2 %in% c(2,3) ~ "0",
                        TRUE~NA_character_),
          work_status_pre = case_when(
                        grepl ("1", JOB.010_cat) ~ "1", 
                        grepl ("2", JOB.010_cat) ~ "1", 
                        grepl ("3", JOB.010_cat) ~ "0", 
                        grepl ("4", JOB.010_cat) ~ "0", 
                        grepl ("5", JOB.010_cat) ~ "1", 
                        TRUE~NA_character_),
          ep_change = case_when(
                        work_status == 1 & work_status_pre == 1 ~ "1", 
                        work_status == 1 & work_status_pre == 0 ~ "2", 
                        work_status == 0 & work_status_pre == 1 ~ "3", 
                        work_status == 0 & work_status_pre == 0 ~ "4", 
                        TRUE~NA_character_))
#1 = stable employed 2 = became unemployed 3 = became employed4 = stable unemployed

master_dem <- master %>%
  group_by (CaregiverID) %>%
  summarise (BaselineWeek = my.max (BaselineWeek),
             race_ethnic = my.max(race_ethnic),
             poverty_cat = my.max(poverty_cat),
             material_hardship = my.max(material_hardship),
             disability = my.max (disability),
             single = my.max (single),
             work_status = my.max (work_status),
             work_status_pre = my.max (work_status_pre),
             ep_change = my.max (ep_change))%>%
  mutate (race_ethnic = case_when (
                        race_ethnic == 1 ~ "Black", 
                        race_ethnic == 2 ~ "Latinx", 
                        race_ethnic == 3 ~ "White"),
          poverty_cat = case_when (
                        poverty_cat == 1 ~ "Below 150%FPL", 
                        poverty_cat == 0 ~ "Above 150%FPL"),
          material_hardship = case_when (
                        material_hardship == 1 ~ "With material hardship", 
                        material_hardship == 0 ~ "Without material hardship"),
          disability = case_when (
                        disability == 1 ~ "With disability", 
                        disability == 0 ~ "Without disability"),
          single = case_when (
                        single == 1 ~ "Single parent", 
                        single == 0 ~ "Dual parent"),
          work_status = case_when (
                        work_status == 1 ~ "Employed", 
                        work_status == 0 ~ "Unemployed"),
          work_status_pre = case_when (
                        work_status_pre == 1 ~ "Employed", 
                        work_status_pre == 0 ~ "Unemployed"),
          ep_change = case_when (
                        ep_change == 1 ~ "Stable employed", 
                        ep_change == 2 ~ "Became unemployed", 
                        ep_change == 3 ~ "Became employed",
                        ep_change == 4 ~ "Stable unemployed"))

```


```{r, echo=FALSE, message = FALSE, warning = FALSE}
#Extract COVID Related Questions
covid <- master %>%
  select (CaregiverID, StartDate, SurveyType, Week, month, baseline, contains ("COVID"))

covid <- merge (x = master_dem, y = covid, by.x = "CaregiverID", by.y = "CaregiverID")

num_responses = function(x){length(which(!is.na(x)))}
covid.num <- covid %>%
  group_by(Week) %>%
  summarize_all(num_responses) %>%
  gather("Variable", "num_responses",-Week) %>%
  mutate(week = paste0("Week", Week),
         week = factor(Week, levels = paste0("Week", c(1:total_week)))) %>%
  spread(Week, num_responses)
```

# 1. Suspect/Diagnose COVID

  * Have you been suspected or diagnosed with COVID-19?\
    + Yes, suspected\
    + Yes, diagnosed with a positive test result\
    + Yes, diagnosed by a healthcare professional or public health official without a test\
    + No\
    
```{r, echo=FALSE, message = FALSE, warning = FALSE}
CaregiverID_fl <- master%>%
  group_by (CaregiverID)%>%
  summarise (SurveyType = my.max (SurveyType))%>%
  ungroup()%>%
  filter (SurveyType == 2)%>%
  select (CaregiverID)

CaregiverID_fl <- as.character (CaregiverID_fl$CaregiverID)
  
covid_fl <- covid %>%
  filter (CaregiverID %in% CaregiverID_fl)
```

## 1.1 Most recent responses
### 1.1.1 Overall
```{r, echo=FALSE, message = FALSE, warning = FALSE}

covid_dg <- covid_fl %>%
  group_by (CaregiverID) %>%
  summarise (COVID.001 = my.max(COVID.001)) %>%
  mutate (diagnosis = ifelse(COVID.001 %in% c(1,2,3), 1, 0),
          suspect = ifelse (COVID.001 == 1, 1, 0), 
          test_positive = ifelse (COVID.001 == 2, 1, 0), 
          diagnose_no_test = ifelse (COVID.001 == 3, 1, 0), 
          no = ifelse (COVID.001 == 0, 1, 0))
covid_dg <- merge (x = master_dem, y = covid_dg, by.x = "CaregiverID", by.y = "CaregiverID")

covid_dg_smy <- covid_dg %>%
  summarise (n = n(),
             a.diagnosis = sum(diagnosis, na.rm = TRUE)/n, 
             b.no = sum(no, na.rm = TRUE)/n,
             a.suspect = sum(suspect, na.rm = TRUE)/n, 
             a.test_positive = sum(test_positive, na.rm = TRUE)/n, 
             a.diagnose_no_test = sum(diagnose_no_test, na.rm = TRUE)/n) %>%
  pivot_longer (cols = c("a.diagnosis", "b.no", "a.suspect", "a.test_positive", "a.diagnose_no_test"), names_to = "condition", values_to = "prop") %>%
  mutate (count = n*prop) %>%
  mutate (moe = map2_dbl(prop, n, moe.p))

covid_dg_smy %>%
  filter (condition != "a.diagnosis")%>%
  ggplot(mapping = aes (x = condition, y = prop*100, fill = condition)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = (prop*100-moe*100), 
                    ymax = (prop*100+moe*100)),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -1, color = "black",  position = position_dodge(1))

```

### 1.1.2 Race/Ethnicity
 
```{r, echo=FALSE, message = FALSE, warning = FALSE}
covid_dg_smy <- covid_dg %>%
  filter (race_ethnic != "NA") %>%
  group_by (race_ethnic) %>%
  summarise (n = n(),
             a.diagnosis = sum(diagnosis, na.rm = TRUE)/n, 
             b.no = sum(no, na.rm = TRUE)/n,
             a.suspect = sum(suspect, na.rm = TRUE)/n, 
             a.test_positive = sum(test_positive, na.rm = TRUE)/n, 
             a.diagnose_no_test = sum(diagnose_no_test, na.rm = TRUE)/n) %>%
  pivot_longer (cols = c("a.diagnosis", "b.no", "a.suspect", "a.test_positive", "a.diagnose_no_test"), names_to = "condition", values_to = "prop") %>%
  mutate (count = n*prop) %>%
  mutate (moe = map2_dbl(prop, n, moe.p))

covid_dg_smy %>%
  filter (condition != "a.diagnosis")%>%
  ggplot(mapping = aes (x = race_ethnic, y = prop*100, fill = race_ethnic)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = (prop*100-moe*100), 
                    ymax = (prop*100+moe*100)),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -1, size = 3, color = "black",  position = position_dodge(1))+
  facet_wrap(~condition, ncol = 4)

```

```{r, results='hide', echo = FALSE, message=FALSE, warning = FALSE}
pairwise.prop.test(x = covid_dg_smy$count, n = covid_dg_smy$n, p.adjust.method = "holm")
```

### 1.1.3 Poverty Level

```{r, echo=FALSE, message = FALSE, warning = FALSE}
covid_dg_smy <- covid_dg %>%
  filter (poverty_cat != "NA") %>%
  group_by (poverty_cat) %>%
  summarise (n = n(),
             a.diagnosis = sum(diagnosis, na.rm = TRUE)/n, 
             b.no = sum(no, na.rm = TRUE)/n,
             a.suspect = sum(suspect, na.rm = TRUE)/n, 
             a.test_positive = sum(test_positive, na.rm = TRUE)/n, 
             a.diagnose_no_test = sum(diagnose_no_test, na.rm = TRUE)/n) %>%
  pivot_longer (cols = c("a.diagnosis", "b.no", "a.suspect", "a.test_positive", "a.diagnose_no_test"), names_to = "condition", values_to = "prop") %>%
  mutate (count = n*prop) %>%
  mutate (moe = map2_dbl(prop, n, moe.p))

covid_dg_smy %>%
  filter (condition != "a.diagnosis")%>%
  ggplot(mapping = aes (x = poverty_cat, y = prop*100, fill = poverty_cat)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = (prop*100-moe*100), 
                    ymax = (prop*100+moe*100)),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -1, size = 3, color = "black",  position = position_dodge(1))+
  facet_wrap(~condition, ncol = 4)
```

```{r, results='hide', echo = FALSE, message=FALSE, warning = FALSE}
pairwise.prop.test(x = covid_dg_smy$count, n = covid_dg_smy$n, p.adjust.method = "holm")
```

### 1.1.4 Poverty Level & race/ethnicity

```{r, echo=FALSE, message = FALSE, warning = FALSE}
covid_dg_smy <- covid_dg %>%
  filter (poverty_cat != "NA" & race_ethnic!= "NA") %>%
  group_by (poverty_cat, race_ethnic) %>%
  summarise (n = n(),
             a.diagnosis = sum(diagnosis, na.rm = TRUE)/n, 
             b.no = sum(no, na.rm = TRUE)/n,
             a.suspect = sum(suspect, na.rm = TRUE)/n, 
             a.test_positive = sum(test_positive, na.rm = TRUE)/n, 
             a.diagnose_no_test = sum(diagnose_no_test, na.rm = TRUE)/n) %>%
  pivot_longer (cols = c("a.diagnosis", "b.no", "a.suspect", "a.test_positive", "a.diagnose_no_test"), names_to = "condition", values_to = "prop") %>%
  mutate (count = n*prop) %>%
  mutate (moe = map2_dbl(prop, n, moe.p))

covid_dg_smy %>%
  filter (condition != "a.diagnosis")%>%
  ggplot(mapping = aes (x = condition, y = prop*100, fill = condition)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = (prop*100-moe*100), 
                    ymax = (prop*100+moe*100)),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -1, size = 3, color = "black",  position = position_dodge(1))+
  facet_wrap(poverty_cat~race_ethnic, ncol = 3)
```

## 1.2 Trend
### 1.2.1 Overall
```{r, echo=FALSE, message = FALSE, warning = FALSE}

covid_fl <- covid_fl %>%
  mutate (suspect = ifelse (COVID.001 == 1, 1, 0), 
          test_positive = ifelse (COVID.001 == 2, 1, 0), 
          diagnose_no_test = ifelse (COVID.001 == 3, 1, 0), 
          no = ifelse (COVID.001 == 0, 1, 0))

covid_trend <- covid_fl %>%
  filter (SurveyType == 2)%>%
  group_by (Week)%>%
  summarise (n = n(),
             b.no = sum(no, na.rm = TRUE)/n,
             a.suspect = sum(suspect, na.rm = TRUE)/n, 
             a.test_positive = sum(test_positive, na.rm = TRUE)/n, 
             a.diagnose_no_test = sum(diagnose_no_test, na.rm = TRUE)/n, 
            date = as.Date(min (StartDate))) %>%
  pivot_longer (cols = c("b.no", "a.suspect", "a.test_positive", "a.diagnose_no_test"), names_to = "condition", values_to = "prop") %>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")

covid_trend %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = condition)) +
  geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  labs (y = "Percentage")+
  ggtitle(label = "Trend of changes")

```

### 1.2.2 By race/ethnicity
```{r, echo=FALSE, message = FALSE, warning = FALSE}

covid_trend <- covid_fl %>%
  filter (SurveyType == 2 & race_ethnic!= "NA")%>%
  group_by (Week, race_ethnic)%>%
  summarise (n = n(),
             b.no = sum(no, na.rm = TRUE)/n,
             a.suspect = sum(suspect, na.rm = TRUE)/n, 
             a.test_positive = sum(test_positive, na.rm = TRUE)/n, 
             a.diagnose_no_test = sum(diagnose_no_test, na.rm = TRUE)/n, 
            date = as.Date(min (StartDate))) %>%
  pivot_longer (cols = c("b.no", "a.suspect", "a.test_positive", "a.diagnose_no_test"), names_to = "condition", values_to = "prop") %>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")

covid_trend %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = condition)) +
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  labs (y = "Percentage")+
  ggtitle(label = "Trend of changes")+
  facet_wrap(~race_ethnic)

```

### 1.2.3 By poverty level
```{r, echo=FALSE, message = FALSE, warning = FALSE}

covid_trend <- covid_fl %>%
  filter (SurveyType == 2 & poverty_cat!= "NA")%>%
  group_by (Week, poverty_cat)%>%
  summarise (n = n(),
             b.no = sum(no, na.rm = TRUE)/n,
             a.suspect = sum(suspect, na.rm = TRUE)/n, 
             a.test_positive = sum(test_positive, na.rm = TRUE)/n, 
             a.diagnose_no_test = sum(diagnose_no_test, na.rm = TRUE)/n, 
            date = as.Date(min (StartDate))) %>%
  pivot_longer (cols = c("b.no", "a.suspect", "a.test_positive", "a.diagnose_no_test"), names_to = "condition", values_to = "prop") %>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")

covid_trend %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = condition)) +
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  labs (y = "Percentage")+
  ggtitle(label = "Trend of changes")+
  facet_wrap(~poverty_cat)

```

### 1.2.4 By poverty level & race/ethnicity
```{r, echo=FALSE, message = FALSE, warning = FALSE}

covid_trend <- covid_fl %>%
  filter (SurveyType == 2 & poverty_cat!= "NA" & race_ethnic != "NA")%>%
  group_by (Week, poverty_cat, race_ethnic)%>%
  summarise (n = n(),
             b.no = sum(no, na.rm = TRUE)/n,
             a.suspect = sum(suspect, na.rm = TRUE)/n, 
             a.test_positive = sum(test_positive, na.rm = TRUE)/n, 
             a.diagnose_no_test = sum(diagnose_no_test, na.rm = TRUE)/n, 
            date = as.Date(min (StartDate))) %>%
  pivot_longer (cols = c("b.no", "a.suspect", "a.test_positive", "a.diagnose_no_test"), names_to = "condition", values_to = "prop") %>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")

covid_trend %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = condition)) +
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  labs (y = "Percentage")+
  ggtitle(label = "Trend of changes")+
  facet_wrap(poverty_cat~race_ethnic, nrow = 2)

```

# 2. Know Anyone Diagnosed/hospitalized with COVID
  * Survey question: Do you personally know anyone in the U.S. who... - Has been officially diagnosed as having COVID-19 by a health care provider - yes/no\
  * Do you personally know anyone in the U.S. who... - Has been hospitalized or died as a result of having COVID-19 - yes/no\
  
## 2.1 Most recent responses
### 2.1.1 Overall

```{r, echo=FALSE, message = FALSE, warning = FALSE}
covid_know_dg <- covid %>%
  filter (Week %in% c(29, 31, 33, 35, 37, 39, 41, 43, 45))%>%
  group_by (CaregiverID) %>%
  filter (Week == max(Week))%>%
  ungroup()%>%
  summarise (n = n(),
             know_diagnose = sum(COVID.003, na.rm = TRUE)/n, 
             know_hospitalized_died = sum (COVID.004, na.rm = T)/n, 
             date = as.Date(min (StartDate))) %>%
  pivot_longer (cols = c("know_diagnose", "know_hospitalized_died"), names_to = "condition", values_to = "prop") %>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")
  
covid_know_dg %>%
  ggplot(mapping = aes (x = condition, y = prop*100, fill = condition)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = (prop*100-moe*100), 
                    ymax = (prop*100+moe*100)),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -1, size = 3, color = "black",  position = position_dodge(1))
```

### 2.1.2 By race/ethnicity

```{r, echo=FALSE, message = FALSE, warning = FALSE}
covid_know_dg <- covid %>%
  filter (Week %in% c(29, 31, 33, 35, 37, 39, 41, 43, 45))%>%
  group_by (CaregiverID) %>%
  filter (Week == max(Week))%>%
  ungroup()%>%
  filter (race_ethnic!= "NA")%>%
  group_by (race_ethnic)%>%
  summarise (n = n(),
             know_diagnose = sum(COVID.003, na.rm = TRUE)/n, 
             know_hospitalized_died = sum (COVID.004, na.rm = T)/n, 
             date = as.Date(min (StartDate))) %>%
  pivot_longer (cols = c("know_diagnose", "know_hospitalized_died"), names_to = "condition", values_to = "prop") %>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")
  
covid_know_dg %>%
  ggplot(mapping = aes (x = race_ethnic, y = prop*100, fill = race_ethnic)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = (prop*100-moe*100), 
                    ymax = (prop*100+moe*100)),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -1, size = 3, color = "black",  position = position_dodge(1))+
  facet_wrap (~condition, ncol = 2)
```

### 2.1.3 By poverty level

```{r, echo=FALSE, message = FALSE, warning = FALSE}
covid_know_dg <- covid %>%
  filter (Week %in% c(29, 31, 33, 35, 37, 39, 41, 43, 45))%>%
  group_by (CaregiverID) %>%
  filter (Week == max(Week))%>%
  ungroup()%>%
  filter (poverty_cat!= "NA")%>%
  group_by (poverty_cat)%>%
  summarise (n = n(),
             know_diagnose = sum(COVID.003, na.rm = TRUE)/n, 
             know_hospitalized_died = sum (COVID.004, na.rm = T)/n, 
             date = as.Date(min (StartDate))) %>%
  pivot_longer (cols = c("know_diagnose", "know_hospitalized_died"), names_to = "condition", values_to = "prop") %>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")
  
covid_know_dg %>%
  ggplot(mapping = aes (x = poverty_cat, y = prop*100, fill = poverty_cat)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = (prop*100-moe*100), 
                    ymax = (prop*100+moe*100)),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -1, size = 3, color = "black",  position = position_dodge(1))+
  facet_wrap (~condition, ncol = 2)
```

### 2.1.4 By poverty level & race/ethnicity

```{r, echo=FALSE, message = FALSE, warning = FALSE}
covid_know_dg <- covid %>%
  filter (Week %in% c(29, 31, 33, 35, 37, 39, 41, 43, 45))%>%
  group_by (CaregiverID) %>%
  filter (Week == max(Week))%>%
  ungroup()%>%
  filter (poverty_cat!= "NA" & race_ethnic != "NA")%>%
  group_by (poverty_cat, race_ethnic)%>%
  summarise (n = n(),
             know_diagnose = sum(COVID.003, na.rm = TRUE)/n, 
             know_hospitalized_died = sum (COVID.004, na.rm = T)/n, 
             date = as.Date(min (StartDate))) %>%
  pivot_longer (cols = c("know_diagnose", "know_hospitalized_died"), names_to = "condition", values_to = "prop") %>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")
  
covid_know_dg %>%
  ggplot(mapping = aes (x = race_ethnic, y = prop*100, fill = poverty_cat)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = (prop*100-moe*100), 
                    ymax = (prop*100+moe*100)),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -1, size = 3, color = "black",  position = position_dodge(1))+
  facet_wrap (~condition, ncol = 2)
```

## 2.2 Trend

### 2.2.1 Overall

```{r, echo=FALSE, message = FALSE, warning = FALSE}
covid_know_dg <- covid %>%
  filter (Week %in% c(29, 31, 33, 35, 37, 39, 41, 43, 45))%>%
  group_by (Week)%>%
  summarise (n = n(),
             know_diagnose = sum(COVID.003, na.rm = TRUE)/n, 
             know_hospitalized_died = sum (COVID.004, na.rm = T)/n, 
             date = as.Date(min (StartDate))) %>%
  pivot_longer (cols = c("know_diagnose", "know_hospitalized_died"), names_to = "condition", values_to = "prop") %>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")
  
covid_know_dg %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = condition)) +
  geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  labs (y = "Percentage")+
  ggtitle(label = "Trend of changes")
```

### 2.2.2 By race/ethnicity

```{r, echo=FALSE, message = FALSE, warning = FALSE}
covid_know_dg <- covid %>%
  filter (Week %in% c(29, 31, 33, 35, 37, 39, 41, 43, 45) & race_ethnic!= "NA")%>%
  group_by (Week, race_ethnic)%>%
  summarise (n = n(),
             know_diagnose = sum(COVID.003, na.rm = TRUE)/n, 
             know_hospitalized_died = sum (COVID.004, na.rm = T)/n, 
             date = as.Date(min (StartDate))) %>%
  pivot_longer (cols = c("know_diagnose", "know_hospitalized_died"), names_to = "condition", values_to = "prop") %>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")
  
covid_know_dg %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = condition)) +
  geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  labs (y = "Percentage")+
  ggtitle(label = "Trend of changes")+
  facet_wrap(~race_ethnic, ncol = 3)
```

### 2.2.3 By poverty level

```{r, echo=FALSE, message = FALSE, warning = FALSE}
covid_know_dg <- covid %>%
  filter (Week %in% c(29, 31, 33, 35, 37, 39, 41, 43, 45) & poverty_cat!= "NA")%>%
  group_by (Week, poverty_cat)%>%
  summarise (n = n(),
             know_diagnose = sum(COVID.003, na.rm = TRUE)/n, 
             know_hospitalized_died = sum (COVID.004, na.rm = T)/n, 
             date = as.Date(min (StartDate))) %>%
  pivot_longer (cols = c("know_diagnose", "know_hospitalized_died"), names_to = "condition", values_to = "prop") %>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")
  
covid_know_dg %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = condition)) +
  geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  labs (y = "Percentage")+
  ggtitle(label = "Trend of changes")+
  facet_wrap(~poverty_cat, ncol = 2)
```

### 2.2.4 By poverty level & race/ethnicity

```{r, echo=FALSE, message = FALSE, warning = FALSE}
covid_know_dg <- covid %>%
  filter (Week %in% c(29, 31, 33, 35, 37, 39, 41, 43, 45) & poverty_cat!= "NA" & race_ethnic != "NA")%>%
  group_by (Week, poverty_cat, race_ethnic)%>%
  summarise (n = n(),
             know_diagnose = sum(COVID.003, na.rm = TRUE)/n, 
             know_hospitalized_died = sum (COVID.004, na.rm = T)/n, 
             date = as.Date(min (StartDate))) %>%
  pivot_longer (cols = c("know_diagnose", "know_hospitalized_died"), names_to = "condition", values_to = "prop") %>%
  mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")
  
covid_know_dg %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = condition)) +
  geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  labs (y = "Percentage")+
  ggtitle(label = "Trend of changes")+
  facet_wrap(poverty_cat ~ race_ethnic, ncol = 3)
```