---
title: "Charting the curve"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r curve-1, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
#re-run all the machine learning models?
rerun = FALSE
dontrerun = !rerun
```

```{r curve-2 }
library(conflicted)
library(here)
library(ggpubr)
#library(tidymodels)
library(brolgar)
library(lme4)
#library(modelr)
library(caret)
library(knitr)
library(kableExtra)
conflict_prefer("group_rows", "kableExtra")
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")
library(sjPlot)
```

```{r curve-3 }
if(rerun) options(mc.cores = parallel::detectCores())
```


```{r curve-4 }
source(here("Scripts/score data.R")) 
```


```{r curve-5 }
#Center emotion variables on caregiver baseline (Week 0)
# identify "baseline" values
baseline = scored %>%
  filter(Week == 0) %>% # only Week 0
  select(CaregiverID, anxiety, depress, stress, lonely, fussy, fear) #only these variables
names(baseline)[-1] = paste(names(baseline)[-1], "pre", sep = "_")  # rename

emotion = scored %>%
  select(CaregiverID, Week, anxiety, depress, stress, lonely, fussy, fear) %>% #only these variables
  filter(Week > 0 & Week <= 10) %>% # remove week 0 and any week after 10
  full_join(baseline) %>% # join with baseline data -- creates columns of "pre" variables
  gather(key, value, -CaregiverID, -Week) %>% 
  mutate(time = ifelse(grepl("_pre", key), "Pre", "Now"),
         key = gsub("_pre","",key)) %>%
  spread(time, value) %>% #now one row per emotion per week per caregiver
  mutate(value = Now-Pre) %>% # subtract
  select(-Now, -Pre) %>% # remove extra variables
  spread(key, value) # now one row per week per caregiver
```

```{r curve-6 }
groups = scored %>%
  group_by(CaregiverID) %>%
  filter(Week == min(Week)) %>%
  ungroup() %>%
  select(CaregiverID, black, poverty150, single, latinx, disability) %>%
  mutate_at(vars(-CaregiverID), 
            .funs = function(x) 1-x) %>%
  mutate_at(vars(-CaregiverID), factor)

emotion_g = full_join(emotion, groups)

contrasts(emotion_g$black) = contr.sum(2)
contrasts(emotion_g$poverty150) = contr.sum(2)
contrasts(emotion_g$single) = contr.sum(2)
contrasts(emotion_g$latinx) = contr.sum(2)

```

# Representativeness disclaimer

```{r curve-7 }
n_care = length(unique(emotion$CaregiverID))
date.min = format(min(as.Date(scored$Date), na.rm = T), format = "%B %d, %Y")
date.max = format(max(as.Date(scored$Date), na.rm = T), format = "%B %d, %Y")
perc = scored %>%
  group_by(CaregiverID) %>%
  filter(Week == max(Week))
perc.black = 100*sum(perc$black, na.rm=T)/nrow(perc)
perc.latinx = 100*sum(perc$latinx, na.rm=T)/nrow(perc)
perc.fpl = 100*sum(perc$poverty150, na.rm=T)/nrow(perc)
```

These analyses are based on responses collected from `r papaja::printnum(n_care, format = "d")` caregivers between the dates of `r date.min` and `r date.max`. These caregivers represent a range of voices: `r papaja::printnum(perc.black)`\% are Black/African American, `r papaja::printnum(perc.latinx)`\% are LatinX, and `r papaja::printnum(perc.fpl)`\% live at or below 1.5 times the federal poverty line. Proportions/percentages are calculated based on the item-level response rates, not out of the total sample size. The data for these analyses are *not* weighted.

# Descriptives

```{r curve-8 }
emotion_g %>%
  select_if(is.numeric) %>%
  psych::describeBy(group = emotion_g$Week, fast = T) 
```



<!-- # Plots{.tabset} -->

<!-- ```{r} -->
<!-- emotion.p <- as_tsibble(emotion, -->
<!--                       index = Week, -->
<!--                       key = CaregiverID, -->
<!--                       regular = FALSE) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- control = lmerControl(check.conv.grad = F, check.nobs.vs.nRE = F) -->
<!-- ``` -->



<!-- ## Anxiety -->

<!-- ```{r} -->
<!-- anxiety_fit <- lmer(anxiety ~ Week + (1 + Week|CaregiverID),  -->
<!--                     data = emotion,  -->
<!--                     control = lmerControl( -->
<!--                       check.conv.grad = "ignore", -->
<!--                       check.nobs.vs.nlev = "ignore")) -->
<!-- emotion %>% -->
<!--   add_predictions(anxiety_fit, type = "pred") %>% -->
<!--   ggplot(aes(x = Week, y = anxiety)) + -->
<!--   geom_smooth(method = "loess", se= F) + -->
<!--   facet_strata(along = -anxiety) -->
<!-- ``` -->


# Polynomials

## Identify best model

```{r curve-9 }
source(here("Functions/curves.R"))
```


```{r curve-10, eval = F}
emotion.recipe = recipe(anxiety + depress + stress + lonely + fussy + fear ~ Week, data = emotion)
emotion.prepped = bake(emotion.recipe, emotion)

anx_fit1 = linear_reg() %>%
  set_engine(engine = "lm") %>%
  fit(anxiety ~ poly(Week, 1), data = emotion.prepped)

anx_fit2 = linear_reg() %>%
  set_engine(engine = "lm") %>%
  fit(anxiety ~ poly(Week, 2), data = emotion.prepped)

anx_fit3 = linear_reg() %>%
  set_engine(engine = "lm") %>%
  fit(anxiety ~ poly(Week, 3), data = emotion.prepped)

anx_fit4 = linear_reg() %>%
  set_engine(engine = "lm") %>%
  fit(anxiety ~ poly(Week, 4), data = emotion.prepped)

  
```


```{r curve-11 }
if(rerun){
  set.seed(115)
  
  fit_models = emotion %>%
    gather("emotion", "value", -CaregiverID, -Week) %>%
    filter(!is.na(value)) %>%
    group_by(emotion) %>%
    nest() %>%
    mutate(train1 = map(data, train_fun, 1),
           train2 = map(data, train_fun, 2),
           train3 = map(data, train_fun, 3),
           train4 = map(data, train_fun, 4))
  
  train_perf = fit_models %>%
    gather("model", "output", contains("train")) %>%
    mutate(performance = map(output, "results")) 
  
  
  save(fit_models, train_perf, file = here("curve_data/fit_models.Rdata"))
}
```

```{r curve-12 }
if(dontrerun){load(file = here("curve_data/fit_models.Rdata"))}
```

```{r curve-13, results = 'asis'}
train_perf %>%
  dplyr::select(emotion, model, performance) %>%
  unnest(cols = c(performance)) %>%
  dplyr::select(-intercept, -contains("SD")) %>%
  arrange(emotion, model) %>%
  mutate(model = factor(model,
                        levels = paste0("train",1:4),
                        labels = c("Linear", "Quadratic", "Cubic", "Quartic"))) %>%
  ungroup() %>%
  dplyr::select(-emotion) %>%
  kable(., digits = 4) %>%
  kable_styling(full_width = T) %>%
  group_rows("Anxiety", 1,4) %>%
  group_rows("Depression", 5,8) %>%
  group_rows("Child Internalizing", 9,12) %>%
  group_rows("Child Externalizing", 13,16) %>%
  group_rows("Loneliness", 17,20) %>%
  group_rows("Stress", 21,24)
```

Based on these results, we will run the following models:

- anxiety: quartic
- depression:quadratic
- stress: linear
- loneliness: linear
- child externalizing: linear
- child internalizing: linear

## Anxiety{.tabset}

### Overall

```{r curve-14 }
overall = overall_model(emotion, anxiety, 4)
overall$plot
```

### Black/African American

```{r curve-15 }
group = group_model(emotion_g, anxiety, black, 4)
group$plot
```

```{r curve-16, results = 'asis'}
group$summary
```

### Latinx

```{r curve-17 }
group = group_model(emotion_g, anxiety, latinx, 4)
group$plot
```

```{r curve-18, results = 'asis'}
group$summary
```

### Poverty

```{r curve-19 }
group = group_model(emotion_g, anxiety, poverty150, 4)
group$plot
```

```{r curve-20, results = 'asis'}
group$summary
```

### Single Parents

```{r curve-21 }
group = group_model(emotion_g, anxiety, single, 4)
group$plot
```

```{r curve-22, results = 'asis'}
group$summary
```

### Children with disabilites

```{r curve-23 }
group = group_model(emotion_g, anxiety, disability, 4)
group$plot
```

```{r curve-24, results = 'asis'}
group$summary
```



## Depression{.tabset}

### Overall

```{r curve-25 }
overall = overall_model(emotion, depress, 2)
overall$plot
```

### Black/African American

```{r curve-26 }
group = group_model(emotion_g, depress, black, 2)
group$plot
```

```{r curve-27, results = 'asis'}
group$summary
```

### Latinx

```{r curve-28 }
group = group_model(emotion_g, depress, latinx, 2)
group$plot
```

```{r curve-29, results = 'asis'}
group$summary
```

### Poverty

```{r curve-30 }
group = group_model(emotion_g, depress, poverty150, 2)
group$plot
```

```{r curve-31, results = 'asis'}
group$summary
```

### Single Parents

```{r curve-32 }
group = group_model(emotion_g, depress, single, 2)
group$plot
```

```{r curve-33, results = 'asis'}
group$summary
```

### Children with disabilites

```{r curve-34 }
group = group_model(emotion_g, depress, disability, 2)
group$plot
```

```{r curve-35, results = 'asis'}
group$summary
```

## Stress{.tabset}

### Overall

```{r curve-36 }
overall = overall_model(emotion, stress, 1)
overall$plot
```

### Black/African American

```{r curve-37 }
group = group_model(emotion_g, stress, black, 1)
group$plot
```


```{r curve-38, results = 'asis'}
group$summary
```

### Latinx

```{r curve-39 }
group = group_model(emotion_g, stress, latinx, 1)
group$plot
```


```{r curve-40, results = 'asis'}
group$summary
```

### Poverty

```{r curve-41 }
group = group_model(emotion_g, stress, poverty150, 1)
group$plot
```

```{r curve-42, results = 'asis'}
group$summary
```

### Single Parents

```{r curve-43 }
group = group_model(emotion_g, stress, single, 1)
group$plot
```

```{r curve-44, results = 'asis'}
group$summary
```

### Children with disabilites

```{r curve-45 }
group = group_model(emotion_g, stress, disability, 1)
group$plot
```

```{r curve-46, results = 'asis'}
group$summary
```

## Loneliness{.tabset}

### Overall

```{r curve-47 }
overall = overall_model(emotion, lonely, 1)
overall$plot
```

### Black/African American

```{r curve-48 }
group = group_model(emotion_g, lonely, black, 1)
group$plot
```

```{r curve-49, results = 'asis'}
group$summary
```

### Latinx

```{r curve-50 }
group = group_model(emotion_g, lonely, latinx, 1)
group$plot
```

```{r curve-51, results = 'asis'}
group$summary
```

### Poverty

```{r curve-52 }
group = group_model(emotion_g, lonely, poverty150, 1)
group$plot
```

```{r curve-53, results = 'asis'}
group$summary
```

### Single Parents

```{r curve-54 }
group = group_model(emotion_g, lonely, single, 1)
group$plot
```

```{r curve-55, results = 'asis'}
group$summary
```

### Children with disabilites

```{r curve-56 }
group = group_model(emotion_g, lonely, disability, 1)
group$plot
```

```{r curve-57, results = 'asis'}
group$summary
```

## Child Externalizing{.tabset}

### Overall

```{r curve-58 }
overall = overall_model(emotion, fussy, 1)
overall$plot
```

### Black/African American

```{r curve-59 }
group = group_model(emotion_g, fussy, black, 1)
group$plot
```

```{r curve-60, results = 'asis'}
group$summary
```

### Latinx

```{r curve-61 }
group = group_model(emotion_g, fussy, latinx, 1)
group$plot
```

```{r curve-62, results = 'asis'}
group$summary
```

### Poverty

```{r curve-63 }
group = group_model(emotion_g, fussy, poverty150, 1)
group$plot
```

```{r curve-64, results = 'asis'}
group$summary
```

### Single Parents

```{r curve-65 }
group = group_model(emotion_g, fussy, single, 1)
group$plot
```

```{r curve-66, results = 'asis'}
group$summary
```

### Children with disabilites

```{r curve-67 }
group = group_model(emotion_g, fussy, disability, 1)
group$plot
```

```{r curve-68, results = 'asis'}
group$summary
```

## Child Internalizing{.tabset}

### Overall

```{r curve-69 }
overall = overall_model(emotion, fear, 1)
overall$plot
```

### Black/African American

```{r curve-70 }
group = group_model(emotion_g, fear, black, 1)
group$plot
```

```{r curve-71, results = 'asis'}
group$summary
```

### Latinx

```{r curve-72 }
group = group_model(emotion_g, fear, latinx, 1)
group$plot
```

```{r curve-73, results = 'asis'}
group$summary
```

### Poverty

```{r curve-74 }
group = group_model(emotion_g, fear, poverty150, 1)
group$plot
```

```{r curve-75, results = 'asis'}
group$summary
```

### Single Parents

```{r curve-76 }
group = group_model(emotion_g, fear, single, 1)
group$plot
```

```{r curve-77, results = 'asis'}
group$summary
```

### Children with disabilites

```{r curve-78 }
group = group_model(emotion_g, fear, disability, 1)
group$plot
```

```{r curve-79, results = 'asis'}
group$summary
```

# Spline models

Spline models are fit with nodes at Week 7, which is the week ending on May 25th, 2020.


## Anxiety{.tabset}

### Overall

```{r curve-80 }
fit = splines.overall(emotion_g, anxiety, 7)
fit$plot
```

```{r curve-81, results = 'asis'}
fit$summary
```

### Black/African American

```{r curve-82 }
fit = splines.groups(emotion_g, anxiety, black, 7)
fit$plot
```

```{r curve-83, results = 'asis'}
fit$summary
```

### LatinX

```{r curve-84 }
fit = splines.groups(emotion_g, anxiety, latinx, 7)
fit$plot
```

```{r curve-85, results = 'asis'}
fit$summary
```

### Poverty

```{r curve-86 }
fit = splines.groups(emotion_g, anxiety, poverty150, 7)
fit$plot
```

```{r curve-87, results = 'asis'}
fit$summary
```

### Single Parents

```{r curve-88 }
fit = splines.groups(emotion_g, anxiety, single, 7)
fit$plot
```

```{r curve-89, results = 'asis'}
fit$summary
```

### Children with disabilites

```{r curve-90 }
fit = splines.groups(emotion_g, anxiety, disability, 7)
fit$plot
```

```{r curve-91, results = 'asis'}
fit$summary
```

## Depression{.tabset}

### Overall

```{r curve-92 }
fit = splines.overall(emotion_g, depress, 7)
fit$plot
```

```{r curve-93, results = 'asis'}
fit$summary
```

### Black/African American

```{r curve-94 }
fit = splines.groups(emotion_g, depress, black, 7)
fit$plot
```

```{r curve-95, results = 'asis'}
fit$summary
```

### LatinX

```{r curve-96 }
fit = splines.groups(emotion_g, depress, latinx, 7)
fit$plot
```

```{r curve-97, results = 'asis'}
fit$summary
```

### Poverty

```{r curve-98 }
fit = splines.groups(emotion_g, depress, poverty150, 7)
fit$plot
```

```{r curve-99, results = 'asis'}
fit$summary
```

### Single Parents

```{r curve-100 }
fit = splines.groups(emotion_g, depress, single, 7)
fit$plot
```

```{r curve-101, results = 'asis'}
fit$summary
```

### Children with disabilites

```{r curve-102 }
fit = splines.groups(emotion_g, depress, disability, 7)
fit$plot
```

```{r curve-103, results = 'asis'}
fit$summary
```

## Stress{.tabset}

### Overall

```{r curve-104 }
fit = splines.overall(emotion_g, stress, 7)
fit$plot
```

```{r curve-105, results = 'asis'}
fit$summary
```

### Black/African American

```{r curve-106 }
fit = splines.groups(emotion_g, stress, black, 7)
fit$plot
```

```{r curve-107, results = 'asis'}
fit$summary
```

### LatinX

```{r curve-108 }
fit = splines.groups(emotion_g, stress, latinx, 7)
fit$plot
```

```{r curve-109, results = 'asis'}
fit$summary
```

### Poverty

```{r curve-110 }
fit = splines.groups(emotion_g, stress, poverty150, 7)
fit$plot
```

```{r curve-111, results = 'asis'}
fit$summary
```

### Single Parents

```{r curve-112 }
fit = splines.groups(emotion_g, stress, single, 7)
fit$plot
```

```{r curve-113, results = 'asis'}
fit$summary
```

### Children with disabilites

```{r curve-114 }
fit = splines.groups(emotion_g, stress, disability, 7)
fit$plot
```

```{r curve-115, results = 'asis'}
fit$summary
```

## Loneliness{.tabset}

### Overall

```{r curve-116 }
fit = splines.overall(emotion_g, lonely, 7)
fit$plot
```

```{r curve-117, results = 'asis'}
fit$summary
```

### Black/African American

```{r curve-118 }
fit = splines.groups(emotion_g, lonely, black, 7)
fit$plot
```

```{r curve-119, results = 'asis'}
fit$summary
```

### LatinX

```{r curve-120 }
fit = splines.groups(emotion_g, lonely, latinx, 7)
fit$plot
```

```{r curve-121, results = 'asis'}
fit$summary
```

### Poverty

```{r curve-122 }
fit = splines.groups(emotion_g, lonely, poverty150, 7)
fit$plot
```

```{r curve-123, results = 'asis'}
fit$summary
```

### Single Parents

```{r curve-124 }
fit = splines.groups(emotion_g, lonely, single, 7)
fit$plot
```

```{r curve-125, results = 'asis'}
fit$summary
```

### Children with disabilites

```{r curve-126 }
fit = splines.groups(emotion_g, lonely, disability, 7)
fit$plot
```

```{r curve-127, results = 'asis'}
fit$summary
```

## Child Externalizing{.tabset}

### Overall

```{r curve-128 }
fit = splines.overall(emotion_g, fussy, 7)
fit$plot
```

```{r curve-129, results = 'asis'}
fit$summary
```

### Black/African American

```{r curve-130 }
fit = splines.groups(emotion_g, fussy, black, 7)
fit$plot
```

```{r curve-131, results = 'asis'}
fit$summary
```

### LatinX

```{r curve-132 }
fit = splines.groups(emotion_g, fussy, latinx, 7)
fit$plot
```

```{r curve-133, results = 'asis'}
fit$summary
```

### Poverty

```{r curve-134 }
fit = splines.groups(emotion_g, fussy, poverty150, 7)
fit$plot
```

```{r curve-135, results = 'asis'}
fit$summary
```

### Single Parents

```{r curve-136 }
fit = splines.groups(emotion_g, fussy, single, 7)
fit$plot
```

```{r curve-137, results = 'asis'}
fit$summary
```

### Children with disabilites

```{r curve-138 }
fit = splines.groups(emotion_g, fussy, disability, 7)
fit$plot
```

```{r curve-139, results = 'asis'}
fit$summary
```

## Child Internalizing{.tabset}

### Overall

```{r curve-140 }
fit = splines.overall(emotion_g, fear, 7)
fit$plot
```

```{r curve-141, results = 'asis'}
fit$summary
```

### Black/African American

```{r curve-142 }
fit = splines.groups(emotion_g, fear, black, 7)
fit$plot
```

```{r curve-143, results = 'asis'}
fit$summary
```

### LatinX

```{r curve-144 }
fit = splines.groups(emotion_g, fear, latinx, 7)
fit$plot
```

```{r curve-145, results = 'asis'}
fit$summary
```

### Poverty

```{r curve-146 }
fit = splines.groups(emotion_g, fear, poverty150, 7)
fit$plot
```

```{r curve-147, results = 'asis'}
fit$summary
```

### Single Parents

```{r curve-148 }
fit = splines.groups(emotion_g, fear, single, 7)
fit$plot
```

```{r curve-149, results = 'asis'}
fit$summary
```

### Children with disabilites

```{r curve-150 }
fit = splines.groups(emotion_g, fear, disability, 7)
fit$plot
```

```{r curve-151, results = 'asis'}
fit$summary
```
