---
title: "Charting the curve"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r curve-1, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
#re-run all the machine learning models?
rerun = FALSE
dontrerun = !rerun
```

```{r curve-2 }
library(conflicted)
library(here)
library(ggpubr)
#library(tidymodels)
library(brolgar)
library(lme4)
#library(modelr)
library(caret)
library(knitr)
library(kableExtra)
conflict_prefer("group_rows", "kableExtra")
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")
library(sjPlot)
```

```{r curve-3 }
if(rerun) options(mc.cores = parallel::detectCores())
```


```{r curve-4 }
source(here("Scripts/score data.R")) 
```

```{r curve-9 }
source(here("Functions/curves.R"))
```

```{r curve-5 }
#Center emotion variables on caregiver baseline (Week 0)
# identify "baseline" values
baseline = scored %>%
  filter(Week == 0) %>% # only Week 0
  select(CaregiverID, anxiety, depress, stress, lonely, fussy, fear) #only these variables
names(baseline)[-1] = paste(names(baseline)[-1], "pre", sep = "_")  # rename

emotion = scored %>%
  select(CaregiverID, Week, anxiety, depress, stress, lonely, fussy, fear) %>% #only these variables
  filter(Week > 0 & Week <= 10) %>% # remove week 0 and any week after 10
  full_join(baseline) %>% # join with baseline data -- creates columns of "pre" variables
  gather(key, value, -CaregiverID, -Week) %>% 
  mutate(time = ifelse(grepl("_pre", key), "Pre", "Now"),
         key = gsub("_pre","",key)) %>%
  spread(time, value) %>% #now one row per emotion per week per caregiver
  #mutate(value = Now-Pre) %>% # subtract
  mutate(value = Now) %>% # subtract
  select(-Now, -Pre) %>% # remove extra variables
  spread(key, value) # now one row per week per caregiver
```

```{r curve-6 }
groups = scored %>%
  group_by(CaregiverID) %>%
  filter(Week == min(Week)) %>%
  ungroup() %>%
  mutate(child2 = ifelse(num_children_raw >= 2, 1, 0),
         child3 = ifelse(num_children_raw >= 3, 1, 0)) %>%
  select(CaregiverID, black, poverty150, single, latinx, disability,
         child2, child3) %>%
  # mutate_at(vars(-CaregiverID), 
  #           .funs = function(x) 1-x) %>%
  mutate_at(vars(-CaregiverID), factor)

emotion_g = full_join(emotion, groups)
# 
# contrasts(emotion_g$black) = contr.sum(2)
# contrasts(emotion_g$poverty150) = contr.sum(2)
# contrasts(emotion_g$single) = contr.sum(2)
# contrasts(emotion_g$latinx) = contr.sum(2)
# contrasts(emotion_g$child2) = contr.sum(2)
# contrasts(emotion_g$child3) = contr.sum(2)
```

# Representativeness disclaimer

```{r curve-7 }
n_care = length(unique(emotion$CaregiverID))
date.min = format(min(as.Date(scored$Date), na.rm = T), format = "%B %d, %Y")
date.max = format(max(as.Date(scored$Date), na.rm = T), format = "%B %d, %Y")
perc = scored %>%
  group_by(CaregiverID) %>%
  filter(Week == max(Week))
perc.black = 100*sum(perc$black, na.rm=T)/nrow(perc)
perc.latinx = 100*sum(perc$latinx, na.rm=T)/nrow(perc)
perc.fpl = 100*sum(perc$poverty150, na.rm=T)/nrow(perc)
```

These analyses are based on responses collected from `r papaja::printnum(n_care, format = "d")` caregivers between the dates of `r date.min` and `r date.max`. These caregivers represent a range of voices: `r papaja::printnum(perc.black)`\% are Black/African American, `r papaja::printnum(perc.latinx)`\% are LatinX, and `r papaja::printnum(perc.fpl)`\% live at or below 1.5 times the federal poverty line. Proportions/percentages are calculated based on the item-level response rates, not out of the total sample size. The data for these analyses are *not* weighted.

# Descriptives

```{r curve-8 }
emotion_g %>%
  select_if(is.numeric) %>%
  psych::describeBy(group = emotion_g$Week, fast = T) 
```



<!-- # Plots{.tabset} -->

<!-- ```{r} -->
<!-- emotion.p <- as_tsibble(emotion, -->
<!--                       index = Week, -->
<!--                       key = CaregiverID, -->
<!--                       regular = FALSE) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- control = lmerControl(check.conv.grad = F, check.nobs.vs.nRE = F) -->
<!-- ``` -->



<!-- ## Anxiety -->

<!-- ```{r} -->
<!-- anxiety_fit <- lmer(anxiety ~ Week + (1 + Week|CaregiverID),  -->
<!--                     data = emotion,  -->
<!--                     control = lmerControl( -->
<!--                       check.conv.grad = "ignore", -->
<!--                       check.nobs.vs.nlev = "ignore")) -->
<!-- emotion %>% -->
<!--   add_predictions(anxiety_fit, type = "pred") %>% -->
<!--   ggplot(aes(x = Week, y = anxiety)) + -->
<!--   geom_smooth(method = "loess", se= F) + -->
<!--   facet_strata(along = -anxiety) -->
<!-- ``` -->


<!-- # Polynomials -->

<!-- ## Identify best model -->


<!-- ```{r curve-10, eval = F} -->
<!-- emotion.recipe = recipe(anxiety + depress + stress + lonely + fussy + fear ~ Week, data = emotion) -->
<!-- emotion.prepped = bake(emotion.recipe, emotion) -->

<!-- anx_fit1 = linear_reg() %>% -->
<!--   set_engine(engine = "lm") %>% -->
<!--   fit(anxiety ~ poly(Week, 1), data = emotion.prepped) -->

<!-- anx_fit2 = linear_reg() %>% -->
<!--   set_engine(engine = "lm") %>% -->
<!--   fit(anxiety ~ poly(Week, 2), data = emotion.prepped) -->

<!-- anx_fit3 = linear_reg() %>% -->
<!--   set_engine(engine = "lm") %>% -->
<!--   fit(anxiety ~ poly(Week, 3), data = emotion.prepped) -->

<!-- anx_fit4 = linear_reg() %>% -->
<!--   set_engine(engine = "lm") %>% -->
<!--   fit(anxiety ~ poly(Week, 4), data = emotion.prepped) -->


<!-- ``` -->


<!-- ```{r curve-11 } -->
<!-- if(rerun){ -->
<!--   set.seed(115) -->

<!--   fit_models = emotion %>% -->
<!--     gather("emotion", "value", -CaregiverID, -Week) %>% -->
<!--     filter(!is.na(value)) %>% -->
<!--     group_by(emotion) %>% -->
<!--     nest() %>% -->
<!--     mutate(train1 = map(data, train_fun, 1), -->
<!--            train2 = map(data, train_fun, 2), -->
<!--            train3 = map(data, train_fun, 3), -->
<!--            train4 = map(data, train_fun, 4)) -->

<!--   train_perf = fit_models %>% -->
<!--     gather("model", "output", contains("train")) %>% -->
<!--     mutate(performance = map(output, "results"))  -->


<!--   save(fit_models, train_perf, file = here("curve_data/fit_models_means.Rdata")) -->
<!-- } -->
<!-- ``` -->

<!-- ```{r curve-12 } -->
<!-- if(dontrerun){load(file = here("curve_data/fit_models_means.Rdata"))} -->
<!-- ``` -->

<!-- ```{r curve-13, results = 'asis'} -->
<!-- train_perf %>% -->
<!--   dplyr::select(emotion, model, performance) %>% -->
<!--   unnest(cols = c(performance)) %>% -->
<!--   dplyr::select(-intercept, -contains("SD")) %>% -->
<!--   arrange(emotion, model) %>% -->
<!--   mutate(model = factor(model, -->
<!--                         levels = paste0("train",1:4), -->
<!--                         labels = c("Linear", "Quadratic", "Cubic", "Quartic"))) %>% -->
<!--   ungroup() %>% -->
<!--   dplyr::select(-emotion) %>% -->
<!--   kable(., digits = 4) %>% -->
<!--   kable_styling(full_width = T) %>% -->
<!--   group_rows("Anxiety", 1,4) %>% -->
<!--   group_rows("Depression", 5,8) %>% -->
<!--   group_rows("Child Internalizing", 9,12) %>% -->
<!--   group_rows("Child Externalizing", 13,16) %>% -->
<!--   group_rows("Loneliness", 17,20) %>% -->
<!--   group_rows("Stress", 21,24) -->
<!-- ``` -->

<!-- Based on these results, we will run the following models: -->

<!-- - anxiety: quartic -->
<!-- - depression: quadratic -->
<!-- - stress: linear -->
<!-- - loneliness: quadratic -->
<!-- - child externalizing: linear -->
<!-- - child internalizing: linear -->

<!-- ## Anxiety{.tabset} -->

<!-- ### Overall -->

<!-- ```{r curve-14 } -->
<!-- overall = overall_model(emotion, anxiety, 4) -->
<!-- overall$plot -->
<!-- ``` -->

<!-- ### Black/African American -->

<!-- ```{r curve-15 } -->
<!-- group = group_model(emotion_g, anxiety, black, 4) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-16, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Latinx -->

<!-- ```{r curve-17 } -->
<!-- group = group_model(emotion_g, anxiety, latinx, 4) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-18, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Poverty -->

<!-- ```{r curve-19 } -->
<!-- group = group_model(emotion_g, anxiety, poverty150, 4) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-20, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Single Parents -->

<!-- ```{r curve-21 } -->
<!-- group = group_model(emotion_g, anxiety, single, 4) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-22, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Children with disabilites -->

<!-- ```{r curve-23 } -->
<!-- group = group_model(emotion_g, anxiety, disability, 4) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-24, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### 3+ Children -->

<!-- ```{r curve-25 } -->
<!-- group = group_model(emotion_g, anxiety, child3, 4) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-26, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->



<!-- ## Depression{.tabset} -->

<!-- ### Overall -->

<!-- ```{r curve-27 } -->
<!-- overall = overall_model(emotion, depress, 2) -->
<!-- overall$plot -->
<!-- ``` -->

<!-- ### Black/African American -->

<!-- ```{r curve-28 } -->
<!-- group = group_model(emotion_g, depress, black, 2) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-29, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Latinx -->

<!-- ```{r curve-30 } -->
<!-- group = group_model(emotion_g, depress, latinx, 2) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-31, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Poverty -->

<!-- ```{r curve-32 } -->
<!-- group = group_model(emotion_g, depress, poverty150, 2) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-33, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Single Parents -->

<!-- ```{r curve-34 } -->
<!-- group = group_model(emotion_g, depress, single, 2) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-35, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Children with disabilites -->

<!-- ```{r curve-36 } -->
<!-- group = group_model(emotion_g, depress, disability, 2) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-37, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### 3+ Children -->

<!-- ```{r curve-38 } -->
<!-- group = group_model(emotion_g, depress, child3, 2) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-39, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ## Stress{.tabset} -->

<!-- ### Overall -->

<!-- ```{r curve-40 } -->
<!-- overall = overall_model(emotion, stress, 1) -->
<!-- overall$plot -->
<!-- ``` -->

<!-- ### Black/African American -->

<!-- ```{r curve-41 } -->
<!-- group = group_model(emotion_g, stress, black, 1) -->
<!-- group$plot -->
<!-- ``` -->


<!-- ```{r curve-42, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Latinx -->

<!-- ```{r curve-43 } -->
<!-- group = group_model(emotion_g, stress, latinx, 1) -->
<!-- group$plot -->
<!-- ``` -->


<!-- ```{r curve-44, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Poverty -->

<!-- ```{r curve-45 } -->
<!-- group = group_model(emotion_g, stress, poverty150, 1) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-46, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Single Parents -->

<!-- ```{r curve-47 } -->
<!-- group = group_model(emotion_g, stress, single, 1) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-48, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Children with disabilites -->

<!-- ```{r curve-49 } -->
<!-- group = group_model(emotion_g, stress, disability, 1) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-50, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### 3+ Children -->

<!-- ```{r curve-51 } -->
<!-- group = group_model(emotion_g, stress, child3, 1) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-52, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ## Loneliness{.tabset} -->

<!-- ### Overall -->

<!-- ```{r curve-53 } -->
<!-- overall = overall_model(emotion, lonely, 2) -->
<!-- overall$plot -->
<!-- ``` -->

<!-- ### Black/African American -->

<!-- ```{r curve-54 } -->
<!-- group = group_model(emotion_g, lonely, black, 2) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-55, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Latinx -->

<!-- ```{r curve-56 } -->
<!-- group = group_model(emotion_g, lonely, latinx, 2) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-57, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Poverty -->

<!-- ```{r curve-58 } -->
<!-- group = group_model(emotion_g, lonely, poverty150, 2) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-59, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Single Parents -->

<!-- ```{r curve-60 } -->
<!-- group = group_model(emotion_g, lonely, single, 2) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-61, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Children with disabilites -->

<!-- ```{r curve-62 } -->
<!-- group = group_model(emotion_g, lonely, disability, 2) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-63, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### 3+ Children -->

<!-- ```{r curve-64 } -->
<!-- group = group_model(emotion_g, lonely, child3, 2) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-65, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ## Child Externalizing{.tabset} -->

<!-- ### Overall -->

<!-- ```{r curve-66 } -->
<!-- overall = overall_model(emotion, fussy, 1) -->
<!-- overall$plot -->
<!-- ``` -->

<!-- ### Black/African American -->

<!-- ```{r curve-67 } -->
<!-- group = group_model(emotion_g, fussy, black, 1) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-68, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Latinx -->

<!-- ```{r curve-69 } -->
<!-- group = group_model(emotion_g, fussy, latinx, 1) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-70, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Poverty -->

<!-- ```{r curve-71 } -->
<!-- group = group_model(emotion_g, fussy, poverty150, 1) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-72, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Single Parents -->

<!-- ```{r curve-73 } -->
<!-- group = group_model(emotion_g, fussy, single, 1) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-74, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Children with disabilites -->

<!-- ```{r curve-75 } -->
<!-- group = group_model(emotion_g, fussy, disability, 1) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-76, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### 3+ Children -->

<!-- ```{r curve-77 } -->
<!-- group = group_model(emotion_g, fussy, child3, 1) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-78, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ## Child Internalizing{.tabset} -->

<!-- ### Overall -->

<!-- ```{r curve-79 } -->
<!-- overall = overall_model(emotion, fear, 1) -->
<!-- overall$plot -->
<!-- ``` -->

<!-- ### Black/African American -->

<!-- ```{r curve-80 } -->
<!-- group = group_model(emotion_g, fear, black, 1) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-81, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Latinx -->

<!-- ```{r curve-82 } -->
<!-- group = group_model(emotion_g, fear, latinx, 1) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-83, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Poverty -->

<!-- ```{r curve-84 } -->
<!-- group = group_model(emotion_g, fear, poverty150, 1) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-85, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Single Parents -->

<!-- ```{r curve-86 } -->
<!-- group = group_model(emotion_g, fear, single, 1) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-87, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### Children with disabilites -->

<!-- ```{r curve-88 } -->
<!-- group = group_model(emotion_g, fear, disability, 1) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-89, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

<!-- ### 3+ Children -->

<!-- ```{r curve-90 } -->
<!-- group = group_model(emotion_g, fear, child3, 1) -->
<!-- group$plot -->
<!-- ``` -->

<!-- ```{r curve-91, results = 'asis'} -->
<!-- group$summary -->
<!-- ``` -->

# Spline models

<!-- Spline models are fit with nodes at Week 7, which is the week ending on May 25th, 2020. -->


## Anxiety{.tabset}

### Overall

```{r curve-92 }
fit = splines.overall(emotion_g, anxiety, 2)
fit$plot
```

```{r curve-93, results = 'asis'}
fit$summary
```

### Black/African American

```{r curve-94 }
fit = splines.groups(emotion_g, anxiety, black, 2)
fit$plot
```

```{r curve-95, results = 'asis'}
fit$summary
```

### LatinX

```{r curve-96 }
fit = splines.groups(emotion_g, anxiety, latinx, 2)
fit$plot
```

```{r curve-97, results = 'asis'}
fit$summary
```

### Poverty

```{r curve-98 }
fit = splines.groups(emotion_g, anxiety, poverty150, 2)
fit$plot
```

```{r curve-99, results = 'asis'}
fit$summary
```

### Single Parents

```{r curve-100 }
fit = splines.groups(emotion_g, anxiety, single, 2)
fit$plot
```

```{r curve-101, results = 'asis'}
fit$summary
```

### Children with disabilites

```{r curve-102 }
fit = splines.groups(emotion_g, anxiety, disability, 2)
fit$plot
```

```{r curve-103, results = 'asis'}
fit$summary
```

### 3+ Children

```{r curve-104 }
fit = splines.groups(emotion_g, anxiety, child3, 2)
fit$plot
```

```{r curve-105, results = 'asis'}
fit$summary
```

## Depression{.tabset}

### Overall

```{r curve-106 }
fit = splines.overall(emotion_g, depress, 2)
fit$plot
```

```{r curve-107, results = 'asis'}
fit$summary
```

### Black/African American

```{r curve-108 }
fit = splines.groups(emotion_g, depress, black, 2)
fit$plot
```

```{r curve-109, results = 'asis'}
fit$summary
```

### LatinX

```{r curve-110 }
fit = splines.groups(emotion_g, depress, latinx, 2)
fit$plot
```

```{r curve-111, results = 'asis'}
fit$summary
```

### Poverty

```{r curve-112 }
fit = splines.groups(emotion_g, depress, poverty150, 2)
fit$plot
```

```{r curve-113, results = 'asis'}
fit$summary
```

### Single Parents

```{r curve-114 }
fit = splines.groups(emotion_g, depress, single, 2)
fit$plot
```

```{r curve-115, results = 'asis'}
fit$summary
```

### Children with disabilites

```{r curve-116 }
fit = splines.groups(emotion_g, depress, disability, 2)
fit$plot
```

```{r curve-117, results = 'asis'}
fit$summary
```

### 3+ Children

```{r curve-118 }
fit = splines.groups(emotion_g, depress, child3, 2)
fit$plot
```

```{r curve-119, results = 'asis'}
fit$summary
```

## Stress{.tabset}

### Overall

```{r curve-120 }
fit = splines.overall(emotion_g, stress, 2)
fit$plot
```

```{r curve-121, results = 'asis'}
fit$summary
```

### Black/African American

```{r curve-122 }
fit = splines.groups(emotion_g, stress, black, 2)
fit$plot
```

```{r curve-123, results = 'asis'}
fit$summary
```

### LatinX

```{r curve-124 }
fit = splines.groups(emotion_g, stress, latinx, 2)
fit$plot
```

```{r curve-125, results = 'asis'}
fit$summary
```

### Poverty

```{r curve-126 }
fit = splines.groups(emotion_g, stress, poverty150, 2)
fit$plot
```

```{r curve-127, results = 'asis'}
fit$summary
```

### Single Parents

```{r curve-128 }
fit = splines.groups(emotion_g, stress, single, 2)
fit$plot
```

```{r curve-129, results = 'asis'}
fit$summary
```

### Children with disabilites

```{r curve-130 }
fit = splines.groups(emotion_g, stress, disability, 2)
fit$plot
```

```{r curve-131, results = 'asis'}
fit$summary
```

### 3+ Children

```{r curve-132 }
fit = splines.groups(emotion_g, stress, child3, 2)
fit$plot
```

```{r curve-133, results = 'asis'}
fit$summary
```

## Loneliness{.tabset}

### Overall

```{r curve-134 }
fit = splines.overall(emotion_g, lonely, 2)
fit$plot
```

```{r curve-135, results = 'asis'}
fit$summary
```

### Black/African American

```{r curve-136 }
fit = splines.groups(emotion_g, lonely, black, 2)
fit$plot
```

```{r curve-137, results = 'asis'}
fit$summary
```

### LatinX

```{r curve-138 }
fit = splines.groups(emotion_g, lonely, latinx, 2)
fit$plot
```

```{r curve-139, results = 'asis'}
fit$summary
```

### Poverty

```{r curve-140 }
fit = splines.groups(emotion_g, lonely, poverty150, 2)
fit$plot
```

```{r curve-141, results = 'asis'}
fit$summary
```

### Single Parents

```{r curve-142 }
fit = splines.groups(emotion_g, lonely, single, 2)
fit$plot
```

```{r curve-143, results = 'asis'}
fit$summary
```

### Children with disabilites

```{r curve-144 }
fit = splines.groups(emotion_g, lonely, disability, 2)
fit$plot
```

```{r curve-145, results = 'asis'}
fit$summary
```

### 3+ Children

```{r curve-146 }
fit = splines.groups(emotion_g, lonely, child3, 2)
fit$plot
```

```{r curve-147, results = 'asis'}
fit$summary
```

## Child Externalizing{.tabset}

### Overall

```{r curve-148 }
fit = splines.overall(emotion_g, fussy, 2)
fit$plot
```

```{r curve-149, results = 'asis'}
fit$summary
```

### Black/African American

```{r curve-150 }
fit = splines.groups(emotion_g, fussy, black, 2)
fit$plot
```

```{r curve-151, results = 'asis'}
fit$summary
```

### LatinX

```{r curve-152 }
fit = splines.groups(emotion_g, fussy, latinx, 2)
fit$plot
```

```{r curve-153, results = 'asis'}
fit$summary
```

### Poverty

```{r curve-154 }
fit = splines.groups(emotion_g, fussy, poverty150, 2)
fit$plot
```

```{r curve-155, results = 'asis'}
fit$summary
```

### Single Parents

```{r curve-156 }
fit = splines.groups(emotion_g, fussy, single, 2)
fit$plot
```

```{r curve-157, results = 'asis'}
fit$summary
```

### Children with disabilites

```{r curve-158 }
fit = splines.groups(emotion_g, fussy, disability, 2)
fit$plot
```

```{r curve-159, results = 'asis'}
fit$summary
```

### 3+ Children

```{r curve-160 }
fit = splines.groups(emotion_g, fussy, child3, 2)
fit$plot
```

```{r curve-161, results = 'asis'}
fit$summary
```

## Child Internalizing{.tabset}

### Overall

```{r curve-162 }
fit = splines.overall(emotion_g, fear, 2)
fit$plot
```

```{r curve-163, results = 'asis'}
fit$summary
```

### Black/African American

```{r curve-164 }
fit = splines.groups(emotion_g, fear, black, 2)
fit$plot
```

```{r curve-165, results = 'asis'}
fit$summary
```

### LatinX

```{r curve-166 }
fit = splines.groups(emotion_g, fear, latinx, 2)
fit$plot
```

```{r curve-167, results = 'asis'}
fit$summary
```

### Poverty

```{r curve-168 }
fit = splines.groups(emotion_g, fear, poverty150, 2)
fit$plot
```

```{r curve-169, results = 'asis'}
fit$summary
```

### Single Parents

```{r curve-170 }
fit = splines.groups(emotion_g, fear, single, 2)
fit$plot
```

```{r curve-171, results = 'asis'}
fit$summary
```

### Children with disabilites

```{r curve-172 }
fit = splines.groups(emotion_g, fear, disability, 2)
fit$plot
```

```{r curve-173, results = 'asis'}
fit$summary
```

### 3+ Children

```{r curve-174 }
fit = splines.groups(emotion_g, fear, child3, 2)
fit$plot
```

```{r curve-175, results = 'asis'}
fit$summary
```

