---
title: "Charting the curve"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r chunk 1, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
#re-run all the machine learning models?
rerun = FALSE
dontrerun = !rerun
```

```{r packages}
library(conflicted)
library(here)
library(ggpubr)
#library(tidymodels)
library(brolgar)
library(lme4)
#library(modelr)
library(caret)
library(knitr)
library(kableExtra)
conflict_prefer("group_rows", "kableExtra")
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")
library(sjPlot)
```

```{r curve-1}
options(mc.cores = parallel::detectCores())
```


```{r load data}
source(here("Scripts/score data.R")) 
```


```{r curve-2}
#Center emotion variables on caregiver baseline (Week 0)
# identify "baseline" values
baseline = scored %>%
  filter(Week == 0) %>% # only Week 0
  select(CaregiverID, anxiety, depress, stress, lonely, fussy, fear) #only these variables
names(baseline)[-1] = paste(names(baseline)[-1], "pre", sep = "_")  # rename

emotion = scored %>%
  select(CaregiverID, Week, anxiety, depress, stress, lonely, fussy, fear) %>% #only these variables
  filter(Week > 0 | Week <= 10) %>% # remove week 0 and any week after 10
  full_join(baseline) %>% # join with baseline data -- creates columns of "pre" variables
  gather(key, value, -CaregiverID, -Week) %>% 
  mutate(time = ifelse(grepl("_pre", key), "Pre", "Now"),
         key = gsub("_pre","",key)) %>%
  spread(time, value) %>% #now one row per emotion per week per caregiver
  mutate(value = Now-Pre) %>% # subtract
  select(-Now, -Pre) %>% # remove extra variables
  spread(key, value) # now one row per week per caregiver
```

```{r}
groups = scored %>%
  group_by(CaregiverID) %>%
  filter(Week == min(Week)) %>%
  ungroup() %>%
  select(CaregiverID, black, poverty150, single, latinx) %>%
  mutate_at(vars(-CaregiverID), 
            .funs = function(x) 1-x) %>%
  mutate_at(vars(-CaregiverID), factor)

emotion_g = full_join(emotion, groups)

contrasts(emotion_g$black) = contr.sum(2)
contrasts(emotion_g$poverty150) = contr.sum(2)
contrasts(emotion_g$single) = contr.sum(2)
contrasts(emotion_g$latinx) = contr.sum(2)

```

# Representativeness disclaimer

```{r}
n_care = length(unique(emotion$CaregiverID))
date.min = format(min(as.Date(scored$Date), na.rm = T), format = "%B %d, %Y")
date.max = format(max(as.Date(scored$Date), na.rm = T), format = "%B %d, %Y")
perc = scored %>%
  group_by(CaregiverID) %>%
  filter(Week == max(Week))
perc.black = 100*sum(perc$black, na.rm=T)/nrow(perc)
perc.latinx = 100*sum(perc$latinx, na.rm=T)/nrow(perc)
perc.fpl = 100*sum(perc$poverty150, na.rm=T)/nrow(perc)
```

These analyses are based on responses collected from `r papaja::printnum(n_care, format = "d")` caregivers between the dates of `r date.min` and `r date.max`. These caregivers represent a range of voices: `r papaja::printnum(perc.black)`\% are Black/African American, `r papaja::printnum(perc.latinx)`\% are LatinX, and `r papaja::printnum(perc.fpl)`\% live at or below 1.5 times the federal poverty line.  The data for these analyses are *not* weighted.

# Descriptives

```{r}
emotion_g %>%
  select_if(is.numeric) %>%
  psych::describeBy(group = emotion_g$Week, fast = T) 
```



<!-- # Plots{.tabset} -->

<!-- ```{r} -->
<!-- emotion.p <- as_tsibble(emotion, -->
<!--                       index = Week, -->
<!--                       key = CaregiverID, -->
<!--                       regular = FALSE) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- control = lmerControl(check.conv.grad = F, check.nobs.vs.nRE = F) -->
<!-- ``` -->



<!-- ## Anxiety -->

<!-- ```{r} -->
<!-- anxiety_fit <- lmer(anxiety ~ Week + (1 + Week|CaregiverID),  -->
<!--                     data = emotion,  -->
<!--                     control = lmerControl( -->
<!--                       check.conv.grad = "ignore", -->
<!--                       check.nobs.vs.nlev = "ignore")) -->
<!-- emotion %>% -->
<!--   add_predictions(anxiety_fit, type = "pred") %>% -->
<!--   ggplot(aes(x = Week, y = anxiety)) + -->
<!--   geom_smooth(method = "loess", se= F) + -->
<!--   facet_strata(along = -anxiety) -->
<!-- ``` -->


# Identify best model

```{r curve-3}
source(here("Functions/curves.R"))
```


```{r curve-4, eval = F}
emotion.recipe = recipe(anxiety + depress + stress + lonely + fussy + fear ~ Week, data = emotion)
emotion.prepped = bake(emotion.recipe, emotion)

anx_fit1 = linear_reg() %>%
  set_engine(engine = "lm") %>%
  fit(anxiety ~ poly(Week, 1), data = emotion.prepped)

anx_fit2 = linear_reg() %>%
  set_engine(engine = "lm") %>%
  fit(anxiety ~ poly(Week, 2), data = emotion.prepped)

anx_fit3 = linear_reg() %>%
  set_engine(engine = "lm") %>%
  fit(anxiety ~ poly(Week, 3), data = emotion.prepped)

anx_fit4 = linear_reg() %>%
  set_engine(engine = "lm") %>%
  fit(anxiety ~ poly(Week, 4), data = emotion.prepped)

  
```


```{r curve-5, eval = rerun}
set.seed(115)

fit_models = emotion %>%
  gather("emotion", "value", -CaregiverID, -Week) %>%
  filter(!is.na(value)) %>%
  group_by(emotion) %>%
  nest() %>%
  mutate(train1 = map(data, train_fun, 1),
         train2 = map(data, train_fun, 2),
         train3 = map(data, train_fun, 3),
         train4 = map(data, train_fun, 4))

train_perf = fit_models %>%
  gather("model", "output", contains("train")) %>%
  mutate(performance = map(output, "results")) 


save(fit_models, train_perf, file = here("curve_data/fit_models.Rdata"))
```

```{r curve-6, eval = dontrerun}
load(file = here("curve_data/fit_models.Rdata"))
```

```{r curve-7, results = 'asis'}
train_perf %>%
  dplyr::select(emotion, model, performance) %>%
  unnest(cols = c(performance)) %>%
  dplyr::select(-intercept, -contains("SD")) %>%
  arrange(emotion, model) %>%
  mutate(model = factor(model,
                        levels = paste0("train",1:4),
                        labels = c("Linear", "Quadratic", "Cubic", "Quartic"))) %>%
  ungroup() %>%
  dplyr::select(-emotion) %>%
  kable(., digits = 4) %>%
  kable_styling(full_width = T) %>%
  group_rows("Anxiety", 1,4) %>%
  group_rows("Depression", 5,8) %>%
  group_rows("Child Internalizing", 9,12) %>%
  group_rows("Child Externalizing", 13,16) %>%
  group_rows("Loneliness", 17,20) %>%
  group_rows("Stress", 21,24)
```

Based on these results, we will run the following models:

- anxiety: quartic
- depression:quadratic
- stress: quadtratic
- loneliness: linear
- child externalizing: linear
- child internalizing: linear

# Anxiety{.tabset}

## Overall

```{r curve-8}
overall = overall_model(emotion, anxiety, 4)
overall$plot
```

## Black/African American

```{r}
group = group_model(emotion_g, anxiety, black, 4)
group$plot
```

```{r, results = 'asis'}
group$summary
```

## Latinx

```{r}
group = group_model(emotion_g, anxiety, latinx, 4)
group$plot
```

```{r, results = 'asis'}
group$summary
```

## Poverty

```{r}
group = group_model(emotion_g, anxiety, poverty150, 4)
group$plot
```

```{r, results = 'asis'}
group$summary
```

## Single Parents

```{r}
group = group_model(emotion_g, anxiety, single, 4)
group$plot
```

```{r, results = 'asis'}
group$summary
```



# Depression{.tabset}

## Overall

```{r curve-9}
overall = overall_model(emotion, depress, 2)
overall$plot
```

## Black/African American

```{r}
group = group_model(emotion_g, depress, black, 2)
group$plot
```

```{r, results = 'asis'}
group$summary
```

## Latinx

```{r}
group = group_model(emotion_g, depress, latinx, 2)
group$plot
```

```{r, results = 'asis'}
group$summary
```

## Poverty

```{r}
group = group_model(emotion_g, depress, poverty150, 2)
group$plot
```

```{r, results = 'asis'}
group$summary
```

## Single Parents

```{r}
group = group_model(emotion_g, depress, single, 2)
group$plot
```

```{r, results = 'asis'}
group$summary
```

# Stress{.tabset}

## Overall

```{r curve-10}
overall = overall_model(emotion, stress, 2)
overall$plot
```

## Black/African American

```{r}
group = group_model(emotion_g, stress, black, 2)
group$plot
```


```{r, results = 'asis'}
group$summary
```

## Latinx

```{r}
group = group_model(emotion_g, stress, latinx, 2)
group$plot
```


```{r, results = 'asis'}
group$summary
```

## Poverty

```{r}
group = group_model(emotion_g, stress, poverty150, 2)
group$plot
```

```{r, results = 'asis'}
group$summary
```

## Single Parents

```{r}
group = group_model(emotion_g, stress, single, 2)
group$plot
```

```{r, results = 'asis'}
group$summary
```

# Loneliness{.tabset}

## Overall

```{r curve-11}
overall = overall_model(emotion, lonely, 1)
overall$plot
```

## Black/African American

```{r}
group = group_model(emotion_g, lonely, black, 1)
group$plot
```

```{r, results = 'asis'}
group$summary
```

## Latinx

```{r}
group = group_model(emotion_g, lonely, latinx, 1)
group$plot
```

```{r, results = 'asis'}
group$summary
```

## Poverty

```{r}
group = group_model(emotion_g, lonely, poverty150, 1)
group$plot
```

```{r, results = 'asis'}
group$summary
```

## Single Parents

```{r}
group = group_model(emotion_g, lonely, single, 1)
group$plot
```

```{r, results = 'asis'}
group$summary
```

# Child Externalizing{.tabset}

## Overall

```{r curve-12}
overall = overall_model(emotion, fussy, 1)
overall$plot
```

## Black/African American

```{r}
group = group_model(emotion_g, fussy, black, 1)
group$plot
```

```{r, results = 'asis'}
group$summary
```

## Latinx

```{r}
group = group_model(emotion_g, fussy, latinx, 1)
group$plot
```

```{r, results = 'asis'}
group$summary
```

## Poverty

```{r}
group = group_model(emotion_g, fussy, poverty150, 1)
group$plot
```

```{r, results = 'asis'}
group$summary
```

## Single Parents

```{r}
group = group_model(emotion_g, fussy, single, 1)
group$plot
```

```{r, results = 'asis'}
group$summary
```

# Child Internalizing{.tabset}

## Overall

```{r curve-13}
overall = overall_model(emotion, fear, 1)
overall$plot
```

## Black/African American

```{r}
group = group_model(emotion_g, fear, black, 1)
group$plot
```

```{r, results = 'asis'}
group$summary
```

## Latinx

```{r}
group = group_model(emotion_g, fear, latinx, 1)
group$plot
```

```{r, results = 'asis'}
group$summary
```

## Poverty

```{r}
group = group_model(emotion_g, fear, poverty150, 1)
group$plot
```

```{r, results = 'asis'}
group$summary
```

## Single Parents

```{r}
group = group_model(emotion_g, fear, single, 1)
group$plot
```

```{r, results = 'asis'}
group$summary
```
