---
title: "Caregivers of children with disabilities"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
  
---

Please note that lines by date and days sheltering in place are smoothed curves -- they may be poor representations of the data in locations with few participants. For example, the largest number of days sheltering in place only applies to a small portion of participants; lines representing small demographic groups at these large should not be interpreted. 

```{r chunk 1, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
```

```{r packages}
library(here)
library(tidyverse)
library(knitr)
library(kableExtra)
library(haven)
# require(devtools)
# install_version("zipcode", version = "1.0", repos = "http://cran.us.r-project.org")
library(zipcode)
library(ggthemr)
library(corx)
library(papaja)
library(zoo)
library(ggpubr)
```


```{r score datafile, echo = F, warning = F, message = F}
# score master --------------------------------------------------------
source(here("Scripts/score data.R"))
scored = scored %>%
  filter(Week > 0)
```

```{rchunk 2}
total_weeks = max(scored$Week, na.rm=T)
```

# Well-being during shelter-in-place 

```{r}
source(here("Functions/trend_days_sheltering_rolling.R"))
```
## Compared to general population {.tabset}

### Caregiver anxiety

```{r anxiety}
anxiety_plot = trend_days_sheltering_binary(variable = "anxiety_current_some",
                                     dataset = scored, 
                                     label = "some or a lot of anxiety",
                                     groups = c("disability"),
                                     group_labels = "Parents of children with disabilities")
anxiety_plot$plot
```

### Caregiver depression

```{r depress}
depress_plot = trend_days_sheltering_binary(variable = "depress_current_some",
                                     dataset = scored, 
                                     label = "some or a lot of depression",
                                     groups = c("disability"),
                                     group_labels = "Parents of children with disabilities")
depress_plot$plot
```

### Caregiver stress

```{r stress}
stress_plot = trend_days_sheltering_binary(variable = "stress_current_some",
                                     dataset = scored, 
                                     label = "some or a lot of stress",
                                     groups = c("disability"),
                                     group_labels = "Parents of children with disabilities")
stress_plot$plot
```


### Caregiver loneliness

```{r }
lonely_plot = trend_days_sheltering_binary(variable = "lonely_current_some",
                                     dataset = scored, 
                                     label = "some or a lot of loneliness",
                                     groups = c("disability"),
                                     group_labels = "Parents of children with disabilities")
lonely_plot$plot
```

### Child externalizing

```{r fussy}
fussy_plot = trend_days_sheltering_binary(variable = "fussy_current_some",
                                     dataset = scored, 
                                     label = "children are sometimes or often fussy or defiant",
                                     groups = c("disability"),
                                     group_labels = "Parents of children with disabilities")
fussy_plot$plot
```



### Child internalizing

```{r fear}
fear_plot = trend_days_sheltering_binary(variable = "fear_current_some",
                                     dataset = scored, 
                                     label = "children are sometimes or often fearful or anxious",
                                     groups = c("disability"),
                                     group_labels = "Parents of children with disabilities")
fear_plot$plot
```

## By poverty level {.tabset}


```{r}
disability = scored %>%
  filter(disability == 1) 

pov.tabs = xtabs(~ poverty, data = disability)
```

Of the `r nrow(disability)` caregivers of children with a disability, `r pov.tabs[2]` report an income below the poverty threshold for their household size and `r pov.tabs[1]` report an income above the threshold. 

```{r}
disability %>%
  select(poverty, anxiety, depress, stress, fussy, fear) %>%
  gather("emotion", "value", -poverty) %>%
  filter(!is.nan(value) & !is.na(poverty) & !is.na(value)) %>%
  group_by(poverty, emotion) %>%
  summarize(n = n(),
            m = mean(value),
            s = sd(value),
            t = qt(p = .975, df = n-1),
            moe = t*(s/sqrt(n))) %>%
  ungroup() %>%
  mutate(emotion = factor(emotion, 
                          levels = c("anxiety", "depress", "stress", "fussy", "fear"),
                          labels = c("Caregiver anxiety", 
                                     "Caregiver depression", 
                                     "Caregiver stress", 
                                     "Child externalizing", "Child internalizing")),
         poverty = factor(poverty, levels = c(0,1), 
                          labels = c("Above poverty threshold","Below poverty threshold"))) %>%
  ggplot(aes(x = emotion, y = m, fill = poverty)) + 
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(min = m-moe, max = m+moe), position = position_dodge(1), width = .5) +
  coord_flip() +
  labs(x = "",
      y = "Average response",
      title = "Well-being in families") + 
  theme_minimal()
```


## By geographic region {.tabset}


### Caregiver anxiety

```{r}
disability %>%
  filter(!is.na(region)) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "anxiety",
          desc_stat = "mean_ci")
```


```{r region anxiety}
anxiety_plot = trend_days_sheltering_cat(variable = "anxiety_current_some",
                                     dataset = disability, 
                                     label = "some or a lot of anxiety",
                                     groups = c("region"),
                                     group_levels = unique(disability$region))
anxiety_plot$plot
```

### Caregiver depression

```{r}
disability %>%
  filter(!is.na(region)) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "depress",
          desc_stat = "mean_ci")
```


```{r region depress}
depress_plot = trend_days_sheltering_cat(variable = "depress_current_some",
                                     dataset = disability, 
                                     label = "some or a lot of depression",
                                     groups = c("region"),
                                     group_levels = unique(disability$region))
depress_plot$plot
```

### Caregiver stress

```{r}
disability %>%
  filter(!is.na(region)) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "stress",
          desc_stat = "mean_ci")
```


```{r region stress}
stress_plot = trend_days_sheltering_cat(variable = "stress_current_some",
                                     dataset = disability, 
                                     label = "some or a lot of stress",
                                     groups = c("region"),
                                     group_levels = unique(disability$region))
stress_plot$plot
```


### Child externalizing

```{r}
disability %>%
  filter(!is.na(region)) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "fussy",
          desc_stat = "mean_ci")
```


```{r region fussy}
fussy_plot = trend_days_sheltering_cat(variable = "fussy_current_some",
                                     dataset = disability, 
                                     label = "children are sometimes or often fussy or defiant",
                                     groups = c("region"),
                                     group_levels = unique(disability$region))
fussy_plot$plot
```

### Child internalizing

```{r}
disability %>%
  filter(!is.na(region)) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "fear",
          desc_stat = "mean_ci")
```


```{r region fear}
fear_plot = trend_days_sheltering_cat(variable = "fear_current_some",
                                     dataset = disability, 
                                     label = "children are sometimes or often fearful or anxious",
                                     groups = c("region"),
                                     group_levels = unique(disability$region))
fear_plot$plot
```

## By childcare

```{r}
disability = disability %>%
  mutate(nonfamliy_cc = ifelse(hours_nonfamilyCC_current == 0, 
                               "No nonfamily care", 
                               "Nonfamily care")) 
tab_nonfamily_cc = table(disability$nonfamliy_cc)
```

Of these caregivers, `r tab_nonfamily_cc[2]` have non-family childcare and `r tab_nonfamily_cc[1]` do not.

```{r}
disability %>%
  select(nonfamliy_cc, anxiety, depress, stress, fussy, fear) %>%
  gather("emotion", "value", -nonfamliy_cc) %>%
  ggerrorplot(data = .,
          x = "emotion", 
          y = "value",
          color = "nonfamliy_cc",
          desc_stat = "mean_ci")
```


```{r}
disability = disability %>%
  mutate(famliy_cc = ifelse(hours_familyCC_current == 0, 
                               "No family care", 
                               "family care")) 
tab_family_cc = table(disability$famliy_cc)
```

Of these caregivers, `r tab_family_cc[1]` have family childcare and `r tab_family_cc[2]` do not.

```{r}
disability %>%
  select(famliy_cc, anxiety, depress, stress, fussy, fear) %>%
  gather("emotion", "value", -famliy_cc) %>%
  ggerrorplot(data = .,
          x = "emotion", 
          y = "value",
          color = "famliy_cc",
          desc_stat = "mean_ci")
```

## By use of online resources

```{r}
disability %>%
  select(access_online, anxiety, depress, stress, fussy, fear) %>%
  gather("emotion", "value", -access_online) %>%
  mutate(access_online = as.factor(access_online)) %>%
  ggerrorplot(data = .,
          x = "emotion", 
          y = "value",
          color = "access_online",
          desc_stat = "mean_ci")
```




# Education 

## Compared to general population {.tabset}

### Parent education interrupted

```{r parent edu}
parent_edu_plot = trend_days_sheltering_binary(variable = "parent_edu_interrupt",
                                     dataset = scored, 
                                     label = "their own education was disrupted",
                                     groups = c("disability"),
                                     group_labels = "Parents of children with disabilities")
parent_edu_plot$plot
```

### Child education interrupted

```{r child edu}
child_edu_plot = trend_days_sheltering_binary(variable = "child_edu_interrupt",
                                     dataset = scored, 
                                     label = "child(ren)'s education was disrupted",
                                     groups = c("disability"),
                                     group_labels = "Caregivers of children with disabilities")
child_edu_plot$plot
```

## By poverty level {.tabset}


```{r}
disability = scored %>%
  filter(disability == 1) 

pov.tabs = xtabs(~ poverty, data = disability)
```

Of the `r nrow(disability)` caregivers of children with a disability, `r pov.tabs[2]` report an income below the poverty threshold for their household size and `r pov.tabs[1]` report an income above the threshold. 

```{r}
disability %>%
  select(poverty, parent_edu_interrupt, child_edu_interrupt) %>%
  gather("student", "value", -poverty) %>%
  filter(!is.nan(value) & !is.na(poverty) & !is.na(value)) %>%
  group_by(poverty, student) %>%
  summarize(n = n(),
            m = mean(value),
            s = sd(value),
            t = qt(p = .975, df = n-1),
            moe = t*(s/sqrt(n))) %>%
  ungroup() %>%
  mutate(student = factor(student, 
                          levels = c("parent_edu_interrupt", 
                                     "child_edu_interrupt"),
                          labels = c("Parent", "Child")),
         poverty = factor(poverty, levels = c(0,1), 
                          labels = c("Above poverty threshold","Below poverty threshold"))) %>%
  ggplot(aes(x = student, y = m, fill = poverty)) + 
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(min = m-moe, max = m+moe), position = position_dodge(1), width = .5) +
  labs(x = "",
      y = "Proprotion interrupted",
      title = "Education interrupted") + 
  theme_minimal() +
  theme(legend.position = "top")
```


## By geographic region


```{r out.width=c('50%', '50%'), fig.show='hold'}
disability %>%
  filter(!is.na(region)) %>%
  select(region, parent_edu_interrupt, child_edu_interrupt) %>%
  gather("student", "value", -region) %>%
   mutate(student = factor(student, 
                          levels = c("parent_edu_interrupt", 
                                     "child_edu_interrupt"),
                          labels = c("Parent", "Child"))) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "value",
          color = "student",
          desc_stat = "mean_ci", 
          title = "Interrupted education ")

```



## By childcare

```{r}
disability = disability %>%
  mutate(nonfamliy_cc = ifelse(hours_nonfamilyCC_current == 0, 
                               "No nonfamily care", 
                               "Nonfamily care")) 
tab_nonfamily_cc = table(disability$nonfamliy_cc)
```

Of these caregivers, `r tab_nonfamily_cc[2]` have non-family childcare and `r tab_nonfamily_cc[1]` do not.

```{r}
disability %>%
  select(nonfamliy_cc, parent_edu_interrupt, child_edu_interrupt) %>%
  gather("student", "value", -nonfamliy_cc) %>%
  mutate(student = factor(student, 
                          levels = c("parent_edu_interrupt", 
                                     "child_edu_interrupt"),
                          labels = c("Parent", "Child"))) %>%
  ggerrorplot(data = .,
          x = "student", 
          y = "value",
          color = "nonfamliy_cc",
          desc_stat = "mean_ci")
```


```{r}
disability = disability %>%
  mutate(famliy_cc = ifelse(hours_familyCC_current == 0, 
                               "No family care", 
                               "family care")) 
tab_family_cc = table(disability$famliy_cc)
```

Of these caregivers, `r tab_family_cc[1]` have family childcare and `r tab_family_cc[2]` do not.

```{r}
disability %>%
  select(famliy_cc, parent_edu_interrupt, child_edu_interrupt) %>%
  gather("student", "value", -famliy_cc) %>%
  mutate(student = factor(student, 
                          levels = c("parent_edu_interrupt", 
                                     "child_edu_interrupt"),
                          labels = c("Parent", "Child"))) %>%
  ggerrorplot(data = .,
          x = "student", 
          y = "value",
          color = "famliy_cc",
          desc_stat = "mean_ci")
```

## By use of online resources

```{r}
disability %>%
  select(access_online, parent_edu_interrupt, child_edu_interrupt) %>%
  gather("student", "value", -access_online) %>%
  mutate(access_online = as.factor(access_online)) %>%
  mutate(student = factor(student, 
                          levels = c("parent_edu_interrupt", 
                                     "child_edu_interrupt"),
                          labels = c("Parent", "Child"))) %>%
  ggerrorplot(data = .,
          x = "student", 
          y = "value",
          color = "access_online",
          desc_stat = "mean_ci")
```

