---
title: "Caregivers of children with disabilities"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
  
---

Please note that lines by date and days sheltering in place are smoothed curves -- they may be poor representations of the data in locations with few participants. For example, the largest number of days sheltering in place only applies to a small portion of participants; lines representing small demographic groups at these large should not be interpreted. 

```{r chunk 1, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
```

```{r packages}
library(here)
library(tidyverse)
library(knitr)
library(kableExtra)
library(haven)
# require(devtools)
# install_version("zipcode", version = "1.0", repos = "http://cran.us.r-project.org")
library(zipcode)
library(ggthemr)
library(corx)
library(papaja)
library(zoo)
library(ggpubr)
library(lme4)
```


```{r score datafile, echo = F, warning = F, message = F}
# score master --------------------------------------------------------
source(here("Scripts/score data.R"))
scored = scored %>%
  filter(Week > 0)
```

```{rchunk 2}
total_weeks = max(scored$Week, na.rm=T)
```

# Well-being during shelter-in-place 

```{r}
source(here("Functions/trend_days_sheltering_rolling.R"))
```
## Compared to general population {.tabset}

### Caregiver anxiety

```{r anxiety}
anxiety_plot = trend_days_sheltering_binary(variable = "anxiety_current_some",
                                     dataset = scored, 
                                     label = "some or a lot of anxiety",
                                     groups = c("disability"),
                                     group_labels = "Parents of children with disabilities")
anxiety_plot$plot
```

### Caregiver depression

```{r depress}
depress_plot = trend_days_sheltering_binary(variable = "depress_current_some",
                                     dataset = scored, 
                                     label = "some or a lot of depression",
                                     groups = c("disability"),
                                     group_labels = "Parents of children with disabilities")
depress_plot$plot
```

### Caregiver stress

```{r stress}
stress_plot = trend_days_sheltering_binary(variable = "stress_current_some",
                                     dataset = scored, 
                                     label = "some or a lot of stress",
                                     groups = c("disability"),
                                     group_labels = "Parents of children with disabilities")
stress_plot$plot
```


### Caregiver loneliness

```{r }
lonely_plot = trend_days_sheltering_binary(variable = "lonely_current_some",
                                     dataset = scored, 
                                     label = "some or a lot of loneliness",
                                     groups = c("disability"),
                                     group_labels = "Parents of children with disabilities")
lonely_plot$plot
```

### Child externalizing

```{r fussy}
fussy_plot = trend_days_sheltering_binary(variable = "fussy_current_some",
                                     dataset = scored, 
                                     label = "children are sometimes or often fussy or defiant",
                                     groups = c("disability"),
                                     group_labels = "Parents of children with disabilities")
fussy_plot$plot
```



### Child internalizing

```{r fear}
fear_plot = trend_days_sheltering_binary(variable = "fear_current_some",
                                     dataset = scored, 
                                     label = "children are sometimes or often fearful or anxious",
                                     groups = c("disability"),
                                     group_labels = "Parents of children with disabilities")
fear_plot$plot
```

## By poverty level {.tabset}


```{r}
disability = scored %>%
  filter(disability == 1) 

pov.tabs = xtabs(~ poverty, data = disability)
```

Of the `r nrow(disability)` caregivers of children with a disability, `r pov.tabs[2]` report an income below the poverty threshold for their household size and `r pov.tabs[1]` report an income above the threshold. 

```{r}
disability %>%
  select(poverty, anxiety, depress, stress, fussy, fear) %>%
  gather("emotion", "value", -poverty) %>%
  filter(!is.nan(value) & !is.na(poverty) & !is.na(value)) %>%
  group_by(poverty, emotion) %>%
  summarize(n = n(),
            m = mean(value),
            s = sd(value),
            t = qt(p = .975, df = n-1),
            moe = t*(s/sqrt(n))) %>%
  ungroup() %>%
  mutate(emotion = factor(emotion, 
                          levels = c("anxiety", "depress", "stress", "fussy", "fear"),
                          labels = c("Caregiver anxiety", 
                                     "Caregiver depression", 
                                     "Caregiver stress", 
                                     "Child externalizing", "Child internalizing")),
         poverty = factor(poverty, levels = c(0,1), 
                          labels = c("Above poverty threshold","Below poverty threshold"))) %>%
  ggplot(aes(x = emotion, y = m, fill = poverty)) + 
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(min = m-moe, max = m+moe), position = position_dodge(1), width = .5) +
  coord_flip() +
  labs(x = "",
      y = "Average response",
      title = "Well-being in families") + 
  theme_minimal()
```


## By geographic region {.tabset}


### Caregiver anxiety

```{r}
disability %>%
  filter(!is.na(region)) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "anxiety",
          desc_stat = "mean_ci")
```


```{r region anxiety}
anxiety_plot = trend_days_sheltering_cat(variable = "anxiety_current_some",
                                     dataset = disability, 
                                     label = "some or a lot of anxiety",
                                     groups = c("region"),
                                     group_levels = unique(disability$region))
anxiety_plot$plot
```

### Caregiver depression

```{r}
disability %>%
  filter(!is.na(region)) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "depress",
          desc_stat = "mean_ci")
```


```{r region depress}
depress_plot = trend_days_sheltering_cat(variable = "depress_current_some",
                                     dataset = disability, 
                                     label = "some or a lot of depression",
                                     groups = c("region"),
                                     group_levels = unique(disability$region))
depress_plot$plot
```

### Caregiver stress

```{r}
disability %>%
  filter(!is.na(region)) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "stress",
          desc_stat = "mean_ci")
```


```{r region stress}
stress_plot = trend_days_sheltering_cat(variable = "stress_current_some",
                                     dataset = disability, 
                                     label = "some or a lot of stress",
                                     groups = c("region"),
                                     group_levels = unique(disability$region))
stress_plot$plot
```


### Child externalizing

```{r}
disability %>%
  filter(!is.na(region)) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "fussy",
          desc_stat = "mean_ci")
```


```{r region fussy}
fussy_plot = trend_days_sheltering_cat(variable = "fussy_current_some",
                                     dataset = disability, 
                                     label = "children are sometimes or often fussy or defiant",
                                     groups = c("region"),
                                     group_levels = unique(disability$region))
fussy_plot$plot
```

### Child internalizing

```{r}
disability %>%
  filter(!is.na(region)) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "fear",
          desc_stat = "mean_ci")
```


```{r region fear}
fear_plot = trend_days_sheltering_cat(variable = "fear_current_some",
                                     dataset = disability, 
                                     label = "children are sometimes or often fearful or anxious",
                                     groups = c("region"),
                                     group_levels = unique(disability$region))
fear_plot$plot
```

## By childcare

```{r}
disability = disability %>%
  mutate(nonfamliy_cc = ifelse(hours_nonfamilyCC_current == 0, 
                               "No nonfamily care", 
                               "Nonfamily care")) 
tab_nonfamily_cc = table(disability$nonfamliy_cc)
```

Of these caregivers, `r tab_nonfamily_cc[2]` have non-family childcare and `r tab_nonfamily_cc[1]` do not.

```{r}
disability %>%
  select(nonfamliy_cc, anxiety, depress, stress, fussy, fear) %>%
  gather("emotion", "value", -nonfamliy_cc) %>%
  ggerrorplot(data = .,
          x = "emotion", 
          y = "value",
          color = "nonfamliy_cc",
          desc_stat = "mean_ci")
```


```{r}
disability = disability %>%
  mutate(famliy_cc = ifelse(hours_familyCC_current == 0, 
                               "No family care", 
                               "family care")) 
tab_family_cc = table(disability$famliy_cc)
```

Of these caregivers, `r tab_family_cc[1]` have family childcare and `r tab_family_cc[2]` do not.

```{r}
disability %>%
  select(famliy_cc, anxiety, depress, stress, fussy, fear) %>%
  gather("emotion", "value", -famliy_cc) %>%
  ggerrorplot(data = .,
          x = "emotion", 
          y = "value",
          color = "famliy_cc",
          desc_stat = "mean_ci")
```

## By use of online resources

```{r}
disability %>%
  select(access_online, anxiety, depress, stress, fussy, fear) %>%
  gather("emotion", "value", -access_online) %>%
  mutate(access_online = as.factor(access_online)) %>%
  ggerrorplot(data = .,
          x = "emotion", 
          y = "value",
          color = "access_online",
          desc_stat = "mean_ci")
```




# Education 

## Compared to general population {.tabset}

### Parent education interrupted

```{r parent edu}
parent_edu_plot = trend_days_sheltering_binary(variable = "parent_edu_interrupt",
                                     dataset = scored, 
                                     label = "their own education was disrupted",
                                     groups = c("disability"),
                                     group_labels = "Parents of children with disabilities")
parent_edu_plot$plot
```

### Child education interrupted

```{r child edu}
child_edu_plot = trend_days_sheltering_binary(variable = "child_edu_interrupt",
                                     dataset = scored, 
                                     label = "child(ren)'s education was disrupted",
                                     groups = c("disability"),
                                     group_labels = "Caregivers of children with disabilities")
child_edu_plot$plot
```

## By poverty level {.tabset}


```{r}
disability = scored %>%
  filter(disability == 1) 

pov.tabs = xtabs(~ poverty, data = disability)
```

Of the `r nrow(disability)` caregivers of children with a disability, `r pov.tabs[2]` report an income below the poverty threshold for their household size and `r pov.tabs[1]` report an income above the threshold. 

```{r}
disability %>%
  select(poverty, parent_edu_interrupt, child_edu_interrupt) %>%
  gather("student", "value", -poverty) %>%
  filter(!is.nan(value) & !is.na(poverty) & !is.na(value)) %>%
  group_by(poverty, student) %>%
  summarize(n = n(),
            m = mean(value),
            s = sd(value),
            t = qt(p = .975, df = n-1),
            moe = t*(s/sqrt(n))) %>%
  ungroup() %>%
  mutate(student = factor(student, 
                          levels = c("parent_edu_interrupt", 
                                     "child_edu_interrupt"),
                          labels = c("Parent", "Child")),
         poverty = factor(poverty, levels = c(0,1), 
                          labels = c("Above poverty threshold","Below poverty threshold"))) %>%
  ggplot(aes(x = student, y = m, fill = poverty)) + 
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(min = m-moe, max = m+moe), position = position_dodge(1), width = .5) +
  labs(x = "",
      y = "Proprotion interrupted",
      title = "Education interrupted") + 
  theme_minimal() +
  theme(legend.position = "top")
```


## By geographic region


```{r out.width=c('50%', '50%'), fig.show='hold'}
disability %>%
  filter(!is.na(region)) %>%
  select(region, parent_edu_interrupt, child_edu_interrupt) %>%
  gather("student", "value", -region) %>%
   mutate(student = factor(student, 
                          levels = c("parent_edu_interrupt", 
                                     "child_edu_interrupt"),
                          labels = c("Parent", "Child"))) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "value",
          color = "student",
          desc_stat = "mean_ci", 
          title = "Interrupted education ")

```



## By childcare

```{r}
disability = disability %>%
  mutate(nonfamliy_cc = ifelse(hours_nonfamilyCC_current == 0, 
                               "No nonfamily care", 
                               "Nonfamily care")) 
tab_nonfamily_cc = table(disability$nonfamliy_cc)
```

Of these caregivers, `r tab_nonfamily_cc[2]` have non-family childcare and `r tab_nonfamily_cc[1]` do not.

```{r}
disability %>%
  select(nonfamliy_cc, parent_edu_interrupt, child_edu_interrupt) %>%
  gather("student", "value", -nonfamliy_cc) %>%
  mutate(student = factor(student, 
                          levels = c("parent_edu_interrupt", 
                                     "child_edu_interrupt"),
                          labels = c("Parent", "Child"))) %>%
  ggerrorplot(data = .,
          x = "student", 
          y = "value",
          color = "nonfamliy_cc",
          desc_stat = "mean_ci")
```


```{r}
disability = disability %>%
  mutate(famliy_cc = ifelse(hours_familyCC_current == 0, 
                               "No family care", 
                               "family care")) 
tab_family_cc = table(disability$famliy_cc)
```

Of these caregivers, `r tab_family_cc[1]` have family childcare and `r tab_family_cc[2]` do not.

```{r}
disability %>%
  select(famliy_cc, parent_edu_interrupt, child_edu_interrupt) %>%
  gather("student", "value", -famliy_cc) %>%
  mutate(student = factor(student, 
                          levels = c("parent_edu_interrupt", 
                                     "child_edu_interrupt"),
                          labels = c("Parent", "Child"))) %>%
  ggerrorplot(data = .,
          x = "student", 
          y = "value",
          color = "famliy_cc",
          desc_stat = "mean_ci")
```

## By use of online resources

```{r}
disability %>%
  select(access_online, parent_edu_interrupt, child_edu_interrupt) %>%
  gather("student", "value", -access_online) %>%
  mutate(access_online = as.factor(access_online)) %>%
  mutate(student = factor(student, 
                          levels = c("parent_edu_interrupt", 
                                     "child_edu_interrupt"),
                          labels = c("Parent", "Child"))) %>%
  ggerrorplot(data = .,
          x = "student", 
          y = "value",
          color = "access_online",
          desc_stat = "mean_ci")
```

# Loss {.tabset}

## Income

```{r}
week1 = scored %>%
  group_by(CaregiverID) %>%
  filter(Week > 0) %>%
  filter(Week == min(Week))

chisq.test(week1$disability, week1$income_decreaed)
week1 %>%
  ungroup()%>%
  select(disability, income_decreaed) %>%
  group_by(disability) %>%
  summarize(n = n(),
            decreased_income = sum(income_decreaed,na.rm = T),
            percent = decreased_income/n)
```

## Non-family childcare

```{r}
chisq.test(week1$disability, week1$decrease_nonfamilyCC)
week1 %>%
  ungroup()%>%
  select(disability, decrease_nonfamilyCC) %>%
  group_by(disability) %>%
  summarize(n = n(),
            decrease_nonfamilyCC = sum(decrease_nonfamilyCC,na.rm = T),
            percent = decrease_nonfamilyCC/n)
```

# Testing predictors of well-being in this demo{.tabset}

```{r}

mlm.model = function(abdata){
  mod = lmer(o.value~p.value + (1|CaregiverID), 
             data = abdata,
             control=lmerControl(check.nobs.vs.nlev="ignore",
                                 check.nobs.vs.nRE = "ignore"),)
  return(mod)
}
```


```{r}
disability = disability %>%
  mutate(children2 = ifelse(num_children_raw >= 2, 1, 0),
         children3 = ifelse(num_children_raw >= 3, 1, 0))
predictors = c("income_decreaed", 
               "employment_decreased",
               "difficulty_basics",
               "children2", 
               "children3", 
               "access_online", 
               "access_telehealth", 
               "poverty", 
               "child_edu_interrupt", 
               "parent_edu_interrupt",
               "delay_healthcare",
               "black",
               "latinx",
               "single",
               "essential")
predictor.labels = c(
  "Lost income since pandemic",
  "Lost employment since pandemic",
  "Have difficulty paying for basics",
  "Two or more children in household",
  "Three or more children in household",
  "Can access online serivices",
  "Can access telehealth serivices",
  "Below the poverty threshold",
  "Child education interrupted",
  "Parent education interrupted",
  "Have delayed healthcare",
  "African American",
  "Latinx",
  "Single",
  "Essential employees"
)
unique = disability %>%
  group_by(CaregiverID) %>%
  filter(Week == min(Week)) %>%
  ungroup()
  
N = apply(unique[,predictors], 2, FUN = sum, na.rm=T)

predictor.labels = paste0(predictor.labels, " (N = ", N, ")")

pred.table = disability %>%
  #censor number of children
  mutate(num_children_raw = ifelse(num_children_raw > 4, 4, num_children_raw)) %>%
  select(CaregiverID, anxiety, depress, stress, 
         fussy, fear, all_of(predictors)) %>%
  gather("outcome", "o.value", anxiety, depress, stress, 
         fussy, fear) %>%
  gather("predictor", "p.value", all_of(predictors)) %>%
  group_by(outcome,predictor) %>%
  nest() %>%
  mutate(model = purrr::map(data, mlm.model)) %>%
  mutate(output = purrr::map(model, broom::tidy)) %>%
  select(outcome, predictor, output) %>%
  unnest(output) %>%
  filter(term == "p.value") %>%
  mutate(pvalue = purrr::map_dbl(statistic, 
                              .f = function(x) pt(q = abs(x), 
                                                  df = 250, 
                                                  lower.tail = F)*2)) %>%
  select(outcome, predictor, estimate, std.error, pvalue) %>%
  ungroup() %>%
  mutate(holm = p.adjust(pvalue,  method = "holm")) %>%
  mutate(outcome = factor(outcome, 
                          levels = c("anxiety", "depress", "stress", 
         "fussy", "fear"),
         labels = c("Caregiver anxiety", "Careviver depression", "Caregver stress", 
         "Child externalzing", "Child internalizing")))
```

```{r}
source(here("Functions/summarizing_report.R"))
```

```{r}
first.row = sapply(predictors, 
                   first_instance, 
                   string = pred.table$predictor)
last.row = sapply(predictors, 
                  last_instance, 
                  string = pred.table$predictor)


each_string = paste0("group_rows(group_label = \" ", 
                     predictor.labels, 
                     "\" , start_row = ", 
                     first.row, 
                     ", end_row = ", 
                     last.row, 
                     ")")
each_string = paste(each_string, collapse = " %>% ")


beginning= "pred.table %>% select(-predictor) %>% kable(., col.names = c(\"Outcome\", \"Coefficient Estimate\", \"Std. Error\", \"p-value\", \" Corrected p-value\"), digits = c(1,2,2,3,3)) %>%
  kable_styling() %>%
footnote(general = \"Coefficients estimated using a multi-level model in which responses are nested within caregivers. In the case of binary predictors, we report the number (N) of participants who fall into the category listed. p-values are adjusted using a Holm correction\") %>%"

eval(parse(text = paste0(beginning, each_string)))
```


