---
title: "Low income households"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
  
---

In these analyses, families are considered to be a low-income household if their reported annual income is less than 2 times the Federal Poverty Level for a household of their size. Household size is calculated as the number of children in the household plus one (if the caregiver reports being singled, divorced, widowed, romantically involved but living papart, or not in any kind of relationship) or plus two otherwise. 


```{r chunk 1, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
```

```{r packages}
library(here)
library(tidyverse)
library(knitr)
library(kableExtra)
library(haven)
## require(devtools)
## install_version("zipcode", version = "1.0", repos = "http://cran.us.r-project.org")
library(zipcode)
library(ggthemr)
library(corx)
library(papaja)
library(zoo)
library(ggpubr)
library(lme4)
```


```{r score datafile, echo = F, warning = F, message = F}
## score master --------------------------------------------------------
source(here("Scripts/score data.R"))
scored0 = scored %>% filter(Week < 4)
scored = scored %>%
  filter(Week > 0) %>%
  filter(Week < 4)
```

```{rchunk 2}
total_weeks = max(scored$Week, na.rm=T)
```
# Analyses May 7

```{r}
control = lmerControl(check.nobs.vs.nlev = "ignore", 
                      check.nobs.vs.nRE = "ignore")

meds = c("insurance", 
         "child_insurance", 
         #"access_online", 
         #"suspected_covid", 
         #"diagnosed_covid", 
         #"hospital", 
         #"hospital_covid", 
         "support_decrease", 
         "lost_free_lunch", 
         "employment_decreased", 
         "losejob_sickleave", 
         "income_decreaed", 
         "difficulty_basics", 
         "minority", 
         "black", 
         "latinx")
```


## Well-being during shelter-in-place {.tabset}
```{r}
source(here("Functions/trend_date_rolling.R"))
source(here("Functions/trend_week.R"))

```

```{r}
poverty = scored %>%
  filter(poverty == 1) 
```

### Caregiver anxiety

#### Plots

```{r, out.width=c('50%', '50%'), fig.show='hold'}
anxiety_plot = trend_date_binary(variable = "anxiety_current_some",
                                     dataset = scored, 
                                     label = "some or a lot of anxiety",
                                     groups = c("poverty"),
                                     group_labels = "Low income households")
anxiety_plot$plot

trend_week_binary(variable = "anxiety", 
                  dataset = scored0,
                  label =  "Caregiver Anxiety", 
                  groups = "poverty", 
                  group_labels = c("Middle or high income","Low income"))

```


#### Test of slope {.tabset}

##### Weeks 1+


**Baseline model**

```{r, results = 'asis'}
model = lmer(anxiety ~ Week*poverty + (1|CaregiverID), 
             data = scored, control = control)

broom::tidy(model) %>%
  mutate(p.value = pt(abs(statistic), 
                      df = nrow(model@frame)-2, lower.tail = F)*2) %>%
  select(term, estimate, std.error, statistic, p.value) %>%
  kable(., col.names = c("Term", "Coef", "SE", "t", "p"),
        digits = c(0,2,2,2,3)) %>%
  kable_styling() %>%
  group_rows("Fixed effects", 1, 4) %>%
  group_rows("Random effects", 5, 6)
```

**Can we explain the effect?**

```{r, results = 'asis'}

model =
  tibble(mediator = meds, 
         model = list(function(d) lmer(anxiety ~ Week*poverty + Week*m.value + 
                                         (1|CaregiverID), 
                                       data = d, 
                                       control = control)))

scored %>%
  gather("mediator", "m.value", all_of(meds)) %>%
  group_by(mediator) %>%
  nest() %>%
  mutate(N = purrr::map_dbl(data, nrow)) %>%
  left_join(model) %>%
  rowwise() %>%
  summarize(mediator = mediator, 
            N = N,
            fit = list(model(data)),
            fit = list(broom::tidy(fit))) %>%
  select(mediator, N, fit) %>%
  unnest() %>%
  filter(grepl(":", term)) %>%
  mutate(estimate = papaja::printnum(estimate),
         p.value = pt(abs(statistic), df = N-3, lower.tail = F)*2,
         estimate = ifelse(p.value < .05, paste0(estimate,"*"), estimate),
         term = gsub("Week:", "",term)) %>%
  select(mediator, term, estimate) %>%
  spread(term, estimate) %>%
  kable(., col.names = c("Mediator", "Coefficient (Income)", "Coefficient of mediator")) %>%
  kable_styling()
```


##### Week 0 to first response

**Baseline model**

```{r, results = 'asis'}

demo.med = scored %>%
  group_by(CaregiverID) %>%
  filter(Week == min(Week)) %>%
    select(CaregiverID, poverty, all_of(meds))

change = scored0 %>%
  select(CaregiverID, Week, anxiety) %>%
  group_by(CaregiverID) %>%
  arrange(Week) %>%
  filter(row_number() %in% c(1,2)) %>%
  mutate(Week = ifelse(Week == 0, "Before", "After")) %>%
  ungroup() %>%
  spread(Week, anxiety) %>%
  mutate(Change = After-Before) %>%
  full_join(demo.med)


model = lm(Change ~ poverty, data = change)
broom::tidy(model) %>%
  kable(., col.names = c("Term", "Coef", "SE", "t", "p"),
        digits = c(0,2,2,2,3)) %>%
  kable_styling() 

change %>%
  filter(!is.na(poverty)) %>%
  group_by(poverty) %>%
  summarize(m = mean(Change,na.rm=T),
         sd = sd(Change,na.rm=T),
         n = n(),
         se = sd/sqrt(n),
         cv = qt(p = .975, df = n-1),
         moe = se*cv) %>%
  mutate(poverty = factor(poverty, labels = c("Middle to high income", "Low income"))) %>%
  ggplot(aes(x = poverty, y = m)) +
  geom_bar(aes(fill = poverty), stat = "identity") +
  geom_errorbar(aes(ymin = m-moe, ymax = m+moe), width = .5) +
  labs(x = "", y = "Change in anxiety") +
  scale_fill_brewer(palette = "Dark2")+
  guides(fill = F) +
  theme_minimal()
```


**Can we explain the effect?**

```{r, results = 'asis'}
model =
  tibble(mediator = meds, 
         model = list(function(d) lm(Change ~ poverty + m.value, 
                                       data = d)))
change %>%
  gather("mediator", "m.value", all_of(meds)) %>%
  group_by(mediator) %>%
  nest() %>%
  mutate(N = purrr::map_dbl(data, nrow)) %>%
  left_join(model) %>%
  rowwise() %>%
  summarize(mediator = mediator, 
            N = N,
            fit = list(model(data)),
            fit = list(broom::tidy(fit))) %>%
  select(mediator, N, fit) %>%
  unnest(cols = c(fit)) %>%
  filter(term %in% c("poverty", "m.value")) %>%
  mutate(estimate = papaja::printnum(estimate),
         estimate = ifelse(p.value < .05, paste0(estimate,"*"), estimate)) %>%
  select(mediator, term, estimate) %>%
  spread(term, estimate) %>%
  kable(., col.names = c("Mediator", "Coefficient (Income)", "Coefficient of mediator")) %>%
  kable_styling()
```

### Caregiver depression

#### Plots

```{r, out.width=c('50%', '50%'), fig.show='hold'}
depress_plot = trend_date_binary(variable = "depress_current_some",
                                 dataset = scored, 
                                 label = "some or a lot of depression",
                                 groups = c("poverty"),
                                 group_labels = "Low income households")
depress_plot$plot

trend_week_binary(variable = "depress", 
                  dataset = scored0,
                  label =  "Caregiver depression", 
                  groups = "poverty", 
                  group_labels = c("Middle or high income","Low income"))

```


#### Test of slope {.tabset}

##### Weeks 1+


**Baseline model**
  
```{r, results = 'asis'}
model = lmer(depress ~ Week*poverty + (1|CaregiverID), data = scored, control = control)
broom::tidy(model) %>%
  mutate(p.value = pt(abs(statistic), df = nrow(model@frame)-2, lower.tail = F)*2) %>%
  select(term, estimate, std.error, statistic, p.value) %>%
  kable(., col.names = c("Term", "Coef", "SE", "t", "p"),
        digits = c(0,2,2,2,3)) %>%
  kable_styling() %>%
  group_rows("Fixed effects", 1, 4) %>%
  group_rows("Random effects", 5, 6)
```

**Can we explain the effect?**
  
```{r, results = 'asis'}

model =
  tibble(mediator = meds, 
         model = list(function(d) lmer(depress ~ Week*poverty + Week*m.value + 
                                         (1|CaregiverID), 
                                       data = d, 
                                       control = control)))
scored %>%
  gather("mediator", "m.value", all_of(meds)) %>%
  group_by(mediator) %>%
  nest() %>%
  mutate(N = purrr::map_dbl(data, nrow)) %>%
  left_join(model) %>%
  rowwise() %>%
  summarize(mediator = mediator, 
            N = N,
            fit = list(model(data)),
            fit = list(broom::tidy(fit))) %>%
  select(mediator, N, fit) %>%
  unnest() %>%
  filter(grepl(":", term)) %>%
  mutate(estimate = papaja::printnum(estimate),
         p.value = pt(abs(statistic), df = N-3, lower.tail = F)*2,
         estimate = ifelse(p.value < .05, paste0(estimate,"*"), estimate),
         term = gsub("Week:", "",term)) %>%
  select(mediator, term, estimate) %>%
  spread(term, estimate) %>%
  kable(., col.names = c("Mediator", "Coefficient (Income)", "Coefficient of mediator")) %>%
  kable_styling()
```


##### Week 0 to first response

**Baseline model**
  
```{r, results = 'asis'}

demo.med = scored %>%
  group_by(CaregiverID) %>%
  filter(Week == min(Week)) %>%
  select(CaregiverID, poverty, all_of(meds))

change = scored0 %>%
  select(CaregiverID, Week, depress) %>%
  group_by(CaregiverID) %>%
  arrange(Week) %>%
  filter(row_number() %in% c(1,2)) %>%
  mutate(Week = ifelse(Week == 0, "Before", "After")) %>%
  ungroup() %>%
  spread(Week, depress) %>%
  mutate(Change = After-Before) %>%
  full_join(demo.med)


model = lm(Change ~ poverty, data = change)
broom::tidy(model) %>%
  kable(., col.names = c("Term", "Coef", "SE", "t", "p"),
        digits = c(0,2,2,2,3)) %>%
  kable_styling() 

change %>%
  filter(!is.na(poverty)) %>%
  group_by(poverty) %>%
  summarize(m = mean(Change,na.rm=T),
            sd = sd(Change,na.rm=T),
            n = n(),
            se = sd/sqrt(n),
            cv = qt(p = .975, df = n-1),
            moe = se*cv) %>%
  mutate(poverty = factor(poverty, labels = c("Middle to high income", "Low income"))) %>%
  ggplot(aes(x = poverty, y = m)) +
  geom_bar(aes(fill = poverty), stat = "identity") +
  geom_errorbar(aes(ymin = m-moe, ymax = m+moe), width = .5) +
  labs(x = "", y = "Change in depression") +
  scale_fill_brewer(palette = "Dark2")+
  guides(fill = F) +
  theme_minimal()
```


**Can we explain the effect?**
  
```{r, results = 'asis'}
model =
  tibble(mediator = meds, 
         model = list(function(d) lm(Change ~ poverty + m.value, 
                                     data = d)))
change %>%
  gather("mediator", "m.value", all_of(meds)) %>%
  group_by(mediator) %>%
  nest() %>%
  mutate(N = purrr::map_dbl(data, nrow)) %>%
  left_join(model) %>%
  rowwise() %>%
  summarize(mediator = mediator, 
            N = N,
            fit = list(model(data)),
            fit = list(broom::tidy(fit))) %>%
  select(mediator, N, fit) %>%
  unnest(cols = c(fit)) %>%
  filter(term %in% c("poverty", "m.value")) %>%
  mutate(estimate = papaja::printnum(estimate),
         estimate = ifelse(p.value < .05, paste0(estimate,"*"), estimate)) %>%
  select(mediator, term, estimate) %>%
  spread(term, estimate) %>%
  kable(., col.names = c("Mediator", "Coefficient (Income)", "Coefficient of mediator")) %>%
  kable_styling()
```

### Caregiver stress

#### Plots

```{r, out.width=c('50%', '50%'), fig.show='hold'}
stress_plot = trend_date_binary(variable = "stress_current_some",
                                 dataset = scored, 
                                 label = "some or a lot of stress",
                                 groups = c("poverty"),
                                 group_labels = "Low income households")
stress_plot$plot

trend_week_binary(variable = "stress", 
                  dataset = scored0,
                  label =  "Caregiver stress", 
                  groups = "poverty", 
                  group_labels = c("Middle or high income","Low income"))

```


#### Test of slope {.tabset}

##### Weeks 1+


**Baseline model**
  
```{r, results = 'asis'}
model = lmer(stress ~ Week*poverty + (1|CaregiverID), data = scored, control = control)
broom::tidy(model) %>%
  mutate(p.value = pt(abs(statistic), df = nrow(model@frame)-2, lower.tail = F)*2) %>%
  select(term, estimate, std.error, statistic, p.value) %>%
  kable(., col.names = c("Term", "Coef", "SE", "t", "p"),
        digits = c(0,2,2,2,3)) %>%
  kable_styling() %>%
  group_rows("Fixed effects", 1, 4) %>%
  group_rows("Random effects", 5, 6)
```

**Can we explain the effect?**
  
```{r, results = 'asis'}

model =
  tibble(mediator = meds, 
         model = list(function(d) lmer(stress ~ Week*poverty + Week*m.value + 
                                         (1|CaregiverID), 
                                       data = d, 
                                       control = control)))
scored %>%
  gather("mediator", "m.value", all_of(meds)) %>%
  group_by(mediator) %>%
  nest() %>%
  mutate(N = purrr::map_dbl(data, nrow)) %>%
  left_join(model) %>%
  rowwise() %>%
  summarize(mediator = mediator, 
            N = N,
            fit = list(model(data)),
            fit = list(broom::tidy(fit))) %>%
  select(mediator, N, fit) %>%
  unnest() %>%
  filter(grepl(":", term)) %>%
  mutate(estimate = papaja::printnum(estimate),
         p.value = pt(abs(statistic), df = N-3, lower.tail = F)*2,
         estimate = ifelse(p.value < .05, paste0(estimate,"*"), estimate),
         term = gsub("Week:", "",term)) %>%
  select(mediator, term, estimate) %>%
  spread(term, estimate) %>%
  kable(., col.names = c("Mediator", "Coefficient (Income)", "Coefficient of mediator")) %>%
  kable_styling()
```


##### Week 0 to first response

**Baseline model**
  
```{r, results = 'asis'}

demo.med = scored %>%
  group_by(CaregiverID) %>%
  filter(Week == min(Week)) %>%
  select(CaregiverID, poverty, all_of(meds))

change = scored0 %>%
  select(CaregiverID, Week, stress) %>%
  group_by(CaregiverID) %>%
  arrange(Week) %>%
  filter(row_number() %in% c(1,2)) %>%
  mutate(Week = ifelse(Week == 0, "Before", "After")) %>%
  ungroup() %>%
  spread(Week, stress) %>%
  mutate(Change = After-Before) %>%
  full_join(demo.med)


model = lm(Change ~ poverty, data = change)
broom::tidy(model) %>%
  kable(., col.names = c("Term", "Coef", "SE", "t", "p"),
        digits = c(0,2,2,2,3)) %>%
  kable_styling() 

change %>%
  filter(!is.na(poverty)) %>%
  group_by(poverty) %>%
  summarize(m = mean(Change,na.rm=T),
            sd = sd(Change,na.rm=T),
            n = n(),
            se = sd/sqrt(n),
            cv = qt(p = .975, df = n-1),
            moe = se*cv) %>%
  mutate(poverty = factor(poverty, labels = c("Middle to high income", "Low income"))) %>%
  ggplot(aes(x = poverty, y = m)) +
  geom_bar(aes(fill = poverty), stat = "identity") +
  geom_errorbar(aes(ymin = m-moe, ymax = m+moe), width = .5) +
  labs(x = "", y = "Change in stress") +
  scale_fill_brewer(palette = "Dark2")+
  guides(fill = F) +
  theme_minimal()
```


**Can we explain the effect?**
  
```{r, results = 'asis'}
model =
  tibble(mediator = meds, 
         model = list(function(d) lm(Change ~ poverty + m.value, 
                                     data = d)))
change %>%
  gather("mediator", "m.value", all_of(meds)) %>%
  group_by(mediator) %>%
  nest() %>%
  mutate(N = purrr::map_dbl(data, nrow)) %>%
  left_join(model) %>%
  rowwise() %>%
  summarize(mediator = mediator, 
            N = N,
            fit = list(model(data)),
            fit = list(broom::tidy(fit))) %>%
  select(mediator, N, fit) %>%
  unnest(cols = c(fit)) %>%
  filter(term %in% c("poverty", "m.value")) %>%
  mutate(estimate = papaja::printnum(estimate),
         estimate = ifelse(p.value < .05, paste0(estimate,"*"), estimate)) %>%
  select(mediator, term, estimate) %>%
  spread(term, estimate) %>%
  kable(., col.names = c("Mediator", "Coefficient (Income)", "Coefficient of mediator")) %>%
  kable_styling()
```

### Caregiver loneliness

#### Plots

```{r, out.width=c('50%', '50%'), fig.show='hold'}
lonely_plot = trend_date_binary(variable = "lonely_current_some",
                                 dataset = scored, 
                                 label = "some or a lot of loneliness",
                                 groups = c("poverty"),
                                 group_labels = "Low income households")
lonely_plot$plot

trend_week_binary(variable = "lonely", 
                  dataset = scored0,
                  label =  "Caregiver lonely", 
                  groups = "poverty", 
                  group_labels = c("Middle or high income","Low income"))

```


#### Test of slope {.tabset}

##### Weeks 1+


**Baseline model**
  
```{r, results = 'asis'}
model = lmer(lonely ~ Week*poverty + (1|CaregiverID), data = scored, control = control)
broom::tidy(model) %>%
  mutate(p.value = pt(abs(statistic), df = nrow(model@frame)-2, lower.tail = F)*2) %>%
  select(term, estimate, std.error, statistic, p.value) %>%
  kable(., col.names = c("Term", "Coef", "SE", "t", "p"),
        digits = c(0,2,2,2,3)) %>%
  kable_styling() %>%
  group_rows("Fixed effects", 1, 4) %>%
  group_rows("Random effects", 5, 6)
```

**Can we explain the effect?**
  
```{r, results = 'asis'}

model =
  tibble(mediator = meds, 
         model = list(function(d) lmer(lonely ~ Week*poverty + Week*m.value + 
                                         (1|CaregiverID), 
                                       data = d, 
                                       control = control)))
scored %>%
  gather("mediator", "m.value", all_of(meds)) %>%
  group_by(mediator) %>%
  nest() %>%
  mutate(N = purrr::map_dbl(data, nrow)) %>%
  left_join(model) %>%
  rowwise() %>%
  summarize(mediator = mediator, 
            N = N,
            fit = list(model(data)),
            fit = list(broom::tidy(fit))) %>%
  select(mediator, N, fit) %>%
  unnest() %>%
  filter(grepl(":", term)) %>%
  mutate(estimate = papaja::printnum(estimate),
         p.value = pt(abs(statistic), df = N-3, lower.tail = F)*2,
         estimate = ifelse(p.value < .05, paste0(estimate,"*"), estimate),
         term = gsub("Week:", "",term)) %>%
  select(mediator, term, estimate) %>%
  spread(term, estimate) %>%
  kable(., col.names = c("Mediator", "Coefficient (Income)", "Coefficient of mediator")) %>%
  kable_styling()
```


##### Week 0 to first response

**Baseline model**
  
```{r, results = 'asis'}

demo.med = scored %>%
  group_by(CaregiverID) %>%
  filter(Week == min(Week)) %>%
  select(CaregiverID, poverty, all_of(meds))

change = scored0 %>%
  select(CaregiverID, Week, lonely) %>%
  group_by(CaregiverID) %>%
  arrange(Week) %>%
  filter(row_number() %in% c(1,2)) %>%
  mutate(Week = ifelse(Week == 0, "Before", "After")) %>%
  ungroup() %>%
  spread(Week, lonely) %>%
  mutate(Change = After-Before) %>%
  full_join(demo.med)


model = lm(Change ~ poverty, data = change)
broom::tidy(model) %>%
  kable(., col.names = c("Term", "Coef", "SE", "t", "p"),
        digits = c(0,2,2,2,3)) %>%
  kable_styling() 

change %>%
  filter(!is.na(poverty)) %>%
  group_by(poverty) %>%
  summarize(m = mean(Change,na.rm=T),
            sd = sd(Change,na.rm=T),
            n = n(),
            se = sd/sqrt(n),
            cv = qt(p = .975, df = n-1),
            moe = se*cv) %>%
  mutate(poverty = factor(poverty, labels = c("Middle to high income", "Low income"))) %>%
  ggplot(aes(x = poverty, y = m)) +
  geom_bar(aes(fill = poverty), stat = "identity") +
  geom_errorbar(aes(ymin = m-moe, ymax = m+moe), width = .5) +
  labs(x = "", y = "Change in lonely") +
  scale_fill_brewer(palette = "Dark2")+
  guides(fill = F) +
  theme_minimal()
```


**Can we explain the effect?**
  
```{r, results = 'asis'}
model =
  tibble(mediator = meds, 
         model = list(function(d) lm(Change ~ poverty + m.value, 
                                     data = d)))
change %>%
  gather("mediator", "m.value", all_of(meds)) %>%
  group_by(mediator) %>%
  nest() %>%
  mutate(N = purrr::map_dbl(data, nrow)) %>%
  left_join(model) %>%
  rowwise() %>%
  summarize(mediator = mediator, 
            N = N,
            fit = list(model(data)),
            fit = list(broom::tidy(fit))) %>%
  select(mediator, N, fit) %>%
  unnest(cols = c(fit)) %>%
  filter(term %in% c("poverty", "m.value")) %>%
  mutate(estimate = papaja::printnum(estimate),
         estimate = ifelse(p.value < .05, paste0(estimate,"*"), estimate)) %>%
  select(mediator, term, estimate) %>%
  spread(term, estimate) %>%
  kable(., col.names = c("Mediator", "Coefficient (Income)", "Coefficient of mediator")) %>%
  kable_styling()
```

### Child Externalizing

#### Plots

```{r, out.width=c('50%', '50%'), fig.show='hold'}
fussy_plot = trend_date_binary(variable = "fussy_current_some",
                                 dataset = scored, 
                                 label = "children are sometimes or often fussy or defiant",
                                 groups = c("poverty"),
                                 group_labels = "Low income households")
fussy_plot$plot

trend_week_binary(variable = "fussy", 
                  dataset = scored0,
                  label =  "Child externalizing", 
                  groups = "poverty", 
                  group_labels = c("Middle or high income","Low income"))

```


#### Test of slope {.tabset}

##### Weeks 1+


**Baseline model**
  
```{r, results = 'asis'}
model = lmer(fussy ~ Week*poverty + (1|CaregiverID), data = scored, control = control)
broom::tidy(model) %>%
  mutate(p.value = pt(abs(statistic), df = nrow(model@frame)-2, lower.tail = F)*2) %>%
  select(term, estimate, std.error, statistic, p.value) %>%
  kable(., col.names = c("Term", "Coef", "SE", "t", "p"),
        digits = c(0,2,2,2,3)) %>%
  kable_styling() %>%
  group_rows("Fixed effects", 1, 4) %>%
  group_rows("Random effects", 5, 6)
```

**Can we explain the effect?**
  
```{r, results = 'asis'}

model =
  tibble(mediator = meds, 
         model = list(function(d) lmer(fussy ~ Week*poverty + Week*m.value + 
                                         (1|CaregiverID), 
                                       data = d, 
                                       control = control)))
scored %>%
  gather("mediator", "m.value", all_of(meds)) %>%
  group_by(mediator) %>%
  nest() %>%
  mutate(N = purrr::map_dbl(data, nrow)) %>%
  left_join(model) %>%
  rowwise() %>%
  summarize(mediator = mediator, 
            N = N,
            fit = list(model(data)),
            fit = list(broom::tidy(fit))) %>%
  select(mediator, N, fit) %>%
  unnest() %>%
  filter(grepl(":", term)) %>%
  mutate(estimate = papaja::printnum(estimate),
         p.value = pt(abs(statistic), df = N-3, lower.tail = F)*2,
         estimate = ifelse(p.value < .05, paste0(estimate,"*"), estimate),
         term = gsub("Week:", "",term)) %>%
  select(mediator, term, estimate) %>%
  spread(term, estimate) %>%
  kable(., col.names = c("Mediator", "Coefficient (Income)", "Coefficient of mediator")) %>%
  kable_styling()
```

##### Week 0 to first response

**Baseline model**
  
```{r, results = 'asis'}

demo.med = scored %>%
  group_by(CaregiverID) %>%
  filter(Week == min(Week)) %>%
  select(CaregiverID, poverty, all_of(meds))

change = scored0 %>%
  select(CaregiverID, Week, fussy) %>%
  group_by(CaregiverID) %>%
  arrange(Week) %>%
  filter(row_number() %in% c(1,2)) %>%
  mutate(Week = ifelse(Week == 0, "Before", "After")) %>%
  ungroup() %>%
  spread(Week, fussy) %>%
  mutate(Change = After-Before) %>%
  full_join(demo.med)


model = lm(Change ~ poverty, data = change)
broom::tidy(model) %>%
  kable(., col.names = c("Term", "Coef", "SE", "t", "p"),
        digits = c(0,2,2,2,3)) %>%
  kable_styling() 

change %>%
  filter(!is.na(poverty)) %>%
  group_by(poverty) %>%
  summarize(m = mean(Change,na.rm=T),
            sd = sd(Change,na.rm=T),
            n = n(),
            se = sd/sqrt(n),
            cv = qt(p = .975, df = n-1),
            moe = se*cv) %>%
  mutate(poverty = factor(poverty, labels = c("Middle to high income", "Low income"))) %>%
  ggplot(aes(x = poverty, y = m)) +
  geom_bar(aes(fill = poverty), stat = "identity") +
  geom_errorbar(aes(ymin = m-moe, ymax = m+moe), width = .5) +
  labs(x = "", y = "Change in fussy") +
  scale_fill_brewer(palette = "Dark2")+
  guides(fill = F) +
  theme_minimal()
```


**Can we explain the effect?**
  
```{r, results = 'asis'}
model =
  tibble(mediator = meds, 
         model = list(function(d) lm(Change ~ poverty + m.value, 
                                     data = d)))
change %>%
  gather("mediator", "m.value", all_of(meds)) %>%
  group_by(mediator) %>%
  nest() %>%
  mutate(N = purrr::map_dbl(data, nrow)) %>%
  left_join(model) %>%
  rowwise() %>%
  summarize(mediator = mediator, 
            N = N,
            fit = list(model(data)),
            fit = list(broom::tidy(fit))) %>%
  select(mediator, N, fit) %>%
  unnest(cols = c(fit)) %>%
  filter(term %in% c("poverty", "m.value")) %>%
  mutate(estimate = papaja::printnum(estimate),
         estimate = ifelse(p.value < .05, paste0(estimate,"*"), estimate)) %>%
  select(mediator, term, estimate) %>%
  spread(term, estimate) %>%
  kable(., col.names = c("Mediator", "Coefficient (Income)", "Coefficient of mediator")) %>%
  kable_styling()
```

### Child Internalizing

#### Plots

```{r, out.width=c('50%', '50%'), fig.show='hold'}
fear_plot = trend_date_binary(variable = "fear_current_some",
                                 dataset = scored, 
                                 label = "children are sometimes or often anxious or fearful",
                                 groups = c("poverty"),
                                 group_labels = "Low income households")
fear_plot$plot

trend_week_binary(variable = "fear", 
                  dataset = scored0,
                  label =  "Child internalizing", 
                  groups = "poverty", 
                  group_labels = c("Middle or high income","Low income"))

```


#### Test of slope {.tabset}

##### Weeks 1+


**Baseline model**
  
```{r, results = 'asis'}
model = lmer(fear ~ Week*poverty + (1|CaregiverID), data = scored, control = control)
broom::tidy(model) %>%
  mutate(p.value = pt(abs(statistic), df = nrow(model@frame)-2, lower.tail = F)*2) %>%
  select(term, estimate, std.error, statistic, p.value) %>%
  kable(., col.names = c("Term", "Coef", "SE", "t", "p"),
        digits = c(0,2,2,2,3)) %>%
  kable_styling() %>%
  group_rows("Fixed effects", 1, 4) %>%
  group_rows("Random effects", 5, 6)
```

**Can we explain the effect?**
  
```{r, results = 'asis'}

model =
  tibble(mediator = meds, 
         model = list(function(d) lmer(fear ~ Week*poverty + Week*m.value + 
                                         (1|CaregiverID), 
                                       data = d, 
                                       control = control)))
scored %>%
  gather("mediator", "m.value", all_of(meds)) %>%
  group_by(mediator) %>%
  nest() %>%
  mutate(N = purrr::map_dbl(data, nrow)) %>%
  left_join(model) %>%
  rowwise() %>%
  summarize(mediator = mediator, 
            N = N,
            fit = list(model(data)),
            fit = list(broom::tidy(fit))) %>%
  select(mediator, N, fit) %>%
  unnest() %>%
  filter(grepl(":", term)) %>%
  mutate(estimate = papaja::printnum(estimate),
         p.value = pt(abs(statistic), df = N-3, lower.tail = F)*2,
         estimate = ifelse(p.value < .05, paste0(estimate,"*"), estimate),
         term = gsub("Week:", "",term)) %>%
  select(mediator, term, estimate) %>%
  spread(term, estimate) %>%
  kable(., col.names = c("Mediator", "Coefficient (Income)", "Coefficient of mediator")) %>%
  kable_styling()
```


##### Week 0 to first response

**Baseline model**
  
```{r, results = 'asis'}

demo.med = scored %>%
  group_by(CaregiverID) %>%
  filter(Week == min(Week)) %>%
  select(CaregiverID, poverty, all_of(meds))

change = scored0 %>%
  select(CaregiverID, Week, fear) %>%
  group_by(CaregiverID) %>%
  arrange(Week) %>%
  filter(row_number() %in% c(1,2)) %>%
  mutate(Week = ifelse(Week == 0, "Before", "After")) %>%
  ungroup() %>%
  spread(Week, fear) %>%
  mutate(Change = After-Before) %>%
  full_join(demo.med)


model = lm(Change ~ poverty, data = change)
broom::tidy(model) %>%
  kable(., col.names = c("Term", "Coef", "SE", "t", "p"),
        digits = c(0,2,2,2,3)) %>%
  kable_styling() 

change %>%
  filter(!is.na(poverty)) %>%
  group_by(poverty) %>%
  summarize(m = mean(Change,na.rm=T),
            sd = sd(Change,na.rm=T),
            n = n(),
            se = sd/sqrt(n),
            cv = qt(p = .975, df = n-1),
            moe = se*cv) %>%
  mutate(poverty = factor(poverty, labels = c("Middle to high income", "Low income"))) %>%
  ggplot(aes(x = poverty, y = m)) +
  geom_bar(aes(fill = poverty), stat = "identity") +
  geom_errorbar(aes(ymin = m-moe, ymax = m+moe), width = .5) +
  labs(x = "", y = "Change in fussy") +
  scale_fill_brewer(palette = "Dark2")+
  guides(fill = F) +
  theme_minimal()
```


**Can we explain the effect?**
  
```{r, results = 'asis'}
model =
  tibble(mediator = meds, 
         model = list(function(d) lm(Change ~ poverty + m.value, 
                                     data = d)))
change %>%
  gather("mediator", "m.value", all_of(meds)) %>%
  group_by(mediator) %>%
  nest() %>%
  mutate(N = purrr::map_dbl(data, nrow)) %>%
  left_join(model) %>%
  rowwise() %>%
  summarize(mediator = mediator, 
            N = N,
            fit = list(model(data)),
            fit = list(broom::tidy(fit))) %>%
  select(mediator, N, fit) %>%
  unnest(cols = c(fit)) %>%
  filter(term %in% c("poverty", "m.value")) %>%
  mutate(estimate = papaja::printnum(estimate),
         estimate = ifelse(p.value < .05, paste0(estimate,"*"), estimate)) %>%
  select(mediator, term, estimate) %>%
  spread(term, estimate) %>%
  kable(., col.names = c("Mediator", "Coefficient (Income)", "Coefficient of mediator")) %>%
  kable_styling()
```

# Analyses May 6

## Well-being during shelter-in-place 

```{r}
source(here("Functions/trend_days_sheltering_rolling.R"))
```


### Compared to general population {.tabset}

#### Caregiver anxiety

```{r anxiety}
anxiety_plot = trend_days_sheltering_binary(variable = "anxiety_current_some",
                                     dataset = scored, 
                                     label = "some or a lot of anxiety",
                                     groups = c("poverty"),
                                     group_labels = "Low income households")
anxiety_plot$plot
```

#### Caregiver depression

```{r depress}
depress_plot = trend_days_sheltering_binary(variable = "depress_current_some",
                                     dataset = scored, 
                                     label = "some or a lot of depression",
                                     groups = c("poverty"),
                                     group_labels = "Low income households")
depress_plot$plot
```

#### Caregiver stress

```{r stress}
stress_plot = trend_days_sheltering_binary(variable = "stress_current_some",
                                     dataset = scored, 
                                     label = "some or a lot of stress",
                                     groups = c("poverty"),
                                     group_labels = "Low income households")
stress_plot$plot
```


#### Caregiver loneliness

```{r }
lonely_plot = trend_days_sheltering_binary(variable = "lonely_current_some",
                                     dataset = scored, 
                                     label = "some or a lot of loneliness",
                                     groups = c("poverty"),
                                     group_labels = "Low income households")
lonely_plot$plot
```

#### Child externalizing

```{r fussy}
fussy_plot = trend_days_sheltering_binary(variable = "fussy_current_some",
                                     dataset = scored, 
                                     label = "children are sometimes or often fussy or defiant",
                                     groups = c("poverty"),
                                     group_labels = "Low income households")
fussy_plot$plot
```



#### Child internalizing

```{r fear}
fear_plot = trend_days_sheltering_binary(variable = "fear_current_some",
                                     dataset = scored, 
                                     label = "children are sometimes or often fearful or anxious",
                                     groups = c("poverty"),
                                     group_labels = "Low income households")
fear_plot$plot
```


### By geographic region {.tabset}


#### Caregiver anxiety

```{r}
poverty %>%
  filter(!is.na(region)) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "anxiety",
          desc_stat = "mean_ci")
```


```{r region anxiety}
anxiety_plot = trend_days_sheltering_cat(variable = "anxiety_current_some",
                                     dataset = poverty, 
                                     label = "some or a lot of anxiety",
                                     groups = c("region"),
                                     group_levels = unique(poverty$region))
anxiety_plot$plot
```

#### Caregiver depression

```{r}
poverty %>%
  filter(!is.na(region)) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "depress",
          desc_stat = "mean_ci")
```


```{r region depress}
depress_plot = trend_days_sheltering_cat(variable = "depress_current_some",
                                     dataset = poverty, 
                                     label = "some or a lot of depression",
                                     groups = c("region"),
                                     group_levels = unique(poverty$region))
depress_plot$plot
```

#### Caregiver stress

```{r}
poverty %>%
  filter(!is.na(region)) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "stress",
          desc_stat = "mean_ci")
```


```{r region stress}
stress_plot = trend_days_sheltering_cat(variable = "stress_current_some",
                                     dataset = poverty, 
                                     label = "some or a lot of stress",
                                     groups = c("region"),
                                     group_levels = unique(poverty$region))
stress_plot$plot
```


#### Child externalizing

```{r}
poverty %>%
  filter(!is.na(region)) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "fussy",
          desc_stat = "mean_ci")
```


```{r region fussy}
fussy_plot = trend_days_sheltering_cat(variable = "fussy_current_some",
                                     dataset = poverty, 
                                     label = "children are sometimes or often fussy or defiant",
                                     groups = c("region"),
                                     group_levels = unique(poverty$region))
fussy_plot$plot
```

#### Child internalizing

```{r}
poverty %>%
  filter(!is.na(region)) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "fear",
          desc_stat = "mean_ci")
```


```{r region fear}
fear_plot = trend_days_sheltering_cat(variable = "fear_current_some",
                                     dataset = poverty, 
                                     label = "children are sometimes or often fearful or anxious",
                                     groups = c("region"),
                                     group_levels = unique(poverty$region))
fear_plot$plot
```

### By childcare

```{r}
poverty = poverty %>%
  mutate(nonfamliy_cc = ifelse(hours_nonfamilyCC_current == 0, 
                               "No nonfamily care", 
                               "Nonfamily care")) 
tab_nonfamily_cc = table(poverty$nonfamliy_cc)
```

Of these caregivers, `r tab_nonfamily_cc[2]` have non-family childcare and `r tab_nonfamily_cc[1]` do not.

```{r}
poverty %>%
  select(nonfamliy_cc, anxiety, depress, stress, fussy, fear) %>%
  gather("emotion", "value", -nonfamliy_cc) %>%
  ggerrorplot(data = .,
          x = "emotion", 
          y = "value",
          color = "nonfamliy_cc",
          desc_stat = "mean_ci")
```


```{r}
poverty = poverty %>%
  mutate(famliy_cc = ifelse(hours_familyCC_current == 0, 
                               "No family care", 
                               "family care")) 
tab_family_cc = table(poverty$famliy_cc)
```

Of these caregivers, `r tab_family_cc[1]` have family childcare and `r tab_family_cc[2]` do not.

```{r}
poverty %>%
  select(famliy_cc, anxiety, depress, stress, fussy, fear) %>%
  gather("emotion", "value", -famliy_cc) %>%
  ggerrorplot(data = .,
          x = "emotion", 
          y = "value",
          color = "famliy_cc",
          desc_stat = "mean_ci")
```

### By use of online resources

```{r}
poverty %>%
  select(access_online, anxiety, depress, stress, fussy, fear) %>%
  gather("emotion", "value", -access_online) %>%
  mutate(access_online = as.factor(access_online)) %>%
  ggerrorplot(data = .,
          x = "emotion", 
          y = "value",
          color = "access_online",
          desc_stat = "mean_ci")
```




## Education 

### Compared to general population {.tabset}

#### Parent education interrupted

```{r parent edu}
parent_edu_plot = trend_days_sheltering_binary(variable = "parent_edu_interrupt",
                                     dataset = scored, 
                                     label = "their own education was disrupted",
                                     groups = c("poverty"),
                                     group_labels = "Low income households")
parent_edu_plot$plot
```

#### Child education interrupted

```{r child edu}
child_edu_plot = trend_days_sheltering_binary(variable = "child_edu_interrupt",
                                     dataset = scored, 
                                     label = "child(ren)'s education was disrupted",
                                     groups = c("poverty"),
                                     group_labels = "Low income households")
child_edu_plot$plot
```


### By geographic region


```{r out.width=c('50%', '50%'), fig.show='hold'}
poverty %>%
  filter(!is.na(region)) %>%
  select(region, parent_edu_interrupt, child_edu_interrupt) %>%
  gather("student", "value", -region) %>%
   mutate(student = factor(student, 
                          levels = c("parent_edu_interrupt", 
                                     "child_edu_interrupt"),
                          labels = c("Parent", "Child"))) %>%
  ggerrorplot(data = .,
          x = "region", 
          y = "value",
          color = "student",
          desc_stat = "mean_ci", 
          title = "Interrupted education ")

```



### By childcare

```{r}
poverty = poverty %>%
  mutate(nonfamliy_cc = ifelse(hours_nonfamilyCC_current == 0, 
                               "No nonfamily care", 
                               "Nonfamily care")) 
tab_nonfamily_cc = table(poverty$nonfamliy_cc)
```

Of these caregivers, `r tab_nonfamily_cc[2]` have non-family childcare and `r tab_nonfamily_cc[1]` do not.

```{r}
poverty %>%
  select(nonfamliy_cc, parent_edu_interrupt, child_edu_interrupt) %>%
  gather("student", "value", -nonfamliy_cc) %>%
  mutate(student = factor(student, 
                          levels = c("parent_edu_interrupt", 
                                     "child_edu_interrupt"),
                          labels = c("Parent", "Child"))) %>%
  ggerrorplot(data = .,
          x = "student", 
          y = "value",
          color = "nonfamliy_cc",
          desc_stat = "mean_ci")
```


```{r}
poverty = poverty %>%
  mutate(famliy_cc = ifelse(hours_familyCC_current == 0, 
                               "No family care", 
                               "family care")) 
tab_family_cc = table(poverty$famliy_cc)
```

Of these caregivers, `r tab_family_cc[1]` have family childcare and `r tab_family_cc[2]` do not.

```{r}
poverty %>%
  select(famliy_cc, parent_edu_interrupt, child_edu_interrupt) %>%
  gather("student", "value", -famliy_cc) %>%
  mutate(student = factor(student, 
                          levels = c("parent_edu_interrupt", 
                                     "child_edu_interrupt"),
                          labels = c("Parent", "Child"))) %>%
  ggerrorplot(data = .,
          x = "student", 
          y = "value",
          color = "famliy_cc",
          desc_stat = "mean_ci")
```

### By use of online resources

```{r}
poverty %>%
  select(access_online, parent_edu_interrupt, child_edu_interrupt) %>%
  gather("student", "value", -access_online) %>%
  mutate(access_online = as.factor(access_online)) %>%
  mutate(student = factor(student, 
                          levels = c("parent_edu_interrupt", 
                                     "child_edu_interrupt"),
                          labels = c("Parent", "Child"))) %>%
  ggerrorplot(data = .,
          x = "student", 
          y = "value",
          color = "access_online",
          desc_stat = "mean_ci")
```

## Differences {.tabset}

### Lost income

```{r}
week1 = scored %>%
  group_by(CaregiverID) %>%
  filter(Week > 0) %>%
  filter(Week == min(Week)) %>%
  filter(!is.na(poverty))

chisq.test(week1$poverty, week1$income_decreaed)
week1 %>%
  ungroup()%>%
  select(poverty, income_decreaed) %>%
  group_by(poverty) %>%
  summarize(n = n(),
            decreased_income = sum(income_decreaed,na.rm = T),
            percent = decreased_income/n)
```

### Lost non-family childcare

```{r}
chisq.test(week1$poverty, week1$decrease_nonfamilyCC)
week1 %>%
  ungroup()%>%
  select(poverty, decrease_nonfamilyCC) %>%
  group_by(poverty) %>%
  summarize(n = n(),
            decrease_nonfamilyCC = sum(decrease_nonfamilyCC,na.rm = T),
            percent = decrease_nonfamilyCC/n)
```

### Trouble paying for basics

```{r}
chisq.test(week1$poverty, week1$difficulty_basics)
week1 %>%
  ungroup()%>%
  select(poverty, difficulty_basics) %>%
  group_by(poverty) %>%
  summarize(n = n(),
            difficulty_basics = sum(difficulty_basics,na.rm = T),
            percent = difficulty_basics/n)
```

### Delayed healthcare

```{r}
chisq.test(week1$poverty, week1$delay_healthcare)
week1 %>%
  ungroup()%>%
  select(poverty, delay_healthcare) %>%
  group_by(poverty) %>%
  summarize(n = n(),
            delay_healthcare = sum(delay_healthcare,na.rm = T),
            percent = delay_healthcare/n)
```

## Testing predictors of well-being in this demo

```{r}

mlm.model = function(abdata){
  mod = lmer(o.value~p.value + (1|CaregiverID),
             data = abdata,
             control=lmerControl(check.nobs.vs.nlev="ignore",
                                 check.nobs.vs.nRE = "ignore"),)
  return(mod)
}
```


```{r}
poverty = poverty %>%
  mutate(children2 = ifelse(num_children_raw >= 2, 1, 0),
         children3 = ifelse(num_children_raw >= 3, 1, 0))
predictors = c("income_decreaed",
               "employment_decreased",
               "difficulty_basics",
               "children2",
               "children3",
               "access_online",
               "access_telehealth",
               "single",
               "child_edu_interrupt",
               "parent_edu_interrupt",
               "delay_healthcare",
               "black",
               "latinx",
               "disability",
               "essential")
predictor.labels = c(
  "Lost income since pandemic",
  "Lost employment since pandemic",
  "Have difficulty paying for basics",
  "Two or more children in household",
  "Three or more children in household",
  "Can access online serivices",
  "Can access telehealth serivices",
  "Single parents",
  "Child education interrupted",
  "Parent education interrupted",
  "Have delayed healthcare",
  "African American",
  "Latinx",
  "Caregivers of children with disabilities",
  "Essential employees"
)
unique = poverty %>%
  group_by(CaregiverID) %>%
  filter(Week == min(Week)) %>%
  ungroup()

N = apply(unique[,predictors], 2, FUN = sum, na.rm=T)

predictor.labels = paste0(predictor.labels, " (N = ", N, ")")

pred.table = poverty %>%
  #censor number of children
  mutate(num_children_raw = ifelse(num_children_raw > 4, 4, num_children_raw)) %>%
  select(CaregiverID, anxiety, depress, stress,
         fussy, fear, all_of(predictors)) %>%
  gather("outcome", "o.value", anxiety, depress, stress,
         fussy, fear) %>%
  gather("predictor", "p.value", all_of(predictors)) %>%
  group_by(outcome,predictor) %>%
  nest() %>%
  mutate(model = purrr::map(data, mlm.model)) %>%
  mutate(output = purrr::map(model, broom::tidy)) %>%
  select(outcome, predictor, output) %>%
  unnest(output) %>%
  filter(term == "p.value") %>%
  mutate(pvalue = purrr::map_dbl(statistic,
                              .f = function(x) pt(q = abs(x),
                                                  df = 250,
                                                  lower.tail = F)*2)) %>%
  select(outcome, predictor, estimate, std.error, pvalue) %>%
  ungroup() %>%
  mutate(holm = p.adjust(pvalue,  method = "holm")) %>%
  mutate(outcome = factor(outcome,
                          levels = c("anxiety", "depress", "stress",
         "fussy", "fear"),
         labels = c("Caregiver anxiety", "Caregiver depression", "Caregiver stress",
         "Child externalzing", "Child internalizing")))
```

```{r}
source(here("Functions/summarizing_report.R"))
```

```{r}
first.row = sapply(predictors,
                   first_instance,
                   string = pred.table$predictor)
last.row = sapply(predictors,
                  last_instance,
                  string = pred.table$predictor)


each_string = paste0("group_rows(group_label = \" ",
                     predictor.labels,
                     "\" , start_row = ",
                     first.row,
                     ", end_row = ",
                     last.row,
                     ")")
each_string = paste(each_string, collapse = " %>% ")


beginning= "pred.table %>% select(-predictor) %>% kable(., col.names = c(\"Outcome\", \"Coefficient Estimate\", \"Std. Error\", \"p-value\", \" Corrected p-value\"), digits = c(1,2,2,3,3)) %>%
  kable_styling() %>%
footnote(general = \"Coefficients estimated using a multi-level model in which responses are nested within caregivers. In the case of binary predictors, we report the number (N) of participants who fall into the category listed. p-values are adjusted using a Holm correction\") %>%"

eval(parse(text = paste0(beginning, each_string)))
```


### Trends by income {.tabset}

#### Caregiver anxiety

```{r }
anxiety_plot = trend_days_sheltering_cat(variable = "anxiety_current_some",
                                     dataset = poverty,
                                     label = "some or a lot of anxiety",
                                     groups = c("difficulty_basics"),
                                     group_levels = c(0,1),
                                     group_labels = c("No difficulty",
                                                      "Difficulty paying for basic necessities"))
anxiety_plot$plot
```

#### Caregiver depression

```{r }
depress_plot = trend_days_sheltering_cat(variable = "depress_current_some",
                                     dataset = poverty,
                                     label = "some or a lot of depression",
                                     groups = c("difficulty_basics"),
                                     group_levels = c(0,1),
                                     group_labels = c("No difficulty",
                                                      "Difficulty paying for basic necessities"))
depress_plot$plot
```

#### Caregiver stress

```{r }
stress_plot = trend_days_sheltering_cat(variable = "stress_current_some",
                                     dataset = poverty,
                                     label = "some or a lot of stress",
                                     groups = c("difficulty_basics"),
                                     group_levels = c(0,1),
                                     group_labels = c("No difficulty",
                                                      "Difficulty paying for basic necessities"))
stress_plot$plot
```

#### Child externalizing

```{r }
fussy_plot = trend_days_sheltering_cat(variable = "fussy_current_some",
                                     dataset = poverty,
                                     label = "children are sometimes or often fussy or defiant",
                                     groups = c("difficulty_basics"),
                                     group_levels = c(0,1),
                                     group_labels = c("No difficulty",
                                                      "Difficulty paying for basic necessities"))
fussy_plot$plot
```

#### Child internalizing

```{r }
fear_plot = trend_days_sheltering_cat(variable = "fear_current_some",
                                     dataset = poverty,
                                     label = "children are sometimes or often fearful or anxious",
                                     groups = c("difficulty_basics"),
                                     group_levels = c(0,1),
                                     group_labels = c("No difficulty",
                                                      "Difficulty paying for basic necessities"))
fear_plot$plot
```

### Child Internalizing

#### Plots

```{r, out.width=c('50%', '50%'), fig.show='hold'}
fear_plot = trend_date_binary(variable = "fear_current_some",
                                 dataset = scored, 
                                 label = "children are sometimes or often too fearful or anxious",
                                 groups = c("poverty"),
                                 group_labels = "Low income households")
fear_plot$plot

trend_week_binary(variable = "fear", 
                  dataset = scored0,
                  label =  "Child Internalizing", 
                  groups = "poverty", 
                  group_labels = c("Middle or high income","Low income"))

```


#### Test of slope {.tabset}

##### Weeks 1+


**Baseline model**
  
```{r, results = 'asis'}
model = lmer(fear ~ Week*poverty + (1|CaregiverID), data = scored, control = control)
broom::tidy(model) %>%
  mutate(p.value = pt(abs(statistic), df = nrow(model@frame)-2, lower.tail = F)*2) %>%
  select(term, estimate, std.error, statistic, p.value) %>%
  kable(., col.names = c("Term", "Coef", "SE", "t", "p"),
        digits = c(0,2,2,2,3)) %>%
  kable_styling() %>%
  group_rows("Fixed effects", 1, 4) %>%
  group_rows("Random effects", 5, 6)
```

**Can we explain the effect?**
  
```{r, results = 'asis'}

model =
  tibble(mediator = meds, 
         model = list(function(d) lmer(fear ~ Week*poverty + Week*m.value + 
                                         (1|CaregiverID), 
                                       data = d, 
                                       control = control)))
scored %>%
  gather("mediator", "m.value", all_of(meds)) %>%
  group_by(mediator) %>%
  nest() %>%
  mutate(N = purrr::map_dbl(data, nrow)) %>%
  left_join(model) %>%
  rowwise() %>%
  summarize(mediator = mediator, 
            N = N,
            fit = list(model(data)),
            fit = list(broom::tidy(fit))) %>%
  select(mediator, N, fit) %>%
  unnest() %>%
  filter(grepl(":", term)) %>%
  mutate(estimate = papaja::printnum(estimate),
         p.value = pt(abs(statistic), df = N-3, lower.tail = F)*2,
         estimate = ifelse(p.value < .05, paste0(estimate,"*"), estimate),
         term = gsub("Week:", "",term)) %>%
  select(mediator, term, estimate) %>%
  spread(term, estimate) %>%
  kable(., col.names = c("Mediator", "Coefficient (Income)", "Coefficient of mediator")) %>%
  kable_styling()
```


##### Week 0 to first response

**Baseline model**
  
```{r, results = 'asis'}

demo.med = scored %>%
  group_by(CaregiverID) %>%
  filter(Week == min(Week)) %>%
  select(CaregiverID, poverty, all_of(meds))

change = scored0 %>%
  select(CaregiverID, Week, fear) %>%
  group_by(CaregiverID) %>%
  arrange(Week) %>%
  filter(row_number() %in% c(1,2)) %>%
  mutate(Week = ifelse(Week == 0, "Before", "After")) %>%
  ungroup() %>%
  spread(Week, fear) %>%
  mutate(Change = After-Before) %>%
  full_join(demo.med)


model = lm(Change ~ poverty, data = change)
broom::tidy(model) %>%
  kable(., col.names = c("Term", "Coef", "SE", "t", "p"),
        digits = c(0,2,2,2,3)) %>%
  kable_styling() 

change %>%
  filter(!is.na(poverty)) %>%
  group_by(poverty) %>%
  summarize(m = mean(Change,na.rm=T),
            sd = sd(Change,na.rm=T),
            n = n(),
            se = sd/sqrt(n),
            cv = qt(p = .975, df = n-1),
            moe = se*cv) %>%
  mutate(poverty = factor(poverty, labels = c("Middle to high income", "Low income"))) %>%
  ggplot(aes(x = poverty, y = m)) +
  geom_bar(aes(fill = poverty), stat = "identity") +
  geom_errorbar(aes(ymin = m-moe, ymax = m+moe), width = .5) +
  labs(x = "", y = "Change in fear") +
  scale_fill_brewer(palette = "Dark2")+
  guides(fill = F) +
  theme_minimal()
```


**Can we explain the effect?**
  
```{r, results = 'asis'}
model =
  tibble(mediator = meds, 
         model = list(function(d) lm(Change ~ poverty + m.value, 
                                     data = d)))
change %>%
  gather("mediator", "m.value", all_of(meds)) %>%
  group_by(mediator) %>%
  nest() %>%
  mutate(N = purrr::map_dbl(data, nrow)) %>%
  left_join(model) %>%
  rowwise() %>%
  summarize(mediator = mediator, 
            N = N,
            fit = list(model(data)),
            fit = list(broom::tidy(fit))) %>%
  select(mediator, N, fit) %>%
  unnest(cols = c(fit)) %>%
  filter(term %in% c("poverty", "m.value")) %>%
  mutate(estimate = papaja::printnum(estimate),
         estimate = ifelse(p.value < .05, paste0(estimate,"*"), estimate)) %>%
  select(mediator, term, estimate) %>%
  spread(term, estimate) %>%
  kable(., col.names = c("Mediator", "Coefficient (Income)", "Coefficient of mediator")) %>%
  kable_styling()
```