---
title: "Discrimination and concerns for children"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---


```{r riser1-1, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
```

```{r riser1-2 }
library(conflicted)
library(here)
library(ggpubr)
conflict_prefer("group_rows", "kableExtra")
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")
conflict_prefer("map", "purrr")
library(plotly)
library(brolgar)
```

```{r riser1-3 }
source(here("Scripts/score data.R")) 
source(here("Functions/pomp.R"))
```

```{r riser1-4 }
concernvars = names(scored)[grepl("^riserconcern", names(scored))]
scored$composite_concern = rowMeans(scored[,concernvars], na.rm=T)

discrimvars = names(scored)[grepl("^discrim", names(scored))]
scored$discrimination = rowMeans(scored[,discrimvars], na.rm=T)

scored = scored %>%
  filter(!is.na(discrimination)) %>%
  mutate_at(vars(starts_with("riserconcern")), 
            factor,
            levels = c(0:3),
            labels = c("Never", "Rarely", "Some of the time", "Most of the time")) %>%
  mutate_at(vars(starts_with("discrim_"), talkchallenge, talkadvantage), 
            factor,
            levels = c(0,1),
            labels = c("No", "Yes")) %>%
  mutate(black_latinx = case_when(
    black == 1 & latinx == 1 ~ 1,
    black == 0 ~ 0, 
    latinx == 0 ~ 0,
    TRUE ~ NA_real_
  )) %>%
  filter(!is.na(Week)) %>%
  group_by(Week) %>%
  mutate(Date = case_when(
    Week == 0 ~ as.Date("2020-03-01"), 
    Week > 0 ~ min(Date, na.rm=T))) 
```


# Representativeness disclaimer

```{r riser1-5 }
scored_full = scored

scored = scored %>%
  filter(Week > 0)

n_care = length(unique(scored$CaregiverID))
date.min = format(min(as.Date(scored$Date), na.rm = T), format = "%B %d, %Y")
date.max = format(max(as.Date(scored$Date), na.rm = T), format = "%B %d, %Y")
perc = scored %>%
  group_by(CaregiverID) %>%
  filter(Week == max(Week)) 
perc.black = 100*sum(perc$black, na.rm=T)/nrow(perc)
perc.latinx = 100*sum(perc$latinx, na.rm=T)/nrow(perc)
perc.bl = 100*sum(perc$black_latinx, na.rm=T)/nrow(perc)
perc.fpl = 100*sum(perc$poverty150, na.rm=T)/nrow(perc)

scored = scored_full %>%
  mutate(
    blackIncome = case_when(
      black == 1 & poverty150 == 1 ~ "Black, Low income",
      black == 1 & poverty150 == 0 ~ "Black, High income",
      black == 0 & poverty150 == 1 ~ "Non-Black, Low income",
      black == 0 & poverty150 == 0 ~ "Non-Black, High income",
      TRUE ~ NA_character_),
    black = factor(black, labels = c("Non-Black", "Black"))
    )
```

These analyses are based on responses collected from `r papaja::printnum(n_care, format = "d")` caregivers between the dates of `r date.min` and `r date.max`. These caregivers represent a range of voices: `r papaja::printnum(perc.black)`\% are Black/African American, `r papaja::printnum(perc.latinx)`\% are LatinX, (`r papaja::printnum(perc.bl)`\% report being both Black/African American and LatinX,) and `r papaja::printnum(perc.fpl)`\% live at or below 1.5 times the federal poverty line. Proportions/percentages are calculated based on the item-level response rates, not out of the total sample size. The data for these analyses are *not* weighted.

# Concerns for children

```{r riser1-6 }
composite_grps = function(variable, groups, data = scored){
  
  plot = data %>%
    filter(!is.na({{variable}})) %>%
    dplyr::filter(!is.na({{groups}})) %>%
  group_by(Date, {{groups}}) %>%
  summarize(m = mean({{variable}}),
            sd = sd({{variable}}),
            n=n()) %>%
  mutate(se = sqrt(sd/n),
         moe = se*qt(p = .975, df = n-1)) %>%
  ggplot(aes(x = Date, 
             y = m,
             group = 1,
             color = {{groups}},
             text = paste0(
               "Date: ", Date,
               "\nGroup: ", {{groups}},
               "\nCount: ", n,
               "\nMean: ", round(m,2),
               "\nLower 95% CI: ", round(m-moe,2),
               "\nLower 95% CI: ", round(m+moe,2)))) +
  geom_errorbar(aes(ymin = m-moe, ymax = m+moe), 
                width = 3,
                position = position_dodge(1)) +
  geom_point(position = position_dodge(1)) +
  geom_line() +
  labs(x = "Date", title = "Average concern for children", y = NULL, color = NULL,
       caption = "Dates represent first date of data collection per wave,except for March 1, which is an arbitrary\ndate representing responses to questions about life prior to the pandemic.") +
  theme_pubr()

ggplotly(plot, tooltip = "text")
}
```


```{r riser1-7 }
concerns_grps = function(variable, groups, data = scored){
  
  plot = data %>%
    filter(!is.na({{variable}})) %>%
    filter(!is.na({{groups}})) %>%
  group_by(Date, {{variable}},{{groups}}) %>%
  summarize(n=n()) %>%
    group_by(Date, {{groups}}) %>%
  mutate(percent = 100*n/sum(n),
         Date = format.Date(Date, "%B %d")) %>%
  ggplot(aes(x = {{variable}}, 
             y = percent,
             #group = 1,
             fill = {{groups}},
             text = paste0(
               "Date: ", Date,
               "\nGroup: ", {{groups}},
               "\nCount: ", n,
               "\nPercent: ", round(percent,2)))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = NULL, title = "I am____ concerned for my child(ren)", y = "Percent", fill = NULL,
       caption = "Dates represent first date of data collection per wave,except for March 1, which is an arbitrary\ndate representing responses to questions about life prior to the pandemic.") +
    facet_wrap(~Date) +
    coord_flip()+
  theme_pubr()

ggplotly(plot, tooltip = "text")
}
```

```{r riser1-8}
change_grps = function(variable, groups, data = scored){
  
  plot = data %>%
    filter(Week %in% c(0,21)) %>%
    filter(!is.na({{groups}})) %>%
    select(CaregiverID, {{groups}}, Week, {{variable}}) %>%
    mutate(Week = ifelse(Week == 0, "Pre", "Current")) %>%
    spread(Week, {{variable}}) %>%
    group_by({{groups}}, Pre, Current) %>%
    summarize(n = n()) %>%
    filter(!is.na(Pre) & !is.na(Current)) %>%
    ungroup() %>%
    mutate(group = row_number()) %>%
    group_by({{groups}}) %>%
    mutate(percent = 100*n/sum(n)) %>%
    ungroup() %>%
    gather("Week", "Response", Pre, Current) %>%
    mutate(Week = ifelse(Week == "Pre", "2020-03-01", "2020-08-25"),
           Week = as.Date(Week),
           Response = factor(Response,
                             levels = c("Never","Rarely", "Some of the time", "Most of the time")))  %>%
  ggplot(aes(x = Week,
             y = Response,
             group = group,
             color = percent)) +
  geom_point(alpha = .2) +
  geom_line(alpha = .3) +
    scale_color_gradient(low = "blue", high = "black")+
  labs(x = "Date", title = "I am____ concerned for my child(ren)", y = NULL, color = NULL,
       caption = "Dates represent first date of data collection per wave,except for March 1, which is an arbitrary\ndate representing responses to questions about life prior to the pandemic.") +
    facet_wrap(facets = vars({{groups}})) +
  theme_pubr()

ggplotly(plot, tooltip = "text")

}
```


```{r riser1-9}
change_grps_simple = function(variable, groups, data = scored){
  
  data %>%
    filter(!is.na({{variable}})) %>%
    filter(!is.na({{groups}})) %>%
    ggplot(aes(x = Date,
               y= {{variable}},
               group = CaregiverID,
               color = {{groups}})) +
    geom_line(alpha = .1) +
    labs(x = "Date", y = NULL, color = NULL,
         title = "Change in concern",
         caption = "Dates represent first date of data collection per wave,except for March 1, which is an arbitrary\ndate representing responses to questions about life prior to the pandemic.") +
    facet_wrap(facets = vars({{groups}})) +
    theme_pubr()
}
  
```



## Composite{.tabset}

This composite was created by treating the 9 "concerns for children" variables as continuous and averageing responses across those items. The resulting index is a measure that ranges from 0 (Never concerned) to 3 (Concerned most of the time).

### All

```{r riser1-10 }
plot = scored %>%
  filter(!is.na(composite_concern)) %>%
  group_by(Date) %>%
  summarize(m = mean(composite_concern),
            sd = sd(composite_concern),
            n=n()) %>%
  mutate(se = sqrt(sd/n),
         moe = se*qt(p = .975, df = n-1)) %>%
  ggplot(aes(x = Date, 
             y = m,
             text = paste0(
               "Date: ", Date,
               "\nCount: ", n,
               "\nMean: ", round(m,2),
               "\nLower 95% CI: ", round(m-moe,2),
               "\nLower 95% CI: ", round(m+moe,2)),
             group = 1)) +
  geom_errorbar(aes(ymin = m-moe, ymax = m+moe), width = 3) +
  geom_point() +
  geom_line() +
  labs(x = "Date", title = "Average Concern for children", y = NULL,
       caption = "Dates represent first date of data collection per wave,except for March 1, which is an arbitrary\ndate representing responses to questions about life prior to the pandemic.") +
  theme_pubr()

ggplotly(plot, tooltip = "text")
```

### Black

```{r riser1-11 }
composite_grps(composite_concern, black)
```


### Black + Income

```{r riser1-12 }
composite_grps(composite_concern, blackIncome)
```

## Getting poor care and education{.tabset}

### All

```{r riser1-13}
plot = scored %>%
  filter(!is.na(riserconcern_1)) %>%
  group_by(Date, riserconcern_1) %>%
  summarize(n=n()) %>%
  group_by(Date) %>%
  mutate(percent = 100*n/sum(n)) %>%
  ggplot(aes(x = Date, 
             y = percent,
             color = riserconcern_1),
             text = paste0(
               "Date: ", Date,
               "\nResponse: ", riserconcern_1,
               "\nCount: ", n,
               "\nPercent: ", round(percent,2))) +
  geom_line() +
  labs(x = "Date", title = "Percent choosing response____", y = NULL, color = NULL,
       caption = "Dates represent first date of data collection per wave,except for March 1, which is an arbitrary\ndate representing responses to questions about life prior to the pandemic.") +
  theme_pubr()

ggplotly(plot, tooltip = "text")
```

### Black

```{r riser1-14}
concerns_grps(riserconcern_1, black)
```

```{r riser1-15}
change_grps_simple(riserconcern_1, black)
```

### Black + Income

```{r riser1-16}
concerns_grps(riserconcern_1, blackIncome)
```

```{r riser1-17}
change_grps_simple(riserconcern_1, blackIncome)
```


## Being mistreated by adults{.tabset}

### All

```{r riser1-18}
plot = scored %>%
  filter(!is.na(riserconcern_2)) %>%
  group_by(Date, riserconcern_2) %>%
  summarize(n=n()) %>%
  group_by(Date) %>%
  mutate(percent = 100*n/sum(n)) %>%
  ggplot(aes(x = Date, 
             y = percent,
             color = riserconcern_2),
             text = paste0(
               "Date: ", Date,
               "\nResponse: ", riserconcern_2,
               "\nCount: ", n,
               "\nPercent: ", round(percent,2))) +
  geom_line() +
  labs(x = "Date", title = "Percent choosing response____", y = NULL, color = NULL,
       caption = "Dates represent first date of data collection per wave,except for March 1, which is an arbitrary\ndate representing responses to questions about life prior to the pandemic.") +
  theme_pubr()

ggplotly(plot, tooltip = "text")
```

### Black

```{r riser1-19}
concerns_grps(riserconcern_2, black)
```

```{r riser1-20}
change_grps_simple(riserconcern_2, black)
```

### Black + Income

```{r riser1-21}
concerns_grps(riserconcern_2, blackIncome)
```

```{r riser1-22}
change_grps_simple(riserconcern_2, blackIncome)
```


## Getting stopped in a white neighborhood{.tabset}

### All

```{r riser1-23}
plot = scored %>%
  filter(!is.na(riserconcern_3)) %>%
  group_by(Date, riserconcern_3) %>%
  summarize(n=n()) %>%
  group_by(Date) %>%
  mutate(percent = 100*n/sum(n)) %>%
  ggplot(aes(x = Date, 
             y = percent,
             color = riserconcern_3),
             text = paste0(
               "Date: ", Date,
               "\nResponse: ", riserconcern_3,
               "\nCount: ", n,
               "\nPercent: ", round(percent,2))) +
  geom_line() +
  labs(x = "Date", title = "Percent choosing response____", y = NULL, color = NULL,
       caption = "Dates represent first date of data collection per wave,except for March 1, which is an arbitrary\ndate representing responses to questions about life prior to the pandemic.") +
  theme_pubr()

ggplotly(plot, tooltip = "text")
```

### Black

```{r riser1-24}
concerns_grps(riserconcern_3, black)
```

```{r riser1-25}
change_grps_simple(riserconcern_3, black)
```

### Black + Income

```{r riser1-26}
concerns_grps(riserconcern_3, blackIncome)
```

```{r riser1-27}
change_grps_simple(riserconcern_3, blackIncome)
```


## Being punished more harshly than others{.tabset}

### All

```{r riser1-28}
plot = scored %>%
  filter(!is.na(riserconcern_4)) %>%
  group_by(Date, riserconcern_4) %>%
  summarize(n=n()) %>%
  group_by(Date) %>%
  mutate(percent = 100*n/sum(n)) %>%
  ggplot(aes(x = Date, 
             y = percent,
             color = riserconcern_4),
             text = paste0(
               "Date: ", Date,
               "\nResponse: ", riserconcern_4,
               "\nCount: ", n,
               "\nPercent: ", round(percent,2))) +
  geom_line() +
  labs(x = "Date", title = "Percent choosing response____", y = NULL, color = NULL,
       caption = "Dates represent first date of data collection per wave,except for March 1, which is an arbitrary\ndate representing responses to questions about life prior to the pandemic.") +
  theme_pubr()

ggplotly(plot, tooltip = "text")
```

### Black

```{r riser1-29}
concerns_grps(riserconcern_4, black)
```

```{r riser1-30}
change_grps_simple(riserconcern_4, black)
```

### Black + Income

```{r riser1-31}
concerns_grps(riserconcern_4, blackIncome)
```

```{r riser1-32}
change_grps_simple(riserconcern_4, blackIncome)
```



## Being discourage from trying new things{.tabset}

### All

```{r riser1-33}
plot = scored %>%
  filter(!is.na(riserconcern_5)) %>%
  group_by(Date, riserconcern_5) %>%
  summarize(n=n()) %>%
  group_by(Date) %>%
  mutate(percent = 100*n/sum(n)) %>%
  ggplot(aes(x = Date, 
             y = percent,
             color = riserconcern_5),
             text = paste0(
               "Date: ", Date,
               "\nResponse: ", riserconcern_5,
               "\nCount: ", n,
               "\nPercent: ", round(percent,2))) +
  geom_line() +
  labs(x = "Date", title = "Percent choosing response____", y = NULL, color = NULL,
       caption = "Dates represent first date of data collection per wave,except for March 1, which is an arbitrary\ndate representing responses to questions about life prior to the pandemic.") +
  theme_pubr()

ggplotly(plot, tooltip = "text")
```

### Black

```{r riser1-34}
concerns_grps(riserconcern_5, black)
```

```{r riser1-35}
change_grps_simple(riserconcern_5, black)
```

### Black + Income

```{r riser1-36}
concerns_grps(riserconcern_5, blackIncome)
```

```{r riser1-37}
change_grps_simple(riserconcern_5, blackIncome)
```



## Being considered less attractive{.tabset}

### All

```{r riser1-38}
plot = scored %>%
  filter(!is.na(riserconcern_6)) %>%
  group_by(Date, riserconcern_6) %>%
  summarize(n=n()) %>%
  group_by(Date) %>%
  mutate(percent = 100*n/sum(n)) %>%
  ggplot(aes(x = Date, 
             y = percent,
             color = riserconcern_6),
             text = paste0(
               "Date: ", Date,
               "\nResponse: ", riserconcern_6,
               "\nCount: ", n,
               "\nPercent: ", round(percent,2))) +
  geom_line() +
  labs(x = "Date", title = "Percent choosing response____", y = NULL, color = NULL,
       caption = "Dates represent first date of data collection per wave,except for March 1, which is an arbitrary\ndate representing responses to questions about life prior to the pandemic.") +
  theme_pubr()

ggplotly(plot, tooltip = "text")
```

### Black

```{r riser1-39}
concerns_grps(riserconcern_6, black)
```

```{r riser1-40}
change_grps_simple(riserconcern_6, black)
```

### Black + Income

```{r riser1-41}
concerns_grps(riserconcern_6, blackIncome)
```

```{r riser1-42}
change_grps_simple(riserconcern_6, blackIncome)
```



## Having fewer choices in life{.tabset}

### All

```{r riser1-43}
plot = scored %>%
  filter(!is.na(riserconcern_7)) %>%
  group_by(Date, riserconcern_7) %>%
  summarize(n=n()) %>%
  group_by(Date) %>%
  mutate(percent = 100*n/sum(n)) %>%
  ggplot(aes(x = Date, 
             y = percent,
             color = riserconcern_7),
             text = paste0(
               "Date: ", Date,
               "\nResponse: ", riserconcern_7,
               "\nCount: ", n,
               "\nPercent: ", round(percent,2))) +
  geom_line() +
  labs(x = "Date", title = "Percent choosing response____", y = NULL, color = NULL,
       caption = "Dates represent first date of data collection per wave,except for March 1, which is an arbitrary\ndate representing responses to questions about life prior to the pandemic.") +
  theme_pubr()

ggplotly(plot, tooltip = "text")
```

### Black

```{r riser1-44}
concerns_grps(riserconcern_7, black)
```

```{r riser1-45}
change_grps_simple(riserconcern_7, black)
```

### Black + Income

```{r riser1-46}
concerns_grps(riserconcern_7, blackIncome)
```

```{r riser1-47}
change_grps_simple(riserconcern_7, blackIncome)
```



## Being excluded from events or groups{.tabset}

### All

```{r riser1-48}
plot = scored %>%
  filter(!is.na(riserconcern_8)) %>%
  group_by(Date, riserconcern_8) %>%
  summarize(n=n()) %>%
  group_by(Date) %>%
  mutate(percent = 100*n/sum(n)) %>%
  ggplot(aes(x = Date, 
             y = percent,
             color = riserconcern_8),
             text = paste0(
               "Date: ", Date,
               "\nResponse: ", riserconcern_8,
               "\nCount: ", n,
               "\nPercent: ", round(percent,2))) +
  geom_line() +
  labs(x = "Date", title = "Percent choosing response____", y = NULL, color = NULL,
       caption = "Dates represent first date of data collection per wave,except for March 1, which is an arbitrary\ndate representing responses to questions about life prior to the pandemic.") +
  theme_pubr()

ggplotly(plot, tooltip = "text")
```

### Black

```{r riser1-49}
concerns_grps(riserconcern_8, black)
```

```{r riser1-50}
change_grps_simple(riserconcern_8, black)
```

### Black + Income

```{r riser1-51}
concerns_grps(riserconcern_8, blackIncome)
```

```{r riser1-52}
change_grps_simple(riserconcern_8, blackIncome)
```



## Being treated unfairly by other children{.tabset}

### All

```{r riser1-53}
plot = scored %>%
  filter(!is.na(riserconcern_9)) %>%
  group_by(Date, riserconcern_9) %>%
  summarize(n=n()) %>%
  group_by(Date) %>%
  mutate(percent = 100*n/sum(n)) %>%
  ggplot(aes(x = Date, 
             y = percent,
             color = riserconcern_9),
             text = paste0(
               "Date: ", Date,
               "\nResponse: ", riserconcern_9,
               "\nCount: ", n,
               "\nPercent: ", round(percent,2))) +
  geom_line() +
  labs(x = "Date", title = "Percent choosing response____", y = NULL, color = NULL,
       caption = "Dates represent first date of data collection per wave,except for March 1, which is an arbitrary\ndate representing responses to questions about life prior to the pandemic.") +
  theme_pubr()

ggplotly(plot, tooltip = "text")
```

### Black

```{r riser1-54}
concerns_grps(riserconcern_9, black)
```

```{r riser1-55}
change_grps_simple(riserconcern_9, black)
```

### Black + Income

```{r riser1-56}
concerns_grps(riserconcern_9, blackIncome)
```

```{r riser1-57}
change_grps_simple(riserconcern_9, blackIncome)
```

# Discrimination

## Composite{.tabset}

This composite was created by treating the 12 discrimination variables as continuous and averageing responses across those items. The resulting index is a measure that ranges from 0 (Endorsed no discrimination items) to 1 (Endorsed all discrimination items).

### All

```{r riser1-58 }
plot = scored %>%
  filter(!is.na(discrimination)) %>%
  group_by(Date) %>%
  summarize(m = mean(discrimination),
            sd = sd(discrimination),
            n=n()) %>%
  mutate(se = sqrt(sd/n),
         moe = se*qt(p = .975, df = n-1)) %>%
  ggplot(aes(x = Date, 
             y = m,
             text = paste0(
               "Date: ", Date,
               "\nCount: ", n,
               "\nMean: ", round(m,2),
               "\nLower 95% CI: ", round(m-moe,2),
               "\nLower 95% CI: ", round(m+moe,2)),
             group = 1)) +
  geom_errorbar(aes(ymin = m-moe, ymax = m+moe), width = 3) +
  geom_point() +
  geom_line() +
  labs(x = "Date", title = "Average discrimination", y = NULL,
       caption = "Dates represent first date of data collection per wave,except for March 1, which is an arbitrary\ndate representing responses to questions about life prior to the pandemic.") +
  theme_pubr()

ggplotly(plot, tooltip = "text")
```

### Black

```{r riser1-59 }
composite_grps(discrimination, black)
```


### Black + Income

```{r riser1-60 }
composite_grps(discrimination, blackIncome)
```

## Individual items{.tabset}

### All

```{r riser1-61}
plot = scored %>%
  ungroup() %>%
  select(Week, starts_with("discrim_")) %>%
  gather(type, response, -Week) %>%
  mutate(type = str_remove(type, "discrim_"),
         type = as.numeric(type),
         type = factor(type, 
                       labels = c(
                         "Worse service",
                         "Denied service",
                         "Police mistreatment",
                         "Fired",
                         "Not hired",
                         "Denied promotion",
                         "Discouraged from education",
                         "Redlining",
                         "Hostile neighbors",
                         "Denied credit",
                         "Denied healthcare",
                         "Called slur")),
         response = ifelse(response == "Yes", 1, 0)) %>%
  group_by(Week, type) %>%
  summarize(n = n(),
    percent = 100*mean(response, na.rm=T)) %>%
  ungroup() %>%
  mutate(Week = factor(Week,
                       labels = c("Pre-pandemic", "Current")))

plot = plot %>%
  ggplot(aes(x = type, 
             y = percent, 
             fill = Week,
             text = paste0(
               "Week: ", Week,
               "\nPercent: ", round(percent, 1),
               "\nNumber of responses:", n
             ))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = NULL, y = NULL, title = "Percent of caregivers experiencing discrimiation through due to their race/ethnicity", fill = NULL) +
  theme_pubclean() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplotly(plot, tooltip = "text")
```

### Black

```{r riser1-62, fig.height=8}
plot = scored %>%
  filter(!is.na(black)) %>%
  ungroup() %>%
  select(Week, black, starts_with("discrim_")) %>%
  gather(type, response, starts_with("discrim_")) %>%
  mutate(type = str_remove(type, "discrim_"),
         type = as.numeric(type),
         type = factor(type, 
                       labels = c(
                         "Worse service",
                         "Denied service",
                         "Police mistreatment",
                         "Fired",
                         "Not hired",
                         "Denied promotion",
                         "Discouraged from education",
                         "Redlining",
                         "Hostile neighbors",
                         "Denied credit",
                         "Denied healthcare",
                         "Called slur")),
         response = ifelse(response == "Yes", 1, 0)) %>%
  group_by(Week, type, black) %>%
  summarize(n = n(),
    percent = 100*mean(response, na.rm=T)) %>%
  ungroup() %>%
  mutate(Week = factor(Week,
                       labels = c("Pre-pandemic", "Current")))

plot = plot %>%
  ggplot(aes(x = type, 
             y = percent, 
             fill = black,
             text = paste0(
               "Group: ", black,
               "\nPercent: ", round(percent, 1),
               "\nNumber of responses:", n
             ))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = NULL, y = NULL, title = "Percent of caregivers experiencing discrimiation through due to their race/ethnicity", fill = NULL) +
  facet_wrap(~Week, nrow = 2) +
  theme_pubclean() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplotly(plot, tooltip = "text")
```
### Black + Income

```{r riser1-63, fig.height=8}
plot = scored %>%
  filter(!is.na(blackIncome)) %>%
  ungroup() %>%
  select(Week, blackIncome, starts_with("discrim_")) %>%
  gather(type, response, starts_with("discrim_")) %>%
  mutate(type = str_remove(type, "discrim_"),
         type = as.numeric(type),
         type = factor(type, 
                       labels = c(
                         "Worse service",
                         "Denied service",
                         "Police mistreatment",
                         "Fired",
                         "Not hired",
                         "Denied promotion",
                         "Discouraged from education",
                         "Redlining",
                         "Hostile neighbors",
                         "Denied credit",
                         "Denied healthcare",
                         "Called slur")),
         response = ifelse(response == "Yes", 1, 0)) %>%
  group_by(Week, type, blackIncome) %>%
  summarize(n = n(),
    percent = 100*mean(response, na.rm=T)) %>%
  ungroup() %>%
  mutate(Week = factor(Week,
                       labels = c("Pre-pandemic", "Current")))

plot = plot %>%
  ggplot(aes(x = type, 
             y = percent, 
             fill = blackIncome,
             text = paste0(
               "Group: ", blackIncome,
               "\nPercent: ", round(percent, 1),
               "\nNumber of responses:", n
             ))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = NULL, y = NULL, title = "Percent of caregivers experiencing discrimiation through due to their race/ethnicity", fill = NULL) +
  facet_wrap(~Week, nrow = 2) +
  theme_pubclean() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplotly(plot, tooltip = "text")
```
