---
title: "School Reopening Q"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---


```{r wellbeing-states-1, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
```

```{r wellbeing-states-2 }
library(conflicted)
library(here)
library(ggpubr)
conflict_prefer("group_rows", "kableExtra")
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")
conflict_prefer("map", "purrr")
library(plotly)
```

```{r wellbeing-states-3 }
source(here("Scripts/score data.R")) 
source(here("Functions/pomp.R"))
```

```{r}
scored = scored %>%
  mutate(SCHOOL.001.a = factor(SCHOOL.001.a, 
                               levels = c(1:7),
                               labels = c(
                                 "Open completely",
                                 "Move to online only",
                                 "Hybrid",
                                 "Choice between in-person and online",
                                 "Other",
                                 "NA",
                                 "I don't know"))) %>%
  mutate(
    black = ifelse(black == 1, "Black", "Not Black"),
    latinx = ifelse(latinx == 1, "LatinX", "Not LatinX"),
    single = ifelse(single == 1, "Single parent", "Dual parent"),
    poverty150 = ifelse(poverty150 == 1, "Low income", "High income")) %>%
  mutate(Week = case_when(
    Week > 17 & (Week %% 2) == 0 ~ Week - 1,
    TRUE ~ Week)) %>%
  group_by(CaregiverID, Week) %>%
  filter(row_number() == 1) %>%
  ungroup()
```


# Older children

## Mental health of families{.tabset}

```{r}
families_with_school = scored %>%
  filter(!is.na(has_schoolage_child)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(CaregiverID, has_schoolage_child) %>%
  rename(schoolage_child = has_schoolage_child) %>%
  left_join(scored)

fam_school_mh = families_with_school %>%
  mutate_at(vars(anxiety, depress, stress, lonely, fussy, fear), pomp) %>%
  rowwise() %>%
  mutate(m_health = mean(c(anxiety, depress, stress, lonely), na.rm = T)) %>%
  mutate(cm_health = mean(c(fussy,fear), na.rm = T)) %>%
  ungroup() %>%
  mutate_at(vars(m_health, cm_health), ~100-.x) %>%
  group_by(Week, schoolage_child) %>%
  mutate(Week = case_when(
    Week == 0 ~ as.Date("2020-03-27"),
    TRUE ~ min(Date, na.rm=T)
  )) %>%
  summarize(n = n(),
            m_health = mean(m_health, na.rm=T),
            cm_health = mean(cm_health, na.rm=T)) %>%
  mutate(schoolage_child = factor(schoolage_child, 
                                  levels = c(0,1),
                                  labels = c("No older children",
                                             "1+ school-age children")))
```

### Caregiver Mental Health

```{r}
plot = fam_school_mh %>%
  ggplot(aes(x = Week, 
             y = m_health, 
             color = schoolage_child,
             group = 1,
             text = paste0(
               "Date: ", Week,
               "\nCount: ", n,
               "\nGroup: ", schoolage_child,
               "\nAvgerage Mental Health: ", round(m_health))
             )) +
  geom_point()+
  geom_line() +
  labs(x = "Date", y = NULL, color = NULL, title = "Average Caregiver Mental Health") +
  theme_pubr()

ggplotly(plot, tooltip = "text")
```

### Child Mental Health

```{r}
plot = fam_school_mh %>%
  ggplot(aes(x = Week, 
             y = cm_health, 
             color = schoolage_child,
             group = 1,
             text = paste0(
               "Date: ", Week,
               "\nCount: ", n,
               "\nGroup: ", schoolage_child,
               "\nAvgerage Mental Health: ", round(cm_health))
             )) +
  geom_point()+
  geom_line() +
  labs(x = "Date", y = NULL, color = NULL, title = "Average Young Child Mental Health") +
  theme_pubr()

ggplotly(plot, tooltip = "text")
```



## School's plans{.tabset}

**What has the school/school district your child(ren) plans to attend/currently attending decided regarding the school-year?**

```{r}
schoolplan_group = function(group = black, data = scored){

  plot = data %>%
  filter(!is.na(SCHOOL.001.a) & !is.na({{group}})) %>%
  group_by(SCHOOL.001.a, {{group}}) %>%
  summarize(count = n()) %>%
    ungroup() %>%
  group_by({{group}}) %>%
  mutate(percent = 100*count/sum(count)) %>%
  ungroup() %>%
  ggplot(aes(x = SCHOOL.001.a, 
             y = percent, 
             fill = {{group}},
             #group = 1,
             text = paste0(
               "Plan: ", SCHOOL.001.a,
               "\nGroup: ",{{group}},
               "\nCount: ", count,
               "\nPercent: ",percent
             ))) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +
  labs(x = NULL, fill = NULL)+
  theme_pubclean() +
  theme(plot.title.position = "plot")
  
  ggplotly(plot, tooltip = "text")
  }

```


### Overall

```{r}
scored %>%
  filter(!is.na(SCHOOL.001.a)) %>%
  ggplot(aes(x = SCHOOL.001.a)) +
  geom_bar(stat = "count") +
  coord_flip() +
  labs(x = NULL)+
  theme_pubclean() +
  theme(plot.title.position = "plot")
```


### Black

```{r}
schoolplan_group(black)
```

### LatinX

```{r}
schoolplan_group(latinx)
```

### Single

```{r}
schoolplan_group(single)
```

### Low Income

```{r}
schoolplan_group(poverty150)
```

### All groups

```{r}
overall = scored %>%
  filter(!is.na(SCHOOL.001.a))%>%
  group_by(SCHOOL.001.a) %>%
  summarize(count = n()) %>%
  mutate(percent = 100*count/sum(count)) %>%
  mutate(response = "Average")

scored %>%
  gather(category, response, black, latinx, single, poverty150) %>%
  filter(response %in% c("Black","LatinX","Single parent","Low income")) %>%
  filter(!is.na(SCHOOL.001.a))%>%
  group_by(SCHOOL.001.a, response) %>%
  summarize(count = n()) %>%
  ungroup() %>%
  group_by(response) %>%
  mutate(percent = 100*count/sum(count)) %>%
  ungroup() %>%
  full_join(overall) %>%
  ggplot(aes(x = SCHOOL.001.a, y = percent, fill = response)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values =  c("Black", "#66C2A5","#FC8D62","#8DA0CB","#E78AC3")) +
  coord_flip() +
  labs(x = NULL)+
  theme_pubclean() +
  theme(plot.title.position = "plot")
```


## Who is managing school?{.tabset}

```{r}
school_managing = function(group, data = scored){
  plot = data %>%
  filter(!is.na({{group}})) %>%
  select({{group}}, starts_with("school_")) %>%
  gather("person", response, starts_with("school_")) %>%
  filter(!is.na(response)) %>%
  group_by(person, {{group}}) %>%
  summarize(count = n(),
            num_respond = sum(response),
            percent = 100*sum(response)/count) %>%
  mutate(person = str_remove(person, "school_")) %>%
  ggplot(aes(x = reorder(person, percent),
             y = percent,
             fill = {{group}},
             text = paste0(
               "Person: ", person,
               "\nGroup:", {{group}},
               "\nCount: ", num_respond,
               "\nPercent: ", round(percent)
             ))) +
  geom_bar(stat = "identity", position = "dodge")+
  coord_flip() +
  labs(x = NULL)+
  theme_pubclean() +
  theme(plot.title.position = "plot")
  
  ggplotly(plot, tooltip = "text")
}
```


**For the time your child will be learning remotely, who will be assisting with your child’s online learning?**

### Overall

```{r}
scored %>%
  select(starts_with("school_")) %>%
  gather("person", response) %>%
  filter(!is.na(response)) %>%
  group_by(person) %>%
  summarize(count = n(),
            percent = 100*sum(response)/count) %>%
  mutate(person = str_remove(person, "school_")) %>%
  ggplot(aes(x = reorder(person, percent), y = percent)) +
  geom_bar(stat = "identity")+
  coord_flip() +
  labs(x = NULL)+
  theme_pubclean() +
  theme(plot.title.position = "plot")
```

### Black

```{r}
school_managing(black)
```

### LatinX

```{r}
school_managing(latinx)
```

### Single

```{r}
school_managing(single)
```

### Low Income

```{r}
school_managing(poverty150)
```
### All groups

```{r}
overall = scored %>%
  select(starts_with("school_")) %>%
  gather("person", response) %>%
  filter(!is.na(response)) %>%
  group_by(person) %>%
  summarize(count = n(),
            num_respond = sum(response),
            percent = 100*sum(response)/count) %>%
  mutate(person = str_remove(person, "school_")) %>%
  mutate(group = "Average")

scored %>%
  gather(category, group, black, latinx, single, poverty150) %>%
  filter(group %in% c("Black","LatinX","Single parent","Low income")) %>%
  gather("person", response, starts_with("school_")) %>%
  filter(!is.na(response)) %>%
  group_by(group, person) %>%
  summarize(count = n(),
            num_respond = sum(response),
            percent = 100*sum(response)/count) %>%
    mutate(person = str_remove(person, "school_")) %>%
  full_join(overall) %>%
  ggplot(aes(x = person, y = percent, fill = group)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values =  c("Black", "#66C2A5","#FC8D62","#8DA0CB","#E78AC3")) +
  coord_flip() +
  labs(x = NULL)+
  theme_pubclean() +
  theme(plot.title.position = "plot")
```

# Pre-K Learning

## How{.tabset}

```{r}
prek_how = function(group, data = scored){
  
  plot = data %>%
  filter(!is.na({{group}})) %>%
  select({{group}}, starts_with("learning_")) %>%
  gather("learning", response, starts_with("learning_"))   %>%
  filter(!is.na(response)) %>%
  group_by(learning, {{group}}) %>%
  summarize(count = n(),
            num_respond = sum(response),
            percent = 100*sum(response)/count) %>%
  mutate(learning = str_remove(learning, "learning_"),
         learning = factor(learning,
                           levels = c("games", "inperson", "apps", "online", "other", "none"),
                           labels = c(
                             "Using in-person games and activities at your home",
                             "Attending in-person learning outside of your home (daycare, childcare, etc.)",
                             "Using online resources (e.g., educational apps, educational TV shows, etc.)",
                             "Attending online classes/activities",
                             "Other",
                             "None of the above")))  %>%
  ggplot(aes(x = reorder(learning, percent), 
             y = percent, 
             fill = {{group}},
             text = paste0(
               "Method: ", learning,
               "\nGroup: ", {{group}},
               "\nCount: ", num_respond,
               "\nPercent: ", round(percent)))) +
  geom_bar(stat = "identity", position = "dodge")+
  coord_flip() +
  labs(x = NULL, fill = NULL)+
  theme_pubclean() +
  theme(plot.title.position = "plot")

  ggplotly(plot, tooltip = "text")
}
```


**For your child(ren) between the ages of 0-5, which of the following are you doing to support their learning?**

### Overall

```{r}
scored %>%
  select(starts_with("learning_")) %>%
  gather("learning", response) %>%
  filter(!is.na(response)) %>%
  group_by(learning) %>%
  summarize(count = n(),
            percent = 100*sum(response)/count) %>%
  mutate(learning = str_remove(learning, "learning_"),
         learning = factor(learning, 
                           levels = c("games", "inperson", "apps", "online", "other", "none"),
                           labels = c(
                             "Using in-person games and activities at your home", 
                             "Attending in-person learning outside of your home (daycare, childcare, etc.)", 
                             "Using online resources (e.g., educational apps, educational TV shows, etc.)", 
                             "Attending online classes/activities", 
                             "Other", 
                             "None of the above"))) %>%
  ggplot(aes(x = reorder(learning, percent), y = percent)) +
  geom_bar(stat = "identity")+
  coord_flip() +
  labs(x = NULL)+
  theme_pubclean() +
  theme(plot.title.position = "plot")
```

### Black

```{r}
prek_how(black)
```

### LatinX

```{r}
prek_how(latinx)
```

### Single

```{r}
prek_how(single)
```

### Low Income

```{r}
prek_how(poverty150)
```

### All groups

```{r}
overall = scored %>%
  select(starts_with("learning_")) %>%
  gather("learning", response) %>%
  filter(!is.na(response)) %>%
  group_by(learning) %>%
  summarize(count = n(),
            percent = 100*sum(response)/count) %>%
  mutate(learning = str_remove(learning, "learning_"),
         learning = factor(learning, 
                           levels = c("games", "inperson", "apps", "online", "other", "none"),
                           labels = c(
                             "Using in-person games and activities at your home", 
                             "Attending in-person learning outside of your home (daycare, childcare, etc.)", 
                             "Using online resources (e.g., educational apps, educational TV shows, etc.)", 
                             "Attending online classes/activities", 
                             "Other", 
                             "None of the above"))) %>%
  mutate(group = "Average")

scored %>%
  gather(category, group, black, latinx, single, poverty150) %>%
  filter(group %in% c("Black","LatinX","Single parent","Low income")) %>%
  gather("learning", response, starts_with("learning_")) %>%
  filter(!is.na(response)) %>%
  group_by(learning, group) %>%
  summarize(count = n(),
            percent = 100*sum(response)/count) %>%
  mutate(learning = str_remove(learning, "learning_"),
         learning = factor(learning, 
                           levels = c("games", "inperson", "apps", "online", "other", "none"),
                           labels = c(
                             "Using in-person games and activities at your home", 
                             "Attending in-person learning outside of your home (daycare, childcare, etc.)", 
                             "Using online resources (e.g., educational apps, educational TV shows, etc.)", 
                             "Attending online classes/activities", 
                             "Other", 
                             "None of the above")))  %>%
  full_join(overall) %>%
  ggplot(aes(x = learning, y = percent, fill = group)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values =  c("Black", "#66C2A5","#FC8D62","#8DA0CB","#E78AC3")) +
  coord_flip() +
  labs(x = NULL)+
  theme_pubclean() +
  theme(plot.title.position = "plot")
```


## Who{.tabset}

```{r}
prek_who = function(group, data = scored){
  plot = data %>%
    filter(!is.na({{group}})) %>%
  select(starts_with("learningp_"), {{group}}) %>%
  gather("person", response, starts_with("learningp_")) %>%
  filter(!is.na(response)) %>%
  group_by(person, {{group}}) %>%
  summarize(count = n(),
            num_respond = sum(response),
            percent = 100*sum(response)/count) %>%
  mutate(person = str_remove(person, "learningp_")) %>%
  ggplot(aes(x = reorder(person, percent), 
             y = percent,
             fill = {{group}},
             text = paste0(
               "Person: ", person,
               "\nGroup:", {{group}},
               "\nCount: ", num_respond,
               "\nPercent: ", round(percent)
             ))) +
  geom_bar(stat = "identity", position = "dodge")+
  coord_flip() +
  labs(x = NULL, title = "Who will be assisting with you child(s) 0-5 learning?")+
  theme_pubclean() +
  theme(plot.title.position = "plot")
  
  ggplotly(plot,tooltip = "text")
}
```


**Who will be assisting with you child(s) 0-5 learning?**

### Overall

```{r}
scored %>%
  select(starts_with("learningp_")) %>%
  gather("person", response) %>%
  filter(!is.na(response)) %>%
  group_by(person) %>%
  summarize(count = n(),
            percent = 100*sum(response)/count) %>%
  mutate(person = str_remove(person, "learningp_")) %>%
  ggplot(aes(x = reorder(person, percent), y = percent)) +
  geom_bar(stat = "identity")+
  coord_flip() +
  labs(x = NULL, title = "Who will be assisting with you child(s) 0-5 learning?")+
  theme_pubclean() +
  theme(plot.title.position = "plot")
```

### Black

```{r}
prek_who(black)
```

### LatinX

```{r}
prek_who(latinx)
```

### Single

```{r}
prek_who(single)
```

### Low Income

```{r}
prek_who(poverty150)
```

### All groups

```{r}
overall = scored %>%
  select(starts_with("learningp_")) %>%
  gather("person", response) %>%
  filter(!is.na(response)) %>%
  group_by(person) %>%
  summarize(count = n(),
            num_respond = sum(response),
            percent = 100*sum(response)/count) %>%
  mutate(person = str_remove(person, "learningp_")) %>%
  mutate(group = "Average")

scored %>%
  gather(category, group, black, latinx, single, poverty150) %>%
  filter(group %in% c("Black","LatinX","Single parent","Low income")) %>%
  gather("person", response, starts_with("learningp_")) %>%
  filter(!is.na(response)) %>%
  group_by(group, person) %>%
  summarize(count = n(),
            num_respond = sum(response),
            percent = 100*sum(response)/count) %>%
    mutate(person = str_remove(person, "learningp_")) %>%
  full_join(overall) %>%
  ggplot(aes(x = person, y = percent, fill = group)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values =  c("Black", "#66C2A5","#FC8D62","#8DA0CB","#E78AC3")) +
  coord_flip() +
  labs(x = NULL)+
  theme_pubclean() +
  theme(plot.title.position = "plot")
```