---
title: "Social support"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
#re-run all the machine learning models?
rerun = FALSE
dontrerun = !rerun
```

```{r  }
library(conflicted)
library(here)
library(ggpubr)
library(knitr)
library(kableExtra)
conflict_prefer("group_rows", "kableExtra")
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")
conflict_prefer("map", "purrr")
library(plotly)
```

```{r }
source(here("Scripts/score data.R")) 
```

```{r }
source(here("Functions/pomp.R"))
```

```{r, results = 'asis'}
#score well-being
scored = scored %>%
  mutate_at(vars(anxiety, depress, stress, lonely, fussy, fear), pomp) %>%
  rowwise() %>%
  mutate(mental_health = mean(c(anxiety, depress, stress, lonely), na.rm=T)) %>%
  ungroup()
```

```{r, results = 'asis'}
scored = filter(scored, Week == 15)
```

```{r, results = 'asis'}
scored = scored %>%
  mutate(poverty150 = factor(poverty150, levels = c(0,1), 
                             labels = c("High Income", "Low Income"))) %>%
  mutate(race_cat = factor(race_cat))

contrasts(scored$race_cat) = contr.treatment(7)
```


```{r, results = 'asis'}
scored = scored %>%
  mutate(current.support = rowMeans(select(., contains("SOCIALSUPP.001")), na.rm=T),
         prior.support = rowMeans(select(., contains("SOCIALSUPP.002")), na.rm=T)) %>%
  mutate(change.support = current.support-prior.support)
```


```{r function wellbeing by continuous predictor}
wellbeing.con = function(predictor, data = scored, outcome = mental_health, title = NULL){
  
  data = data %>%
    filter(!is.na({{outcome}})) %>%
    filter(!is.na({{predictor}})) 
  
  plot = data %>%
    ggplot(aes(x = {{predictor}}, y = {{outcome}})) +
    geom_jitter(alpha = .3, size = .5)  +
    geom_smooth(method = lm, se = F) +
    scale_x_continuous("___ of the time", breaks = c(1:5), labels = c("None", "A little", "Some", "A lot", "Most")) +
    labs(y = "Poor Mental Health", title = title) +
    theme_pubclean()
  
  formula = as.formula(paste(deparse(substitute(outcome)), "~", deparse(substitute(predictor))))
  
  model = lm(formula, data) %>%
    broom::tidy() %>%
    mutate(p.value = papaja::printp(p.value)) %>%
    kable(digits = 2) %>%
    kable_styling(full_width = T)
  
  return.list = list(plot = plot, summary = model)
  return(return.list)
}
```

```{r function wellbeing by continuous predictor moderated by categorical groups}
wellbeing.con.group = function(predictor, group, outcome = mental_health, data = scored, title = NULL){
  
  data = data %>%
    filter(!is.na({{outcome}})) %>%
    filter(!is.na({{predictor}})) %>%
    filter(!is.na({{group}}))
  
  plot = data %>%
    ggplot(aes(x = {{predictor}}, y = {{outcome}}, color = {{group}})) +
    geom_jitter(alpha = .3, size = .5)  +
    geom_smooth(method = lm, se = F) +
    scale_x_continuous("___ of the time", breaks = c(1:5), labels = c("None", "A little", "Some", "A lot", "Most")) +
    labs(y = "Poor Mental Health", title = title) +
    theme_pubclean()
  
  formula = as.formula(paste(deparse(substitute(outcome)), "~", deparse(substitute(group)), "*", deparse(substitute(predictor))))
  
  model = lm(formula, data) %>%
    broom::tidy() %>%
    mutate(p.value = papaja::printp(p.value)) %>%
    kable(digits = 2) %>%
    kable_styling(full_width = T)
  
  return.list = list(plot = plot, summary = model)
  return(return.list)
}
```

# Current social support

```{r, results = 'asis'}
scored %>%
  ggplot(aes(x = current.support)) +
  geom_density(fill = "grey") +
  scale_x_continuous(
    breaks = c(1:5), 
    labels = c("None", "A little", "Some", "A lot", "Most")) +
  labs(title = "Current levels of support", x = NULL) +
  theme_pubclean()
```


## Caregiver Wellbeing{.tabset}

### Overall

```{r, results = 'asis'}
wellbeing.con(current.support)
```

### Income

```{r, results = 'asis'}
wellbeing.con.group(current.support, poverty150)
```

### Race/ethnicity

```{r, results = 'asis'}
wellbeing.con.group(current.support, race_cat)
```


## Child Externalizing{.tabset}

### Overall

```{r, results = 'asis'}
wellbeing.con(current.support, outcome = fussy)
```

### Income

```{r, results = 'asis'}
wellbeing.con.group(current.support, poverty150, outcome = fussy)
```

### Race/ethnicity

```{r, results = 'asis'}
wellbeing.con.group(current.support, race_cat, outcome = fussy)
```

## Child Internalizing{.tabset}

### Overall

```{r, results = 'asis'}
wellbeing.con(current.support, outcome = fear)
```

### Income

```{r, results = 'asis'}
wellbeing.con.group(current.support, poverty150, outcome = fear)
```

### Race/ethnicity

```{r, results = 'asis'}
wellbeing.con.group(current.support, race_cat, outcome = fear)
```


# Prior social support

```{r, results = 'asis'}
scored %>%
  ggplot(aes(x = prior.support)) +
  geom_density(fill = "grey") +
  scale_x_continuous(
    breaks = c(1:5), 
    labels = c("None", "A little", "Some", "A lot", "Most")) +
  labs(title = "Current levels of support", x = NULL) +
  theme_pubclean()
```


## Caregiver Wellbeing{.tabset}

### Overall

```{r, results = 'asis'}
wellbeing.con(prior.support)
```

### Income

```{r, results = 'asis'}
wellbeing.con.group(prior.support, poverty150)
```

### Race/ethnicity

```{r, results = 'asis'}
wellbeing.con.group(prior.support, race_cat)
```


## Child Externalizing{.tabset}

### Overall

```{r, results = 'asis'}
wellbeing.con(prior.support, outcome = fussy)
```

### Income

```{r, results = 'asis'}
wellbeing.con.group(prior.support, poverty150, outcome = fussy)
```

### Race/ethnicity

```{r, results = 'asis'}
wellbeing.con.group(prior.support, race_cat, outcome = fussy)
```

## Child Internalizing{.tabset}

### Overall

```{r, results = 'asis'}
wellbeing.con(prior.support, outcome = fear)
```

### Income

```{r, results = 'asis'}
wellbeing.con.group(prior.support, poverty150, outcome = fear)
```

### Race/ethnicity

```{r, results = 'asis'}
wellbeing.con.group(prior.support, race_cat, outcome = fear)
```


# Change in social support

```{r, results = 'asis'}
scored %>%
  ggplot(aes(x = change.support)) +
  geom_density(fill = "grey") +
  scale_x_continuous(
    breaks = c(1:5), 
    labels = c("None", "A little", "Some", "A lot", "Most")) +
  labs(title = "Current levels of support", x = NULL) +
  theme_pubclean()
```


## Caregiver Wellbeing{.tabset}

### Overall

```{r, results = 'asis'}
wellbeing.con(change.support)
```

### Income

```{r, results = 'asis'}
wellbeing.con.group(change.support, poverty150)
```

### Race/ethnicity

```{r, results = 'asis'}
wellbeing.con.group(change.support, race_cat)
```


## Child Externalizing{.tabset}

### Overall

```{r, results = 'asis'}
wellbeing.con(change.support, outcome = fussy)
```

### Income

```{r, results = 'asis'}
wellbeing.con.group(change.support, poverty150, outcome = fussy)
```

### Race/ethnicity

```{r, results = 'asis'}
wellbeing.con.group(change.support, race_cat, outcome = fussy)
```

## Child Internalizing{.tabset}

### Overall

```{r, results = 'asis'}
wellbeing.con(change.support, outcome = fear)
```

### Income

```{r, results = 'asis'}
wellbeing.con.group(change.support, poverty150, outcome = fear)
```

### Race/ethnicity

```{r, results = 'asis'}
wellbeing.con.group(change.support, race_cat, outcome = fear)
```

