---
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
params: 
  mainstate: "MI" 
  title: "my title!"
---

---
title: `r params$title`
---

```{r state-specific-1, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
```

```{r state-specific-2 }
library(here)
library(haven)
library(tidyverse)
library(ggpubr)
library(knitr)
library(kableExtra)
library(plotly)
```

```{r state-specific-3}
source(here("Scripts/score data.R"))
source(here("Functions/core_funs.R"))
scored = scored %>%
  mutate(wellbeing = 100-mental_health)

mainstate = params$mainstate
statedata = scored %>% filter(state == mainstate)

scored$group = "US"
statedata$group = mainstate

stateplus = full_join(scored, statedata)

state_cross = statedata %>%
  group_by(CaregiverID) %>%
  filter(Week == max(Week))
```

RAPID has sampled `r nrow(state_cross)` caregivers from your state.

```{r}
plot = statedata %>%
  filter(Week > 0) %>%
  group_by(Week) %>%
  summarize(
    Date = min(Date),
    Number = n() 
  ) %>%
  ggplot(aes(x = Date,
             y = Number)) +
  geom_line()+
  geom_point() +
  labs(x = NULL, y = NULL, title = "Number of caregivers by survey week") +
  theme_pubclean()

ggplotly(plot)
```




# Demographics

## Age

```{r}
dist_cat_group(age, group, stateplus)
```

## Race

```{r}
dist_cat_group(race_cat, group, stateplus)
```

## Ethnicity

```{r}
dist_cat_group(latinx_cat, group, stateplus)
```



# Caregiver Well-being

## Overall{.tabset}

Caregivers complete measures of anxiety, depression, stress, and loneliness. These measures are averaged to create a single mental health variable, called "well-being" which ranges from 0 (worst possible mental health) to 100 (best possible mental health).

### Across the sample

```{r}
average_by_group(wellbeing, group, label = "caregiver well-being", stateplus)
```

### Race/ethnicity

```{r}
average_by_group2(wellbeing, race_ethnic, group, label = "caregiver well-being", stateplus)
```

### Income

```{r}
average_by_group2(wellbeing, poverty_cat, group, label = "caregiver well-being", stateplus)
```

### Race by income (state only)

```{r}
average_by_group2(wellbeing, race_ethnic, poverty_cat, label = "caregiver well-being", statedata)
```


### Over time

```{r state-specific-4}
state_mh = statedata %>%
  filter(!is.na(mental_health)) %>%
  group_by(Date_group) %>%
  summarize(n = n(),
            wellbeing = 100-mean(mental_health),
            sd = sd(mental_health)) %>%
  mutate(moe = sd/sqrt(n)*qt(.975, df = n-1)) 

plot = scored %>%
  filter(!is.na(mental_health)) %>%
  group_by(Date_group) %>%
  summarize(n = n(),
            wellbeing = 100-mean(mental_health),
            sd = sd(mental_health)) %>%
  mutate(moe = sd/sqrt(n)*qt(.975, df = n-1)) %>%
  ggplot(aes(x = Date_group, 
             y = wellbeing, 
             group = 1,
             text = paste0(
               "Well-being Average: ", round(wellbeing,1),
               "\nSample size: ", n
             ))) +
  # geom_ribbon(aes(ymin = wellbeing-moe, 
  #                 ymax = wellbeing+moe,
  #                 fill = "US Average"),
              # alpha = .2) +
  geom_point(aes(color = "US Average")) +
  geom_line(aes(color = "US Average")) +
  geom_ribbon(aes(ymin = wellbeing-moe,
                  ymax = wellbeing+moe,
                  fill = mainstate),
              data = state_mh,
              alpha = .2) +
  geom_point(data = state_mh, aes(color = mainstate)) +
  geom_line(data = state_mh, aes(color = mainstate)) +
  scale_color_manual(breaks = c(mainstate, "US Average"), values = c("red", "black")) +
#  scale_fill_manual(values = c("red", "black")) +
  labs(x = NULL, y = NULL, color = NULL, fill = NULL, title = "Average caregiver well-being by week") +
  theme_pubclean()
  
plot = ggplotly(plot, tooltip = "text")

for (i in 1:length(plot$x$data)){
    if (!is.null(plot$x$data[[i]]$name)){
        plot$x$data[[i]]$name =  gsub("\\(","",str_split(plot$x$data[[i]]$name,",")[[1]][1])
    }
}

plot
```

## Anxiety{.tabset}


### Across the sample

```{r}
average_by_group(anxiety, group, label = "caregiver well-being", stateplus)
```

### Race/ethnicity

```{r}
average_by_group2(anxiety, race_ethnic, group, label = "caregiver well-being", stateplus)
```

### Income

```{r}
average_by_group2(anxiety, poverty_cat, group, label = "caregiver well-being", stateplus)
```

### Race by income (state only)

```{r}
average_by_group2(anxiety, race_ethnic, poverty_cat, label = "caregiver well-being", statedata)
```


### Over time

```{r state-specific-5}
state_mh = statedata %>%
  filter(!is.na(anxiety)) %>%
  group_by(Date_group) %>%
  summarize(n = n(),
            wellbeing = mean(anxiety),
            sd = sd(anxiety)) %>%
  mutate(moe = sd/sqrt(n)*qt(.975, df = n-1)) 

plot = scored %>%
  filter(!is.na(anxiety)) %>%
  group_by(Date_group) %>%
  summarize(n = n(),
            wellbeing = mean(anxiety),
            sd = sd(anxiety)) %>%
  mutate(moe = sd/sqrt(n)*qt(.975, df = n-1)) %>%
  ggplot(aes(x = Date_group, 
             y = wellbeing, 
             group = 1,
             text = paste0(
               "Anxiety Average: ", round(wellbeing,1),
               "\nSample size: ", n
             ))) +
  # geom_ribbon(aes(ymin = wellbeing-moe, 
  #                 ymax = wellbeing+moe,
  #                 fill = "US Average"),
              # alpha = .2) +
  geom_point(aes(color = "US Average")) +
  geom_line(aes(color = "US Average")) +
  geom_ribbon(aes(ymin = wellbeing-moe,
                  ymax = wellbeing+moe,
                  fill = mainstate),
              data = state_mh,
              alpha = .2) +
  geom_point(data = state_mh, aes(color = mainstate)) +
  geom_line(data = state_mh, aes(color = mainstate)) +
  scale_color_manual(breaks = c(mainstate, "US Average"), values = c("red", "black")) +
#  scale_fill_manual(values = c("red", "black")) +
  labs(x = NULL, y = NULL, color = NULL, fill = NULL, title = "Average caregiver anxiety by week") +
  theme_pubclean()
  
plot = ggplotly(plot, tooltip = "text")

for (i in 1:length(plot$x$data)){
    if (!is.null(plot$x$data[[i]]$name)){
        plot$x$data[[i]]$name =  gsub("\\(","",str_split(plot$x$data[[i]]$name,",")[[1]][1])
    }
}

plot
```

## Depression{.tabset}


### Across the sample

```{r}
average_by_group(depress, group, label = "caregiver well-being", stateplus)
```

### Race/ethnicity

```{r}
average_by_group2(depress, race_ethnic, group, label = "caregiver well-being", stateplus)
```

### Income

```{r}
average_by_group2(depress, poverty_cat, group, label = "caregiver well-being", stateplus)
```

### Race by income (state only)

```{r}
average_by_group2(depress, race_ethnic, poverty_cat, label = "caregiver well-being", statedata)
```

### Over time

```{r state-specific-6}
state_mh = statedata %>%
  filter(!is.na(depress)) %>%
  group_by(Date_group) %>%
  summarize(n = n(),
            wellbeing = mean(depress),
            sd = sd(depress)) %>%
  mutate(moe = sd/sqrt(n)*qt(.975, df = n-1)) 

plot = scored %>%
  filter(!is.na(depress)) %>%
  group_by(Date_group) %>%
  summarize(n = n(),
            wellbeing = mean(depress),
            sd = sd(depress)) %>%
  mutate(moe = sd/sqrt(n)*qt(.975, df = n-1)) %>%
  ggplot(aes(x = Date_group, 
             y = wellbeing, 
             group = 1,
             text = paste0(
               "Anxiety Average: ", round(wellbeing,1),
               "\nSample size: ", n
             ))) +
  # geom_ribbon(aes(ymin = wellbeing-moe, 
  #                 ymax = wellbeing+moe,
  #                 fill = "US Average"),
              # alpha = .2) +
  geom_point(aes(color = "US Average")) +
  geom_line(aes(color = "US Average")) +
  geom_ribbon(aes(ymin = wellbeing-moe,
                  ymax = wellbeing+moe,
                  fill = mainstate),
              data = state_mh,
              alpha = .2) +
  geom_point(data = state_mh, aes(color = mainstate)) +
  geom_line(data = state_mh, aes(color = mainstate)) +
  scale_color_manual(breaks = c(mainstate, "US Average"), values = c("red", "black")) +
#  scale_fill_manual(values = c("red", "black")) +
  labs(x = NULL, y = NULL, color = NULL, fill = NULL, title = "Average caregiver depression by week") +
  theme_pubclean()
  
plot = ggplotly(plot, tooltip = "text")

for (i in 1:length(plot$x$data)){
    if (!is.null(plot$x$data[[i]]$name)){
        plot$x$data[[i]]$name =  gsub("\\(","",str_split(plot$x$data[[i]]$name,",")[[1]][1])
    }
}

plot
```

## Stress{.tabset}


### Across the sample

```{r}
average_by_group(stress, group, label = "caregiver well-being", stateplus)
```

### Race/ethnicity

```{r}
average_by_group2(stress, race_ethnic, group, label = "caregiver well-being", stateplus)
```

### Income

```{r}
average_by_group2(stress, poverty_cat, group, label = "caregiver well-being", stateplus)
```

### Race by income (state only)

```{r}
average_by_group2(stress, race_ethnic, poverty_cat, label = "caregiver well-being", statedata)
```

### Over time
```{r state-specific-7}
state_mh = statedata %>%
  filter(!is.na(stress)) %>%
  group_by(Date_group) %>%
  summarize(n = n(),
            wellbeing = mean(stress),
            sd = sd(stress)) %>%
  mutate(moe = sd/sqrt(n)*qt(.975, df = n-1)) 

plot = scored %>%
  filter(!is.na(stress)) %>%
  group_by(Date_group) %>%
  summarize(n = n(),
            wellbeing = mean(stress),
            sd = sd(stress)) %>%
  mutate(moe = sd/sqrt(n)*qt(.975, df = n-1)) %>%
  ggplot(aes(x = Date_group, 
             y = wellbeing, 
             group = 1,
             text = paste0(
               "Anxiety Average: ", round(wellbeing,1),
               "\nSample size: ", n
             ))) +
  # geom_ribbon(aes(ymin = wellbeing-moe, 
  #                 ymax = wellbeing+moe,
  #                 fill = "US Average"),
              # alpha = .2) +
  geom_point(aes(color = "US Average")) +
  geom_line(aes(color = "US Average")) +
  geom_ribbon(aes(ymin = wellbeing-moe,
                  ymax = wellbeing+moe,
                  fill = mainstate),
              data = state_mh,
              alpha = .2) +
  geom_point(data = state_mh, aes(color = mainstate)) +
  geom_line(data = state_mh, aes(color = mainstate)) +
  scale_color_manual(breaks = c(mainstate, "US Average"), values = c("red", "black")) +
#  scale_fill_manual(values = c("red", "black")) +
  labs(x = NULL, y = NULL, color = NULL, fill = NULL, title = "Average caregiver stress by week") +
  theme_pubclean()
  
plot = ggplotly(plot, tooltip = "text")

for (i in 1:length(plot$x$data)){
    if (!is.null(plot$x$data[[i]]$name)){
        plot$x$data[[i]]$name =  gsub("\\(","",str_split(plot$x$data[[i]]$name,",")[[1]][1])
    }
}

plot
```

## Loneliness{.tabset}


### Across the sample

```{r}
average_by_group(lonely, group, label = "caregiver well-being", stateplus)
```

### Race/ethnicity

```{r}
average_by_group2(lonely, race_ethnic, group, label = "caregiver well-being", stateplus)
```

### Income

```{r}
average_by_group2(lonely, poverty_cat, group, label = "caregiver well-being", stateplus)
```

### Race by income (state only)

```{r}
average_by_group2(lonely, race_ethnic, poverty_cat, label = "caregiver well-being", statedata)
```

### Over time

```{r state-specific-8}
state_mh = statedata %>%
  filter(!is.na(lonely)) %>%
  group_by(Date_group) %>%
  summarize(n = n(),
            wellbeing = mean(lonely),
            sd = sd(lonely)) %>%
  mutate(moe = sd/sqrt(n)*qt(.975, df = n-1)) 

plot = scored %>%
  filter(!is.na(lonely)) %>%
  group_by(Date_group) %>%
  summarize(n = n(),
            wellbeing = mean(lonely),
            sd = sd(lonely)) %>%
  mutate(moe = sd/sqrt(n)*qt(.975, df = n-1)) %>%
  ggplot(aes(x = Date_group, 
             y = wellbeing, 
             group = 1,
             text = paste0(
               "Anxiety Average: ", round(wellbeing,1),
               "\nSample size: ", n
             ))) +
  # geom_ribbon(aes(ymin = wellbeing-moe, 
  #                 ymax = wellbeing+moe,
  #                 fill = "US Average"),
              # alpha = .2) +
  geom_point(aes(color = "US Average")) +
  geom_line(aes(color = "US Average")) +
  geom_ribbon(aes(ymin = wellbeing-moe,
                  ymax = wellbeing+moe,
                  fill = mainstate),
              data = state_mh,
              alpha = .2) +
  geom_point(data = state_mh, aes(color = mainstate)) +
  geom_line(data = state_mh, aes(color = mainstate)) +
  scale_color_manual(breaks = c(mainstate, "US Average"), values = c("red", "black")) +
#  scale_fill_manual(values = c("red", "black")) +
  labs(x = NULL, y = NULL, color = NULL, fill = NULL, title = "Average caregiver loneliness by week") +
  theme_pubclean()
  
plot = ggplotly(plot, tooltip = "text")

for (i in 1:length(plot$x$data)){
    if (!is.null(plot$x$data[[i]]$name)){
        plot$x$data[[i]]$name =  gsub("\\(","",str_split(plot$x$data[[i]]$name,",")[[1]][1])
    }
}

plot
```


# Child well-being{.tabset}

## Overall{.tabset}

Caregivers complete measures of child internalizing and externalizing behavior. These measures are averaged to create a single mental health variable, called "well-being" which ranges from 0 (worst possible mental health) to 100 (best possible mental health).

### Across the sample

```{r}
average_by_group(child_mental, group, label = "caregiver well-being", stateplus)
```

### Race/ethnicity

```{r}
average_by_group2(child_mental, race_ethnic, group, label = "caregiver well-being", stateplus)
```

### Income

```{r}
average_by_group2(child_mental, poverty_cat, group, label = "caregiver well-being", stateplus)
```

### Race by income (state only)

```{r}
average_by_group2(child_mental, race_ethnic, poverty_cat, label = "caregiver well-being", statedata)
```

### Over time

```{r state-specific-9}
state_mh = statedata %>%
  filter(!is.na(child_mental)) %>%
  group_by(Date_group) %>%
  summarize(n = n(),
            wellbeing = 100-mean(child_mental),
            sd = sd(child_mental)) %>%
  mutate(moe = sd/sqrt(n)*qt(.975, df = n-1)) 

plot = scored %>%
  filter(!is.na(child_mental)) %>%
  group_by(Date_group) %>%
  summarize(n = n(),
            wellbeing = 100-mean(child_mental),
            sd = sd(child_mental)) %>%
  mutate(moe = sd/sqrt(n)*qt(.975, df = n-1)) %>%
  ggplot(aes(x = Date_group, 
             y = wellbeing, 
             group = 1,
             text = paste0(
               "Well-being Average: ", round(wellbeing,1),
               "\nSample size: ", n
             ))) +
  # geom_ribbon(aes(ymin = wellbeing-moe, 
  #                 ymax = wellbeing+moe,
  #                 fill = "US Average"),
              # alpha = .2) +
  geom_point(aes(color = "US Average")) +
  geom_line(aes(color = "US Average")) +
  geom_ribbon(aes(ymin = wellbeing-moe,
                  ymax = wellbeing+moe,
                  fill = mainstate),
              data = state_mh,
              alpha = .2) +
  geom_point(data = state_mh, aes(color = mainstate)) +
  geom_line(data = state_mh, aes(color = mainstate)) +
  scale_color_manual(breaks = c(mainstate, "US Average"), values = c("red", "black")) +
#  scale_fill_manual(values = c("red", "black")) +
  labs(x = NULL, y = NULL, color = NULL, fill = NULL, title = "Average child well-being by week") +
  theme_pubclean()
  
plot = ggplotly(plot, tooltip = "text")

for (i in 1:length(plot$x$data)){
    if (!is.null(plot$x$data[[i]]$name)){
        plot$x$data[[i]]$name =  gsub("\\(","",str_split(plot$x$data[[i]]$name,",")[[1]][1])
    }
}

plot
```

## Internalizing behaviors (fear){.tabset}


### Across the sample

```{r}
average_by_group(fear, group, label = "caregiver well-being", stateplus)
```

### Race/ethnicity

```{r}
average_by_group2(fear, race_ethnic, group, label = "caregiver well-being", stateplus)
```

### Income

```{r}
average_by_group2(fear, poverty_cat, group, label = "caregiver well-being", stateplus)
```

### Race by income (state only)

```{r}
average_by_group2(fear, race_ethnic, poverty_cat, label = "caregiver well-being", statedata)
```

### Over time

```{r state-specific-10}
state_mh = statedata %>%
  filter(!is.na(fear)) %>%
  group_by(Date_group) %>%
  summarize(n = n(),
            wellbeing = mean(fear),
            sd = sd(fear)) %>%
  mutate(moe = sd/sqrt(n)*qt(.975, df = n-1)) 

plot = scored %>%
  filter(!is.na(fear)) %>%
  group_by(Date_group) %>%
  summarize(n = n(),
            wellbeing = mean(fear),
            sd = sd(fear)) %>%
  mutate(moe = sd/sqrt(n)*qt(.975, df = n-1)) %>%
  ggplot(aes(x = Date_group, 
             y = wellbeing, 
             group = 1,
             text = paste0(
               "Anxiety Average: ", round(wellbeing,1),
               "\nSample size: ", n
             ))) +
  # geom_ribbon(aes(ymin = wellbeing-moe, 
  #                 ymax = wellbeing+moe,
  #                 fill = "US Average"),
              # alpha = .2) +
  geom_point(aes(color = "US Average")) +
  geom_line(aes(color = "US Average")) +
  geom_ribbon(aes(ymin = wellbeing-moe,
                  ymax = wellbeing+moe,
                  fill = mainstate),
              data = state_mh,
              alpha = .2) +
  geom_point(data = state_mh, aes(color = mainstate)) +
  geom_line(data = state_mh, aes(color = mainstate)) +
  scale_color_manual(breaks = c(mainstate, "US Average"), values = c("red", "black")) +
#  scale_fill_manual(values = c("red", "black")) +
  labs(x = NULL, y = NULL, color = NULL, fill = NULL, title = "Average child fear by week") +
  theme_pubclean()
  
plot = ggplotly(plot, tooltip = "text")

for (i in 1:length(plot$x$data)){
    if (!is.null(plot$x$data[[i]]$name)){
        plot$x$data[[i]]$name =  gsub("\\(","",str_split(plot$x$data[[i]]$name,",")[[1]][1])
    }
}

plot
```

## Externalizing behavior (fussiness){.tabset}


### Across the sample

```{r}
average_by_group(fussy, group, label = "caregiver well-being", stateplus)
```

### Race/ethnicity

```{r}
average_by_group2(fussy, race_ethnic, group, label = "caregiver well-being", stateplus)
```

### Income

```{r}
average_by_group2(fussy, poverty_cat, group, label = "caregiver well-being", stateplus)
```

### Race by income (state only)

```{r}
average_by_group2(fussy, race_ethnic, poverty_cat, label = "caregiver well-being", statedata)
```

### Over time

```{r state-specific-11}
state_mh = statedata %>%
  filter(!is.na(fussy)) %>%
  group_by(Date_group) %>%
  summarize(n = n(),
            wellbeing = mean(fussy),
            sd = sd(fussy)) %>%
  mutate(moe = sd/sqrt(n)*qt(.975, df = n-1)) 

plot = scored %>%
  filter(!is.na(fussy)) %>%
  group_by(Date_group) %>%
  summarize(n = n(),
            wellbeing = mean(fussy),
            sd = sd(fussy)) %>%
  mutate(moe = sd/sqrt(n)*qt(.975, df = n-1)) %>%
  ggplot(aes(x = Date_group, 
             y = wellbeing, 
             group = 1,
             text = paste0(
               "Anxiety Average: ", round(wellbeing,1),
               "\nSample size: ", n
             ))) +
  # geom_ribbon(aes(ymin = wellbeing-moe, 
  #                 ymax = wellbeing+moe,
  #                 fill = "US Average"),
              # alpha = .2) +
  geom_point(aes(color = "US Average")) +
  geom_line(aes(color = "US Average")) +
  geom_ribbon(aes(ymin = wellbeing-moe,
                  ymax = wellbeing+moe,
                  fill = mainstate),
              data = state_mh,
              alpha = .2) +
  geom_point(data = state_mh, aes(color = mainstate)) +
  geom_line(data = state_mh, aes(color = mainstate)) +
  scale_color_manual(breaks = c(mainstate, "US Average"), values = c("red", "black")) +
#  scale_fill_manual(values = c("red", "black")) +
  labs(x = NULL, y = NULL, color = NULL, fill = NULL, title = "Average child fussiness by week") +
  theme_pubclean()
  
plot = ggplotly(plot, tooltip = "text")

for (i in 1:length(plot$x$data)){
    if (!is.null(plot$x$data[[i]]$name)){
        plot$x$data[[i]]$name =  gsub("\\(","",str_split(plot$x$data[[i]]$name,",")[[1]][1])
    }
}

plot
```

# Material Hardship{.tabset}


_Which needs are hard to pay for?:_
  - _Food_
  - _Housing_
  - _Utilities (electric, water, trash)_
  - _Healthcare_
  - _Social_
  - _Emotional_
  - _Childcare_
  - _Other_

Caregivers grouped into two categories: trouble paying for 1+ basic need, or no trouble paying for any.

### Across the sample

```{r}
percent_by_group(material_hardship, group, stateplus)
```

### Race/ethnicity

```{r}
percent_by_group2(material_hardship, race_ethnic, group, stateplus)
```

### Income

```{r}
percent_by_group2(material_hardship, poverty_cat, group, stateplus)
```

### Race by income (state only)

```{r}
percent_by_group2(material_hardship, race_ethnic, poverty_cat, statedata)
```


### Over time

```{r state-specific-12}
state_mh = scored %>%
  filter(state == mainstate) %>%
  filter(!is.na(material_hardship)) %>%
  group_by(Date_group) %>%
  summarize(
    n = n(),
    percent = mean(material_hardship)
  ) %>%
  mutate(
    moe = 1.96*sqrt((percent*(1-percent))/n)
  ) %>%
  mutate_at(vars(percent, moe), ~100*.x)

plot = scored %>%
  filter(!is.na(material_hardship)) %>%
  group_by(Date_group) %>%
  summarize(
    n = n(),
    percent = mean(material_hardship)
  ) %>%
  mutate(
    moe = 1.96*sqrt((percent*(1-percent))/n)
  ) %>%
  mutate_at(vars(percent, moe), ~100*.x) %>%
  ggplot(aes(x = Date_group,
             y = percent, 
             group = 1, 
             text = round(percent,1))) +
  geom_point(aes(color = "Entire US")) +
  geom_line(aes(color = "Entire US")) +
  geom_ribbon(aes(ymin = percent-moe,
                  ymax = percent+moe,
                  fill = mainstate),
              data = state_mh,
              alpha = .2) +
  geom_point(data = state_mh, aes(color = mainstate)) +
  geom_line(data = state_mh, aes(color = mainstate)) +
  scale_color_manual(breaks = c(mainstate, "US Average"), values = c("red", "black")) +
#  scale_fill_manual(values = c("red", "black")) +
  labs(x = NULL, y = NULL, color = NULL, fill = NULL, title = "Percent of caregivers experiencing material hardship") +
  theme_pubclean()
  
plot = ggplotly(plot, tooltip = "text")

for (i in 1:length(plot$x$data)){
    if (!is.null(plot$x$data[[i]]$name)){
        plot$x$data[[i]]$name =  gsub("\\(","",str_split(plot$x$data[[i]]$name,",")[[1]][1])
    }
}

plot

```

## Sources of hardship

```{r state-specific-13}
state_sources = scored %>%
  filter(state == mainstate) %>%
  select(Week, CaregiverID, starts_with("diff_pay")) %>%
  filter(Week > 0) %>%
  group_by(CaregiverID) %>%
  filter(Week == max(Week)) %>%
  ungroup() %>%
  select(-Week, -CaregiverID) %>%
  gather(need, response) %>%
  mutate(need = str_remove(need, "diff_pay_")) %>%
  filter(!is.na(response)) %>%
  group_by(need) %>%
  summarize(percent = 100*mean(response)) %>%
  ungroup() %>%
  mutate(group = mainstate)

sources = scored %>%
  select(Week, CaregiverID, starts_with("diff_pay")) %>%
  filter(Week > 0) %>%
  group_by(CaregiverID) %>%
  filter(Week == max(Week)) %>%
  ungroup() %>%
  select(-Week, -CaregiverID) %>%
  gather(need, response) %>%
  mutate(need = str_remove(need, "diff_pay_")) %>%
  filter(!is.na(response)) %>%
  group_by(need) %>%
  summarize(percent = 100*mean(response)) %>%
  ungroup() %>%
  mutate(group = "Entire US") %>%
  full_join(state_sources) %>%
  arrange(group, desc(percent)) %>%
  mutate(order = row_number()) 

sources %>%
  ggplot(aes(x = order, y = percent, fill = percent)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  # Add categories to axis
  scale_x_continuous(
    breaks = sources$order,
    labels = sources$need,
    expand = c(0,0)
  ) +
  guides(fill = F) +
  labs(x = NULL, y = NULL, title = "Percent of caregivers having difficulty paying for needs") +
  facet_wrap(~group, scales = "free_y")+
  theme_pubr()
```

