---
title: "Structural topic modeling of open-ended responses"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---



```{r chunk 1, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE)
options(knitr.kable.NA = '')
```

```{r}
library(here)
library(stm)
library(tidyverse)
library(tidytext)
library(furrr)
library(ggpubr)
library(psych)
library(conflicted)
library(LDAvis)
library(tidystm)
library(ggrepel)
library(plotly)
library(zoo)
library(wordcloud)
conflict_prefer("summarize", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")
conflict_prefer("map", "purrr")
source(here("Functions/pomp.R"))
```

```{r}
load(here("../../Data Management R3/R Data/scored_static_Nov11.Rdata"))
```

```{r}
open_ended = scored %>%
  filter(Week <= 26) %>%
  filter(language != "ES") %>%
  filter(language != "SPA") %>%
  select(-contains("OPEN.006")) %>%
  filter(!is.na(race_ethnic)) %>%
  filter(!is.na(poverty_cat)) %>%
  filter(!is.na(mental_health)) %>%
  gather("question", "response", contains("OPEN")) %>%
  mutate(question = str_extract(question, ".$")) %>%
  filter(!is.na(response)) 

# word count for each response

open_ended = open_ended %>%
  mutate(word_count = map_dbl(response, ~str_count(.x, "\\S+")))
```

# Question 1: Challenges

```{r}
open_ended1 = open_ended %>% filter(question == "1")


processed1 <- textProcessor(open_ended1$response, metadata = open_ended1)
out1 <- prepDocuments(processed1$documents, processed1$vocab, processed1$meta)
docs1 <- out1$documents
vocab1 <- out1$vocab
meta1 <- out1$meta

heldout1 = make.heldout(docs1, vocab1)
```

```{r, eval = F}
set.seed(07312020)
plan(multiprocess)

many_models <- tibble(K =seq(5,90, by=5)) %>%
  mutate(topic_model = future_map(K, ~stm(heldout1$documents, 
                                          heldout1$vocab, 
                                          K = .,
                                          prevalence =~ race_ethnic + poverty150 + mental_health + s(Week),
                                          data = meta1, 
                                          verbose = FALSE)))
k_result <- many_models %>%
  mutate(exclusivity = map(topic_model, exclusivity),
         semantic_coherence = map(topic_model, semanticCoherence, heldout1$documents),
         eval_heldout = map(topic_model, eval.heldout, heldout1$missing),
         residual = map(topic_model, checkResiduals, heldout1$documents),
         bound =  map_dbl(topic_model, function(x) max(x$convergence$bound)),
         lfact = map_dbl(topic_model, function(x) lfactorial(x$settings$dim$K)),
         lbound = bound + lfact,
         iterations = map_dbl(topic_model, function(x) length(x$convergence$bound)))

save(many_models, k_result, file = here("data/open1_many_models.Rdata"))

k_result %>%
  transmute(K,
            `Lower bound` = lbound,
            Residuals = map_dbl(residual, "dispersion"),
            `Semantic coherence` = map_dbl(semantic_coherence, mean),
            `Held-out likelihood` = map_dbl(eval_heldout, "expected.heldout")) %>%
  gather(Metric, Value, -K) %>%
  ggplot(aes(K, Value, color = Metric)) +
  geom_line(size = 1.5, alpha = 0.7, show.legend = FALSE) +
  facet_wrap(~Metric, scales = "free_y") +
  scale_x_continuous()+
  labs(x = "K (number of topics)",
       y = NULL,
       title = "Model diagnostics by number of topics") +
  theme_pubclean()

# looks like solution between 25 and 35 would be ideal

many_models_v2 <- tibble(K =seq(25,35, by=1)) %>%
  mutate(topic_model = future_map(K, ~stm(heldout1$documents, 
                                          heldout1$vocab, 
                                          K = .,
                                          prevalence =~ race_ethnic + poverty150 + mental_health + s(Week),
                                          data = meta1, 
                                          verbose = FALSE)))
k_result_v2 <- many_models_v2 %>%
  mutate(exclusivity = map(topic_model, exclusivity),
         semantic_coherence = map(topic_model, semanticCoherence, heldout1$documents),
         eval_heldout = map(topic_model, eval.heldout, heldout1$missing),
         residual = map(topic_model, checkResiduals, heldout1$documents),
         bound =  map_dbl(topic_model, function(x) max(x$convergence$bound)),
         lfact = map_dbl(topic_model, function(x) lfactorial(x$settings$dim$K)),
         lbound = bound + lfact,
         iterations = map_dbl(topic_model, function(x) length(x$convergence$bound)))

save(many_models_v2, k_result_v2, file = here("data/open1_many_models_v2.Rdata"))

k_result_v2 %>%
  transmute(K,
            `Lower bound` = lbound,
            Residuals = map_dbl(residual, "dispersion"),
            `Semantic coherence` = map_dbl(semantic_coherence, mean),
            `Held-out likelihood` = map_dbl(eval_heldout, "expected.heldout")) %>%
  gather(Metric, Value, -K) %>%
  ggplot(aes(K, Value, color = Metric)) +
  geom_line(size = 1.5, alpha = 0.7, show.legend = FALSE) +
  facet_wrap(~Metric, scales = "free_y") +
  scale_x_continuous()+
  labs(x = "K (number of topics)",
       y = NULL,
       title = "Model diagnostics by number of topics") +
  theme_pubclean()

# try solutions 27, 30, and 34
```

```{r, eval = F}
stmq1_27 <- stm(documents = docs1, 
                  vocab = vocab1,
                   K = 27, 
                   prevalence =~ race_ethnic + poverty150 + mental_health + s(Week),
                   data = meta1, 
                   init.type = "Spectral")

stmq1_30 <- stm(documents = docs1, 
                vocab = vocab1,
                K = 30, 
                prevalence =~ race_ethnic + poverty150 + mental_health + s(Week),
                data = meta1, 
                init.type = "Spectral")

stmq1_34 <- stm(documents = docs1, 
                vocab = vocab1,
                K = 34, 
                prevalence =~ race_ethnic + poverty150 + mental_health + s(Week),
                data = meta1, 
                init.type = "Spectral")

save(stmq1_27, stmq1_30, stmq1_34, file = here("data/stmq1_models.Rdata"))
```

```{r}
load(here("data/stmq1_models.Rdata"))
```

Testing three solutions: 27, 30 and 34 topics

## Most common topics{.tabset}

### 27

```{r}
td_beta27 <- tidy(stmq1_27)
td_gamma27 <- tidy(stmq1_27, matrix = "gamma")

meta1 = meta1 %>%
  mutate(document = row_number())

top_terms27 <- td_beta27 %>%
  arrange(beta) %>%
  group_by(topic) %>%
  top_n(7, beta) %>%
  arrange(-beta) %>%
  select(topic, term) %>%
  summarise(terms = list(term)) %>%
  mutate(terms = map(terms, paste, collapse = ", ")) %>% 
  unnest(cols = c(terms))

gamma_terms27 <- td_gamma27 %>%
  group_by(topic) %>%
  summarise(gamma = mean(gamma)) %>%
  arrange(desc(gamma)) %>%
  left_join(top_terms27, by = "topic") %>%
  mutate(topic = paste0("Topic ", topic),
         topic = reorder(topic, gamma))

gamma_terms27 %>%
  top_n(20, gamma) %>%
  ggplot(aes(topic, gamma, label = terms, fill = topic)) +
  geom_col(show.legend = FALSE) +
  geom_text(hjust = 0, nudge_y = 0.0005, size = 3) +
  scale_y_continuous(limits =c(0, .10))+
  coord_flip() +
  #theme_tufte(base_family = "IBMPlexSans", ticks = FALSE) +
  labs(x = NULL, y = expression(gamma),
       title = "Top 20 topics in 27 topic solution",
       subtitle = "With the top words that contribute to each topic") +
  theme_pubr()
```

### 30

```{r}
td_beta30 <- tidy(stmq1_30)
td_gamma30 <- tidy(stmq1_30, matrix = "gamma")

meta1 = meta1 %>%
  mutate(document = row_number())

top_terms30 <- td_beta30 %>%
  arrange(beta) %>%
  group_by(topic) %>%
  top_n(7, beta) %>%
  arrange(-beta) %>%
  select(topic, term) %>%
  summarise(terms = list(term)) %>%
  mutate(terms = map(terms, paste, collapse = ", ")) %>% 
  unnest(cols = c(terms))

gamma_terms30 <- td_gamma30 %>%
  group_by(topic) %>%
  summarise(gamma = mean(gamma)) %>%
  arrange(desc(gamma)) %>%
  left_join(top_terms30, by = "topic") %>%
  mutate(topic = paste0("Topic ", topic),
         topic = reorder(topic, gamma))

gamma_terms30 %>%
  top_n(20, gamma) %>%
  ggplot(aes(topic, gamma, label = terms, fill = topic)) +
  geom_col(show.legend = FALSE) +
  geom_text(hjust = 0, nudge_y = 0.0005, size = 3) +
  scale_y_continuous(limits =c(0, .10))+
  coord_flip() +
  #theme_tufte(base_family = "IBMPlexSans", ticks = FALSE) +
  labs(x = NULL, y = expression(gamma),
       title = "Top 20 topics in 30 topic solution",
       subtitle = "With the top words that contribute to each topic") +
  theme_pubr()
```

### 34

```{r}
td_beta34 <- tidy(stmq1_34)
td_gamma34 <- tidy(stmq1_34, matrix = "gamma")

meta1 = meta1 %>%
  mutate(document = row_number())

top_terms34 <- td_beta34 %>%
  arrange(beta) %>%
  group_by(topic) %>%
  top_n(7, beta) %>%
  arrange(-beta) %>%
  select(topic, term) %>%
  summarise(terms = list(term)) %>%
  mutate(terms = map(terms, paste, collapse = ", ")) %>% 
  unnest(cols = c(terms))

gamma_terms34 <- td_gamma34 %>%
  group_by(topic) %>%
  summarise(gamma = mean(gamma)) %>%
  arrange(desc(gamma)) %>%
  left_join(top_terms34, by = "topic") %>%
  mutate(topic = paste0("Topic ", topic),
         topic = reorder(topic, gamma))

gamma_terms34 %>%
  top_n(20, gamma) %>%
  ggplot(aes(topic, gamma, label = terms, fill = topic)) +
  geom_col(show.legend = FALSE) +
  geom_text(hjust = 0, nudge_y = 0.0005, size = 3) +
  scale_y_continuous(limits =c(0, .10))+
  coord_flip() +
  #theme_tufte(base_family = "IBMPlexSans", ticks = FALSE) +
  labs(x = NULL, y = expression(gamma),
       title = "Top 20 topics in 34 topic solution",
       subtitle = "With the top words that contribute to each topic") +
  theme_pubr()
```

## Identify topics{.tabset}

### 27{.tabset}

#### 1-5

**Topic 1: Defiance**

```{r}
topic_num = 1
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 2**

```{r}
topic_num = 2
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 3: Fall school plans**

```{r}
topic_num = 3
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 4: Relocating**

```{r}
topic_num = 4
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 5: Monotony and nerves**

```{r}
topic_num = 5
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

#### 6-10

**Topic 6: Balancing WFH and childcare**

```{r}
topic_num = 6
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 7: Keeping kids entertained**

```{r}
topic_num = 7
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 8: Social development of kids**

```{r}
topic_num = 8
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 9: Not being able to see family**

```{r}
topic_num = 9
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 10**

```{r}
topic_num = 10
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

#### 11-15

**Topic 11**

```{r}
topic_num = 11
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 12**

```{r}
topic_num = 12
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 13**

```{r}
topic_num = 13
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 14**

```{r}
topic_num = 14
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 15**

```{r}
topic_num = 15
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

#### 16-20

**Topic 16**

```{r}
topic_num = 16
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 17**

```{r}
topic_num = 17
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 18**

```{r}
topic_num = 18
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 19**

```{r}
topic_num = 19
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 20**

```{r}
topic_num = 20
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

#### 21-25

**Topic 21**

```{r}
topic_num = 21
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 22**

```{r}
topic_num = 22
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 23**

```{r}
topic_num = 23
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 24**

```{r}
topic_num = 24
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 25**

```{r}
topic_num = 25
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

#### 26-27

**Topic 26**

```{r}
topic_num = 26
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 27**

```{r}
topic_num = 27
labelTopics(stmq1_27, topics = topic_num)
findThoughts(stmq1_27, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

### 30{.tabset}

#### 1-5

**Topic 1**

```{r}
topic_num = 1
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 2**

```{r}
topic_num = 2
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 3**

```{r}
topic_num = 3
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 4**

```{r}
topic_num = 4
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 5**

```{r}
topic_num = 5
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

#### 6-10

**Topic 6**

```{r}
topic_num = 6
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 7**

```{r}
topic_num = 7
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 8**

```{r}
topic_num = 8
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 9**

```{r}
topic_num = 9
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 10**

```{r}
topic_num = 10
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

#### 11-15

**Topic 11**

```{r}
topic_num = 11
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 12**

```{r}
topic_num = 12
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 13**

```{r}
topic_num = 13
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 14**

```{r}
topic_num = 14
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 15**

```{r}
topic_num = 15
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

#### 16-20

**Topic 16**

```{r}
topic_num = 16
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 17**

```{r}
topic_num = 17
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 18**

```{r}
topic_num = 18
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 19**

```{r}
topic_num = 19
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 20**

```{r}
topic_num = 20
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

#### 21-25

**Topic 21**

```{r}
topic_num = 21
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 22**

```{r}
topic_num = 22
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 23**

```{r}
topic_num = 23
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 24**

```{r}
topic_num = 24
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 25**

```{r}
topic_num = 25
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

#### 26-30

**Topic 26**

```{r}
topic_num = 26
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 27**

```{r}
topic_num = 27
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 28**

```{r}
topic_num = 28
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 29**

```{r}
topic_num = 29
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 30**

```{r}
topic_num = 30
labelTopics(stmq1_30, topics = topic_num)
findThoughts(stmq1_30, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

### 34{.tabset}

#### 1-5

**Topic 1**

```{r}
topic_num = 1
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 2**

```{r}
topic_num = 2
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 3**

```{r}
topic_num = 3
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 4**

```{r}
topic_num = 4
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 5**

```{r}
topic_num = 5
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

#### 6-10

**Topic 6**

```{r}
topic_num = 6
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 7**

```{r}
topic_num = 7
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 8**

```{r}
topic_num = 8
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 9**

```{r}
topic_num = 9
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 10**

```{r}
topic_num = 10
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

#### 11-15

**Topic 11**

```{r}
topic_num = 11
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 12**

```{r}
topic_num = 12
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 13**

```{r}
topic_num = 13
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 14**

```{r}
topic_num = 14
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 15**

```{r}
topic_num = 15
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

#### 16-20

**Topic 16**

```{r}
topic_num = 16
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 17**

```{r}
topic_num = 17
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 18**

```{r}
topic_num = 18
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 19**

```{r}
topic_num = 19
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 20**

```{r}
topic_num = 20
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

#### 21-25

**Topic 21**

```{r}
topic_num = 21
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 22**

```{r}
topic_num = 22
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 23**

```{r}
topic_num = 23
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 24**

```{r}
topic_num = 24
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 25**

```{r}
topic_num = 25
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

#### 26-30

**Topic 26**

```{r}
topic_num = 26
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 27**

```{r}
topic_num = 27
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 28**

```{r}
topic_num = 28
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 29**

```{r}
topic_num = 29
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 30**

```{r}
topic_num = 30
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

#### 31-34

**Topic 31**

```{r}
topic_num = 31
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 32**

```{r}
topic_num = 32
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 33**

```{r}
topic_num = 33
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

**Topic 34**

```{r}
topic_num = 34
labelTopics(stmq1_34, topics = topic_num)
findThoughts(stmq1_34, 
             texts = out1$meta$response, 
             topics = topic_num, 
             n = 5)
```

# Topic correlations{.tabset}

## 27

```{r}
plot(topicCorr(stmq1_27))
```

## 30

```{r}
plot(topicCorr(stmq1_30))
```

## 34

```{r}
plot(topicCorr(stmq1_34))
```


# Effects

```{r}
predict_27 <- estimateEffect(formula = 1:27 ~ race_ethnic + mental_health + poverty150 + s(Week, df = 6), 
                               stmobj = stmq1_27, 
                               metadata = out1$meta, 
                               uncertainty = "Global")

predict_30 <- estimateEffect(formula = 1:30 ~ race_ethnic + mental_health + poverty150 + s(Week, df = 6),  
                               stmobj = stmq1_30, 
                               metadata = out1$meta, 
                               uncertainty = "Global")

predict_34<- estimateEffect(formula = 1:34 ~ race_ethnic + mental_health + poverty150 + s(Week, df = 6), 
                               stmobj = stmq1_34, 
                               metadata = out1$meta, 
                               uncertainty = "Global")
```


