---
title: "Child behavior"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
  
---

Please note that lines by date and days sheltering in place are smoothed curves -- they may be poor representations of the data in locations with few participants. For example, the largest number of days sheltering in place only applies to a small portion of participants; lines representing small demographic groups at these large should not be interpreted. 

```{r trend-child-1, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
```

```{r packages}
library(here)
library(tidyverse)
library(knitr)
library(kableExtra)
library(haven)
# require(devtools)
# install_version("zipcode", version = "1.0", repos = "http://cran.us.r-project.org")
library(zipcode)
library(ggthemr)
library(plotly)
```


```{r score datafile, echo = F, warning = F, message = F}
# score master --------------------------------------------------------

source(here("Scripts/score data.R"))
```

```{r trend-child-2}
total_weeks = max(scored$Week, na.rm=T)
```


```{r trend-child-3}
source(here("Functions/trend_days_sheltering_rolling.R"))
```


# Externalizing behavior {.tabset}

## By week

```{r trend-child-4}
fussy_date_demo = scored %>%
  select(CaregiverID, Week, all_of(binary_demos), fussy_current_some) %>%
  gather("demo", "value", all_of(binary_demos)) %>%
  filter(value == 1) %>%
  group_by(demo, Week) %>%
  summarize(total = n(),
            percent = 100*sum(fussy_current_some, na.rm=T)/total) %>%
  ungroup() %>% 
  mutate(demo = factor(demo, 
                       levels = binary_demos, 
                       labels = binary_labels))

fussy_date_all = scored %>%
  select(CaregiverID, Week, fussy_current_some) %>%
  group_by(Week) %>%
  summarize(total = n(),
            percent = 100*sum(fussy_current_some, na.rm=T)/total) 

fussy_date_demo = fussy_date_demo %>%
  ggplot(aes(x = Week, y = percent)) +
  geom_point(aes(color = demo)) + 
  geom_line(aes(color = demo)) +
  geom_point(data = fussy_date_all)+
  geom_line(data = fussy_date_all, linetype = "dashed") +
  labs(x = "Week",
       y = "Percent of demographic group",
       title = "__ Percent of caregivers report children are sometimes or often fussy or defiant",
       color = "Key demographics", 
       caption = "Entire sample is represented by the black, dashed line.") +
  theme_minimal() +
  theme(plot.title.position = "plot")

ggplotly(fussy_date_demo)
```

## By date

```{r trend-child-5}
fussy_date_demo = scored %>%
  select(CaregiverID, Date, all_of(binary_demos), fussy_current_some) %>%
  gather("demo", "value", all_of(binary_demos)) %>%
  filter(value == 1) %>%
  group_by(demo, Date) %>%
  summarize(total = n(),
            percent = 100*sum(fussy_current_some, na.rm=T)/total) %>%
  ungroup() %>% 
  mutate(demo = factor(demo, 
                       levels = binary_demos, 
                       labels = binary_labels))

fussy_date_all = scored %>%
  select(CaregiverID, Date, fussy_current_some) %>%
  group_by(Date) %>%
  summarize(total = n(),
            percent = 100*sum(fussy_current_some, na.rm=T)/total) 

fussy_date_demo = fussy_date_demo %>%
  ggplot(aes(x = Date, y = percent)) +
  geom_smooth(aes(color = demo),se = F) +
  geom_smooth(data = fussy_date_all, linetype = "dashed", se = F, color = "black") +
  labs(x = "Date",
       y = "Percent of demographic group",
       title = "__ Percent of caregivers report  children are sometimes or often fussy or defiant",
       color = "Key demographics", 
       caption = "Entire sample is represented by the black, dashed line.") +
  theme_minimal() +
  theme(plot.title.position = "plot")

ggplotly(fussy_date_demo)
```

## By days sheltering in place

```{r trend-child-6}
after_shelter = scored %>%
  filter(Week > 0)

fussy_plot = trend_days_sheltering_binary(variable = "fussy_current_some",
                                     dataset = after_shelter, 
                                     label = "children are sometimes or often defiant or fussy",
                                     groups = binary_demos,
                                     group_labels = binary_labels)
ggplotly(fussy_plot$plot)
```

```{r trend-child-7}
after_shelter = scored %>%
  filter(Week > 0)

fussy_plot = trend_days_sheltering_cat(variable = "fussy_current_some",
                                     dataset = after_shelter, 
                                     label = "children are sometimes or often defiant or fussy",
                                     groups = c("region"),
                                     group_levels = unique(after_shelter$region))
ggplotly(fussy_plot$plot)
```




# Internalizing behavior {.tabset}

## By week

```{r trend-child-8}
fear_date_demo = scored %>%
  select(CaregiverID, Week, all_of(binary_demos), fear_current_some) %>%
  gather("demo", "value", all_of(binary_demos)) %>%
  filter(value == 1) %>%
  group_by(demo, Week) %>%
  summarize(total = n(),
            percent = 100*sum(fear_current_some, na.rm=T)/total) %>%
  ungroup() %>% 
  mutate(demo = factor(demo, 
                       levels = binary_demos, 
                       labels = binary_labels))

fear_date_all = scored %>%
  select(CaregiverID, Week, fear_current_some) %>%
  group_by(Week) %>%
  summarize(total = n(),
            percent = 100*sum(fear_current_some, na.rm=T)/total) 

fear_date_demo = fear_date_demo %>%
  ggplot(aes(x = Week, y = percent)) +
  geom_point(aes(color = demo)) + 
  geom_line(aes(color = demo)) +
  geom_point(data = fear_date_all)+
  geom_line(data = fear_date_all, linetype = "dashed") +
  labs(x = "Week",
       y = "Percent of demographic group",
       title = "__ Percent of caregivers report children are sometimes or often too fearful or anxious",
       color = "Key demographics", 
       caption = "Entire sample is represented by the black, dashed line.") +
  theme_minimal() +
  theme(plot.title.position = "plot")

ggplotly(fear_date_demo)
```

## By date

```{r trend-child-9}
fear_date_demo = scored %>%
  select(CaregiverID, Date, all_of(binary_demos), fear_current_some) %>%
  gather("demo", "value", all_of(binary_demos)) %>%
  filter(value == 1) %>%
  group_by(demo, Date) %>%
  summarize(total = n(),
            percent = 100*sum(fear_current_some, na.rm=T)/total) %>%
  ungroup() %>% 
  mutate(demo = factor(demo, 
                       levels = binary_demos, 
                       labels = binary_labels))

fear_date_all = scored %>%
  select(CaregiverID, Date, fear_current_some) %>%
  group_by(Date) %>%
  summarize(total = n(),
            percent = 100*sum(fear_current_some, na.rm=T)/total) 

fear_date_demo = fear_date_demo %>%
  ggplot(aes(x = Date, y = percent)) +
  geom_smooth(aes(color = demo),se = F) +
  geom_smooth(data = fear_date_all, linetype = "dashed", se = F, color = "black") +
  labs(x = "Date",
       y = "Percent of demographic group",
       title = "__ Percent of caregivers report children are sometimes or often too fearful or anxious",
       color = "Key demographics", 
       caption = "Entire sample is represented by the black, dashed line.") +
  theme_minimal() +
  theme(plot.title.position = "plot")

ggplotly(fear_date_demo)
```

## By days sheltering in place

```{r trend-child-10}
after_shelter = scored %>%
  filter(Week > 0)

fear_plot = trend_days_sheltering_binary(variable = "fear_current_some",
                                     dataset = after_shelter, 
                                     label = "children are sometimes or often anxious or fearful",
                                     groups = binary_demos,
                                     group_labels = binary_labels)
ggplotly(fear_plot$plot)
```

```{r trend-child-11}
after_shelter = scored %>%
  filter(Week > 0)

fear_plot = trend_days_sheltering_cat(variable = "fear_current_some",
                                     dataset = after_shelter, 
                                     label = "children are sometimes or often anxious or fearful",
                                     groups = c("region"),
                                     group_levels = unique(after_shelter$region))
ggplotly(fear_plot$plot)
```

