---
title: "Food Insecurity and Material Hardship"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---


```{r usda-1, echo = F}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE, 
                      fig.width=12)
options(knitr.kable.NA = '')
```

```{r usda-2 }
library(conflicted)
library(here)
library(ggpubr)
conflict_prefer("group_rows", "kableExtra")
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")
conflict_prefer("map", "purrr")
library(plotly)
```

```{r usda-3 }
source(here("Scripts/score data.R")) 
source(here("Functions/pomp.R"))
cutoffv = 1
```

```{r usda-4 }
scored = scored %>%
  mutate(black_cat = factor(black, labels = c("non-Black", "Black")),
         poverty_cat = factor(poverty150, labels = c("High Income", "Low Income")),
         single_cat = factor(single, labels = c("Dual parent", "Single parent")),
         disability_cat = factor(disability, labels = c("No disability", "Child with disability")),
         race_ethnic = case_when(
           black == 1 ~ "Black",
           latinx == 1 ~ "LatinX",
           !is.na(black) ~ "White",
           !is.na(latinx) ~ "White",
           TRUE ~ NA_character_
         ),
         black_poverty = case_when(
           black == 1 & poverty150 == 1 ~ "Low income, Black",
           black == 1 & poverty150 == 0 ~ "High income, Black",
           latinx == 1 & poverty150 == 1 ~ "Low income, LatinX",
           latinx == 1 & poverty150 == 0 ~ "High income, LatinX",
           white == 1 & poverty150 == 1 ~ "Low income, White",
           white == 1 & poverty150 == 0 ~ "High income, White",
           TRUE ~ NA_character_))
```


# Food insecurity{.tabset}

```{r usda-5 }
usda_group = function(group, data = usda_scored){
  plot = data %>%
    filter(!is.na({{group}})) %>%
  group_by(Date, food_cat, {{group}}) %>%
  summarize(count = n()) %>%
  group_by(Date, {{group}}) %>%
  mutate(percent = 100*count/sum(count)) %>%
  filter(food_cat != "No") %>%
  ggplot(aes(x = Date, 
             y = percent, 
             color = {{group}},
             group = 1, 
             text = paste0(
               "Group: ", {{group}}, 
               "\nCount:", count,
               "\nPercent: ", round(percent, 1)
             ))) +
  geom_point() +
  geom_line()+  
  scale_x_time(breaks = date_labels$Date, labels = date_labels$label) +
  labs(title = "Percent of caregivers experiencing ___ food insecurity", 
       x = NULL,
       color = NULL, 
       y = NULL)+
    facet_wrap(~food_cat) +
  theme_pubclean() +
    theme(axis.text.x = element_text(angle = 35, hjust = 1, vjust = 1))

ggplotly(plot, tooltip = "text")

}
```

## Representativeness disclaimer

```{r usda-6 }
usda_scored = scored %>%
  filter(!is.na(food))

n_care = length(unique(usda_scored$CaregiverID))
date.min = format(min(as.Date(usda_scored$Date), na.rm = T), format = "%B %d, %Y")
date.max = format(max(as.Date(usda_scored$Date), na.rm = T), format = "%B %d, %Y")
perc = usda_scored %>%
  group_by(CaregiverID) %>%
  filter(Week == max(Week)) 
perc.black = 100*sum(perc$black, na.rm=T)/nrow(perc)
perc.latinx = 100*sum(perc$latinx, na.rm=T)/nrow(perc)
perc.fpl = 100*sum(perc$poverty150, na.rm=T)/nrow(perc)
```

These analyses are based on responses collected from `r papaja::printnum(n_care, format = "d")` caregivers between the dates of `r date.min` and `r date.max`. These caregivers represent a range of voices: `r papaja::printnum(perc.black)`\% are Black/African American, `r papaja::printnum(perc.latinx)`\% are LatinX, and `r papaja::printnum(perc.fpl)`\% live at or below 1.5 times the federal poverty line. Proportions/percentages are calculated based on the item-level response rates, not out of the total sample size. The data for these analyses are *not* weighted.

```{r usda-7 }
usda_scored = usda_scored  %>%
  group_by(Week) %>%
  mutate(Date = case_when(
    !is.na(Date) ~ min(Date),
    TRUE ~ as.Date("2020-08-01"))) %>%
  ungroup() %>%
  mutate(food_cat = case_when(
    food < 2 ~ "No",
    food >=2 & food <=4 ~ "Some",
    food > 4 ~ "A lot"
  )) 

date_labels = usda_scored %>%
  group_by(Date) %>%
  summarize(N = n()) %>%
  ungroup() %>%
  mutate(label = case_when(
    Date == "2020-08-01" ~ "Pre-pandemic",
    TRUE ~ format(Date, "%b %d")))
```



## All

```{r usda-8 }
plot = usda_scored %>%
  group_by(Date, food_cat) %>%
  summarize(count = n()) %>%
  group_by(Date) %>%
  mutate(percent = 100*count/sum(count)) %>%
  #mutate(Week = paste("Week", Week)) %>%
  filter(food_cat != "No") %>%
  ggplot(aes(x = Date, 
             y = percent, 
             color = food_cat,
             group = 1, 
             text = paste0(
               "Response: ", food_cat, 
               "\nPercent: ", round(percent, 1)
             ))) +
  geom_point() +
  geom_line()+  
  scale_x_time(breaks = date_labels$Date, labels = date_labels$label) +
  labs(title = "Percent of caregivers experiencing ___ food insecurity", 
       x = NULL,
       color = NULL, 
       y = NULL)+
  theme_pubclean()

ggplotly(plot, tooltip = "text")

```

## Race/ethnicity

```{r usda-9 }
usda_group(race_ethnic)
```


## Black

```{r usda-10 }
usda_group(black_cat)
```

## Income

```{r usda-11 }
usda_group(poverty_cat)
```

## Race + Income

```{r usda-12 }
usda_group(black_poverty)
```


## Medicaid expansion

```{r usda-13 }
usda_group(medicaid_expansion)
```



# Material hardship{.tabset}

_Which needs are hard to pay for?:_
- _Food_
- _Housing_
- _Utilities (electric, water, trash)_
- _Healthcare_
- _Social_
- _Emotional_
- _Childcare_
- _Other_

Caregivers grouped into two categories: trouble paying for 1+ basic need, or no trouble paying for any.

For these analyses, data collected in even numbered weeks starting in August were merged with data in the previous week -- this was due to a shift to a recruitment strategy that prioritized recruiting underrepresented communities and marginalized caregivers every other week.

## Representativeness disclaimer

```{r usda-14 }
hardship_scored = scored %>%
  rowwise() %>%
  mutate(material_hardship = sum(c_across(starts_with("diff_pay_")), na.rm=T)) %>%
  ungroup() %>%
  filter(!is.na(material_hardship) & Week > 0) %>%
  mutate(material_hardship = ifelse(material_hardship > 0, 1, 0)) %>%
  mutate(Week = case_when(
    Week < 17 ~ Week, 
    (Week %% 2) == 0 ~ NA_real_,
    TRUE ~ Week)) %>%
  filter(!is.na(Week)) %>%
  group_by(Week) %>%
  mutate(Date = case_when(
    !is.na(Date) ~ min(Date))) %>%
  ungroup() 

n_care = length(unique(hardship_scored$CaregiverID))
date.min = format(min(as.Date(hardship_scored$Date), na.rm = T), format = "%B %d, %Y")
date.max = format(max(as.Date(hardship_scored$Date), na.rm = T), format = "%B %d, %Y")
perc = hardship_scored %>%
  group_by(CaregiverID) %>%
  filter(Week == max(Week)) 
perc.black = 100*sum(perc$black, na.rm=T)/nrow(perc)
perc.latinx = 100*sum(perc$latinx, na.rm=T)/nrow(perc)
perc.fpl = 100*sum(perc$poverty150, na.rm=T)/nrow(perc)
```

These analyses are based on responses collected from `r papaja::printnum(n_care, format = "d")` caregivers between the dates of `r date.min` and `r date.max`. These caregivers represent a range of voices: `r papaja::printnum(perc.black)`\% are Black/African American, `r papaja::printnum(perc.latinx)`\% are LatinX, and `r papaja::printnum(perc.fpl)`\% live at or below 1.5 times the federal poverty line. Proportions/percentages are calculated based on the item-level response rates, not out of the total sample size. The data for these analyses are *not* weighted.


```{r usda-15 }
hardship_group = function(group, data = hardship_scored){
  
  plot = data %>%
    filter(!is.na({{group}})) %>%
    group_by(Week, Date, {{group}}) %>%
    summarize(count = n(),
              hardship = 100*sum(material_hardship)/count)  %>%
       ungroup()   %>%
    ggplot(aes(x = Date,
             y = hardship,
             group = 1,
             color = {{group}},
             text = paste0(
               "Date: ", Date,
               "\n Count: ", count,
               "\n Percent: ", round(hardship)))) +
  geom_point() +
  geom_line() +
  geom_vline(aes(xintercept = as.numeric(as.Date("2020-07-31"))), color = "red") +
  labs(x = NULL, y = NULL, color = NULL,
       title = "Percent of households experiencing at least one material hardship") +
  theme_pubr()
  
  ggplotly(plot, tooltip = "text")
  
}
```


## All

```{r usda-16 }
plot = hardship_scored %>%
  group_by(Week, Date) %>%
  summarize(count = n(),
            hardship = 100*sum(material_hardship)/count) %>%
  ggplot(aes(x = Date, 
             y = hardship, 
             text = paste0(
               "Date: ", Date, 
               "\n Count: ", count,
               "\n Percent: ", round(hardship)
             ),
             group = 1)) +
  geom_point() + 
  geom_line() +
  geom_vline(aes(xintercept = as.numeric(as.Date("2020-07-31"))), color = "red") +
  labs(x = NULL, y = NULL, title = "Percent of households experiencing at least one material hardship") +
  theme_pubr()

ggplotly(plot, tooltip = "text")
```

## Black

```{r usda-17 }
hardship_group(black_cat)
```

## Income

```{r usda-18 }
hardship_group(poverty_cat)
```

## Race + Income

```{r usda-19 }
hardship_group(black_poverty)
```

## Medicaid expansion

```{r usda-20 }
hardship_group(medicaid_expansion)
```

## Single 

```{r usda-21 }
hardship_group(single_cat)
```


## Disability

```{r usda-22 }
hardship_group(disability_cat)
```


# Family financial status{.tabset}


_Which describes your family financially at this time?:_
- _No problems_
- _Minor problems_
- _Major problems_
_ _Extreme problems_



For these analyses, data collected in even numbered weeks starting in August were merged with data in the previous week -- this was due to a shift to a recruitment strategy that prioritized recruiting underrepresented communities and marginalized caregivers every other week.

## Representativeness disclaimer

```{r usda-23 }
hardship_scored = scored %>%
  rowwise() %>%
  mutate(material_hardship = sum(c_across(starts_with("diff_pay_")), na.rm=T)) %>%
  ungroup() %>%
  filter(!is.na(material_hardship) & Week > 0) %>%
  mutate(material_hardship = ifelse(material_hardship > 0, 1, 0)) %>%
  mutate(Week = case_when(
    Week < 17 ~ Week, 
    (Week %% 2) == 0 ~ Week - 1,
    TRUE ~ Week)) %>%
  group_by(Week) %>%
  mutate(Date = case_when(
    !is.na(Date) ~ min(Date))) %>%
  ungroup() 

n_care = length(unique(hardship_scored$CaregiverID))
date.min = format(min(as.Date(hardship_scored$Date), na.rm = T), format = "%B %d, %Y")
date.max = format(max(as.Date(hardship_scored$Date), na.rm = T), format = "%B %d, %Y")
perc = hardship_scored %>%
  group_by(CaregiverID) %>%
  filter(Week == max(Week)) 
perc.black = 100*sum(perc$black, na.rm=T)/nrow(perc)
perc.latinx = 100*sum(perc$latinx, na.rm=T)/nrow(perc)
perc.fpl = 100*sum(perc$poverty150, na.rm=T)/nrow(perc)
```

These analyses are based on responses collected from `r papaja::printnum(n_care, format = "d")` caregivers between the dates of `r date.min` and `r date.max`. These caregivers represent a range of voices: `r papaja::printnum(perc.black)`\% are Black/African American, `r papaja::printnum(perc.latinx)`\% are LatinX, and `r papaja::printnum(perc.fpl)`\% live at or below 1.5 times the federal poverty line. Proportions/percentages are calculated based on the item-level response rates, not out of the total sample size. The data for these analyses are *not* weighted.


```{r usda-24 }
financial_group = function(group, data = hardship_scored){
  
  plot = data %>%
   filter(!is.na(financial_status) & !is.na({{group}})) %>%
  group_by(Week, Date, financial_status, {{group}}) %>%
  summarize(count = n()) %>%
  group_by(Week, Date, {{group}}) %>%
  mutate(percent = 100*count/sum(count)) %>%
  ggplot(aes(x = Date, 
             y = percent, 
             color = {{group}},
             group = 1, 
             text = paste0(
               "Date: ", Date, 
               "\n Count: ", count,
               "\n Percent: ", round(percent)
             ))) +
  geom_point() + 
  geom_line() +
  geom_vline(aes(xintercept = as.numeric(as.Date("2020-07-31"))), color = "red") +
  labs(x = NULL, y = NULL, color = NULL, 
       title = "Percent of households experiencing ___ problems") +
    facet_wrap(~financial_status) +
  theme_pubr()
  
  ggplotly(plot, tooltip = "text")
}
```


## All

```{r usda-25 }
plot = hardship_scored %>%
  filter(!is.na(financial_status)) %>%
  group_by(Week, Date, financial_status) %>%
  summarize(count = n()) %>%
  group_by(Week, Date) %>%
  mutate(percent = 100*count/sum(count)) %>%
  ggplot(aes(x = Date, 
             y = percent, 
             color = financial_status,
             group = 1, 
             text = paste0(
               "Date: ", Date, 
               "\n Count: ", count,
               "\n Percent: ", round(percent)
             ))) +
  geom_point() + 
  geom_line() +
  geom_vline(aes(xintercept = as.numeric(as.Date("2020-07-31"))), color = "red") +
  labs(x = NULL, y = NULL, color = NULL, 
       title = "Percent of households experiencing ___ problems") +
  theme_pubr()

ggplotly(plot, tooltip = "text")
```

## Black

```{r usda-26 }
financial_group(black_cat)
```

## Income

```{r usda-27 }
financial_group(poverty_cat)
```

## Race + Income

```{r usda-28 }
financial_group(black_poverty)
```

## Medicaid expansion

```{r usda-29 }
financial_group(medicaid_expansion)
```

## Single

```{r usda-30 }
financial_group(single_cat)
```

## Disability

```{r usda-31 }
financial_group(disability_cat)
```

# Looking ahead{.tabset}

_How worried are you about having enough money to pay for food to feed your household in the next month?_

_If you rent the place you currently live, how worried are you about being evicted in the next month?_

_If you own the home where you currently live, how worried are you about your mortgage being foreclosed on in the next month?_

_How worried are you about your utilities (water, electric, gas) being turned off in the next month?_

Response options:
- Not at all worried
- Slightly worried
- Somewhat worried
- Very worried
- Extremely worried



For these analyses, data collected in even numbered weeks starting in August were merged with data in the previous week -- this was due to a shift to a recruitment strategy that prioritized recruiting underrepresented communities and marginalized caregivers every other week.

## Representativeness disclaimer

```{r usda-32 }
hardship_scored = scored %>%
  filter(!is.na(mh_food) | !is.na(mh_eviction) | !is.na(mh_foreclose) | !is.na(mh_utilities)) %>%
  mutate_at(vars(starts_with("mh_")), ~ifelse(.x == 6, NA, .x)) %>%
  group_by(Week) %>%
  mutate(Date = case_when(
    !is.na(Date) ~ min(Date))) %>%
  ungroup() 

n_care = length(unique(hardship_scored$CaregiverID))
date.min = format(min(as.Date(hardship_scored$Date), na.rm = T), format = "%B %d, %Y")
date.max = format(max(as.Date(hardship_scored$Date), na.rm = T), format = "%B %d, %Y")
perc = hardship_scored %>%
  group_by(CaregiverID) %>%
  filter(Week == max(Week)) 
perc.black = 100*sum(perc$black, na.rm=T)/nrow(perc)
perc.latinx = 100*sum(perc$latinx, na.rm=T)/nrow(perc)
perc.fpl = 100*sum(perc$poverty150, na.rm=T)/nrow(perc)
```

These analyses are based on responses collected from `r papaja::printnum(n_care, format = "d")` caregivers between the dates of `r date.min` and `r date.max`. These caregivers represent a range of voices: `r papaja::printnum(perc.black)`\% are Black/African American, `r papaja::printnum(perc.latinx)`\% are LatinX, and `r papaja::printnum(perc.fpl)`\% live at or below 1.5 times the federal poverty line. Proportions/percentages are calculated based on the item-level response rates, not out of the total sample size. The data for these analyses are *not* weighted.


```{r usda-33 }

mh_all = function(variable, cutoff = cutoffv, data = hardship_scored){
    
    plot = data %>%
      filter(!is.na({{variable}})) %>%
      mutate_at(vars({{variable}}), ~ifelse(.x > cutoff, 1, 0)) %>%
      group_by(Date) %>%
      summarize(count = n(),
                percent = 100*sum({{variable}}/count)) %>%
      ungroup()  %>%
      ggplot(aes(x = Date,
                 y = percent,
                 group = 1,
                 text = paste0(
                   "Date: ", Date,
                   "\n Count: ", count,
                   "\n Percent: ", round(percent)
                 ))) +
      geom_point() +
      geom_line() +
      geom_vline(aes(xintercept = as.numeric(as.Date("2020-07-31"))), color = "red") +
      labs(x = NULL, y = NULL, color = NULL,
           title = "Percent of households worried") +
      theme_pubr()

  ggplotly(plot, tooltip = "text")
}


mh_group = function(variable, group, cutoff = cutoffv, data = hardship_scored){
  
    plot = data %>%
  filter(!is.na({{variable}}) & !is.na({{group}})) %>%
  mutate_at(vars({{variable}}), ~ifelse(.x > cutoff, 1, 0)) %>%
  group_by(Week, Date, {{group}}) %>%
  summarize(count = n(),
            percent = 100*sum({{variable}}/count)) %>%
    ungroup()  %>%
  ggplot(aes(x = Date,
             y = percent,
             color = {{group}},
             group = 1,
             text = paste0(
               "Date: ", Date,
               "\n Count: ", count,
               "\n Percent: ", round(percent)
             ))) +
  geom_point() +
  geom_line() +
  geom_vline(aes(xintercept = as.numeric(as.Date("2020-07-31"))), color = "red") +
  labs(x = NULL, y = NULL, color = NULL,
       title = "Percent of households worried") +
  theme_pubr()
  

  ggplotly(plot, tooltip = "text")
}
```

## Food{.tabset}

### All

```{r usda-34 }
mh_all(mh_food)
```

### Black

```{r usda-35 }
mh_group(mh_food, black_cat)
```

### Income

```{r usda-36 }
mh_group(mh_food, poverty_cat)
```

### Race + Income

```{r usda-37 }
mh_group(mh_food, black_poverty)
```

### Medicaid expansion

```{r usda-38 }
mh_group(mh_food, medicaid_expansion)
```

### Single

```{r usda-39 }
mh_group(mh_food, single_cat)
```

### Disability

```{r usda-40 }
mh_group(mh_food, disability_cat)
```

## Eviction{.tabset}

### All

```{r usda-41 }
mh_all(mh_eviction)
```

### Black

```{r usda-42 }
mh_group(mh_eviction, black_cat)
```

### Income

```{r usda-43 }
mh_group(mh_eviction, poverty_cat)
```

### Race + Income

```{r usda-44 }
mh_group(mh_eviction, black_poverty)
```

### Medicaid expansion

```{r usda-45 }
mh_group(mh_eviction, medicaid_expansion)
```

### Single

```{r usda-46 }
mh_group(mh_eviction, single_cat)
```

### Disability

```{r usda-47 }
mh_group(mh_eviction, disability_cat)
```

## Foreclosure{.tabset}

### All

```{r usda-48 }
mh_all(mh_foreclose)
```

### Black

```{r usda-49 }
mh_group(mh_foreclose, black_cat)
```

### Income

```{r usda-50 }
mh_group(mh_eviction, poverty_cat)
```

### Race + Income

```{r usda-51 }
mh_group(mh_foreclose, black_poverty)
```

### Medicaid expansion

```{r usda-52 }
mh_group(mh_foreclose, medicaid_expansion)
```

### Single

```{r usda-53 }
mh_group(mh_foreclose, single_cat)
```

### Disability

```{r usda-54 }
mh_group(mh_foreclose, disability_cat)
```

## Utilities{.tabset}

### All

```{r usda-55 }
mh_all(mh_utilities)
```

### Black

```{r usda-56 }
mh_group(mh_utilities, black_cat)
```

### Income

```{r usda-57 }
mh_group(mh_utilities, poverty_cat)
```

### Race + Income

```{r usda-58 }
mh_group(mh_utilities, black_poverty)
```

### Medicaid expansion

```{r usda-59 }
mh_group(mh_utilities, medicaid_expansion)
```


### Single

```{r usda-60 }
mh_group(mh_utilities, single_cat)
```

### Disability

```{r usda-61 }
mh_group(mh_utilities, disability_cat)
```

## All{.tabset}

```{r usda-62 }
hardship_scored = hardship_scored %>%
  mutate_at(vars(starts_with("mh_")), .funs = function(x) ifelse(x > cutoffv, 1, 0)) %>%
  mutate(mh_housing = case_when(
    mh_eviction == 1 ~ 1, 
    mh_foreclose == 1 ~ 1,
    mh_eviction == 0 ~ 0,
    mh_foreclose == 0 ~ 0,
    !is.na(mh_food) ~ 0,
    !is.na(mh_utilities) ~ 0,
    TRUE ~ NA_real_
  ),
  mh_food = case_when(
    !is.na(mh_food) ~ mh_food,
    !is.na(mh_housing) ~ 0
  ),
  mh_utilities = case_when(
    !is.na(mh_utilities) ~ mh_utilities,
    !is.na(mh_housing) ~ 0
  )) %>%
  select(-mh_eviction, -mh_foreclose) %>%
  mutate(mh_all = rowMeans(select(., contains("mh_")), na.rm=T)*3) 
```

```{r usda-63 }

mh_all = function(variable, cutoff = cutoffv, data = hardship_scored){
    
    plot = data %>%
      filter(!is.na({{variable}})) %>%
      group_by(Date, {{variable}}) %>%
      summarize(count = n()) %>%
      group_by(Date) %>%
      mutate(percent = 100*count/sum(count)) %>%
      filter({{variable}} > 0) %>%
      mutate_at(vars({{variable}}), factor) %>%
      ggplot(aes(x = Date,
                 y = percent,
                 group = 1,
                 color = {{variable}},
                 text = paste0(
                   "Date: ", Date,
                   "\n Count: ", count,
                   "\n Percent: ", round(percent)
                 ))) +
      geom_point() +
      geom_line() +
      geom_vline(aes(xintercept = as.numeric(as.Date("2020-07-31"))), color = "red") +
      labs(x = NULL, y = NULL, color = NULL,
           title = "Percent of households worried") +
      theme_pubr()

  ggplotly(plot, tooltip = "text")
}


mh_group = function(variable, group, cutoff = cutoffv, data = hardship_scored){
  
    plot = data %>%
   filter(!is.na({{variable}}) & !is.na({{group}})) %>%
      group_by(Date, {{variable}}, {{group}}) %>%
      summarize(count = n()) %>%
      group_by(Date, {{group}}) %>%
      mutate(percent = 100*count/sum(count)) %>%
      filter({{variable}} > 0) %>%
      mutate_at(vars({{variable}}), factor) %>%
  ggplot(aes(x = Date,
             y = percent,
             color = {{group}},
             group = 1,
             text = paste0(
               "Date: ", Date,
               "\n Count: ", count,
               "\n Percent: ", round(percent)
             ))) +
  geom_point() +
  geom_line() +
  geom_vline(aes(xintercept = as.numeric(as.Date("2020-07-31"))), color = "red") +
  labs(x = NULL, y = NULL, color = NULL,
       title = "Percent of households worried") +
    facet_wrap(facets = vars({{variable}})) +
  theme_pubr()
  

  ggplotly(plot, tooltip = "text")
}
```



### All

```{r usda-64 }
mh_all(mh_all)
```

### Black

```{r usda-65 }
mh_group(mh_all, black_cat)
```

### Income

```{r usda-66 }
mh_group(mh_all, poverty_cat)
```

### Race + Income

```{r usda-67 }
mh_group(mh_all, black_poverty)
```

### Medicaid expansion

```{r usda-68 }
mh_group(mh_all, medicaid_expansion)
```

### Single

```{r usda-69 }
mh_group(mh_all, single_cat)
```

### Disability

```{r usda-70 }
mh_group(mh_all, disability_cat)
```
