---
title: "Vaccine March 2021"
author: "Sihong"
date: "3/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include = FALSE}
library(here)
library(knitr)
library(readr)
library(haven)
library(tidyverse)
library(lavaan)
```


```{r, echo=FALSE, message = FALSE}
#Define functions
moe.p = function(p, n){
  q = 1-p
  moe = 1.96*sqrt((p*q)/n)
  return(moe)
}

moe.m = function(sd,n){
  moe = 1.96*sd/sqrt(n)
  return(moe)}

combine.cat = function(x, cols, id, newvar.name){
  subset = x[,c(id, "Week", cols)]
  names(subset) = c("id", "Week", paste0("X",1:length(cols)))
  subset = suppressWarnings(gather(subset, "key", "value", -id, -Week))
  subset = filter(subset, !is.na(value))
  subset$key = gsub("X", "", subset$key)
  subset = group_by(subset, id, Week)
  subset = summarise(subset, newvar = paste(key, collapse = ",")) %>% ungroup()
  names(subset) = c(id,"Week", newvar.name)
  x = suppressMessages(full_join(x, subset))
  return(x)
}

find_items = function(string, data2){
  items = names(data2)
  locations = which(grepl(string, items))
  final = items[locations]
  return(final)
}

my.max = function(x) ifelse (!all(is.na(x)), max(x,na.rm = TRUE), NA)
my.min = function(x) ifelse (!all(is.na(x)), min(x,na.rm = TRUE), NA)
```

```{r, echo=FALSE, message = FALSE, warning = FALSE, include=FALSE}
#OR load master data file
master_2020 <- read_sav(here("../../Data Management R3/CC_Clean Survey Data/00_R3 MasterFile/MasterFile_groupings_2020.sav"))
master_2021 <- read_sav(here("../../Data Management R3/CC_Clean Survey Data/00_R3 MasterFile/MasterFile_groupings_2021.sav"))

master <- full_join (master_2020, master_2021)

# Remove cases should be excluded
master <- master %>%
  filter ( CaregiverID != "" & is.na(Exclude) == T)

master = master %>%
  group_by(CaregiverID, Week) %>%
  filter(row_number() == max(row_number())) %>%
  ungroup()

total_week <- my.max(master$Week)


```


```{r, echo=FALSE, message = FALSE, warning = FALSE}
#Code demographics
master <- master %>%
  mutate (month = case_when(
                  Week == 0 ~ "Pre-COVID",
                  Week >0 & Week <= 4 ~ "April",
                  Week >=5 & Week <=8 ~ "May",
                  Week >=9 & Week <=13 ~ "June",
                  Week >=14 & Week <=17 ~ "July",
                  Week >=18 & Week <=21 ~ "August",
                  Week >=22 & Week <=26 ~ "September",
                  Week >=27 ~ "October"), 
           baseline = case_when (Week - BaselineWeek == 1 ~ 1, 
                                 Week - BaselineWeek > 1 ~ 0))

##Race/ethnicity - 1 = black, 2 = latinx, 3 = white

master <- master %>%
  mutate (RaceGroup = na_if (RaceGroup, 99))%>%
    mutate(
      minority = ifelse(RaceGroup != 5, 1, 0),
      black = ifelse(RaceGroup == 3, 1, 0),
      native = ifelse(RaceGroup == 1, 1, 0),
      asian = ifelse(RaceGroup == 2, 1, 0),
      hawaii = ifelse(RaceGroup == 4, 1, 0),
      white = ifelse(RaceGroup == 5, 1, 0),
      other_race = ifelse(RaceGroup %in% c(6, 7), 1, 0))

master <- master %>%
      mutate(latinx = case_when(
        DEMO.008 == 1 ~ 1,
        DEMO.008 == 0 ~ 0,
        DEMO.008.2 == 0 ~ 0,
        DEMO.008.2 == 1 ~ 1,
        DEMO.008.2 == 2 ~ 1,
        TRUE ~ NA_real_))

master <- master %>%
mutate (race_ethnic = case_when(
      black == 1 ~ "1",
      latinx == 1 ~ "2",
      !is.na(black) ~ "3",
      !is.na(latinx) ~ "3",
      TRUE ~ NA_character_))  

##Povertyline - 0 = high income, 1 = low income
master <- master %>%
  mutate (poverty_100 = FPL.2019.UM.100, 
          poverty_200 = FPL.2019.UM.200, 
          poverty_3c = case_when (FPL.2019.UM == 1 ~ 1,
                                  FPL.2019.UM %in% c(2,3,4)~ 2,
                                  FPL.2019.UM == 5 ~ 3))

master <- master %>%
  mutate (FPL_line = case_when (STATE_CODED == 1 & JOB.002 == 1 ~ 12760,
                                STATE_CODED == 1 & JOB.002 == 2 ~ 17240,
                                STATE_CODED == 1 & JOB.002 == 3 ~ 21720,
                                STATE_CODED == 1 & JOB.002 == 4 ~ 26200,
                                STATE_CODED == 1 & JOB.002 == 5 ~ 30680,
                                STATE_CODED == 1 & JOB.002 == 6 ~ 35160,
                                STATE_CODED == 1 & JOB.002 == 7 ~ 39640,
                                STATE_CODED == 1 & JOB.002 == 8 ~ 44120,
                                STATE_CODED == 1 & JOB.002 == 9 ~ 48600,
                                STATE_CODED == 1 & JOB.002 == 10 ~ 53080,
                                STATE_CODED == 1 & JOB.002 == 11 ~ 57560,
                                STATE_CODED == 1 & JOB.002 == 12 ~ 62040,
                                STATE_CODED == 1 & JOB.002 == 13 ~ 66520,
                                STATE_CODED == 1 & JOB.002 == 14 ~ 71000,
                                STATE_CODED == 1 & JOB.002 == 15 ~ 75480,
                                STATE_CODED == 1 & JOB.002 == 16 ~ 79960,
                                STATE_CODED == 1 & JOB.002 == 17 ~ 84440,
                                STATE_CODED == 1 & JOB.002 == 18 ~ 88920,
                                STATE_CODED == 1 & JOB.002 == 19 ~ 93400,
                                STATE_CODED == 1 & JOB.002 == 20 ~ 97880,
                                STATE_CODED == 1 & JOB.002 == 21 ~ 102360, 
                                STATE_CODED == 2 & JOB.002 == 1 ~ 15950,
                                STATE_CODED == 2 & JOB.002 == 2 ~ 21550,
                                STATE_CODED == 2 & JOB.002 == 3 ~ 27150,
                                STATE_CODED == 2 & JOB.002 == 4 ~ 32750,
                                STATE_CODED == 2 & JOB.002 == 5 ~ 38350,
                                STATE_CODED == 2 & JOB.002 == 6 ~ 43950,
                                STATE_CODED == 2 & JOB.002 == 7 ~ 49550,
                                STATE_CODED == 2 & JOB.002 == 8 ~ 55150,
                                STATE_CODED == 2 & JOB.002 == 9 ~ 60750,
                                STATE_CODED == 2 & JOB.002 == 10 ~ 66350,
                                STATE_CODED == 2 & JOB.002 == 11 ~ 71950,
                                STATE_CODED == 2 & JOB.002 == 12 ~ 77550,
                                STATE_CODED == 2 & JOB.002 == 13 ~ 83150,
                                STATE_CODED == 2 & JOB.002 == 14 ~ 88750,
                                STATE_CODED == 2 & JOB.002 == 15 ~ 94350,
                                STATE_CODED == 2 & JOB.002 == 16 ~ 99950,
                                STATE_CODED == 2 & JOB.002 == 17 ~ 105550,
                                STATE_CODED == 2 & JOB.002 == 18 ~ 111150,
                                STATE_CODED == 2 & JOB.002 == 19 ~ 116750,
                                STATE_CODED == 2 & JOB.002 == 20 ~ 122350,
                                STATE_CODED == 2 & JOB.002 == 21 ~ 127950,
                                STATE_CODED == 3 & JOB.002 == 1 ~ 14680,
                                STATE_CODED == 3 & JOB.002 == 2 ~ 19830,
                                STATE_CODED == 3 & JOB.002 == 3 ~ 24980,
                                STATE_CODED == 3 & JOB.002 == 4 ~ 30130,
                                STATE_CODED == 3 & JOB.002 == 5 ~ 35280,
                                STATE_CODED == 3 & JOB.002 == 6 ~ 40430,
                                STATE_CODED == 3 & JOB.002 == 7 ~ 45580,
                                STATE_CODED == 3 & JOB.002 == 8 ~ 50730,
                                STATE_CODED == 3 & JOB.002 == 9 ~ 55880,
                                STATE_CODED == 3 & JOB.002 == 10 ~ 61030,
                                STATE_CODED == 3 & JOB.002 == 11 ~ 66180,
                                STATE_CODED == 3 & JOB.002 == 12 ~ 71330,
                                STATE_CODED == 3 & JOB.002 == 13 ~ 76480,
                                STATE_CODED == 3 & JOB.002 == 14 ~ 81630,
                                STATE_CODED == 3 & JOB.002 == 15 ~ 86780,
                                STATE_CODED == 3 & JOB.002 == 16 ~ 91930,
                                STATE_CODED == 3 & JOB.002 == 17 ~ 97080,
                                STATE_CODED == 3 & JOB.002 == 18 ~ 102230,
                                STATE_CODED == 3 & JOB.002 == 19 ~ 107380,
                                STATE_CODED == 3 & JOB.002 == 20 ~ 112530,
                                STATE_CODED == 3 & JOB.002 == 21 ~ 117680))

#Material hardship
master <- master %>%
  combine.cat(cols = find_items("FSTR.002_.{1}$", master), 
              id = "CaregiverID",
              newvar.name = "FSTR.002_cat")
  

master <- master %>%
  mutate (diff_pay_food = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("1", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_), 
          diff_pay_utilities = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("3", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_house = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("2", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_healthcare = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("4", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_social = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("5", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_emotional = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("6", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_childcare = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("7", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_),
          diff_pay_other = case_when(
                          FSTR.001 == 0 ~ 0, 
                          grepl("8", FSTR.002_cat) ~ 1,
                          TRUE ~ NA_real_))

master <- master %>%
  rowwise() %>%
  mutate(material_hardship = case_when(
    Week == 0 ~ NA_real_,
    TRUE ~ sum(c_across(starts_with("diff_pay_")), na.rm=T))) %>%
  ungroup() %>%
  mutate(num_hardship = material_hardship,
    material_hardship = ifelse(material_hardship > 0, 1, 0)) 

## Children with special needs
master <- combine.cat(x = master, 
                       cols = find_items("HEALTH.005_[0-9]{1}$", master), 
                       id = "CaregiverID",
                       newvar.name = "HEALTH.005_cat")
master <- master %>%
   mutate (disability = case_when (HEALTH.005_1 == 1 ~ 1,
                                   HEALTH.005_2 == 1 ~ 1,
                                   HEALTH.005_3 == 1 ~ 1,
                                   HEALTH.005_4 == 1 ~ 1,
                                   HEALTH.005_5 == 1 ~ 0,
                                   HEALTH.005_6 == 1 ~ 1,
                                   TRUE ~ NA_real_))


## Single parent status
master <- master %>%
  mutate (single = case_when (
                   DEMO.002 %in% c(3,4,5,7,8)~1, 
                   DEMO.011 %in% c(2,4)~1,
                   !is.na(DEMO.002)~0,
                   !is.na(DEMO.011)~0,
                   TRUE ~ NA_real_))
                     
## Employment status
master <- combine.cat (x = master,
                       cols = find_items ("JOB.010_.{1,2}$", master), 
                       id = "CaregiverID",
                       newvar.name = "JOB.010_cat")
  
master$JOB.010_cat = gsub("10", "0", master$JOB.010_cat)
master$working_pre = ifelse (grepl("[1,2,6]", master$JOB.010_cat), 1, 0)
master = combine.cat (x = master,
                       cols = find_items ("JOB.008_.{1,2}$", master), 
                       id = "CaregiverID",
                       newvar.name = "JOB.008_cat")
master$JOB.008_cat = gsub("10", "0", master$JOB.008_cat)
master <- master %>%
  mutate (work_status = case_when(
                        grepl ("1", JOB.008_cat) ~ "1", 
                        grepl ("2", JOB.008_cat) ~ "1", 
                        grepl ("3", JOB.008_cat) ~ "0", 
                        grepl ("4", JOB.008_cat) ~ "0", 
                        grepl ("5", JOB.008_cat) ~ "1", 
                        JOB.008.2 == 1 ~ "1",
                        JOB.008.2 %in% c(2,3) ~ "0",
                        TRUE~NA_character_),
          work_status_pre = case_when(
                        grepl ("1", JOB.010_cat) ~ "1", 
                        grepl ("2", JOB.010_cat) ~ "1", 
                        grepl ("3", JOB.010_cat) ~ "0", 
                        grepl ("4", JOB.010_cat) ~ "0", 
                        grepl ("5", JOB.010_cat) ~ "1", 
                        TRUE~NA_character_))
#1 = stable employed 2 = became unemployed 3 = became employed4 = stable unemployed

# Region
master <- master %>%
  mutate (region = na_if (DEMO.001.b, 5))

master_dem <- master %>%
  group_by (CaregiverID) %>%
  summarise (BaselineWeek = my.max (BaselineWeek),
             race_ethnic = my.max(race_ethnic),
             poverty_cat = my.max (FPL.2019.UM.150),
             poverty_100 = my.max(poverty_100),
             poverty_200 = my.max(poverty_200),
             poverty_3c = my.min(poverty_3c),
             income19 = my.min (allyearly2019),
             FPL_line = my.min (FPL_line),
             disability = my.max (disability),
             num_hm = my.max (JOB.002),
             num_cd = my.max (DEMO.003),
             single = my.max (single),
             work_status = my.max (work_status),
             work_status_pre = my.max (work_status_pre), 
             region = my.max(region))%>%
  mutate ( ep_change = case_when(
                        work_status == 1 & work_status_pre == 1 ~ "1", 
                        work_status == 1 & work_status_pre == 0 ~ "2", 
                        work_status == 0 & work_status_pre == 1 ~ "3", 
                        work_status == 0 & work_status_pre == 0 ~ "4", 
                        TRUE~NA_character_), 
           num_adult = num_hm - num_cd, 
           FPL_pct = income19/FPL_line)%>%
  mutate (race_ethnic = case_when (
                        race_ethnic == 1 ~ "Black", 
                        race_ethnic == 2 ~ "Latinx", 
                        race_ethnic == 3 ~ "White", 
                        TRUE~NA_character_),
          poverty_cat = case_when (poverty_cat == 1 ~ "Below 150%FPL", 
                                   poverty_cat == 0 ~ "Above 150%FPL", 
                                   TRUE~NA_character_),
          poverty_100 = case_when (
                        poverty_100 == 1 ~ "Below 100%FPL", 
                        poverty_100 == 0 ~ "Above 100%FPL", 
                        TRUE~NA_character_),
          poverty_200 = case_when (
                        poverty_200 == 1 ~ "Below 200%FPL", 
                        poverty_200 == 0 ~ "Above 200%FPL", 
                        TRUE~NA_character_),
          poverty_3c = case_when (
                        poverty_3c == 1 ~ "1.Below 100%FPL", 
                        poverty_3c == 2 ~ "2.100-200%FPL", 
                        poverty_3c == 3 ~ "3.Above 200%FPL", 
                        TRUE~NA_character_),
          disability = case_when (
                        disability == 1 ~ "With disability", 
                        disability == 0 ~ "Without disability", 
                        TRUE~NA_character_),
          single = case_when (
                        single == 1 ~ "Single parent", 
                        single == 0 ~ "Dual parent", 
                        TRUE~NA_character_),
          work_status = case_when (
                        work_status == 1 ~ "Employed", 
                        work_status == 0 ~ "Unemployed", 
                        TRUE~NA_character_),
          work_status_pre = case_when (
                        work_status_pre == 1 ~ "Employed", 
                        work_status_pre == 0 ~ "Unemployed", 
                        TRUE~NA_character_),
          ep_change = case_when (
                        ep_change == 1 ~ "Stable employed", 
                        ep_change == 2 ~ "Became employed", 
                        ep_change == 3 ~ "Became unemployed",
                        ep_change == 4 ~ "Stable unemployed",
                        TRUE~NA_character_), 
          region = case_when (
                        region == 1 ~ "Northeast", 
                        region == 2 ~ "Midwest", 
                        region == 3 ~ "South", 
                        region == 4 ~ "West",
                        TRUE~NA_character_))
```


```{r, echo=FALSE, message = FALSE, warning = FALSE}
vaccine <- master %>%
  select (CaregiverID, StartDate, Week, contains ("HEALTH.016"), contains ("HEALTH.017"), contains ("HEALTH.020"), contains("HEALTH.021"), HEALTH.022, HEALTH.023 )%>%
  filter (Week %in% c(25,27,29,31,33,35,41,43,45))

vaccine <- merge (x = vaccine, y = master_dem, by.x = "CaregiverID", by.y = "CaregiverID", all.x = T)

num_responses = function(x){length(which(!is.na(x)))}
vaccine.num <- vaccine %>%
  group_by(Week) %>%
  summarize_all(num_responses) %>%
  gather("Variable", "num_responses",-Week) %>%
  mutate(week = paste0("Week", Week),
         week = factor(Week, levels = paste0("Week", c(1:total_week)))) %>%
  spread(Week, num_responses)

vaccine_rct <- vaccine %>%
  group_by (CaregiverID)%>%
  filter (Week == max (Week))%>%
  ungroup()
```

# 0. Sample Disclaimer
  * This set of analyses on stimulus spending is based on responses collected from 3,860 caregivers between the dates of September 21st, 2020 and February 20th, 2021. These caregivers represent a range of voices: 7.00% are Black/African American, 12.52% are Latinx, and 26.57% live at or below 1.5 times the federal poverty line.  Proportions/percentages are calculated based on the item-level response rates, not out of the total sample size. The data for these analyses are not weighted. \


# 1. COVID Vaccine
  * Survey question: How likely are you to get the first generation COVID-19 vaccine, as soon as it's available? - very likely/somewhat likely/not very likely/not at all likely/already vaccinated\
  * How likely are you to get your child the first generation COVID-19 vaccine, as soon as it's available?- very likely/somewhat likely/not very likely/not at all likely/already vaccinated\
  * Note that "already vaccinated" option was added from week 43 (early February), so the % of participants reporting on this option before week 43 were all 0. \

```{r, echo=FALSE, message = FALSE, warning = FALSE, fig.show='hide'}

## 1.1 Most recent responses
### 1.1.1 Overall

vaccine_parent <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   group_by (CaregiverID)%>%
   filter (Week == max (Week))%>%
   ungroup ()%>%
   mutate (a.very_likely = ifelse (HEALTH.022 == 1, 1, 0),
           b.somewhat_likely = ifelse (HEALTH.022 == 2, 1, 0),
           c.not_very_likely = ifelse (HEALTH.022 == 3, 1, 0),
           d.not_at_all_likely = ifelse (HEALTH.022 == 4, 1, 0), 
           e.already_vaccinated = ifelse (HEALTH.022 == 5, 1, 0))%>%
   summarise (n = n(),
              a.very_likely = sum(a.very_likely, na.rm = T)/n,
              b.somewhat_likely = sum(b.somewhat_likely, na.rm = T)/n,
              c.not_very_likely = sum(c.not_very_likely, na.rm = T)/n, 
              d.not_at_all_likely = sum(d.not_at_all_likely, na.rm = T)/n, 
              e.already_vaccinated = sum(e.already_vaccinated, na.rm = T)/n)%>%
   pivot_longer (cols = c("a.very_likely", "b.somewhat_likely", "c.not_very_likely", "d.not_at_all_likely", "e.already_vaccinated"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")
   
vaccine_child <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   group_by (CaregiverID)%>%
   filter (Week == max (Week))%>%
   ungroup ()%>%
   mutate (a.very_likely = ifelse (HEALTH.023 == 1, 1, 0),
           b.somewhat_likely = ifelse (HEALTH.023 == 2, 1, 0),
           c.not_very_likely = ifelse (HEALTH.023 == 3, 1, 0),
           d.not_at_all_likely = ifelse (HEALTH.023 == 4, 1, 0), 
           e.already_vaccinated = ifelse (HEALTH.023 == 5, 1, 0))%>%
   summarise (n = n(),
              a.very_likely = sum(a.very_likely, na.rm = T)/n,
              b.somewhat_likely = sum(b.somewhat_likely, na.rm = T)/n,
              c.not_very_likely = sum(c.not_very_likely, na.rm = T)/n, 
              d.not_at_all_likely = sum(d.not_at_all_likely, na.rm = T)/n, 
              e.already_vaccinated = sum(e.already_vaccinated, na.rm = T)/n)%>%
   pivot_longer (cols = c("a.very_likely", "b.somewhat_likely", "c.not_very_likely", "d.not_at_all_likely", "e.already_vaccinated"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "child")
   
vaccine_smy <- rbind (vaccine_parent, vaccine_child)         

vaccine_smy %>%
  ggplot(mapping = aes (x =  rsp, y = prop*100, fill = rsp)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = ci_low*100, 
                    ymax = ci_high*100),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -2,hjust = 0.5, size = 3, color = "black",  position = position_dodge(1))+
  facet_wrap(~who, ncol = 2)+
  theme(axis.text.x = element_text(angle = 90))


```


```{r, echo=FALSE, message = FALSE, warning = FALSE, fig.show='hide'}
### 1.1.2 By race/ethnicity
vaccine_parent <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   group_by (CaregiverID)%>%
   filter (Week == max (Week))%>%
   ungroup ()%>%
   mutate (a.very_likely = ifelse (HEALTH.022 == 1, 1, 0),
           b.somewhat_likely = ifelse (HEALTH.022 == 2, 1, 0),
           c.not_very_likely = ifelse (HEALTH.022 == 3, 1, 0),
           d.not_at_all_likely = ifelse (HEALTH.022 == 4, 1, 0), 
           e.already_vaccinated = ifelse (HEALTH.022 == 5, 1, 0))%>%
  filter (race_ethnic!= "NA")%>%
  group_by (race_ethnic)%>%
   summarise (n = n(),
              a.very_likely = sum(a.very_likely, na.rm = T)/n,
              b.somewhat_likely = sum(b.somewhat_likely, na.rm = T)/n,
              c.not_very_likely = sum(c.not_very_likely, na.rm = T)/n, 
              d.not_at_all_likely = sum(d.not_at_all_likely, na.rm = T)/n, 
              e.already_vaccinated = sum(e.already_vaccinated, na.rm = T)/n)%>%
   pivot_longer (cols = c("a.very_likely", "b.somewhat_likely", "c.not_very_likely", "d.not_at_all_likely", "e.already_vaccinated"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")
   
vaccine_child <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   group_by (CaregiverID)%>%
   filter (Week == max (Week))%>%
   ungroup ()%>%
   mutate (a.very_likely = ifelse (HEALTH.023 == 1, 1, 0),
           b.somewhat_likely = ifelse (HEALTH.023 == 2, 1, 0),
           c.not_very_likely = ifelse (HEALTH.023 == 3, 1, 0),
           d.not_at_all_likely = ifelse (HEALTH.023 == 4, 1, 0), 
           e.already_vaccinated = ifelse (HEALTH.023 == 5, 1, 0))%>%
  filter (race_ethnic!= "NA")%>%
  group_by (race_ethnic)%>%
   summarise (n = n(),
              a.very_likely = sum(a.very_likely, na.rm = T)/n,
              b.somewhat_likely = sum(b.somewhat_likely, na.rm = T)/n,
              c.not_very_likely = sum(c.not_very_likely, na.rm = T)/n, 
              d.not_at_all_likely = sum(d.not_at_all_likely, na.rm = T)/n, 
              e.already_vaccinated = sum(e.already_vaccinated, na.rm = T)/n)%>%
   pivot_longer (cols = c("a.very_likely", "b.somewhat_likely", "c.not_very_likely", "d.not_at_all_likely", "e.already_vaccinated"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "child")
   
vaccine_smy <- rbind (vaccine_parent, vaccine_child)         

vaccine_smy %>%
  ggplot(mapping = aes (x =  rsp, y = prop*100, fill = rsp)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = ci_low*100, 
                    ymax = ci_high*100),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -1,hjust = 0.5, size = 2.5, color = "black",  position = position_dodge(1))+
  facet_wrap(who~race_ethnic, ncol = 3)+
  theme(axis.text.x = element_blank())


```


```{r, echo=FALSE, message = FALSE, warning = FALSE, fig.show='hide'}
### 1.1.3 By poverty level
vaccine_parent <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   group_by (CaregiverID)%>%
   filter (Week == max (Week))%>%
   ungroup ()%>%
   mutate (a.very_likely = ifelse (HEALTH.022 == 1, 1, 0),
           b.somewhat_likely = ifelse (HEALTH.022 == 2, 1, 0),
           c.not_very_likely = ifelse (HEALTH.022 == 3, 1, 0),
           d.not_at_all_likely = ifelse (HEALTH.022 == 4, 1, 0), 
           e.already_vaccinated = ifelse (HEALTH.022 == 5, 1, 0))%>%
  filter (poverty_cat!= "NA")%>%
  group_by (poverty_cat)%>%
   summarise (n = n(),
              a.very_likely = sum(a.very_likely, na.rm = T)/n,
              b.somewhat_likely = sum(b.somewhat_likely, na.rm = T)/n,
              c.not_very_likely = sum(c.not_very_likely, na.rm = T)/n, 
              d.not_at_all_likely = sum(d.not_at_all_likely, na.rm = T)/n, 
              e.already_vaccinated = sum(e.already_vaccinated, na.rm = T)/n)%>%
   pivot_longer (cols = c("a.very_likely", "b.somewhat_likely", "c.not_very_likely", "d.not_at_all_likely", "e.already_vaccinated"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")
   
vaccine_child <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   group_by (CaregiverID)%>%
   filter (Week == max (Week))%>%
   ungroup ()%>%
   mutate (a.very_likely = ifelse (HEALTH.023 == 1, 1, 0),
           b.somewhat_likely = ifelse (HEALTH.023 == 2, 1, 0),
           c.not_very_likely = ifelse (HEALTH.023 == 3, 1, 0),
           d.not_at_all_likely = ifelse (HEALTH.023 == 4, 1, 0), 
           e.already_vaccinated = ifelse (HEALTH.023 == 5, 1, 0))%>%
  filter (poverty_cat!= "NA")%>%
  group_by (poverty_cat)%>%
   summarise (n = n(),
              a.very_likely = sum(a.very_likely, na.rm = T)/n,
              b.somewhat_likely = sum(b.somewhat_likely, na.rm = T)/n,
              c.not_very_likely = sum(c.not_very_likely, na.rm = T)/n, 
              d.not_at_all_likely = sum(d.not_at_all_likely, na.rm = T)/n,
              e.already_vaccinated = sum(e.already_vaccinated, na.rm = T)/n)%>%
   pivot_longer (cols = c("a.very_likely", "b.somewhat_likely", "c.not_very_likely", "d.not_at_all_likely", "e.already_vaccinated"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "child")
   
vaccine_smy <- rbind (vaccine_parent, vaccine_child)         

vaccine_smy %>%
  ggplot(mapping = aes (x =  rsp, y = prop*100, fill = poverty_cat)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = ci_low*100, 
                    ymax = ci_high*100),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -1,hjust = 0.5, size = 2.5, color = "black",  position = position_dodge(1))+
  facet_wrap(~who, ncol = 2)+
  theme(axis.text.x = element_text(angle = 90))


```


```{r, echo=FALSE, message = FALSE, warning = FALSE, fig.show='hide'}
### 1.1.4 By poverty level & race/ethnicity
vaccine_parent <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   group_by (CaregiverID)%>%
   filter (Week == max (Week))%>%
   ungroup ()%>%
   mutate (a.very_likely = ifelse (HEALTH.022 == 1, 1, 0),
           b.somewhat_likely = ifelse (HEALTH.022 == 2, 1, 0),
           c.not_very_likely = ifelse (HEALTH.022 == 3, 1, 0),
           d.not_at_all_likely = ifelse (HEALTH.022 == 4, 1, 0), 
           e.already_vaccinated = ifelse (HEALTH.022 == 5, 1, 0))%>%
  filter (poverty_cat!= "NA" & race_ethnic!= "NA")%>%
  group_by (poverty_cat, race_ethnic)%>%
   summarise (n = n(),
              a.very_likely = sum(a.very_likely, na.rm = T)/n,
              b.somewhat_likely = sum(b.somewhat_likely, na.rm = T)/n,
              c.not_very_likely = sum(c.not_very_likely, na.rm = T)/n, 
              d.not_at_all_likely = sum(d.not_at_all_likely, na.rm = T)/n,
              e.already_vaccinated = sum(e.already_vaccinated, na.rm = T)/n)%>%
   pivot_longer (cols = c("a.very_likely", "b.somewhat_likely", "c.not_very_likely", "d.not_at_all_likely", "e.already_vaccinated"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")
   
vaccine_child <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   group_by (CaregiverID)%>%
   filter (Week == max (Week))%>%
   ungroup ()%>%
   mutate (a.very_likely = ifelse (HEALTH.023 == 1, 1, 0),
           b.somewhat_likely = ifelse (HEALTH.023 == 2, 1, 0),
           c.not_very_likely = ifelse (HEALTH.023 == 3, 1, 0),
           d.not_at_all_likely = ifelse (HEALTH.023 == 4, 1, 0), 
           e.already_vaccinated = ifelse (HEALTH.023 == 5, 1, 0))%>%
  filter (poverty_cat!= "NA" & race_ethnic!= "NA")%>%
  group_by (poverty_cat, race_ethnic)%>%
   summarise (n = n(),
              a.very_likely = sum(a.very_likely, na.rm = T)/n,
              b.somewhat_likely = sum(b.somewhat_likely, na.rm = T)/n,
              c.not_very_likely = sum(c.not_very_likely, na.rm = T)/n, 
              d.not_at_all_likely = sum(d.not_at_all_likely, na.rm = T)/n,
              e.already_vaccinated = sum(e.already_vaccinated, na.rm = T)/n)%>%
   pivot_longer (cols = c("a.very_likely", "b.somewhat_likely", "c.not_very_likely", "d.not_at_all_likely", "e.already_vaccinated"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "child")
   
vaccine_smy <- rbind (vaccine_parent, vaccine_child)         

vaccine_smy %>%
  ggplot(mapping = aes (x =  rsp, y = prop*100, fill = poverty_cat)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = ci_low*100, 
                    ymax = ci_high*100),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,0)),vjust = -2,hjust = 0.5, size = 2, color = "black",  position = position_dodge(1))+
  facet_wrap(who~race_ethnic, ncol = 3)+
  theme(axis.text.x = element_text(angle = 90))
```

## 1.1 Trend
### 1.1.1 Overall
```{r, echo=FALSE, message = FALSE, warning = FALSE}

vaccine_parent <- vaccine %>%
   filter (Week != 25 & Week != 27 )%>%
   mutate (a.very_likely = ifelse (HEALTH.022 == 1, 1, 0),
           b.somewhat_likely = ifelse (HEALTH.022 == 2, 1, 0),
           c.not_very_likely = ifelse (HEALTH.022 == 3, 1, 0),
           d.not_at_all_likely = ifelse (HEALTH.022 == 4, 1, 0), 
           e.already_vaccinated = ifelse (HEALTH.022 == 5, 1, 0))%>%
  group_by (Week)%>%
   summarise (n = n(),
              a.very_likely = sum(a.very_likely, na.rm = T)/n,
              b.somewhat_likely = sum(b.somewhat_likely, na.rm = T)/n,
              c.not_very_likely = sum(c.not_very_likely, na.rm = T)/n, 
              d.not_at_all_likely = sum(d.not_at_all_likely, na.rm = T)/n, 
              e.already_vaccinated = sum(e.already_vaccinated, na.rm = T)/n,
              date = as.Date(min (StartDate)))%>%
   pivot_longer (cols = c("a.very_likely", "b.somewhat_likely", "c.not_very_likely", "d.not_at_all_likely", "e.already_vaccinated"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")
   
vaccine_child <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   mutate (a.very_likely = ifelse (HEALTH.023 == 1, 1, 0),
           b.somewhat_likely = ifelse (HEALTH.023 == 2, 1, 0),
           c.not_very_likely = ifelse (HEALTH.023 == 3, 1, 0),
           d.not_at_all_likely = ifelse (HEALTH.023 == 4, 1, 0), 
           e.already_vaccinated = ifelse (HEALTH.023 == 5, 1, 0))%>%
  group_by (Week)%>%
   summarise (n = n(),
              a.very_likely = sum(a.very_likely, na.rm = T)/n,
              b.somewhat_likely = sum(b.somewhat_likely, na.rm = T)/n,
              c.not_very_likely = sum(c.not_very_likely, na.rm = T)/n, 
              d.not_at_all_likely = sum(d.not_at_all_likely, na.rm = T)/n, 
              e.already_vaccinated = sum(e.already_vaccinated, na.rm = T)/n,
              date = as.Date(min (StartDate)))%>%
   pivot_longer (cols = c("a.very_likely", "b.somewhat_likely", "c.not_very_likely", "d.not_at_all_likely", "e.already_vaccinated"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "child")
   
vaccine_smy <- rbind (vaccine_parent, vaccine_child)         
date <- vaccine %>%
  group_by (Week)%>%
  summarise (date = min (StartDate))%>%
  ungroup()


vaccine_smy %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = rsp)) +
  geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  labs (y = "Percentage")+
  ggtitle(label = "Trend of changes")+
  facet_wrap(~who, nrow = 2)

```

### 1.2.2 By race/ethnicity
```{r, echo=FALSE, message = FALSE, warning = FALSE}

vaccine_parent <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   mutate (a.very_likely = ifelse (HEALTH.022 == 1, 1, 0),
           b.somewhat_likely = ifelse (HEALTH.022 == 2, 1, 0),
           c.not_very_likely = ifelse (HEALTH.022 == 3, 1, 0),
           d.not_at_all_likely = ifelse (HEALTH.022 == 4, 1, 0), 
           e.already_vaccinated = ifelse (HEALTH.022 == 5, 1, 0))%>%
  filter (race_ethnic!= "NA")%>%
  group_by (Week, race_ethnic)%>%
   summarise (n = n(),
              a.very_likely = sum(a.very_likely, na.rm = T)/n,
              b.somewhat_likely = sum(b.somewhat_likely, na.rm = T)/n,
              c.not_very_likely = sum(c.not_very_likely, na.rm = T)/n, 
              d.not_at_all_likely = sum(d.not_at_all_likely, na.rm = T)/n, 
              e.already_vaccinated = sum(e.already_vaccinated, na.rm = T)/n,
              date = as.Date(min (StartDate)))%>%
   pivot_longer (cols = c("a.very_likely", "b.somewhat_likely", "c.not_very_likely", "d.not_at_all_likely", "e.already_vaccinated"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")
   
vaccine_child <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   mutate (a.very_likely = ifelse (HEALTH.023 == 1, 1, 0),
           b.somewhat_likely = ifelse (HEALTH.023 == 2, 1, 0),
           c.not_very_likely = ifelse (HEALTH.023 == 3, 1, 0),
           d.not_at_all_likely = ifelse (HEALTH.023 == 4, 1, 0), 
           e.already_vaccinated = ifelse (HEALTH.023 == 5, 1, 0))%>%
   filter (race_ethnic!= "NA")%>%
  group_by (Week, race_ethnic)%>%
   summarise (n = n(),
              a.very_likely = sum(a.very_likely, na.rm = T)/n,
              b.somewhat_likely = sum(b.somewhat_likely, na.rm = T)/n,
              c.not_very_likely = sum(c.not_very_likely, na.rm = T)/n, 
              d.not_at_all_likely = sum(d.not_at_all_likely, na.rm = T)/n, 
              e.already_vaccinated = sum(e.already_vaccinated, na.rm = T)/n,
              date = as.Date(min (StartDate)))%>%
   pivot_longer (cols = c("a.very_likely", "b.somewhat_likely", "c.not_very_likely", "d.not_at_all_likely", "e.already_vaccinated"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "child")
   
vaccine_smy <- rbind (vaccine_parent, vaccine_child)         
date <- vaccine %>%
  group_by (Week)%>%
  summarise (date = min (StartDate))%>%
  ungroup()


vaccine_smy %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = rsp)) +
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  labs (y = "Percentage")+
  ggtitle(label = "Trend of changes")+
  facet_wrap(who~race_ethnic, nrow = 2)

```

### 1.2.3 By poverty level
```{r, echo=FALSE, message = FALSE, warning = FALSE}

vaccine_parent <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   mutate (a.very_likely = ifelse (HEALTH.022 == 1, 1, 0),
           b.somewhat_likely = ifelse (HEALTH.022 == 2, 1, 0),
           c.not_very_likely = ifelse (HEALTH.022 == 3, 1, 0),
           d.not_at_all_likely = ifelse (HEALTH.022 == 4, 1, 0), 
           e.already_vaccinated = ifelse (HEALTH.022 == 5, 1, 0))%>%
  filter (poverty_cat!= "NA")%>%
  group_by (Week, poverty_cat)%>%
   summarise (n = n(),
              a.very_likely = sum(a.very_likely, na.rm = T)/n,
              b.somewhat_likely = sum(b.somewhat_likely, na.rm = T)/n,
              c.not_very_likely = sum(c.not_very_likely, na.rm = T)/n, 
              d.not_at_all_likely = sum(d.not_at_all_likely, na.rm = T)/n, 
              e.already_vaccinated = sum(e.already_vaccinated, na.rm = T)/n,
              date = as.Date(min (StartDate)))%>%
   pivot_longer (cols = c("a.very_likely", "b.somewhat_likely", "c.not_very_likely", "d.not_at_all_likely", "e.already_vaccinated"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")
   
vaccine_child <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   mutate (a.very_likely = ifelse (HEALTH.023 == 1, 1, 0),
           b.somewhat_likely = ifelse (HEALTH.023 == 2, 1, 0),
           c.not_very_likely = ifelse (HEALTH.023 == 3, 1, 0),
           d.not_at_all_likely = ifelse (HEALTH.023 == 4, 1, 0), 
           e.already_vaccinated = ifelse (HEALTH.023 == 5, 1, 0))%>%
   filter (poverty_cat!= "NA")%>%
  group_by (Week, poverty_cat)%>%
   summarise (n = n(),
              a.very_likely = sum(a.very_likely, na.rm = T)/n,
              b.somewhat_likely = sum(b.somewhat_likely, na.rm = T)/n,
              c.not_very_likely = sum(c.not_very_likely, na.rm = T)/n, 
              d.not_at_all_likely = sum(d.not_at_all_likely, na.rm = T)/n, 
              e.already_vaccinated = sum(e.already_vaccinated, na.rm = T)/n,
              date = as.Date(min (StartDate)))%>%
   pivot_longer (cols = c("a.very_likely", "b.somewhat_likely", "c.not_very_likely", "d.not_at_all_likely", "e.already_vaccinated"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "child")
   
vaccine_smy <- rbind (vaccine_parent, vaccine_child)         
date <- vaccine %>%
  group_by (Week)%>%
  summarise (date = min (StartDate))%>%
  ungroup()


vaccine_smy %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = rsp)) +
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  labs (y = "Percentage")+
  ggtitle(label = "Trend of changes")+
  facet_wrap(who~poverty_cat, nrow = 2)

```
  

# 2. 2020-2021 Flu Vaccine
  * Survey question: Did you receive an influenza (Flu) vaccine for the 2019 flu season? - yes/no/unsure\
  * How likely are you to get a flu vaccination this season (2020-2021)—that is, this Fall or Winter? - Already received/Will definitely get one/Will probably get one/Will probably not get one/Will definitely not get one\
  * Did your child(ren) aged 0-5 receive an influenza (Flu) vaccine for the 2019 flu season?- yes/no/unsure\
  * How likely is/are your child(ren) aged 0-5 to get a flu vaccination this season (2020-2021)—that is, this Fall or Winter? -  Already received/Will definitely get one/Will probably get one/Will probably not get one/Will definitely not get one\

## 2.1 Most recent responses
### 2.1.1 Overall
```{r, echo=FALSE, message = FALSE, warning = FALSE}
vaccine_parent <- vaccine %>%
  filter (Week != 45)%>%
  group_by (CaregiverID)%>%
  filter (Week == max (Week))%>%
  ungroup ()%>%
  mutate (a.Already_got_vaccine = ifelse(HEALTH.016.a == 1 | HEALTH.016.b == 1, 1, 0), 
          b.Notyet_will_definitely_get = ifelse (HEALTH.016.b == 2, 1, 0), 
          c.Notyet_will_probably_get = ifelse (HEALTH.016.b == 3, 1, 0),
          d.Notyet_will_probably_not_get = ifelse (HEALTH.016.b == 4, 1, 0),
          e.Notyet_will_definitely_not_get = ifelse (HEALTH.016.b == 5, 1, 0))%>%
  summarise (n = n(),
             a.Already_got_vaccine = sum(a.Already_got_vaccine, na.rm = T)/n,
             b.Notyet_will_definitely_get = sum(b.Notyet_will_definitely_get, na.rm = T)/n,
             c.Notyet_will_probably_get = sum(c.Notyet_will_probably_get, na.rm = T)/n,
             d.Notyet_will_probably_not_get = sum(d.Notyet_will_probably_not_get, na.rm = T)/n,
             e.Notyet_will_definitely_not_get = sum(e.Notyet_will_definitely_not_get, na.rm = T)/n)%>%
   pivot_longer (cols = c("a.Already_got_vaccine", "b.Notyet_will_definitely_get", "c.Notyet_will_probably_get", "d.Notyet_will_probably_not_get", "e.Notyet_will_definitely_not_get"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")

vaccine_child <- vaccine %>%
  filter (Week != 45)%>%
  group_by (CaregiverID)%>%
  filter (Week == max (Week))%>%
  ungroup ()%>%
  mutate (a.Already_got_vaccine = ifelse(HEALTH.017.a == 1 | HEALTH.017.b == 1, 1, 0), 
          b.Notyet_will_definitely_get = ifelse (HEALTH.017.b == 2, 1, 0), 
          c.Notyet_will_probably_get = ifelse (HEALTH.017.b == 3, 1, 0),
          d.Notyet_will_probably_not_get = ifelse (HEALTH.017.b == 4, 1, 0),
          e.Notyet_will_definitely_not_get = ifelse (HEALTH.017.b == 5, 1, 0))%>%
  summarise (n = n(),
             a.Already_got_vaccine = sum(a.Already_got_vaccine, na.rm = T)/n,
             b.Notyet_will_definitely_get = sum(b.Notyet_will_definitely_get, na.rm = T)/n,
             c.Notyet_will_probably_get = sum(c.Notyet_will_probably_get, na.rm = T)/n,
             d.Notyet_will_probably_not_get = sum(d.Notyet_will_probably_not_get, na.rm = T)/n,
             e.Notyet_will_definitely_not_get = sum(e.Notyet_will_definitely_not_get, na.rm = T)/n)%>%
   pivot_longer (cols = c("a.Already_got_vaccine", "b.Notyet_will_definitely_get", "c.Notyet_will_probably_get", "d.Notyet_will_probably_not_get", "e.Notyet_will_definitely_not_get"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "child")
  
vaccine_smy <- rbind (vaccine_parent, vaccine_child)         

vaccine_smy %>%
  ggplot(mapping = aes (x =  rsp, y = prop*100, fill = rsp)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = ci_low*100, 
                    ymax = ci_high*100),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -1,hjust = 0.5, size = 2.5, color = "black",  position = position_dodge(1))+
  facet_wrap(~who, ncol = 2)+
  theme(axis.text.x = element_blank())
  

```

### 2.1.2 By race/ethnicity
```{r, echo=FALSE, message = FALSE, warning = FALSE}
vaccine_parent <- vaccine %>%
  filter (Week != 45)%>%
  group_by (CaregiverID)%>%
  filter (Week == max (Week))%>%
  ungroup ()%>%
  filter (race_ethnic!= "NA")%>%
  group_by (race_ethnic)%>%
  mutate (a.Already_got_vaccine = ifelse(HEALTH.016.a == 1 | HEALTH.016.b == 1, 1, 0), 
          b.Notyet_will_definitely_get = ifelse (HEALTH.016.b == 2, 1, 0), 
          c.Notyet_will_probably_get = ifelse (HEALTH.016.b == 3, 1, 0),
          d.Notyet_will_probably_not_get = ifelse (HEALTH.016.b == 4, 1, 0),
          e.Notyet_will_definitely_not_get = ifelse (HEALTH.016.b == 5, 1, 0))%>%
  summarise (n = n(),
             a.Already_got_vaccine = sum(a.Already_got_vaccine, na.rm = T)/n,
             b.Notyet_will_definitely_get = sum(b.Notyet_will_definitely_get, na.rm = T)/n,
             c.Notyet_will_probably_get = sum(c.Notyet_will_probably_get, na.rm = T)/n,
             d.Notyet_will_probably_not_get = sum(d.Notyet_will_probably_not_get, na.rm = T)/n,
             e.Notyet_will_definitely_not_get = sum(e.Notyet_will_definitely_not_get, na.rm = T)/n)%>%
   pivot_longer (cols = c("a.Already_got_vaccine", "b.Notyet_will_definitely_get", "c.Notyet_will_probably_get", "d.Notyet_will_probably_not_get", "e.Notyet_will_definitely_not_get"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")

vaccine_child <- vaccine %>%
  filter (Week != 45)%>%
  group_by (CaregiverID)%>%
  filter (Week == max (Week))%>%
  ungroup ()%>%
  filter (race_ethnic!= "NA")%>%
  group_by (race_ethnic)%>%
  mutate (a.Already_got_vaccine = ifelse(HEALTH.017.a == 1 | HEALTH.017.b == 1, 1, 0), 
          b.Notyet_will_definitely_get = ifelse (HEALTH.017.b == 2, 1, 0), 
          c.Notyet_will_probably_get = ifelse (HEALTH.017.b == 3, 1, 0),
          d.Notyet_will_probably_not_get = ifelse (HEALTH.017.b == 4, 1, 0),
          e.Notyet_will_definitely_not_get = ifelse (HEALTH.017.b == 5, 1, 0))%>%
  summarise (n = n(),
             a.Already_got_vaccine = sum(a.Already_got_vaccine, na.rm = T)/n,
             b.Notyet_will_definitely_get = sum(b.Notyet_will_definitely_get, na.rm = T)/n,
             c.Notyet_will_probably_get = sum(c.Notyet_will_probably_get, na.rm = T)/n,
             d.Notyet_will_probably_not_get = sum(d.Notyet_will_probably_not_get, na.rm = T)/n,
             e.Notyet_will_definitely_not_get = sum(e.Notyet_will_definitely_not_get, na.rm = T)/n)%>%
   pivot_longer (cols = c("a.Already_got_vaccine", "b.Notyet_will_definitely_get", "c.Notyet_will_probably_get", "d.Notyet_will_probably_not_get", "e.Notyet_will_definitely_not_get"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "child")
  
vaccine_smy <- rbind (vaccine_parent, vaccine_child)         

vaccine_smy %>%
  ggplot(mapping = aes (x =  rsp, y = prop*100, fill = rsp)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = ci_low*100, 
                    ymax = ci_high*100),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -1,hjust = 0.5, size = 2.5, color = "black",  position = position_dodge(1))+
  facet_wrap(who~race_ethnic, ncol = 3)+
  theme(axis.text.x = element_blank())

```

### 2.1.3 By poverty level
```{r, echo=FALSE, message = FALSE, warning = FALSE}
vaccine_parent <- vaccine %>%
  filter (Week != 45)%>%
  group_by (CaregiverID)%>%
  filter (Week == max (Week))%>%
  ungroup ()%>%
  filter (poverty_cat!= "NA")%>%
  group_by (poverty_cat)%>%
  mutate (a.Already_got_vaccine = ifelse(HEALTH.016.a == 1 | HEALTH.016.b == 1, 1, 0), 
          b.Notyet_will_definitely_get = ifelse (HEALTH.016.b == 2, 1, 0), 
          c.Notyet_will_probably_get = ifelse (HEALTH.016.b == 3, 1, 0),
          d.Notyet_will_probably_not_get = ifelse (HEALTH.016.b == 4, 1, 0),
          e.Notyet_will_definitely_not_get = ifelse (HEALTH.016.b == 5, 1, 0))%>%
  summarise (n = n(),
             a.Already_got_vaccine = sum(a.Already_got_vaccine, na.rm = T)/n,
             b.Notyet_will_definitely_get = sum(b.Notyet_will_definitely_get, na.rm = T)/n,
             c.Notyet_will_probably_get = sum(c.Notyet_will_probably_get, na.rm = T)/n,
             d.Notyet_will_probably_not_get = sum(d.Notyet_will_probably_not_get, na.rm = T)/n,
             e.Notyet_will_definitely_not_get = sum(e.Notyet_will_definitely_not_get, na.rm = T)/n)%>%
   pivot_longer (cols = c("a.Already_got_vaccine", "b.Notyet_will_definitely_get", "c.Notyet_will_probably_get", "d.Notyet_will_probably_not_get", "e.Notyet_will_definitely_not_get"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")

vaccine_child <- vaccine %>%
  filter (Week != 45)%>%
  group_by (CaregiverID)%>%
  filter (Week == max (Week))%>%
  ungroup ()%>%
  filter (poverty_cat!= "NA")%>%
  group_by (poverty_cat)%>%
  mutate (a.Already_got_vaccine = ifelse(HEALTH.017.a == 1 | HEALTH.017.b == 1, 1, 0), 
          b.Notyet_will_definitely_get = ifelse (HEALTH.017.b == 2, 1, 0), 
          c.Notyet_will_probably_get = ifelse (HEALTH.017.b == 3, 1, 0),
          d.Notyet_will_probably_not_get = ifelse (HEALTH.017.b == 4, 1, 0),
          e.Notyet_will_definitely_not_get = ifelse (HEALTH.017.b == 5, 1, 0))%>%
  summarise (n = n(),
             a.Already_got_vaccine = sum(a.Already_got_vaccine, na.rm = T)/n,
             b.Notyet_will_definitely_get = sum(b.Notyet_will_definitely_get, na.rm = T)/n,
             c.Notyet_will_probably_get = sum(c.Notyet_will_probably_get, na.rm = T)/n,
             d.Notyet_will_probably_not_get = sum(d.Notyet_will_probably_not_get, na.rm = T)/n,
             e.Notyet_will_definitely_not_get = sum(e.Notyet_will_definitely_not_get, na.rm = T)/n)%>%
   pivot_longer (cols = c("a.Already_got_vaccine", "b.Notyet_will_definitely_get", "c.Notyet_will_probably_get", "d.Notyet_will_probably_not_get", "e.Notyet_will_definitely_not_get"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "child")
  
vaccine_smy <- rbind (vaccine_parent, vaccine_child)         

vaccine_smy %>%
  ggplot(mapping = aes (x =  rsp, y = prop*100, fill = poverty_cat)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = ci_low*100, 
                    ymax = ci_high*100),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -1,hjust = 0.5, size = 2.5, color = "black",  position = position_dodge(1))+
  facet_wrap(~who, ncol = 2)+
  theme(axis.text.x = element_text(angle = 90))

```

### 2.1.4 By poverty level & race/ethnicity
```{r, echo=FALSE, message = FALSE, warning = FALSE}
vaccine_parent <- vaccine %>%
  filter (Week != 45)%>%
  group_by (CaregiverID)%>%
  filter (Week == max (Week))%>%
  ungroup ()%>%
  filter (poverty_cat!= "NA" & race_ethnic!= "NA")%>%
  group_by (poverty_cat, race_ethnic)%>%
  mutate (a.Already_got_vaccine = ifelse(HEALTH.016.a == 1 | HEALTH.016.b == 1, 1, 0), 
          b.Notyet_will_definitely_get = ifelse (HEALTH.016.b == 2, 1, 0), 
          c.Notyet_will_probably_get = ifelse (HEALTH.016.b == 3, 1, 0),
          d.Notyet_will_probably_not_get = ifelse (HEALTH.016.b == 4, 1, 0),
          e.Notyet_will_definitely_not_get = ifelse (HEALTH.016.b == 5, 1, 0))%>%
  summarise (n = n(),
             a.Already_got_vaccine = sum(a.Already_got_vaccine, na.rm = T)/n,
             b.Notyet_will_definitely_get = sum(b.Notyet_will_definitely_get, na.rm = T)/n,
             c.Notyet_will_probably_get = sum(c.Notyet_will_probably_get, na.rm = T)/n,
             d.Notyet_will_probably_not_get = sum(d.Notyet_will_probably_not_get, na.rm = T)/n,
             e.Notyet_will_definitely_not_get = sum(e.Notyet_will_definitely_not_get, na.rm = T)/n)%>%
   pivot_longer (cols = c("a.Already_got_vaccine", "b.Notyet_will_definitely_get", "c.Notyet_will_probably_get", "d.Notyet_will_probably_not_get", "e.Notyet_will_definitely_not_get"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")

vaccine_child <- vaccine %>%
  filter (Week != 45)%>%
  group_by (CaregiverID)%>%
  filter (Week == max (Week))%>%
  ungroup ()%>%
  filter (poverty_cat!= "NA" & race_ethnic!= "NA")%>%
  group_by (poverty_cat, race_ethnic)%>%
  mutate (a.Already_got_vaccine = ifelse(HEALTH.017.a == 1 | HEALTH.017.b == 1, 1, 0), 
          b.Notyet_will_definitely_get = ifelse (HEALTH.017.b == 2, 1, 0), 
          c.Notyet_will_probably_get = ifelse (HEALTH.017.b == 3, 1, 0),
          d.Notyet_will_probably_not_get = ifelse (HEALTH.017.b == 4, 1, 0),
          e.Notyet_will_definitely_not_get = ifelse (HEALTH.017.b == 5, 1, 0))%>%
  summarise (n = n(),
             a.Already_got_vaccine = sum(a.Already_got_vaccine, na.rm = T)/n,
             b.Notyet_will_definitely_get = sum(b.Notyet_will_definitely_get, na.rm = T)/n,
             c.Notyet_will_probably_get = sum(c.Notyet_will_probably_get, na.rm = T)/n,
             d.Notyet_will_probably_not_get = sum(d.Notyet_will_probably_not_get, na.rm = T)/n,
             e.Notyet_will_definitely_not_get = sum(e.Notyet_will_definitely_not_get, na.rm = T)/n)%>%
   pivot_longer (cols = c("a.Already_got_vaccine", "b.Notyet_will_definitely_get", "c.Notyet_will_probably_get", "d.Notyet_will_probably_not_get", "e.Notyet_will_definitely_not_get"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "child")
  
vaccine_smy <- rbind (vaccine_parent, vaccine_child)         

vaccine_smy %>%
  ggplot(mapping = aes (x =  rsp, y = prop*100, fill = poverty_cat)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = ci_low*100, 
                    ymax = ci_high*100),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,0)),vjust = -1,hjust = 0.5, size = 2, color = "black",  position = position_dodge(1))+
  facet_wrap(who~race_ethnic, ncol = 3)+
  theme(axis.text.x = element_text(angle = 90))


```

## 2.2 Trend
### 2.2.1 Overall
```{r, echo=FALSE, message = FALSE, warning = FALSE}
vaccine_parent <- vaccine %>%
  filter (Week != 45)%>%
  mutate (a.Already_got_vaccine = ifelse(HEALTH.016.a == 1 | HEALTH.016.b == 1, 1, 0), 
          b.Notyet_will_definitely_get = ifelse (HEALTH.016.b == 2, 1, 0), 
          c.Notyet_will_probably_get = ifelse (HEALTH.016.b == 3, 1, 0),
          d.Notyet_will_probably_not_get = ifelse (HEALTH.016.b == 4, 1, 0),
          e.Notyet_will_definitely_not_get = ifelse (HEALTH.016.b == 5, 1, 0))%>%
  group_by (Week)%>%
  summarise (n = n(),
             a.Already_got_vaccine = sum(a.Already_got_vaccine, na.rm = T)/n,
             b.Notyet_will_definitely_get = sum(b.Notyet_will_definitely_get, na.rm = T)/n,
             c.Notyet_will_probably_get = sum(c.Notyet_will_probably_get, na.rm = T)/n,
             d.Notyet_will_probably_not_get = sum(d.Notyet_will_probably_not_get, na.rm = T)/n,
             e.Notyet_will_definitely_not_get = sum(e.Notyet_will_definitely_not_get, na.rm = T)/n, 
             date = as.Date(min (StartDate)))%>%
   pivot_longer (cols = c("a.Already_got_vaccine", "b.Notyet_will_definitely_get", "c.Notyet_will_probably_get", "d.Notyet_will_probably_not_get", "e.Notyet_will_definitely_not_get"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")

vaccine_child <- vaccine %>%
  filter (Week != 45)%>%
  mutate (a.Already_got_vaccine = ifelse(HEALTH.017.a == 1 | HEALTH.017.b == 1, 1, 0), 
          b.Notyet_will_definitely_get = ifelse (HEALTH.017.b == 2, 1, 0), 
          c.Notyet_will_probably_get = ifelse (HEALTH.017.b == 3, 1, 0),
          d.Notyet_will_probably_not_get = ifelse (HEALTH.017.b == 4, 1, 0),
          e.Notyet_will_definitely_not_get = ifelse (HEALTH.017.b == 5, 1, 0))%>%
  group_by (Week)%>%
  summarise (n = n(),
             a.Already_got_vaccine = sum(a.Already_got_vaccine, na.rm = T)/n,
             b.Notyet_will_definitely_get = sum(b.Notyet_will_definitely_get, na.rm = T)/n,
             c.Notyet_will_probably_get = sum(c.Notyet_will_probably_get, na.rm = T)/n,
             d.Notyet_will_probably_not_get = sum(d.Notyet_will_probably_not_get, na.rm = T)/n,
             e.Notyet_will_definitely_not_get = sum(e.Notyet_will_definitely_not_get, na.rm = T)/n, 
             date = as.Date(min (StartDate)))%>%
   pivot_longer (cols = c("a.Already_got_vaccine", "b.Notyet_will_definitely_get", "c.Notyet_will_probably_get", "d.Notyet_will_probably_not_get", "e.Notyet_will_definitely_not_get"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "child")
  
vaccine_smy <- rbind (vaccine_parent, vaccine_child)

date <- vaccine %>%
  group_by (Week)%>%
  summarise (date = min (StartDate))%>%
  ungroup()

vaccine_smy %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = rsp)) +
  geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  labs (y = "Percentage")+
  ggtitle(label = "Trend of changes")+
  facet_wrap(~who, nrow = 2)

```

### 2.2.2 By race/ethnicity
  * Categories "Not yet get and will probably get" & "Not yet get and will probably not get" are stable over time for all groups. Removed from grouping analyses so that figures are clearer.\
  
```{r, echo=FALSE, message = FALSE, warning = FALSE}
vaccine_parent <- vaccine %>%
  filter (Week != 45)%>%
  mutate (a.Already_got_vaccine = ifelse(HEALTH.016.a == 1 | HEALTH.016.b == 1, 1, 0), 
          b.Notyet_will_definitely_get = ifelse (HEALTH.016.b == 2, 1, 0), 
          #c.Notyet_will_probably_get = ifelse (HEALTH.016.b == 3, 1, 0),
          #d.Notyet_will_probably_not_get = ifelse (HEALTH.016.b == 4, 1, 0),
          e.Notyet_will_definitely_not_get = ifelse (HEALTH.016.b == 5, 1, 0))%>%
  filter (race_ethnic!= "NA")%>%
  group_by (Week, race_ethnic)%>%
  summarise (n = n(),
             a.Already_got_vaccine = sum(a.Already_got_vaccine, na.rm = T)/n,
             b.Notyet_will_definitely_get = sum(b.Notyet_will_definitely_get, na.rm = T)/n,
             #c.Notyet_will_probably_get = sum(c.Notyet_will_probably_get, na.rm = T)/n,
             #d.Notyet_will_probably_not_get = sum(d.Notyet_will_probably_not_get, na.rm = T)/n,
             e.Notyet_will_definitely_not_get = sum(e.Notyet_will_definitely_not_get, na.rm = T)/n, 
             date = as.Date(min (StartDate)))%>%
   pivot_longer (cols = c("a.Already_got_vaccine", "b.Notyet_will_definitely_get",  "e.Notyet_will_definitely_not_get"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")

vaccine_child <- vaccine %>%
  filter (Week != 45)%>%
  mutate (a.Already_got_vaccine = ifelse(HEALTH.017.a == 1 | HEALTH.017.b == 1, 1, 0), 
          b.Notyet_will_definitely_get = ifelse (HEALTH.017.b == 2, 1, 0), 
          #c.Notyet_will_probably_get = ifelse (HEALTH.017.b == 3, 1, 0),
          #d.Notyet_will_probably_not_get = ifelse (HEALTH.017.b == 4, 1, 0),
          e.Notyet_will_definitely_not_get = ifelse (HEALTH.017.b == 5, 1, 0))%>%
  filter (race_ethnic!= "NA")%>%
  group_by (Week, race_ethnic)%>%
  summarise (n = n(),
             a.Already_got_vaccine = sum(a.Already_got_vaccine, na.rm = T)/n,
             b.Notyet_will_definitely_get = sum(b.Notyet_will_definitely_get, na.rm = T)/n,
             #c.Notyet_will_probably_get = sum(c.Notyet_will_probably_get, na.rm = T)/n,
             #d.Notyet_will_probably_not_get = sum(d.Notyet_will_probably_not_get, na.rm = T)/n,
             e.Notyet_will_definitely_not_get = sum(e.Notyet_will_definitely_not_get, na.rm = T)/n, 
             date = as.Date(min (StartDate)))%>%
   pivot_longer (cols = c("a.Already_got_vaccine", "b.Notyet_will_definitely_get",  "e.Notyet_will_definitely_not_get"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "child")
  
vaccine_smy <- rbind (vaccine_parent, vaccine_child)

date <- vaccine %>%
  group_by (Week)%>%
  summarise (date = min (StartDate))%>%
  ungroup()

vaccine_smy %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = rsp)) +
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  labs (y = "Percentage")+
  ggtitle(label = "Trend of changes")+
  facet_wrap(who~race_ethnic, nrow = 2)

```

### 2.2.3 By poverty level
```{r, echo=FALSE, message = FALSE, warning = FALSE}
vaccine_parent <- vaccine %>%
  filter (Week != 45)%>%
  mutate (a.Already_got_vaccine = ifelse(HEALTH.016.a == 1 | HEALTH.016.b == 1, 1, 0), 
          b.Notyet_will_definitely_get = ifelse (HEALTH.016.b == 2, 1, 0), 
          #c.Notyet_will_probably_get = ifelse (HEALTH.016.b == 3, 1, 0),
          #d.Notyet_will_probably_not_get = ifelse (HEALTH.016.b == 4, 1, 0),
          e.Notyet_will_definitely_not_get = ifelse (HEALTH.016.b == 5, 1, 0))%>%
  filter (poverty_cat!= "NA")%>%
  group_by (Week, poverty_cat)%>%
  summarise (n = n(),
             a.Already_got_vaccine = sum(a.Already_got_vaccine, na.rm = T)/n,
             b.Notyet_will_definitely_get = sum(b.Notyet_will_definitely_get, na.rm = T)/n,
             #c.Notyet_will_probably_get = sum(c.Notyet_will_probably_get, na.rm = T)/n,
             #d.Notyet_will_probably_not_get = sum(d.Notyet_will_probably_not_get, na.rm = T)/n,
             e.Notyet_will_definitely_not_get = sum(e.Notyet_will_definitely_not_get, na.rm = T)/n, 
             date = as.Date(min (StartDate)))%>%
   pivot_longer (cols = c("a.Already_got_vaccine", "b.Notyet_will_definitely_get",  "e.Notyet_will_definitely_not_get"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "caregiver")

vaccine_child <- vaccine %>%
  filter (Week != 45)%>%
  mutate (a.Already_got_vaccine = ifelse(HEALTH.017.a == 1 | HEALTH.017.b == 1, 1, 0), 
          b.Notyet_will_definitely_get = ifelse (HEALTH.017.b == 2, 1, 0), 
          #c.Notyet_will_probably_get = ifelse (HEALTH.017.b == 3, 1, 0),
          #d.Notyet_will_probably_not_get = ifelse (HEALTH.017.b == 4, 1, 0),
          e.Notyet_will_definitely_not_get = ifelse (HEALTH.017.b == 5, 1, 0))%>%
  filter (poverty_cat!= "NA")%>%
  group_by (Week, poverty_cat)%>%
  summarise (n = n(),
             a.Already_got_vaccine = sum(a.Already_got_vaccine, na.rm = T)/n,
             b.Notyet_will_definitely_get = sum(b.Notyet_will_definitely_get, na.rm = T)/n,
             #c.Notyet_will_probably_get = sum(c.Notyet_will_probably_get, na.rm = T)/n,
             #d.Notyet_will_probably_not_get = sum(d.Notyet_will_probably_not_get, na.rm = T)/n,
             e.Notyet_will_definitely_not_get = sum(e.Notyet_will_definitely_not_get, na.rm = T)/n, 
             date = as.Date(min (StartDate)))%>%
   pivot_longer (cols = c("a.Already_got_vaccine", "b.Notyet_will_definitely_get",  "e.Notyet_will_definitely_not_get"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          who = "child")
  
vaccine_smy <- rbind (vaccine_parent, vaccine_child)

date <- vaccine %>%
  group_by (Week)%>%
  summarise (date = min (StartDate))%>%
  ungroup()

vaccine_smy %>%
  ggplot(mapping = aes (x = date, y = prop*100, fill = rsp)) +
  #geom_point(stat = 'summary') +
  geom_ribbon(aes(ymin = ci_low*100, ymax = ci_high*100), alpha = .3) +
  geom_line() +
  labs (y = "Percentage")+
  ggtitle(label = "Trend of changes")+
  facet_wrap(who~poverty_cat, nrow = 2)

```


 
# 3. Delayed/Not getting Vaccine
  * Survey question: Have you ever delayed having your child get a shot for reasons other than illness or allergy? Select all that apply\
    + Yes, prior to the COVID-19 pandemic\
    + Yes, since the COVID-19 pandemic\
    + No\
    + I don't know\
  * Have you ever decided not to have your child get a shot for reasons other than illness or allergy? Select all that apply.\
    + Yes, prior to the COVID-19 pandemic\
    + Yes, since the COVID-19 pandemic\
    + No\
    + I don't know\

## 3.1 Overall
```{r, echo=FALSE, message = FALSE, warning = FALSE}
vaccine$HEALTH.020_4[is.na(vaccine$HEALTH.020_4)] <- 0
vaccine$HEALTH.021_4[is.na(vaccine$HEALTH.021_4)] <- 0

 vaccine_delay <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   group_by (CaregiverID)%>%
   filter (Week == max (Week))%>%
   ungroup ()%>%
   filter (HEALTH.020_4 == 0)%>%
   summarise (n = n(),
              Yes_before_COVID = sum(HEALTH.020_1, na.rm = T)/n,
              Yes_since_COVID = sum(HEALTH.020_2, na.rm = T)/n,
              Never = sum(HEALTH.020_3, na.rm = T)/n)%>%
   pivot_longer (cols = c("Yes_before_COVID", "Yes_since_COVID", "Never"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          action = "Delay Vaccine")
 
 vaccine_not <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   group_by (CaregiverID)%>%
   filter (Week == max (Week))%>%
   ungroup ()%>%
   filter (HEALTH.021_4 == 0)%>%
   summarise (n = n(),
              Yes_before_COVID = sum(HEALTH.021_1, na.rm = T)/n,
              Yes_since_COVID = sum(HEALTH.021_2, na.rm = T)/n,
              Never = sum(HEALTH.021_3, na.rm = T)/n)%>%
   pivot_longer (cols = c("Yes_before_COVID", "Yes_since_COVID", "Never"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          action = "Not Get Vaccine")
  
 vaccine_smy <- rbind (vaccine_delay, vaccine_not)         

vaccine_smy %>%
  ggplot(mapping = aes (x =  rsp, y = prop*100, fill = rsp)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = ci_low*100, 
                    ymax = ci_high*100),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -1,hjust = 0.5, size = 3, color = "black",  position = position_dodge(1))+
  facet_wrap(~action, ncol = 2)+
  theme(axis.text.x = element_text(angle = 30))
```

## 3.2 By race/ethnicity
```{r, echo=FALSE, message = FALSE, warning = FALSE}
 vaccine_delay <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   group_by (CaregiverID)%>%
   filter (Week == max (Week))%>%
   ungroup ()%>%
   filter (HEALTH.020_4 == 0 & race_ethnic != "NA")%>%
   group_by (race_ethnic)%>%
   summarise (n = n(),
              Yes_before_COVID = sum(HEALTH.020_1, na.rm = T)/n,
              Yes_since_COVID = sum(HEALTH.020_2, na.rm = T)/n,
              Never = sum(HEALTH.020_3, na.rm = T)/n)%>%
   pivot_longer (cols = c("Yes_before_COVID", "Yes_since_COVID", "Never"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          action = "Delay Vaccine")
 
 vaccine_not <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   group_by (CaregiverID)%>%
   filter (Week == max (Week))%>%
   ungroup ()%>%
   filter (HEALTH.021_4 == 0 & race_ethnic != "NA")%>%
   group_by (race_ethnic)%>%
   summarise (n = n(),
              Yes_before_COVID = sum(HEALTH.021_1, na.rm = T)/n,
              Yes_since_COVID = sum(HEALTH.021_2, na.rm = T)/n,
              Never = sum(HEALTH.021_3, na.rm = T)/n)%>%
   pivot_longer (cols = c("Yes_before_COVID", "Yes_since_COVID", "Never"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          action = "Not Get Vaccine")
  
 vaccine_smy <- rbind (vaccine_delay, vaccine_not)         

vaccine_smy %>%
  ggplot(mapping = aes (x =  rsp, y = prop*100, fill = race_ethnic)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = ci_low*100, 
                    ymax = ci_high*100),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -1,hjust = 0.5, size = 2.5, color = "black",  position = position_dodge(1))+
  facet_wrap(~action, ncol = 2)+
  theme(axis.text.x = element_text(angle = 30))
```
    
## 3.3 By poverty level
```{r, echo=FALSE, message = FALSE, warning = FALSE}
vaccine_delay <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   group_by (CaregiverID)%>%
   filter (Week == max (Week))%>%
   ungroup ()%>%
   filter (HEALTH.020_4 == 0 & poverty_cat != "NA")%>%
   group_by (poverty_cat)%>%
   summarise (n = n(),
              Yes_before_COVID = sum(HEALTH.020_1, na.rm = T)/n,
              Yes_since_COVID = sum(HEALTH.020_2, na.rm = T)/n,
              Never = sum(HEALTH.020_3, na.rm = T)/n)%>%
   pivot_longer (cols = c("Yes_before_COVID", "Yes_since_COVID", "Never"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          action = "Delay Vaccine")
 
 vaccine_not <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   group_by (CaregiverID)%>%
   filter (Week == max (Week))%>%
   ungroup ()%>%
   filter (HEALTH.021_4 == 0 & poverty_cat != "NA")%>%
   group_by (poverty_cat)%>%
   summarise (n = n(),
              Yes_before_COVID = sum(HEALTH.021_1, na.rm = T)/n,
              Yes_since_COVID = sum(HEALTH.021_2, na.rm = T)/n,
              Never = sum(HEALTH.021_3, na.rm = T)/n)%>%
   pivot_longer (cols = c("Yes_before_COVID", "Yes_since_COVID", "Never"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          action = "Not Get Vaccine")
  
 vaccine_smy <- rbind (vaccine_delay, vaccine_not)         

vaccine_smy %>%
  ggplot(mapping = aes (x =  rsp, y = prop*100, fill = poverty_cat)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = ci_low*100, 
                    ymax = ci_high*100),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -1,hjust = 0.5, size = 2.5, color = "black",  position = position_dodge(1))+
  facet_wrap(~action, ncol = 2)+
  theme(axis.text.x = element_text(angle = 30))
```
  
## 3.4 By poverty level & race/ethnicity
```{r, echo=FALSE, message = FALSE, warning = FALSE}
vaccine_delay <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   group_by (CaregiverID)%>%
   filter (Week == max (Week))%>%
   ungroup ()%>%
   filter (HEALTH.020_4 == 0 & poverty_cat != "NA" & race_ethnic != "NA")%>%
   group_by (poverty_cat, race_ethnic)%>%
   summarise (n = n(),
              Yes_before_COVID = sum(HEALTH.020_1, na.rm = T)/n,
              Yes_since_COVID = sum(HEALTH.020_2, na.rm = T)/n,
              Never = sum(HEALTH.020_3, na.rm = T)/n)%>%
   pivot_longer (cols = c("Yes_before_COVID", "Yes_since_COVID", "Never"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          action = "Delay Vaccine")
 
 vaccine_not <- vaccine %>%
   filter (Week != 25 & Week != 27)%>%
   group_by (CaregiverID)%>%
   filter (Week == max (Week))%>%
   ungroup ()%>%
   filter (HEALTH.021_4 == 0 & poverty_cat != "NA" & race_ethnic != "NA")%>%
   group_by (poverty_cat, race_ethnic)%>%
   summarise (n = n(),
              Yes_before_COVID = sum(HEALTH.021_1, na.rm = T)/n,
              Yes_since_COVID = sum(HEALTH.021_2, na.rm = T)/n,
              Never = sum(HEALTH.021_3, na.rm = T)/n)%>%
   pivot_longer (cols = c("Yes_before_COVID", "Yes_since_COVID", "Never"), names_to = "rsp", values_to = "prop")%>%
   mutate (count = prop * n, 
          moe = map2_dbl(prop, n, moe.p), 
          ci_low = prop-moe,
          ci_high = prop+moe, 
          action = "Not Get Vaccine")
  
 vaccine_smy <- rbind (vaccine_delay, vaccine_not)         

vaccine_smy %>%
  ggplot(mapping = aes (x =  rsp, y = prop*100, fill = poverty_cat)) +
  geom_bar (stat = "identity", position = position_dodge(1))+
  geom_errorbar(aes(ymin = ci_low*100, 
                    ymax = ci_high*100),
                    width = .3,
                    position = position_dodge(1)) +
  geom_text(aes(label = round(prop*100,2)),vjust = -1,hjust = 0.5, size = 2.5, color = "black",  position = position_dodge(1))+
  facet_wrap(action~race_ethnic, ncol = 3)+
  theme(axis.text.x = element_text(angle = 30))
```
