---
title: "Social Support II"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r wellbeing-states-1, echo = F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.kable.NA = '')
```

```{r wellbeing-states-2 }
library(conflicted)
library(here)
library(ggpubr)
conflict_prefer("group_rows", "kableExtra")
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")
conflict_prefer("map", "purrr")
library(plotly)
```

```{r wellbeing-states-3 }
source(here("Scripts/score data.R")) 
```

```{r wellbeing-states-4 }
source(here("Functions/pomp.R"))
```

<!-- Prep data -->

```{r social-support2-1}
dates = scored %>%
  group_by(Week) %>%
  summarize(start = min(Date),
            end = max(Date)) 
```


```{r social-support2-2}
scored = scored %>%
  filter(Week < 20) %>%
  group_by(Week) %>%
  mutate(Week = min(Date, na.rm=T)) %>%
  ungroup() %>%
  select(CaregiverID, Week, Date, single, income,
         contains("poverty"), work_status, black,
         white, latinx, disability,
         contains("diff_pay"), 
         starts_with("mh"), contains("SOCIALSUPP"),
         contains("food"), state)

scored = scored %>%
  mutate(current.support = rowMeans(select(., contains("SOCIALSUPP.001")), na.rm=T),
         prior.support = rowMeans(select(., contains("SOCIALSUPP.002")), na.rm=T)) %>%
  gather("key", "value", contains("SOCIALSUPP.003")) %>%
  mutate(key = gsub("SOCIALSUPP\\.003\\.", "", key)) %>%
  separate(key, into = c("source", "time")) %>% 
  spread(source, value) %>%
  mutate(answered = ceiling(rowMeans(select(., matches("^.{1}$")), na.rm=T))) %>%
  mutate_at(vars(matches("^.{1}$")), .funs = function(x) ifelse(is.na(x), 0, 1)) %>%
  gather("source", "support", matches("^.{1}$")) %>%
  mutate(source = case_when(
    source == "a" ~ "Partner/Spouse",
    source == "b" ~ "Child(ren)",
    source == "c" ~ "Parent(s)",
    source == "d" ~ "Other relative(s)",
    source == "e" ~ "Friend(s)",
    source == "f" ~ "Neighbor(s)",
    source == "g" ~ "Co-worker(s)",
    source == "h" ~ "Religious group",
    source == "i" ~ "Spiritual figure",
    source == "j" ~ "Parent group",
    source == "k" ~ "Health professional",
    source == "l" ~ "Childcare provider",
    source == "m" ~ "Babysitter"
  )) %>%
  mutate(support = case_when(
    single == 1 & source == "Partner/Spouse" ~ NA_real_,
    TRUE ~ support
  )) %>%
  rowwise() %>%
  mutate(material_hardship = sum(c_across(starts_with("diff_pay_")), na.rm=T)) %>%
  ungroup()
```

# Representativeness disclaimer

```{r spline-final-10 }
n_care = length(unique(scored$CaregiverID))
date.min = format(min(as.Date(scored$Date), na.rm = T), format = "%B %d, %Y")
date.max = format(max(as.Date(scored$Date), na.rm = T), format = "%B %d, %Y")
perc = scored %>%
  group_by(CaregiverID) %>%
  filter(Week == max(Week)) %>%
  filter(row_number() == 1)
perc.black = 100*sum(perc$black, na.rm=T)/nrow(perc)
perc.latinx = 100*sum(perc$latinx, na.rm=T)/nrow(perc)
perc.fpl = 100*sum(perc$poverty150, na.rm=T)/nrow(perc)
```

These analyses are based on responses collected from `r papaja::printnum(n_care, format = "d")` caregivers between the dates of `r date.min` and `r date.max`. These caregivers represent a range of voices: `r papaja::printnum(perc.black)`\% are Black/African American, `r papaja::printnum(perc.latinx)`\% are LatinX, and `r papaja::printnum(perc.fpl)`\% live at or below 1.5 times the federal poverty line. Proportions/percentages are calculated based on the item-level response rates, not out of the total sample size. The data for these analyses are *not* weighted.


# Material hardship

## Old questions{.tabset}

### Number (overall)

```{r social-support2-3}
scored %>%
  group_by(CaregiverID, Week) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  filter(Week > 0) %>%
  filter(!is.na(material_hardship)) %>%
  group_by(Week) %>%
  summarize(count = n(),
            hardship = mean(material_hardship)) %>%
  ggplot(aes(x = Week, y = hardship)) +
  geom_point() + 
  geom_line() +
  geom_vline(aes(xintercept = as.Date("2020-07-31")), color = "red")
```

### Number (Black/African American)

```{r social-support2-4}
plot = scored %>%
  group_by(CaregiverID, Week) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  filter(Week > 0) %>%
  filter(!is.na(material_hardship)) %>%
  group_by(Week, black) %>%
  summarize(count = n(),
            hardship = mean(material_hardship)) %>%
  mutate(black = factor(black, levels = c(0,1), labels = c("Not Black", "Black"))) %>%
  ggplot(aes(x = Week, 
             y = hardship, 
             color = black,
             group = 1,
             text = paste0(
               "Group:", black,
               "\n Week:", Week,
               "\n Count:", count,
               "\n Hardship:", round(hardship,2)
             ))) +
  geom_point() + 
  geom_line() +
  geom_vline(aes(xintercept = as.Date("2020-07-31")), color = "red") +
  theme_pubr()
ggplotly(plot, tooltip = "text")
```

### Number (by income)

```{r social-support2-5}
plot = scored %>%
  group_by(CaregiverID, Week) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  filter(Week > 0) %>%
  filter(!is.na(material_hardship)) %>%
  group_by(Week, poverty150) %>%
  summarize(count = n(),
            hardship = mean(material_hardship)) %>%
  mutate(poverty150 = factor(poverty150, levels = c(0,1), labels = c("High Income", "Low Income"))) %>%
  ggplot(aes(x = Week, 
             y = hardship, 
             color = poverty150,
             group = 1,
             text = paste0(
               "Group:", poverty150,
               "\n Week:", Week,
               "\n Count:", count,
               "\n Hardship:", round(hardship,2)
             ))) +
  geom_point() + 
  geom_line() +
  geom_vline(aes(xintercept = as.Date("2020-07-31")), color = "red") +
  theme_pubr()
ggplotly(plot, tooltip = "text")
```

### At least one hardship (overall)

```{r social-support2-6}
plot = scored %>%
  group_by(CaregiverID, Week) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  filter(Week > 0) %>%
  filter(!is.na(material_hardship)) %>%
  mutate(material_hardship = ifelse(material_hardship > 0, 1, 0)) %>%
  group_by(Week) %>%
  summarize(count = n(),
            hardship = 100*sum(material_hardship)/count) %>%
  ggplot(aes(x = Week, y = hardship, group = 1, 
             text = paste0(
               "Week: ", Week, 
               "\n Count: ", count,
               "\n Percent: ", round(hardship)
             ))) +
  geom_point() + 
  geom_line() +
  geom_vline(aes(xintercept = as.Date("2020-07-31")), color = "red") +
  labs(x = "Week", y = NULL, title = "Percent of households experiencing at least one material hardship") +
  theme_pubr()

ggplotly(plot, tooltip = "text")
```

### At least one hardship (Black/African American)

```{r social-support2-7}
plot = scored %>%
  filter(!is.na(black)) %>%
  group_by(CaregiverID, Week) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  filter(Week > 0) %>%
  filter(!is.na(material_hardship)) %>%
  mutate(material_hardship = ifelse(material_hardship > 0, 1, 0)) %>%
  group_by(Week, black) %>%
  summarize(count = n(),
            hardship = 100*sum(material_hardship)/count) %>%
  mutate(black = factor(black, 
                             levels = c(0,1), 
                             labels = c("Not Black", "Black"))) %>%
  ggplot(aes(x = Week, 
             y = hardship, 
             color = black,
             group = 1,
             text = paste0(
               "Group:", black,
               "\n Week:", Week,
               "\n Count:", count,
               "\n Hardship:", round(hardship,2)
             ))) +
  geom_point() + 
  geom_line() +
  geom_vline(aes(xintercept = as.Date("2020-07-31")), color = "red") +
  labs(x = "Week", y = NULL, title = "Percent of households experiencing at least one material hardship") +
  theme_pubr()

ggplotly(plot, tooltip = "text")

```

### At least one hardship (LatinX)

```{r social-support2-8}
plot = scored %>%
  filter(!is.na(latinx)) %>%
  group_by(CaregiverID, Week) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  filter(Week > 0) %>%
  filter(!is.na(material_hardship)) %>%
  mutate(material_hardship = ifelse(material_hardship > 0, 1, 0)) %>%
  group_by(Week, latinx) %>%
  summarize(count = n(),
            hardship = 100*sum(material_hardship)/count) %>%
  mutate(latinx = factor(latinx, 
                             levels = c(0,1), 
                             labels = c("Not LatinX", "LatinX"))) %>%
  ggplot(aes(x = Week, 
             y = hardship, 
             color = latinx,
             group = 1,
             text = paste0(
               "Group:", latinx,
               "\n Week:", Week,
               "\n Count:", count,
               "\n Hardship:", round(hardship,2)
             ))) +
  geom_point() + 
  geom_line() +
  geom_vline(aes(xintercept = as.Date("2020-07-31")), color = "red") +
  labs(x = "Week", y = NULL, title = "Percent of households experiencing at least one material hardship") +
  theme_pubr()

ggplotly(plot, tooltip = "text")

```

### At least one hardship (White)

```{r social-support2-9}
plot = scored %>%
  filter(!is.na(white)) %>%
  group_by(CaregiverID, Week) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  filter(Week > 0) %>%
  filter(!is.na(material_hardship)) %>%
  mutate(material_hardship = ifelse(material_hardship > 0, 1, 0)) %>%
  group_by(Week, white) %>%
  summarize(count = n(),
            hardship = 100*sum(material_hardship)/count) %>%
  mutate(white = factor(white, 
                             levels = c(0,1), 
                             labels = c("Not White", "White"))) %>%
  ggplot(aes(x = Week, 
             y = hardship, 
             color = white,
             group = 1,
             text = paste0(
               "Group:", white,
               "\n Week:", Week,
               "\n Count:", count,
               "\n Hardship:", round(hardship,2)
             ))) +
  geom_point() + 
  geom_line() +
  geom_vline(aes(xintercept = as.Date("2020-07-31")), color = "red") +
  labs(x = "Week", y = NULL, title = "Percent of households experiencing at least one material hardship") +
  theme_pubr()

ggplotly(plot, tooltip = "text")

```

### At least one hardship (by income)

```{r social-support2-10}
plot = scored %>%
  filter(!is.na(poverty150)) %>%
  group_by(CaregiverID, Week) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  filter(Week > 0) %>%
  filter(!is.na(material_hardship)) %>%
  mutate(material_hardship = ifelse(material_hardship > 0, 1, 0)) %>%
  group_by(Week, poverty150) %>%
  summarize(count = n(),
            hardship = 100*sum(material_hardship)/count) %>%
  mutate(poverty150 = factor(poverty150, 
                             levels = c(0,1), 
                             labels = c("High Income", "Low Income"))) %>%
  ggplot(aes(x = Week, 
             y = hardship, 
             color = poverty150,
             group = 1,
             text = paste0(
               "Group:", poverty150,
               "\n Week:", Week,
               "\n Count:", count,
               "\n Hardship:", round(hardship,2)
             ))) +
  geom_point() + 
  geom_line() +
  geom_vline(aes(xintercept = as.Date("2020-07-31")), color = "red") +
  labs(x = "Week", y = NULL, title = "Percent of households experiencing at least one material hardship") +
  theme_pubr()

ggplotly(plot, tooltip = "text")

```

### At least one hardship (by employment)

```{r social-support2-11}
plot = scored %>%
  filter(!is.na(work_status)) %>%
  group_by(CaregiverID, Week) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  filter(Week > 0) %>%
  filter(!is.na(material_hardship)) %>%
  mutate(material_hardship = ifelse(material_hardship > 0, 1, 0)) %>%
  group_by(Week, work_status) %>%
  summarize(count = n(),
            hardship = 100*sum(material_hardship)/count) %>%
  ggplot(aes(x = Week, 
             y = hardship, 
             color = work_status,
             group = 1,
             text = paste0(
               "Group:", work_status,
               "\n Week:", Week,
               "\n Count:", count,
               "\n Hardship:", round(hardship,2)
             ))) +
  geom_point() + 
  geom_line() +
  geom_vline(aes(xintercept = as.Date("2020-07-31")), color = "red") +
  labs(x = "Week", y = NULL, title = "Percent of households experiencing at least one material hardship") +
  theme_pubr()

ggplotly(plot, tooltip = "text")

```

## New questions{.tabset}

### Food{.tabset}

How worried are you about having enough money to pay for food to feed your household for the next month?

#### Overall

```{r social-support2-12}
plot = scored %>%
  filter(!is.na(mh_food)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  group_by(mh_food) %>%
  summarize(count = n()) %>%
  mutate(percent = 100*count/sum(count),
         percent = round(percent, 1)) %>%
  mutate(mh_food = factor(mh_food, labels = c("Not at all","Slightly", "Somewhat","Very","Extremely"))) %>%
  ggplot(aes(x = mh_food, y = percent)) +
  geom_bar(stat = "identity") +
  coord_flip()+
  labs(title = "Worried about food", y = "Percent", x = NULL) +
  theme_pubr()
ggplotly(plot)
```

#### Income

```{r social-support2-13}
plot = scored %>%
  filter(!is.na(mh_food) & !is.na(poverty150)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  group_by(mh_food, poverty150) %>%
  summarize(count = n()) %>%
  group_by(poverty150)  %>%
  mutate(percent = 100*count/sum(count)) %>%
  mutate(percent = round(percent, 1)) %>%
  mutate(mh_food = factor(mh_food, labels = c("Not at all","Slightly", "Somewhat","Very","Extremely"))) %>%
  mutate(poverty150 = factor(poverty150, 
                             levels = c(0,1), 
                             labels = c("High Income", "Low Income"))) %>%
  ggplot(aes(x = mh_food, y = percent, fill = poverty150)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip()+
  labs(title = "Worried about food", y = "Percent", x = NULL) +
  theme_pubr()
ggplotly(plot)
```


#### Black/African American

```{r social-support2-14}
plot = scored %>%
  filter(!is.na(mh_food) & !is.na(black)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  group_by(mh_food, black) %>%
  summarize(count = n()) %>%
  group_by(black)  %>%
  mutate(percent = 100*count/sum(count)) %>%
  mutate(percent = round(percent, 1)) %>%
  mutate(mh_food = factor(mh_food, labels = c("Not at all","Slightly", "Somewhat","Very","Extremely"))) %>%
  mutate(black = factor(black, 
                             levels = c(0,1), 
                             labels = c("Not Black",
                                        "Black"))) %>%
  ggplot(aes(x = mh_food, y = percent, fill = black)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip()+
  labs(title = "Worried about food", y = "Percent", x = NULL) +
  theme_pubr()
ggplotly(plot)
```


#### Employment

```{r social-support2-15}
plot = scored %>%
  filter(!is.na(mh_food) & !is.na(work_status)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  group_by(mh_food, work_status) %>%
  summarize(count = n()) %>%
  group_by(work_status)  %>%
  mutate(percent = 100*count/sum(count)) %>%
  mutate(percent = round(percent, 1)) %>%
  mutate(mh_food = factor(mh_food, labels = c("Not at all","Slightly", "Somewhat","Very","Extremely"))) %>%
  ggplot(aes(x = mh_food, y = percent, fill = work_status)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip()+
  labs(title = "Worried about food", y = "Percent", x = NULL) +
  theme_pubr()
ggplotly(plot)
```

### Eviction{.tabset}

If you rent the place where you currently live, how worried are you about being evicted in the next month?

#### Overall

```{r social-support2-16}
plot = scored %>%
  filter(!is.na(mh_eviction)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  filter(mh_eviction != 6) %>%
  group_by(mh_eviction) %>%
  summarize(count = n()) %>%
  mutate(percent = 100*count/sum(count),
         percent = round(percent, 1)) %>%
  mutate(mh_eviction = factor(mh_eviction, labels = c("Not at all","Slightly", "Somewhat","Very","Extremely"))) %>%
  ggplot(aes(x = mh_eviction, y = percent)) +
  geom_bar(stat = "identity") +
  coord_flip()+
  labs(title = "Worried about being evicted", y = "Percent", x = NULL) +
  theme_pubr()
ggplotly(plot)
```


#### Income

```{r social-support2-17}
plot = scored %>%
  filter(!is.na(mh_eviction) & !is.na(poverty150)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
    filter(mh_eviction != 6) %>%
  group_by(mh_eviction, poverty150) %>%
  summarize(count = n()) %>%
  group_by(poverty150)  %>%
  mutate(percent = 100*count/sum(count)) %>%
  mutate(percent = round(percent, 1)) %>%
  mutate(mh_eviction = factor(mh_eviction, labels = c("Not at all","Slightly", "Somewhat","Very","Extremely"))) %>%
  mutate(poverty150 = factor(poverty150, 
                             levels = c(0,1), 
                             labels = c("High Income", "Low Income"))) %>%
  ggplot(aes(x = mh_eviction, y = percent, fill = poverty150)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip()+
  labs(title = "Worried about eviction", y = "Percent", x = NULL) +
  theme_pubr()
ggplotly(plot)
```


#### Black/African American

```{r social-support2-18}
plot = scored %>%
    filter(mh_eviction != 6) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
filter(!is.na(mh_eviction) & !is.na(black)) %>%
  group_by(mh_eviction, black) %>%
  summarize(count = n()) %>%
  group_by(black)  %>%
  mutate(percent = 100*count/sum(count)) %>%
  mutate(percent = round(percent, 1)) %>%
  mutate(mh_eviction = factor(mh_eviction, labels = c("Not at all","Slightly", "Somewhat","Very","Extremely"))) %>%
  mutate(black = factor(black, 
                             levels = c(0,1), 
                             labels = c("Not Black",
                                        "Black"))) %>%
  ggplot(aes(x = mh_eviction, y = percent, fill = black)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip()+
  labs(title = "Worried about eviction", y = "Percent", x = NULL) +
  theme_pubr()
ggplotly(plot)
```


#### Employment

```{r social-support2-19}
plot = scored %>%
    filter(mh_eviction != 6) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
filter(!is.na(mh_eviction) & !is.na(work_status)) %>%
  group_by(mh_eviction, work_status) %>%
  summarize(count = n()) %>%
  group_by(work_status)  %>%
  mutate(percent = 100*count/sum(count)) %>%
  mutate(percent = round(percent, 1)) %>%
  mutate(mh_eviction = factor(mh_eviction, labels = c("Not at all","Slightly", "Somewhat","Very","Extremely"))) %>%
  ggplot(aes(x = mh_eviction, y = percent, fill = work_status)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip()+
  labs(title = "Worried about eviction", y = "Percent", x = NULL) +
  theme_pubr()
ggplotly(plot)
```

### Foreclosure{.tabset}

If you own the house you currently live in, how worried are you that the mortgage will be foreclosed in the next month?

#### Overall

```{r social-support2-20}
plot = scored %>%
  filter(!is.na(mh_foreclose)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  filter(mh_foreclose != 6) %>%
  group_by(mh_foreclose) %>%
  summarize(count = n()) %>%
  mutate(percent = 100*count/sum(count),
         percent = round(percent, 1)) %>%
  mutate(mh_foreclose = factor(mh_foreclose, labels = c("Not at all","Slightly", "Somewhat","Very","Extremely"))) %>%
  ggplot(aes(x = mh_foreclose, y = percent)) +
  geom_bar(stat = "identity") +
  coord_flip()+
  labs(title = "Worried about foreclosure", y = "Percent", x = NULL) +
  theme_pubr()
ggplotly(plot)
```




#### Income

```{r social-support2-21}
plot = scored %>%
    filter(mh_foreclose != 6) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  filter(!is.na(mh_foreclose) & !is.na(poverty150)) %>%
  group_by(mh_foreclose, poverty150) %>%
  summarize(count = n()) %>%
  group_by(poverty150)  %>%
  mutate(percent = 100*count/sum(count)) %>%
  mutate(percent = round(percent, 1)) %>%
  mutate(mh_foreclose = factor(mh_foreclose, labels = c("Not at all","Slightly", "Somewhat","Very","Extremely"))) %>%
  mutate(poverty150 = factor(poverty150, 
                             levels = c(0,1), 
                             labels = c("High Income", "Low Income"))) %>%
  ggplot(aes(x = mh_foreclose, y = percent, fill = poverty150)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip()+
  labs(title = "Worried about foreclose", y = "Percent", x = NULL) +
  theme_pubr()
ggplotly(plot)
```


#### Black/African American

```{r social-support2-22}
plot = scored %>%
   filter(mh_foreclose != 6) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  filter(!is.na(mh_foreclose) & !is.na(black)) %>%
  group_by(mh_foreclose, black) %>%
  summarize(count = n()) %>%
  ungroup() %>%
  mutate(mh_foreclose = factor(mh_foreclose, 
                               labels = c("Not at all","Slightly", "Somewhat","Very","Extremely"))) %>%
  group_by(black)  %>%
  mutate(percent = 100*count/sum(count)) %>%
  mutate(percent = round(percent, 1)) %>%
 
  mutate(black = factor(black, 
                             levels = c(0,1), 
                             labels = c("Not Black",
                                        "Black"))) %>%
  ggplot(aes(x = mh_foreclose, y = percent, fill = black)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip()+
  labs(title = "Worried about foreclose", y = "Percent", x = NULL) +
  theme_pubr()
ggplotly(plot)
```


#### Employment

```{r social-support2-23}
plot = scored %>%
   filter(mh_foreclose != 6) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  filter(!is.na(mh_foreclose) & !is.na(work_status)) %>%
  group_by(mh_foreclose, work_status) %>%
  summarize(count = n()) %>%
  group_by(work_status)  %>%
  mutate(percent = 100*count/sum(count)) %>%
  mutate(percent = round(percent, 1)) %>%
  mutate(mh_foreclose = factor(mh_foreclose, labels = c("Not at all","Slightly", "Somewhat","Very","Extremely"))) %>%
  ggplot(aes(x = mh_foreclose, y = percent, fill = work_status)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip()+
  labs(title = "Worried about foreclose", y = "Percent", x = NULL) +
  theme_pubr()
ggplotly(plot)
```


### Utilities{.tabset}

How worried are you that your utilities (water, electricity, gas) will turn off in the next month?

#### Overall

```{r social-support2-24}
plot = scored %>%
  filter(!is.na(mh_utilities)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  group_by(mh_utilities) %>%
  summarize(count = n()) %>%
  mutate(percent = 100*count/sum(count),
         percent = round(percent, 1)) %>%
  mutate(mh_utilities = factor(mh_utilities, labels = c("Not at all","Slightly", "Somewhat","Very","Extremely"))) %>%
  ggplot(aes(x = mh_utilities, y = percent)) +
  geom_bar(stat = "identity") +
  coord_flip()+
  labs(title = "Worried about losing utilities", y = "Percent", x = NULL) +
  theme_pubr()
ggplotly(plot)
```


#### Income

```{r social-support2-25}
plot = scored %>%
  filter(!is.na(mh_utilities) & !is.na(poverty150)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  group_by(mh_utilities, poverty150) %>%
  summarize(count = n()) %>%
  group_by(poverty150)  %>%
  mutate(percent = 100*count/sum(count)) %>%
  mutate(percent = round(percent, 1)) %>%
  mutate(mh_utilities = factor(mh_utilities, labels = c("Not at all","Slightly", "Somewhat","Very","Extremely"))) %>%
  mutate(poverty150 = factor(poverty150, 
                             levels = c(0,1), 
                             labels = c("High Income", "Low Income"))) %>%
  ggplot(aes(x = mh_utilities, y = percent, fill = poverty150)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip()+
  labs(title = "Worried about food", y = "Percent", x = NULL) +
  theme_pubr()
ggplotly(plot)
```


#### Black/African American

```{r social-support2-26}
plot = scored %>%
  filter(!is.na(mh_utilities) & !is.na(black)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  group_by(mh_utilities, black) %>%
  summarize(count = n()) %>%
  group_by(black)  %>%
  mutate(percent = 100*count/sum(count)) %>%
  mutate(percent = round(percent, 1)) %>%
  mutate(mh_utilities = factor(mh_utilities, labels = c("Not at all","Slightly", "Somewhat","Very","Extremely"))) %>%
  mutate(black = factor(black, 
                             levels = c(0,1), 
                             labels = c("Not Black",
                                        "Black"))) %>%
  ggplot(aes(x = mh_utilities, y = percent, fill = black)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip()+
  labs(title = "Worried about utilities", y = "Percent", x = NULL) +
  theme_pubr()
ggplotly(plot)
```


#### Employment

```{r social-support2-27}
plot = scored %>%
  filter(!is.na(mh_utilities) & !is.na(work_status)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  group_by(mh_utilities, work_status) %>%
  summarize(count = n()) %>%
  group_by(work_status)  %>%
  mutate(percent = 100*count/sum(count)) %>%
  mutate(percent = round(percent, 1)) %>%
  mutate(mh_utilities = factor(mh_utilities, labels = c("Not at all","Slightly", "Somewhat","Very","Extremely"))) %>%
  ggplot(aes(x = mh_utilities, y = percent, fill = work_status)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip()+
  labs(title = "Worried about utilities", y = "Percent", x = NULL) +
  theme_pubr()
ggplotly(plot)
```

### All{.tabset}

Note that foreclosure and housing were combined into a single variable.

#### Overall

```{r social-support2-28}
scored = scored %>%
  mutate_at(vars(mh_eviction, mh_foreclose), .funs = function(x) ifelse(x == 6, NA, x)) %>%
  mutate_at(vars(starts_with("mh_")), .funs = function(x) ifelse(x > 1, 1, 0)) %>%
  mutate(mh_housing = case_when(
    mh_eviction == 1 ~ 1, 
    mh_foreclose == 1 ~ 1,
    mh_eviction == 0 ~ 0,
    mh_foreclose == 0 ~ 0,
    !is.na(mh_food) ~ 0,
    !is.na(mh_utilities) ~ 0,
    TRUE ~ NA_real_
  ),
  mh_food = case_when(
    !is.na(mh_food) ~ mh_food,
    !is.na(mh_housing) ~ 0
  ),
  mh_utilities = case_when(
    !is.na(mh_utilities) ~ mh_utilities,
    !is.na(mh_housing) ~ 0
  )) %>%
  select(-mh_eviction, -mh_foreclose) %>%
  mutate(mh_all = rowMeans(select(., contains("mh_")), na.rm=T)*3) 

plot_data = scored %>%
  filter(!is.na(mh_all)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  group_by(mh_all) %>%
  summarize(count = n()) %>%
  mutate(percent = 100*count/sum(count),
         percent = round(percent, 1)) %>%
  mutate(number = mh_all,
         mh_all = ifelse(mh_all == 0, "0", "1+"))

plot_data %>%
  ggplot(aes(x = mh_all, y = percent, fill = number)) +
  geom_bar(stat = "identity") +
  scale_fill_gradient(low = "lightblue", high = "darkblue")+
  coord_flip()+
  labs(title = "Material hardship", y = "Percent", x = NULL) +
  theme_pubr()

plot_data %>%
  select(-count) %>%
  write.csv(here("figure data/0822_figure1.csv"))
```

#### Income


```{r social-support2-29}
plot_data = scored %>%
  filter(!is.na(mh_all)) %>%
  filter(!is.na(poverty150)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  group_by(mh_all, poverty150) %>%
  summarize(count = n()) %>%
  group_by(poverty150) %>%
  mutate(percent = 100*count/sum(count),
         percent = round(percent, 1)) %>%
   mutate(poverty150 = factor(poverty150, 
                             levels = c(0,1), 
                             labels = c("High Income", "Low Income"))) %>%
  mutate(number = mh_all,
         mh_all = ifelse(mh_all == 0, "0", "1+"))

plot_data %>%
  ggplot(aes(x = poverty150, y = percent, fill = number)) +
  geom_bar(stat = "identity") +
  coord_flip()+
    scale_fill_gradient(low = "lightblue", high = "darkblue")+

  labs(title = "Material hardship", y = "Percent", x = NULL) +
  facet_wrap(~mh_all)+
  theme_pubr()

plot_data %>%
  select(-count) %>%
  write.csv(here("figure data/0822_figure2.csv"))
```

#### Black/African American


```{r social-support2-30}
plot_data = scored %>%
  filter(!is.na(mh_all)) %>%
  filter(!is.na(black)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  group_by(mh_all, black) %>%
  summarize(count = n()) %>%
  group_by(black) %>%
  mutate(percent = 100*count/sum(count),
         percent = round(percent, 1)) %>%
   mutate(black = factor(black, 
                             levels = c(0,1), 
                             labels = c("Not Black", 
                                        "Black"))) %>%
  mutate(number = as.factor(mh_all),
         mh_all = ifelse(mh_all == 0, "0", "1+"))

plot_data %>%
  ggplot(aes(x = mh_all, y = percent, fill = number)) +
  geom_bar(stat = "identity") +
  coord_flip()+
  labs(title = "Material hardship", y = "Percent", x = NULL) +
  facet_wrap(~black)+
  theme_pubr()

plot_data %>%
  select(-count) %>%
  write.csv(here("figure data/0822_figure3a.csv"))
```

#### LatinX


```{r social-support2-31}
plot_data = scored %>%
  filter(!is.na(mh_all)) %>%
  filter(!is.na(latinx)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  group_by(mh_all, latinx) %>%
  summarize(count = n()) %>%
  group_by(latinx) %>%
  mutate(percent = 100*count/sum(count),
         percent = round(percent, 1)) %>%
   mutate(latinx = factor(latinx, 
                             levels = c(0,1), 
                             labels = c("Not LatinX", 
                                        "LatinX"))) %>%
  mutate(number = as.factor(mh_all),
         mh_all = ifelse(mh_all == 0, "0", "1+"))

plot_data %>%
  ggplot(aes(x = mh_all, y = percent, fill = number)) +
  geom_bar(stat = "identity") +
  coord_flip()+
  labs(title = "Material hardship", y = "Percent", x = NULL) +
  facet_wrap(~latinx)+
  theme_pubr()

plot_data %>%
  select(-count) %>%
  write.csv(here("figure data/0822_figure3b.csv"))
```

#### White


```{r social-support2-32}
plot_data = scored %>%
 filter(!is.na(mh_all)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  group_by(mh_all, white) %>%
  summarize(count = n()) %>%
  group_by(white) %>%
  mutate(percent = 100*count/sum(count),
         percent = round(percent, 1)) %>%
   mutate(white = factor(white, 
                             levels = c(0,1), 
                             labels = c("Not White", 
                                        "White"))) %>%
  mutate(number = as.factor(mh_all),
         mh_all = ifelse(mh_all == 0, "0", "1+"))

plot_data %>%
  ggplot(aes(x = mh_all, y = percent, fill = number)) +
  geom_bar(stat = "identity") +
  coord_flip()+
  labs(title = "Material hardship", y = "Percent", x = NULL) +
  facet_wrap(~white)+
  theme_pubr()
```

#### Single 


```{r social-support2-33}
plot_data = scored %>%
  filter(!is.na(mh_all)) %>%
  filter(!is.na(single)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  group_by(mh_all, single) %>%
  summarize(count = n()) %>%
  group_by(single) %>%
  mutate(percent = 100*count/sum(count),
         percent = round(percent, 1)) %>%
   mutate(single = factor(single, 
                             levels = c(0,1), 
                             labels = c("Two-parent", 
                                        "Single parent"))) %>%
  mutate(number = as.factor(mh_all),
         mh_all = ifelse(mh_all == 0, "0", "1+"))

plot_data %>%
  ggplot(aes(x = mh_all, y = percent, fill = number)) +
  geom_bar(stat = "identity") +
  coord_flip()+
  labs(title = "Material hardship", y = "Percent", x = NULL) +
  facet_wrap(~single)+
  theme_pubr()

plot_data %>%
  select(-count) %>%
  write.csv(here("figure data/0822_figure3c.csv"))
```

<!-- #### Disability  -->


<!-- ```{r social-support2-34} -->
<!-- plot)data = scored %>% -->
<!--   filter(!is.na(mh_all)) %>% -->
<!--   group_by(CaregiverID) %>% -->
<!--   filter(row_number() == 1) %>% -->
<!--   group_by(mh_all, disability) %>% -->
<!--   summarize(count = n()) %>% -->
<!--   group_by(disability) %>% -->
<!--   mutate(percent = 100*count/sum(count), -->
<!--          percent = round(percent, 1)) %>% -->
<!--    mutate(disability = factor(disability,  -->
<!--                              levels = c(0,1),  -->
<!--                              labels = c("No disability",  -->
<!--                                         "Child with disability"))) %>% -->
<!--   mutate(number = as.factor(mh_all), -->
<!--          mh_all = ifelse(mh_all == 0, "0", "1+")) -->

<!-- plot_data %>% -->
<!--   ggplot(aes(x = mh_all, y = percent, fill = number)) + -->
<!--   geom_bar(stat = "identity") + -->
<!--   coord_flip()+ -->
<!--   labs(title = "Material hardship", y = "Percent", x = NULL) + -->
<!--   facet_wrap(~disablity)+ -->
<!--   theme_pubr() -->
<!-- ``` -->

#### Unemployed


```{r social-support2-35}
plot_data = scored %>%
  filter(!is.na(mh_all)) %>%
  filter(!is.na(work_status)) %>%
  group_by(CaregiverID) %>%
  filter(row_number() == 1) %>%
  group_by(mh_all, work_status) %>%
  summarize(count = n()) %>%
  group_by(work_status) %>%
  mutate(percent = 100*count/sum(count),
         percent = round(percent, 1)) %>%
  mutate(number = as.factor(mh_all),
         mh_all = ifelse(mh_all == 0, "0", "1+"))

plot_data %>%
  ggplot(aes(x = mh_all, y = percent, fill = number)) +
  geom_bar(stat = "identity") +
  coord_flip()+
  labs(title = "Material hardship", y = "Percent", x = NULL) +
  facet_wrap(~work_status)+
  theme_pubr()
```


# Food insecurity{.tabset}

## All

```{r social-support2-36}
plot = scored %>%
  group_by(CaregiverID, Week) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  filter(!is.na(food)) %>%
  mutate(food = case_when(
    food < 2 ~ "No",
    food >=2 & food <=4 ~ "Some",
    food > 4 ~ "A lot"
  )) %>%
  group_by(Week, food) %>%
  summarize(count = n()) %>%
  group_by(Week) %>%
  mutate(percent = 100*count/sum(count)) %>%
  #mutate(Week = paste("Week", Week)) %>%
  filter(food != "No") %>%
  ggplot(aes(x = Week, y = percent, color = food)) +
  geom_point() +
  geom_line()+
  # geom_bar(stat = "identity") +
  # coord_flip() +
  # facet_wrap(~Week) +
  labs(title = "Percent of caregivers experiencing ___ food insecurity", 
       x = NULL)+
  theme_pubr()

ggplotly(plot)

```

## Low Income

```{r social-support2-37}
plot = scored %>%
  filter(!is.na(poverty150)) %>%
  group_by(CaregiverID, Week) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  filter(!is.na(food)) %>%
  mutate(food = case_when(
    food < 2 ~ "No",
    food >=2 & food <=4 ~ "Some",
    food > 4 ~ "A lot"
  )) %>%
  group_by(Week, poverty150, food) %>%
  summarize(count = n()) %>%
  group_by(Week, poverty150) %>%
  mutate(percent = 100*count/sum(count),
         percent = round(percent,1)) %>%
  filter(food != "No") %>%
  mutate(poverty150 = factor(poverty150, levels = c(0,1), labels = c("High Income", "Low Income"))) %>%
  ggplot(aes(x = Week, y = percent, 
             color = food)) +
  geom_point() +
  geom_line()+
  labs(title = "Percent of caregivers experiencing ___ food insecurity", 
       x = NULL)+
  facet_grid(. ~ poverty150, scales = "free")+
  theme_pubclean()

ggplotly(plot)
```

## Black/African American

```{r social-support2-38}
plot = scored %>%
  filter(!is.na(black)) %>%
  group_by(CaregiverID, Week) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  filter(!is.na(food)) %>%
  mutate(food = case_when(
    food < 2 ~ "No",
    food >=2 & food <=4 ~ "Some",
    food > 4 ~ "A lot"
  )) %>%
  group_by(Week, black, food) %>%
  summarize(count = n()) %>%
  group_by(Week, black) %>%
  mutate(percent = 100*count/sum(count),
         percent = round(percent,1)) %>%
  filter(food != "No") %>%
  mutate(black = factor(black, levels = c(0,1), labels = c("Not Black", "Black"))) %>%
  ggplot(aes(x = Week, y = percent, 
             color = food)) +
  geom_point() +
  geom_line()+
  labs(title = "Percent of caregivers experiencing ___ food insecurity", 
       x = NULL)+
  facet_grid(. ~ black, scales = "free")+
  theme_pubclean()

ggplotly(plot)
```

## Unemployed

```{r social-support2-39}
plot = scored %>%
  filter(!is.na(work_status)) %>%
  group_by(CaregiverID, Week) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  filter(!is.na(food)) %>%
  mutate(food = case_when(
    food < 2 ~ "No",
    food >=2 & food <=4 ~ "Some",
    food > 4 ~ "A lot"
  )) %>%
  group_by(Week, work_status, food) %>%
  summarize(count = n()) %>%
  group_by(Week, work_status) %>%
  mutate(percent = 100*count/sum(count),
         percent = round(percent,1)) %>%
  filter(food != "No") %>%
  ggplot(aes(x = Week, y = percent, 
             color = food)) +
  geom_point() +
  geom_line()+
  labs(title = "Percent of caregivers experiencing ___ food insecurity", 
       x = NULL)+
  facet_grid(. ~ work_status, scales = "free")+
  theme_pubclean()

ggplotly(plot)
```

# Social support{.tabset}

_Note that for single caregivers, responses to "partner/spouse" support are removed._

## Source of support

```{r social-support-70}
plot = scored %>%
  #filter(time == 1) %>%
  filter(!is.na(support)) %>%
  #mutate(Week = paste("Week", Week)) %>%
  group_by(source, Week) %>%
  summarize(n = n(),
            support = sum(support, na.rm=T)) %>%
  mutate(percent = 100*support/n) %>%
  mutate_at(vars(support, percent), round, 2) %>%
  ggplot(aes(x = reorder(source, percent), y = percent,
             group=1,
               text = paste("\nPercent:", percent,
                            "Count:", n))) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(x = "", y = "Percent", title = "Source of support in the last week") +
  facet_wrap(~Week)+
  theme_pubclean()

ggplotly(plot, tooltip = "text")
```

## Children as support{.tabset}

### Ages

```{r social-support2-40}
plot = scored %>%
  filter(time == 1) %>%
  filter(Week == "2020-08-11") %>%
  filter(source == "Child(ren)") %>%
  filter(support == 1) %>%
  gather("variable", "response", contains("SOCIALSUPP")) %>%
  filter(str_detect(variable, "SOCIALSUPP.00[4-9]\\.a")) %>% 
  group_by(response) %>%
  summarize(count = n()) %>%
  filter(!is.na(response)) %>%
  ggplot(aes(x = as.factor(response), y = count))+
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(x = "", y = "Count", title = "Age of child providing support") +
  theme_pubclean()

ggplotly(plot, tooltip = "text")
```

### Number per household

```{r social-support2-41}
plot = scored %>%
  filter(time == 1) %>%
  filter(Week == "2020-08-11") %>%
  filter(source == "Child(ren)") %>%
  gather("variable", "response", contains("SOCIALSUPP")) %>%
  filter(str_detect(variable, "SOCIALSUPP.00[4-9]\\.a")) %>% 
    filter(!is.na(response)) %>%
group_by(CaregiverID) %>%
  summarize(num_child = n()) %>%
  group_by(num_child) %>%
  summarize(count = n()) %>%
  ggplot(aes(x = num_child, y = count))+
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(x = "", y = "Count", title = "Number of children providing support") +
  theme_pubclean()

ggplotly(plot, tooltip = "text")
  
```

### Type of support

```{r social-support2-42}
plot = scored %>%
  filter(time == 1) %>%
  filter(Week == "2020-08-11") %>%
  filter(source == "Child(ren)") %>%
  filter(support == 1) %>%
  gather("variable", "response", contains("SOCIALSUPP")) %>%
  mutate(response =ifelse(is.na(response), 0, 1)) %>%
  filter(str_detect(variable, "SOCIALSUPP.00[4-9]\\.[a,b]")) %>%
  mutate(support_type = case_when(
    str_detect(variable, "a$") ~ "Age",
    str_detect(variable, "_1$") ~ "Emotional",
    str_detect(variable, "_2$") ~ "OtherChildren",
    str_detect(variable, "_3$") ~ "Household"
  ),
    variable = str_remove(variable, "\\.a$"),
  variable = str_remove(variable, "\\.b_[1-3]$")) %>%
  spread(support_type, response) %>%
  summarize_at(vars(Emotional, OtherChildren, Household), sum, na.rm=T) %>%
  gather("support_type", count) %>%
  mutate(support_type = factor(support_type, labels = c("Emotional", "Other household chores", "Watching other children"))) %>%
  ggplot(aes(x = support_type, y = count)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(x = "", y = "Count", title = "Number of children providing support") +
  theme_pubclean()

ggplotly(plot, tooltip = "text")
```

### Type of support by age

```{r social-support2-43}
plot = scored %>%
  filter(time == 1) %>%
  filter(Week == "2020-08-11") %>%
  filter(source == "Child(ren)") %>%
  filter(support == 1) %>%
  gather("variable", "response", contains("SOCIALSUPP")) %>%
  mutate(response =ifelse(is.na(response), 0, response)) %>%
  filter(str_detect(variable, "SOCIALSUPP.00[4-9]\\.[a,b]")) %>%
  mutate(support_type = case_when(
    str_detect(variable, "a$") ~ "Age",
    str_detect(variable, "_1$") ~ "Emotional",
    str_detect(variable, "_2$") ~ "OtherChildren",
    str_detect(variable, "_3$") ~ "Household"
  ),
    variable = str_remove(variable, "\\.a$"),
  variable = str_remove(variable, "\\.b_[1-3]$")) %>%
  spread(support_type, response) %>%
  group_by(Age) %>%
  summarize_at(vars(Emotional, OtherChildren, Household), sum, na.rm=T) %>%
  gather("support_type", count, -Age) %>%
  mutate(support_type = factor(support_type, labels = c("Emotional", "Other household chores", "Watching other children"))) %>%
  group_by(Age) %>%
  mutate(percent = 100*count/sum(count),
         percent = round(percent,1)) %>%
  ggplot(aes(x = Age, y = count, fill = support_type)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  facet_wrap(~support_type)+
  labs(x = "", y = "Percent", title = "Number of children providing support") +
  theme_pubclean()

ggplotly(plot, tooltip = "text")
```

# Hardship and social support{.tabset}

## Has material hardship (old questions)

```{r social-support2-44}
plot = scored %>%
  filter(Week == "2020-08-11") %>%
  filter(!is.na(material_hardship)) %>%
  filter(!is.na(support)) %>%
  mutate(material_hardship = ifelse(material_hardship > 0, 1, 0)) %>%
  group_by(material_hardship, source) %>% 
  summarize(count = sum(support),
            percent = round(100*count/n(),1)) %>%
  ungroup() %>%
  mutate(material_hardship = factor(material_hardship,
                                    labels = c("No hardship", "Hardship"))) %>%
  ggplot(aes(x = reorder(source, percent), y = percent))+
  geom_bar(stat = "identity") +
  coord_flip() +
  facet_grid(.~material_hardship) +
  labs(x = NULL, y = NULL, "Percent of caregivers finding support in _____") +
  theme_pubr()

ggplotly(plot)
```

## Has material hardship (new questions)

```{r social-support2-45}
plot = scored %>%
  filter(Week == "2020-08-11") %>%
  filter(!is.na(support)) %>%
  mutate(material_hardship = ifelse(mh_all > 0, "Hardship", "No hardship")) %>%
  group_by(material_hardship, source) %>% 
  summarize(count = sum(support),
            percent = round(100*count/n(),1)) %>%
  ungroup() %>%
  mutate(material_hardship = factor(material_hardship,
                                    labels = c("No hardship", "Hardship"))) %>%
  ggplot(aes(x = reorder(source, percent), y = percent))+
  geom_bar(stat = "identity") +
  coord_flip() +
  facet_grid(.~material_hardship) +
  labs(x = NULL, y = NULL, "Percent of caregivers finding support in _____") +
  theme_pubr()

ggplotly(plot)
```


## Number of material hardship (new questions)

```{r social-support2-46}
plot = scored %>%
  filter(Week == "2020-08-11") %>%
  filter(support == 1) %>%
  group_by(source) %>%
  summarize(mh = mean(mh_all, na.rm=T)) %>%
  ggplot(aes(x = reorder(source, mh), y = mh)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(x = NULL, y = "Material Hardship", title = "Average material hardship by source of support") +
  theme_pubr()

ggplotly(plot)
```

